### 2018-03-21 paper/paper.tex
adding paper

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt, conference, compsocconf]{IEEEtran}
% Add the compsocconf option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

\usepackage{float}
\usepackage{graphicx}
\usepackage{balance}
\RequirePackageWithOptions{multicol}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

\usepackage{color}
\newcommand{\trishita}[1]{{\color{magenta}\bfseries[Trishita: #1]}}
\newcommand{\dennis}[1]{{\color{cyan}\bfseries[Dennis: #1]}}
% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

\usepackage{amsmath}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Distributed Web Browser Mining for Ethereum}

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

\author{\IEEEauthorblockN{
Trishita Tiwari\IEEEauthorrefmark{1}
David Starobinski\IEEEauthorrefmark{2}
Ari Trachtenberg\IEEEauthorrefmark{3}
}
\IEEEauthorblockA{Department of Electrical and Computer Engineering,
Boston University\\
Boston, MA, 02215\\
Email: 
\IEEEauthorrefmark{1}trtiwari@bu.edu
\IEEEauthorrefmark{2}staro@bu.edu
\IEEEauthorrefmark{3}trachten@bu.edu
}}
\maketitle

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
% \maketitle

\begin{abstract}

Given the seemingly endless growing popularity of crypto-currencies, there is an increasing interest in different mining possibilities. This paper proposes a web browser based mining implementation for Ethereum implemented both in JavaScript and WebAssembly to perform the necessary Proof-of-Work (PoW) computations to mine the Ethereum blockchain. We explore a variety of techniques to distribute the inherently memory and memory intensive PoW of Ethereum over multiple browser-based clients that have limited resources. We obtain the best results with the WebAssembly implementation, with hash rates reaching upto X hashes/second, which, as we demonstrate, is merely X\% slower than a native miner that uses the same algorithm for mining. We show that this solution is practical for a variety of purposes, such as web content monetization, web based authentication rate limiting and private Ethereum networks.

%Given the increasing need of effective ways to monetize web content and the growing popularity of crypto-currencies, we propose a new implementation of a distributed miner using web browsers. We implement this for the Ethereum crypto-currency, which shows that the use of web browsers is inefficient if the cryptocurrency requires large amount of storage for mining. However, we believe that such an approach can have merit depending on the crypto-currency that is being mined.

\end{abstract}

\begin{IEEEkeywords}
crypto-currency, Ethereum, distributed computing, mining
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
In today's world, crypto-currencies are gaining more and more traction as a viable form of currency. As such, people have been looking for efficient ways to mine the numerous crypto-currencies available. While much of these efforts have included creating new hardware, there has been considerable work done in re-using existing infrastructure in smarter ways to increase performance. One such effort is seen in using web browser as a platform for distributed computing ~\cite{Cushing}, and more recently, specifically for distributed crypto-currency mining ~\cite{coinhive}. In this work, we propose approaches to mine Ethereum, a popular crypto-currency, in a distributed fashion through web browsers. Our approach can be used for a variety of purposes, outlined as follows: 
\begin{enumerate}

\item \textbf{Web Content Monetization}: With the growth in global Internet usage, websites have become a lucrative way for people to earn monetary profit. As a result, new methods of monetizing electronic content have surfaced with time. While some are more successful than others, all of them have issues associated with them. For instance, selling advertisement space is now resulting in declining revenue \cite{decliningRevenue} for website owners due to the advent of new technologies such as AdBlock \cite{Adblock}, Brave Browser \cite{BraveBrowser}, etc. In addition, too many advertisements also tend to increase the loading time for web-pages. Moreover, such advertisements are sometimes not placed correctly and cover the contents of the website. Thus, this approach does not provide good user experience. Another approach involves subscriptions, however, it is not very successful. Indeed, as this study finds, users are becoming increasingly unlikely to pay for content \cite{noSubscriptions}. Website owners also use pay-per-click Advertising, however an approach often leads to the content being split over an excessive number of pages, thereby leading to consumer frustration \cite{payPerClick}. Thus, we see that each approach has its own issues, be it with  with website owners or clients. Hence, it is important to strike a balance and create a solution that would be able to benefit both parties. Our web-based miner would solve this situation as it does not 
\item \textbf{Web-Authentication Rate Limiting}: Brute forcing web login pages is becoming an all too common issue ~\cite{webLoginBruteForce}, and the way website owners mitigate this issue is by locking out a user for a certain amount of time after a fixed number of unsuccessful login attempts. While this approach works in theory, in today's fast-paced world, users tend to dislike waiting for even a few seconds ~\cite{usersDislikeWaiting}. Another solution to this problem involves embedding a Proof-of-Work (PoW) computation in the web page that the user's browser needs to successfully solve in order to be able to login. Our implementation uses the Ethereum PoW, which is extremely feasible for legitimate users attempting to login, but will thwart any attacker that attempts to brute force the login. Furthermore, the difficulty of the PoW can be tuned to obtain a balance between user experience and security. 
\item \textbf{Website usage tracking}: Website advertising sponsors decide on the remuneration for a website by inspecting the logs of the web servers in order to deduce how much traffic the site receives. However, it is well known that these logs can be easily manipulated by the website owner in order to generate the impression of a large amount of traffic ~\cite{webLogsManipulation}. Our web miner could solve these issues as it has this unique property of a direct correlation between a users hashrate and the time spent on the website (i.e., the longer the user spends on the web page, better the hashrate gets). Hence, our miner can be embedded within advertisements and allow advertisers to directly extrapolate how much traffic the website gets just by extrapolating from the average hash rate.
\item \textbf{Private Ethereum networks}: Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- i.e., networks that do not on mine the actual, public Ethereum block-chain, but rather on private (and often smaller) instances of the crypto-currency. Our browser miner can be used on any such private network to serve the network owner whatever he/she wishes to implement with the mining PoW.
\end{enumerate}

\section{Related Work}
So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling},~\cite{parallel},~\cite{orca}. Additionally, with the growing popularity of dynamic web-content and client side scripting languages like \verb|JavaScript| and \verb|WebAssembly|, web-browsers have also become a lucrative option for implementing distributed systems. As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow} ~\cite{Duda}. 
Indeed, ``Distributed Computing on an Ensemble of Browsers'' by Cushing~\cite{Cushing} shows that the \verb|JavaScript| Engine has had enough improvements in performance to make computationally heavy programs feasible in a distributed web browsing unit. In addition, the work by Duda and Dłubacz~\cite{Duda} was instrumental in the field as one of the first web browsing computational systems to not require the host machine to install any additional applications in order to participate. This is important since we would want our web miner to be operable without requiring the user to install any unfamiliar software. Furthermore, \verb|WebAssembly| is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to offer X\% speed as \verb|JavsScript| ~\cite{WebAssembly}. Instead of relying on \verb|JavaScript|, web developers can now write C/C++ or Rust code and compile it into \verb|WebAssembly| using some of the openly available \verb|WebAssembly| compilers ~\cite{emscripten} ~\cite{rustCompiler} . Indeed, given that now \verb|WebAssembly| is supported by all major browsers ~\cite{webasmSupport}, industry is also making use of this powerful framework. One sees this through the recent development of increasingly popular Monero mining \verb|WebAssembly| library CoinHive ~\cite{coinhive}.

\section{Our Contributions}
Our research involves providing an implementation of a distributed, web browser based \verb|JavaScript| and \verb|WebAssembly| based Ethereum miners, and studying whether or not it is feasible for real world purposes. While there has been prior academic work done in related fields, none of the distributed web browser implementations in these works do not involve crypto-currency mining. While CoinHive does perform distributed mining using web browsers, it is closed source, and also works with a different crypto-currency (Monero). Hence, we are pioneering in offering an open source architecture for mining with web browsers.

\section{Outline}
The remainder of the paper is organized as follows. In Section 5 we present a detailed description of the Ethereum mining algorithm and the current state of Ethereum. Section 6 describes the Architecture of our implementation of the Distributed Web Browser Miner. Section 7 goes over the challenges that we have dealt with during our implementation and their effect on the project. Section 8 examines the results of our solution and compares it to current mining data to evaluate the efficacy of our work. Finally, in Section 9 we lay out possible future work, and in Section 10 provide conclusions and insight on the project.

% \item Affiliate Marketing: Unlike pay-per-click advertisements, such marketing might not cause inconvenience to users. However, it sometimes leads to ethically questionable situations when users are not able to distinguish when the website owner is advertising a product versus when the owner truly endorses it without monetary incentive \cite{celebEndorse}.

% \item Donations: While donations are perhaps the most benign of all approaches, they lead to unsteady revenue for the website owner.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)

\section{Background}
% \subsection{Distributed Web Browser Computing}
% One of the core concepts that this research is based on is the use of web browsers to perform computations; in our case that computation is the act of mining crypto-currency. First, we need to define the idea of distributed computing. Distributed computing is a network of computers that are working together to achieve a single goal. Web browser computing is a subset of distributed computing. In this scenario, the web browsers on the client machines are the workers. The use of web browsers for computation has come to light in the past 15-20 years because of improvements the \verb|JavaScript| engine ~\cite{Cushing}. In fact, the advent of powerful frameworks such as \verb|WebAssembly| are further closing down the gaps between web browser computations and native programs.

% To be able to implement an effective distributed system, each of the ``workers'' must have a way to communicate effectively with each other. There are two ways this is accomplished. One approach is to follow a server-client model in which there is a central server machine and all other machines are the clients. The clients speak to the server and the server can relay information from one client to another or broadcast information to all clients. The other way to have communication is a peer-to-peer model where all machines are aware of each other and can talk directly. When it comes to browsers, however, the only logical way to pass data is through the server-client architecture because web browsers are not created to perform peer-to-peer communication. So with that in mind, distributed web browser computing systems typically have a structure with a central server which distributes tasks to each web browser it is connected to. In general, these tasks are very small because there is no guarantee that the browser will be open for a sustained period of time, i.e. a user moves away from the necessary website or closes the browser altogether. Furthermore, the tasks must also not consume too many resources of the user, as such browser based computation would ruin user experience. Given these two constraints, we propose two approaches to distribute ethereum mining in over web browsers.

\subsection{Ethereum}
\trishita{Not sure if I need this paragraph, since I think the readers will probably be familiar with what crypto-curriencies are}
Ethereum is a crypto-currency that was released in July 2015 by Vitalik Buterin, Gavin Wood and Jeffrey Wilcke. Like most crypto-currencies, it too is backed by a distributed block-chain, each block of which holds transactions for that particular block-chain. This block chain is operated on by the Ethereum Virtual Machine (EVM) ~\cite{EVM}, which, unlike Bitcoin Script, is Turing Complete ~\cite{turingComplete}. Furthermore, this currency is also a Proof-of-Work based currency, which means that the new blocks are appended to the block-chain through a process called ``mining''. Mining involves a race amongst miners to solve a Proof-of-Work puzzle (usually an energy intensive computation), the winner of which gets to have his block appended to the block-chain. The winner also receives a payout, which acts as an incentive to mine. This process of mining is essential to deciding the order in which transactions are appended to the inherently decentralized block-chain, thereby stabilizing the chain. Ethereum uses Ethash as its Proof-of-Work (PoW) algorithm, which is explained in detail below.

\subsection{Ethash}
Ethereum uses a Proof-of-Work algorithm called Ethash for verification of blocks. Derived from the Dagger and Hashimoto algorithms ~\cite{dagger-hashimoto}, Ethash operates by first generating a 256 bit seed. This seed is different for every epoch (30,000 blocks). For the first epoch it is the Keccak-256 hash of a series of 32 bytes of zeros. For every other epoch it is always the Keccak-256 hash of the previous seed hash. This seed is then used to compute a pseudo-random cache. The cache production process involves using the seed hash to first sequentially filling up X bytes of memory (size of the cache), then performing Y passes of the RandMemoHash algorithm ~\cite{randmemohash}. This transforms the initial cache to give us the final value for the cache. This cache is simply a byte array of 64-byte values ~\cite{Ethmining}. Lightweight clients may use this cache for verification, while full node clients can use it to calculate a DAG (Directed Acyclic Graph) file. Essentially, each node in the DAG is generated by combining data from 256 pseudorandomly selected cache nodes and hashing them together. This process is repeated to generate all nodes in the DAG. Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128B wide “Mix” (another byte array). The Mix is then used to fetch a specific slice of the DAG from memory. (Each slice is 512 bits long.) After this, the Mix is updated with the fetched part of the DAG. Then, this updated Mix is used to fetch a new part of the DAG. This process of sequentially fetching parts of the DAG is repeated 64 times, and the final value of the Mix is put through a transformation to obtain a 32 byte digest. This digest is then compared to the threshold, and if it is lesser than it, the nonce is valid and the block is successfully mined and can be broadcast to the network. However, if the digest is greater than the threshold, the nonce was unsuccessful, and the entire process must be repeated with a new nonce ~\cite{Ethmining}. This procedure for mining is depicted in figure ~\ref{fig:ethash}. It is important to note that the parts of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence no way to pre-determine which parts will be useful to have in memory. Hence this forces miners to store entire DAG, making mining "Memory Hard". This is intended to even the playing field, as ASIC miners no longer have any advantage as they do for Bitcoin. GPU miners, however, do have an advantage, normally having hashrates of over 10 times that of a CPU miner.
While mining is memory intensive, verification is relatively lightweight. This is because of the property that each ``item'' in the DAG depends on a set of pseudo-randomly selected items from the cache. Hence, the cache is used to regenerate only the specific pieces of the DAG that are needed to recalculate the hash for the particular nonce. And so only the cache needs to be stored by clients that just perform verification.

\begin{figure}[H]
\centering
\includegraphics[width=250px,keepaspectratio]{ethash_algorithm.png}
\caption{\label{fig:ethash} Ethash}
\end{figure}

As time goes on, mining Ethereum becomes more and more difficult. The Proof-of-Work difficulty and total hashrate of the network has been steadily increasing over time, with the current difficulty at 1612.737TH and the respective hashrate at 109.138TH/s ~\cite{etherscan}. This reflects the design of mining one block approximately every 12 seconds. As for mining rewards, the reward for mining a block has gone from 5 Ether to 3 ether, though the difficulty has significantly decreased, both due to the Byzantium fork. Furthermore, the DAG used for the Ethereum network is now more than 2GB, causing many GPU miners with cards of 2GB of memory to suffer in terms of hashrate.

For a normal Ethereum miner to function, the current block headers and the DAG are required to even begin mining. As we simply cannot afford to transfer the entire DAG to the browser and store it in memory, we propose an an alternative approach addresses some of these concerns.

% \subsection{Choice of Crypto-currency}
% \trishita{We had this section in the project report, but I am not sure if we need this anymore, so I commented it out}
% In choosing crypto-currencies to mine, it was preferable to mine a larger, well known currency to ensure that the research would have real-world implications if adopted. Monero was the clear favorite, as it was created with the intent of providing no benefit over CPU mining. However, there has already been a web browser miner implemented for the Monero in the form of CoinHive~\cite{coinhive}, so any such efforts with Monero would not be novel. CoinHive also takes in a certain percentage of all currency generated and as such has kept their code closed sourced which meant that we could not easily extend or improve their current implementation as part of our research. In addition, many websites that utilize Coinhive have not informed users of their "stealing of computing power". This has drawn negative attention toward Coinhive to the extent that the code has been classified as malware and is automatically blocked by most firewalls and anti-viruses by default. Bitcoin was another option that we considered, however, there were two foreseeable problems with the crypto-currency that we felt would be insurmountable in our research timeline. First, ASIC technology has become the new norm for mining Bitcoin which would mean our web browser solution would hardly be able to compete. Second, the sheer popularity of Bitcoin means the mining is highly competitive in itself so our baseline threshold for seeing results would be too high for any reasonable amount of work.

% In the end, we decided that Ethereum would be the most beneficial crypto-currency for a new web browser implementation of a miner. First of all, there is no existing web browser miner for Ethereum, so our implementation would have a certain novelty. In addition, Ethereum also allows developers to create private testnets to experiment with the network, which is a valuable asset to create a distributed network of miners. Another major benefit of Ethereum is that its smart contracts are Turing complete, meaning that the system can be used for a lot more than just sending or receiving currency. This could lead to a growing popularity of the crypto-currency in the coming years. Lastly, using Ethereum also leaves room for further exciting research, as will be discussed in a later section.

% \subsection*{Work Distribution}
% Trishita produced the \verb|JavaScript| implementation of the browser miner and the \verb|Python| test node with some help from Daniel. Dennis provided statistics and data for comparison to the browser miner in addition to setting up and managing the private testnet to perform operations on. All of the members participated in research and understanding of core Ethereum functions such as Ethash and how to mine via Ethereum.

% ~\dennis{https://github.com/ethereum/wiki/wiki/Ethash-Design-Rationale, should cite this so that they know that we are aware that compute from cache is designed to be inefficient, maybe add a diagram?)}

\section{Our Approach}
We propose a lazy-evaluation based approach to alleviate the network and memory requirements for mining ethereum in a distributed scenario on browsers. Specifically, as soon as each browser connects to the central node, the node sends it the current header of the block being mined and the Cache. Once the browser receives the Cache, it allocates an array buffer to store the DAG slices that will be computed in the future. (Note that the length of the buffer is a variable parameter that we experiment with in our analysis). Once this happens, the browser can start iterating over nonces to compute hashes.

% The approach involves each browser allocating a fixed buffer to store the DAG, which is initially empty when the web page first loads. (Note that the size of this buffer is a parameter that can be adjusted depending on how much memory the client has.) The browser then starts mining, and 
Since, to begin with, the browser does not have any slices of the DAG, it must compute each slice on the fly using the Cache. However, for every such slice that the browser computes, it then stores it in the buffer (if it fits within the allocated bounds, otherwise it is simply discarded), for quicker access in the future. Hence, as time passes, the buffer starts filling up and so more and more slices are quickly accessed from the buffer rather than being computed from the ground-up, which makes hash computations faster with time. This has the effect that the longer the user remains on the web-page, the better the hashrate gets for that user. 
% If the allocated buffer is too small (as would be needed for some clients that do not have enough memory), and the computed slice cannot be fit in it, it is simply thrown away and again recomputed from the cache when needed.

% With respect to DAG lookups to compute each hash, the browser first checks if it already has the required slice in its buffer. If it does, it simply uses that, else it uses the Cache to compute that slice on the fly and then store it for future reference (if it fits in the buffer). Hence, initially the buffer starts out empty and so all DAG slices must be computed on the fly, and then stored in the buffer. However,

\subsection{Information theoretic bounds}
With this lazy-evaluation based approach, we can calculate exactly how many hashes we would have to compute in order to fill up a buffer of a given size. This approach is a variation of the coupon collector problem \cite{couponCollector}. For our purposes, let us assume the following:
\begin{gather}
    Number\;of\;DAG\;slices = n\\
    Number\;slices\;buffer\;can\;store = i
\end{gather}
If we have buffered \verb|x| slices so far, the probability of obtaining a new slices is given by:
\begin{gather}
  P_x = \frac{i-x}{n}
\end{gather}
The event of obtaining a new slice after having already collected \verb|x| out of the \verb|i| slices that can be buffered can be modeled as a geometric distribution. Hence, the expected number of trials $t_x$ it takes to get a new  slice after having seen \verb|x| out of the \verb|i| slices is:
\begin{gather}
  E(t_x) = \frac{1}{P_x} = \frac{n}{i-x}
\end{gather}
By linearity of expectation, the total number of trials it would take to see all \verb|x| slices is:
\begin{gather}
  E(t) = \sum_{x=0}^{i-1}E(t_x)\\
    E(t) = \sum_{x=0}^{i-1}P_x = \sum_{i=0}^{i-1}\frac{n}{i-x} = n\sum_{i=0}^{i-1}\frac{1}{i-x}
\end{gather}
Since the summation represents the harmonic series, the expected value can be approximated as follows:
\begin{gather}
  E(t) = n\log{i}
\end{gather}
Now, let us do a simple calculation for one extreme case, where \verb|i| = \verb|n| (i.e., we allocate a buffer as large as the entire DAG on the browser), in order to get an upper bound on the number of hashes it would take to fill this buffer up. The private test network for Ethereum we used had a total of 16777186 slices in the DAG, which means it would take:
\begin{gather}
  E(t) = 16777186*\log{16777186} = 2.79*10^8\;trials
\end{gather}
Now, each hash involved 64 random accesses of the DAG, which means the total number of hashes it would take to buffer the entire DAG is:
\begin{gather}
  Hashes = \frac{2.79*10^8}{64} = 4.36*10^6
\end{gather}
Hence, it takes around 4 million hashes to fill up a buffer as large as the entire DAG. If $i < n$, the number of hashes should be less than 4 million. Since 4 million hashes is about as long as it could take to fill up the buffer, all of our experiments involve computing 4 million hashes, as we will see below.
Furthermore, let:
\begin{gather}
  Buffer\;hit\;rate = R \\
    Number\;of\;hashes\;computed = H
\end{gather}
Then,
\begin{gather}
  \lim_{H\to\infty}R = \frac{i}{n}
\end{gather}
This is because as $H\to\infty$, the buffer becomes full. Which means for any random slice of the DAG we pull out, the probability of it being in the buffer is $\frac{i}{n}$.

% We must also point out that in order to optimize the code for the specific cases, we have separate implementations for each of these two extreme edge cases. We also have another two separate implementations for the hybrid approach (where we store parts of the DAG and compute the other slices from the cache). The first hybrid implementation does not store the slices of the DAG the browser computes from the cache, while the second does (until it exhausts the storage space allocated to the DAG). The differences between each of the four implementations mainly lies in the data structures used to store the DAG, and is outlined follows:
% \begin{enumerate}
% \item Browser stores entire DAG in memory: We store the DAG in an array in order to get constant lookup times. The Cache is stored in an array of integers.
% \item Browser stores part of the DAG sent by the central node in memory and computes the other necessary slices from the Cache and stores these slices for future reference: Here, we need to store the DAG in a \verb|JavaScript| object (which is akin to a Hash Map). In this data structure, the keys correspond to the index of the DAG slice, and the value corresponds to the slice itself. We need a Hash Map as opposed to an array because we also store the slices that are generated on-the-fly from the Cache in this data structure. Since these slices are from random indices, we cannot store them at their correct indices in the array without allocating an array as large as the entire DAG itself -- which defeats the purpose of storing just a part of the DAG.
% \item Browser stores part of the DAG sent by the central node in memory and computes the other necessary slices from the Cache and \emph{does not} store these slices for future reference: Here, we just store the part of the DAG sent by the central server in memory, which we can compactly keep in an array since the central server sends consecutive slices.
% \item Browser stores none of the DAG and computes all the slices from the Cache: We do not store the DAG at all, but just the Cache in an array of integers.
% \end{enumerate}

\section{Architecture}
\begin{figure}[H]
\centering
\includegraphics[width=250px,keepaspectratio]{miningpool.png}
\caption{\label{fig:miningpool} Distributed Ethereum Mining}
\end{figure}

% A private Ethereum testnet is deployed to decrease the difficulty of mining so that the browsers clients can reliably mine at least some Ether. This can be easily ported to the real Ethereum network as we are using \verb|geth|, the Go implementation written for interacting with the Ethereum network. 
% The central Ethereum node is set up using \verb|geth|, which serves as the wallet that all the browser miners will point to.

Our architecture was centered around two client-side Ethereum miners written in \verb|JavaScript| and \verb|WebAssembly|. The central node that co-ordinates all workers (browsers) was an improvised version of \verb|geth| ~\cite{geth}, a real world Ethereum miner written in \verb|Go|. \verb|Geth| typically runs as a standalone miner that mines on the machine it is running. We modified it so that instead of mining all by itself, it simply sends over the necessary data needed to mine (the hash of the Block Header and the Cache) to any client that connects to it on port \verb|9000|. After recieving the necessary data, the browser allocates a buffer for the DAG in order to store future slices. Note that the buffer for the DAG is implemented an array of ints (with a DAG slice being 16 ints long), so as to make each lookup in the buffer $\theta(1)$. At this point, it can then begin to search for a solution.

For our miner, we modeled our \verb|JavaScript| implementation based on the ~\verb|node.js| implementation of Ethash ~\cite{ethash}. To begin, the miner creates a random nonce and the computes the hash (using the Cache and the buffered DAG) as discussed in the previous section. It will continue to perform this action on new nonces until one of two scenarios occur; it finds a nonce such that the computed hash is below the given threshold or the process has timed out. In the former case, the browser submits the result back to the node and then asks the node for a new block header and the Cache. Otherwise if it has timed out without finding a result, the browser simply polls the node for the current block header and Cache . This process will continue until the user moves away from the website or closes their browser. 
We must point out that this time out is necessary since we want the browser to work with the most recent block header and Cache. The block header can become stale if that particular block has already been mined, and the Cache can become stale if the Ethereum network transitions into a new Epoch (happens once every 30,000 blocks). 
We must point out that both our current implementations in \verb|JavaScript| and \verb|WebAssembly| require no external dependencies, and therefore can be directly embedded into any website. For a diagramatic view our our design, see Figures~\ref{fig:hybridArchitecture}.

\begin{figure}[H]
\centering
\includegraphics[width=250px,keepaspectratio]{Hybrid-Miner.pdf}
\caption{\label{fig:hybridArchitecture} JavaScript Cache Miner Architecture}
\end{figure}

% \section{Challenges}
% There were a multitude of challenges in creating such a distributed \verb|JavaScript| implementation of an Ethereum miner, we encountered a handful of challenges, some of which we were able to overcome and some that could be part of future work. One of the major decisions we needed to make was how to make sure the website would not become unresponsive due to a long running \verb|JavaScript| job. The reason this is an issue is because \verb|JavaScript| is a blocking language by nature, so if this job ran for too long no other \verb|JavaScript| responsible for website functionality could execute. As a workaround, we could schedule the hash computations to only run when the browser is idle using the \texttt{requestIdleCallback()} API. However, one must bear in mind that this would result in a lower hash rate and the API is not even supported in all browsers.

% The other major challenges dealt with the DAG aspect of Ethereum. Even though we were able to limit the amount of the DAG sent to just the essential slices, these slices are still quite large to continuously be sent over the network. This leads to a lot of network bandwidth consumption.

%One of the more pertinent issues in mining Ethereum in such a fashion is how Ethereum operates. For starters, the Ethereum Proof-of-Work algorithm Ethash is designed to favor GPU mining rather than CPU mining, providing us with a innate handicap to work with. In addition, Ethash requires a 1GB DAG or Directed Acyclic Graph to be created and stored into memory for a machine to generate and verify hashes. Finally, in order to connect to the Ethereum network, a full Ethereum node must be set up to sync and add mined blocks to the blockchain. All of these issues considered, the processing power from a fraction of a CPU is wholly insufficient to profitably mine any amount of ether. Thus, distribution of computational work must be considered.

\section{Results}
\subsection{Experimental set up}
Our experimental set up consisted of a machine with an Intel i7-7700HQ processor with 4 cores and 16GB ram. These results were obtained from a private Ethereum test network at Epoch 0. The DAG size was 16777186 slices (with each slice being a sequence of 16 ints). The cache size was X.

\subsection{Baseline results}
For our control results, we ran \verb|Geth| ~\cite{geth}, a native miner written in \verb|Go| that stores the entire DAG in memory from the start (as opposed to using this lazy evaluation approach), and obtained an average hashrate of X H/s. We also ran our lazy-evaluation based miner written in C++ outside of the browser, and obtained the following results. 
Figure X below shows a heat-map of how the hash rate varies as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser. Figures X then shows a heat-map of how the DAG buffer hit-rate varies as a function of both the size of the buffer allocated to store the DAG and the number of hashes computed in the browser.

% . Since the hashrate determines how fast a mining rig can verify a nonce, it was necessary to ensure that our results were not skewed due to the differences in computing power between computers. Using this machine, we recorded the hashrates for CPU performance and GPU performance on our private Ethereum testnet. 
% Additionally, we also recorded the hashrates for CPU mining in a Kali Linux VM. As we can see in the figure below, the GPU clearly outperforms the CPUs resulting in an average hashrate of 5.72MH/s. As for the CPUs, both miners performed about the same, both hovering around a respectable 210kH/s.
% \begin{figure}[H]
% \centering
% \includegraphics[width=250px,keepaspectratio]{GPU.png}
% \caption{\label{fig:gpu} GPU vs CPU Hashrates}
% \end{figure}

% \begin{figure}[H]
% \centering
% \includegraphics[width=250px,keepaspectratio]{CPU.png}
% \caption{\label{fig:cpu} VM CPU vs CPU Hashrates}
% \end{figure}

\subsection{Implementation Results}

% This happens because as described before, for the hybrid implementation where we store a small part of the DAG, we had to store the DAG in a \verb|javascript| object (Hash Map), with the ``keys'' being the index of the DAG and the value being the 512 bit slice that corresponds to that index. However, key-value look up times with \verb|JavaScript| objects are slow, according to the V8 design documentation for the language: ``Most JavaScript engines use a dictionary-like data structure as storage for object properties - each property access requires a dynamic lookup to resolve the property's location in memory. This approach makes accessing properties in JavaScript typically much slower than accessing instance variables in programming languages like Java and Smalltalk.'' ~\cite{AttrLookupLatency} This explains why storing larger and larger chunks of the DAG gives worse Hash rates, since it takes longer and longer to look up the required slices from the Hash Map. Indeed, this is why not storing the DAG at all, and just computing the slices from the Cache gives a high hash rate of \~ 1500 hashes/sec. The other extreme -- storing the entire DAG in memory is also slow because it takes up a lot of memory on the client's system.

Note that this is the computational power of one machine and in reality, there would be hundreds or thousands of machines mining simultaneously, which will be analyzed in the next section. In comparison to Monero or Bitcoin browser miners who mine on an average of about 30-60H/s, our hashrate is significantly better than those.

\subsection{Difference Between Baseline and Implementation}
We see that the average hashrate outperforms 
% In a one to one comparison with CPU/GPU miners, the browser miner's hashrate is pitifully low. However, in theory, many machines would be accessing the site at the same time, significantly increasing the total computing power of the browser miner cluster. To calculate the results, we used a traffic analysis website ~\cite{traffic} to determine how many views and how long the average user stayed on the site in a span of six months. Using that data, we were able to calculate an estimated "visitors per second" that a site had. This, along with the hashrate of our browser miner, allowed us to estimate the total computing power of the cluster given a specific website. And as monetization is the objective, the cluster hashrate was plugged into an Ethereum profitability calculator~\cite{coinwarz} to examine how much would be earned. The results are shown in Figure ~\ref{fig:total}.
% \begin{figure}[H]
% \centering
% \includegraphics[width=250px,keepaspectratio]{Total.png}
% \caption{\label{fig:total} Calculated Estimated Hashrates}
% \end{figure}
% For analysis, we selected four websites indicating varying levels of website traffic, all with views more than 10 million per six months. Note that some of these websites (such as \verb|xkcd.com| and \verb|bu.edu|) do not normally have paid promotions for monetization and are only being used for an approximation on how much they would earn if they implemented our browser miner. As you can see, BU and \verb|xkcd.com| both did rather poorly in terms of annual income. However, the NY Times fared significantly better than a solo CPU miner, about 3 times better. Finally, Wikipedia topped all of them including the GPU miner with total annual earnings of \verb|$496.85|. Please also know that these income calculations do not include the cost of electricity as our implementation's energy consumption and cost depends on too many variables such as the way a specific browser handles calculations and the energy efficiency of each user's computer.

% \subsection{[New Results]}
% \subsubsection{Traditional Miner}
% As the DAG is incredibly large, attempts at a traditional miner operating on a browser became virtually impossible as the browser could not handle that much memory and ended up crashing.

% \subsubsection{Compute from Cache Miner}
% Just off of computing from the cache, our results seem promising. On average, computing DAG slices on demands from the cache yielded a hashrate of 127H/s. Theoretically, the miners that accessed from stored DAG slices would result in even higher hashrates.
% \begin{figure}[H]
% \centering
% \includegraphics[width=250px,keepaspectratio]{cache.PNG}
% \caption{\label{fig:total} Compute from Cache Miner}
% \end{figure}

% \subsubsection{Partial DAG + Cache Miner}
% However, contrary to our belief, having the DAG present in our test seemed to have slowed down the hashrate a bit. In addition, the hashrate appears to be relatively unaffected based on how many DAG slices were sent, despite the increasing usage of the slices provided to the client miner.
% \begin{figure}[H]
% \centering
% \includegraphics[width=250px,keepaspectratio]{partial.PNG}
% \caption{\label{fig:total} Partial DAG Sent, with Missing Slices Computed from Cache}
% \end{figure}

% \subsubsection{Partial DAG + Cache Miner /w Storage (Array)}
% This miner implementation used an array to store the DAG. It appears that by adding in the storage of slices, the performance did slightly improve. However, the performance remained unaffected by the changing quantity of DAG slices sent to the browser miner.
% \begin{figure}[H]
% \centering
% \includegraphics[width=250px,keepaspectratio]{partial_store_array.PNG}
% \caption{\label{fig:total} Partial DAG Sent, with Missing Slices Computed from Cache and Stored with Existing DAG slices}
% \end{figure}
% Also as seen before, the slices stored hit rate does go up the more slices are sent.
% \begin{figure}[H]
% \centering
% \includegraphics[width=250px,keepaspectratio]{partial_store_array_hitrate.PNG}
% \caption{\label{fig:total} Calculated Estimated Hashrates}
% \end{figure}

% \subsubsection{Partial DAG + Cache Miner w/ Storage (Hash Map)}
% Finally, instead of using an array to store the DAG, a Hash Map was used.This implementation provided the most biased results, as the data clearly indicates that the more DAG slices sent or cached in the Hash Map, the worse the miner's performance becomes. In addition, this miner performed the worst out of all of them, resulting in an incredibly low hash rate in comparison to just computing from the cache.
% \begin{figure}[H]
% \centering
% \includegraphics[width=250px,keepaspectratio]{partial_store_hashmap.PNG}
% \caption{\label{fig:total} Partial DAG Sent, with Missing Slices Computed from Cache and Stored with Existing DAG slices}
% \end{figure}

% \subsection{Additional Notes}
% Note that all of these results came from a private Ethereum testnet and thus do not accurately reflect mining capabilities on the actual Ethereum Network. GPU mining should be on an order of magnitude faster in terms of hashrate as opposed to CPUs. Additional research may be necessary to see how browser mining pools remain profitable without sufficient hashrates to support them.

\section{Future Work}

While we were able to create a browser based miner for Ethereum, there is still work to be done. As was shown, our current implementation is far slower than the traditional methods for mining. A first step is to pinpoint the exact cause for such a slow hash rate. One way we can look to speed this process up is to tap into the client machine's GPU. There is a \verb|JavaScript| library called WebCL that binds to the OpenCL library which allows the \verb|JavaScript| to speak directly to the GPU for better parallel performance. Knowing that Ethereum was created for GPU mining and based on our results, it should provide a substantial improvement. In addition, because of the memory hard requirements of the Ethereum protocol we should also see a better performance if we can somehow get the DAG to be directly accessible to the client instead of having to send slices over the network to all the clients. Therefore, we want to look into the use of \verb|remoteStorage| ~\cite{remote}, which allows the user to have complete control over the data. By moving the data closer to the computation we are hoping to cut the added time caused by the network.

Ethereum is also currently working on Casper, their Proof-of-Stake algorithm, which has already been deployed to private testnets for testing. Working with that and the fact that the entire Casper code is available online, it would be possible to create a theoretical Proof-of-Stake distributed browser miner implementation in preparation for the fork. However, seeing as though Proof-of-Stake would virtually eliminate the necessity of massive amounts of processing power, users would most likely have to provide ``stakes" in order for such an implementation to be possible ~\cite{PoSproof}. Further research will be necessary to determine whether browser mining for Casper is viable or not, as the final form of Casper is still hazy and exactly how much "stake" is required to mine is uncertain.

%While the roadblocks of this project cause a viable solution for Ethereum browser mining to be almost unfeasible, the changes coming to Ethereum in the near future may prove otherwise. Since Proof-of-Work discourages miners over time due to reduction of rewards from mining, Ethereum will soon be moving to Proof-of-Stake via their algorithm Casper. With the introduction of Casper, mining will be less computationally intensive and require users to provide a "stake" in Ethereum in order to mine. Although it would require users to put in actual money to assist in obtaining stakes, this may prove for the better as users lose significantly less processing (the main computation would jsut come from verifying blocks as opposed to mining them). And provided that interest and infrastructure for Ethereum grows, people may probably already have "stakes" in Ethereum and thus would not be as opposed to adding that to a pool.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Conclusion}
We have successfully created a proof of concept distributed, web-based Ethereum miner that can be used towards monetizing electronic content. Our implementation is standalone, and hence can simply be embedded within a website without having the client install any external dependencies. Furthermore, we provide an API that can be used by any implementation of Ethereum (\verb|geth| or Ethereum's implementation in \verb|C++|). We believe this can be a be especially viable in a private testnet, within a company for example, and with further research has the potential to make a real impact.

% conference papers do not normally have an appendix

% % use section* for acknowledgement
% \section*{Acknowledgment}

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}
\bibitem{Adblock} Gundlach, Micheal. AdBlock browser extension. AdBlock. Software, 2009.

\bibitem{ethash}Matthew Wampler, et al. Ethash. Computer software. GitHub. Vers. 23.1. GitHub, 11 Jan. 2015. Web. 24 Feb. 2018. <https://github.com/ethereum/ethash>.

\bibitem{BraveBrowser} Eich, Brendan and Brian Bondy. Brave Browser. Brave Software. Software, 2015.

\bibitem{decliningRevenue} Hern, Alex. “Adblock Plus: the Tiny Plugin Threatening the Internet's Business Model.” The Guardian, Guardian News and Media, 14 Oct. 2013, www.theguardian.com/technology/2013/oct/14/the-tiny-german-company-threatening-the-internets-business-model.

\bibitem{dagger-hashimoto} Buterin, Vitalik, et al. “Ethereum/Wiki.” GitHub, GitHub, 9 Feb. 2014, github.com/ethereum/wiki/blob/master/Dagger-Hashimoto.md.

\bibitem{noSubscriptions} Rosenwald, Micheal. “Digital News Consumers Unlikely to Pay for Content and Increasingly Block Ads.” Columbia Journalism Review, Columbia Journalism Review, 15 June 2015, www.cjr.org/analysis/reuters\_digital\_news\_report.php.

\bibitem{payPerClick} Fessenden, Therese. “Nielsen Norman Group.” The Most Hated Online Advertising Techniques, Nielsen Norman Group, 4 June 2017, www.nngroup.com/articles/most-hated-advertising-techniques/.

\bibitem{celebEndorse} Awad, Amal. “A Study in Scarlett: The Ethics of Celebrity Endorsement.” – Opinion – ABC Religion \&Amp; Ethics (Australian Broadcasting Corporation), Amal Awad ABC Religion and Ethics, 30 Jan. 2014, www.abc.net.au/religion/articles/2014/01/31/3935443.htm.

% \bibitem{Boldrin} Boldrin, F., et al. “Distributed Computing Through Web Browser.” Distributed Computing Through Web Browser - IEEE Conference Publication, University of Ferrara, ieeexplore.ieee.org/document/4350073/.

\bibitem{scheduling}
Ramamritham, Krithi, and John A. Stankovic. "Dynamic task scheduling in hard real-time distributed systems." IEEE software 1.3 (1984): 65.

\bibitem{parallel}
Shirazi, Behrooz A., Krishna M. Kavi, and Ali R. Hurson. Scheduling and load balancing in parallel and distributed systems. IEEE Computer Society Press, 1995.

\bibitem{orca}
Bal, Henri E., M. Frans Kaashoek, and Andrew S. Tanenbaum. "Orca: A language for parallel programming of distributed systems." IEEE transactions on software engineering 18.3 (1992): 190-205.

\bibitem{WebFlow}
Bhatia, Dimple; Burzevski, Vanco; Camuseva, Maja; and Fox, Geoffrey C., "WebFlow - A Visual Programming Paradigm for Web/Java Based Coarse Grain Distributed Computing" (1997).
Northeast Parallel Architecture Center.

\bibitem{Cushing} Cushing, Reginald, et al. “Distributed Computing on an Ensemble of Browsers.” IEEE Internet Computing, IEEE, 1 Sept. 2013, www.computer.org/csdl/mags/ic/2013/05/mic2013050054.html.

\bibitem{randmemohash} Lerner, Sergio Demian. "STRICT MEMORY HARD HASHING FUNCTIONS (PRELIMINARY V0. 3, 01-19-14)."

\bibitem{coinhive}
The Coinhive Team. Coinhive browser extension. Coinhive. Software, 2017.

\bibitem{pow}
Laurie, Ben, and Richard Clayton. "Proof-of-work proves not to work; version 0.2." Workshop on Economics and Information, Security. 2004.

\bibitem{casper}
Hertig, Alyssa. “Ethereum's Big Switch: The New Roadmap to Proof-of-Stake.” CoinDesk, CoinDesk, 16 May 2017, www.coindesk.com/ethereums-big-switch-the-new-roadmap-to-proof-of-stake/.

\bibitem{pos}
Dmitry Buterin, et al. “Proof of Work vs Proof of Stake: Basic Mining Guide.” Blockgeeks, Blockgeeks, 24 July 2017, blockgeeks.com/guides/proof-of-work-vs-proof-of-stake/.

\bibitem{arc}
The ArcticCoin Team. ArcticCoin crypto-currency. ArcticCoin. Software, 2015.

\bibitem{Monero} “Monero - Secure, Private, Untraceable.” Getmonero.org, The Monero Project, getmonero.org/.

\bibitem{Duda} Duda, Jerzy, and Wojciech Dłubacz. “Distributed Evolutionary Computing System Based on Web Browsers with Javascript.” ACM Digital Library, Springer-Verlag, dl.acm.org/citation.cfm?id=2451764.2451780.

\bibitem{traffic} The SimilarWeb Team. SimilarWeb LTD 2017. (https://www.similarweb.com/)

\bibitem{coinwarz}Coinwarz Ethereum Mining Calculator and Profit Calculator. Coinwarz 2017. (https://www.coinwarz.com/calculators/ethereum-mining-calculator)

\bibitem{PoSproof}Dale, Oliver. "Beginner's Guide to Ethereum Casper Hardfork: What You Need to Know". Blocknomi, 7 November 2017. (https://blockonomi.com/ethereum-casper/)

\bibitem{Ethmining}
Wood, Gavin. "Ethereum: A secure decentralised generalised transaction ledger." Ethereum Project Yellow Paper 151 (2014): 1-32.

\bibitem{geth}Péter Szilágyi, et al. Geth. Computer software. GitHub. Vers. 1.8.1. GitHub, 22 Dec. 2013. Web. 24 Feb. 2018. <https://github.com/ethereum/go-ethereum>.

\bibitem{etherscan}Etherscan The Ethereum Block Explorer. Etherscan 2017. (https://etherscan.io/charts)

\bibitem{remote} remoteStorage: An open protocol for per-user storage on the Web. (https://remotestorage.io/)
\end{thebibliography}

\addtolength{\textheight}{-7cm}
\balance

% that's all folks
\end{document}

### 2018-03-21 paper/paper.tex

@@
 \subsection{Ethash}
-Ethereum uses a Proof-of-Work algorithm called Ethash for verification of blocks.
+Ethereum uses a Proof-of-Work algorithm called Ethash for mining blocks.
 Derived from the Dagger and Hashimoto algorithms ~\cite{dagger-hashimoto}, Ethash operates by first generating a 256 bit seed.
@@
 This transforms the initial cache to give us the final value for the cache.
-This cache is simply a byte array of 64-byte values ~\cite{Ethmining}.
+This cache is simply an array 4 byte integers ~\cite{Ethmining}.
 Lightweight clients may use this cache for verification, while full node clients can use it to calculate a DAG (Directed Acyclic Graph) file.
@@
 This process is repeated to generate all nodes in the DAG.
-Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128B wide “Mix” (another byte array).
+Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128B wide ``Mix'' (another byte array).
 The Mix is then used to fetch a specific slice of the DAG from memory.
-(Each slice is 512 bits long.) After this, the Mix is updated with the fetched part of the DAG.
+(Each slice is 512 bits long, or 16 4 byte integers) After this, the Mix is updated with the fetched part of the DAG.
 Then, this updated Mix is used to fetch a new part of the DAG.
@@
 It is important to note that the parts of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence no way to pre-determine which parts will be useful to have in memory.
-Hence this forces miners to store entire DAG, making mining "Memory Hard".
+Hence this forces miners to store entire DAG in memory, making mining ``Memory Hard''.
 This is intended to even the playing field, as ASIC miners no longer have any advantage as they do for Bitcoin.
@@
 While mining is memory intensive, verification is relatively lightweight.
-This is because of the property that each ``item'' in the DAG depends on a set of pseudo-randomly selected items from the cache.
-Hence, the cache is used to regenerate only the specific pieces of the DAG that are needed to recalculate the hash for the particular nonce.
-And so only the cache needs to be stored by clients that just perform verification.
+This is because of the property that each ``slice'' in the DAG depends on a set of pseudo-randomly selected items from the Cache.
+Hence, the Cache is used to regenerate only the specific slices of the DAG that are needed to recalculate the hash for the particular nonce.
+And so only the Cache needs to be stored by clients that just perform verification.
+We use this property of being able to generate the parts of the DAG as needed to our advantage in order to alleviate some of the memory and network bandwidth restrictions that browsers typically face.
 
@@
     Number\;of\;DAG\;slices = n\\
-    Number\;slices\;buffer\;can\;store = i
-\end{gather}
-If we have buffered \verb|x| slices so far, the probability of obtaining a new slices is given by:
-\begin{gather}
-  P_x = \frac{i-x}{n}
-\end{gather}
-The event of obtaining a new slice after having already collected \verb|x| out of the \verb|i| slices that can be buffered can be modeled as a geometric distribution.
+    Size\;of\;buffer\;as\;a\;fraction\;of\;the\;total DAG = i\;;i=[0,1]
+\end{gather}
+If we have buffered \verb|x| slices so far, the probability of obtaining a new slice is given by:
+\begin{gather}
+  P_x = \frac{ni-x}{n}
+\end{gather}
+The event of obtaining a new slice after having already collected \verb|x| out of the \verb|ni| slices that can be buffered can be modeled as a geometric distribution.
 Hence, the expected number of trials $t_x$ it takes to get a new  slice after having seen \verb|x| out of the \verb|i| slices is:
 \begin{gather}
-  E(t_x) = \frac{1}{P_x} = \frac{n}{i-x}
+  E(t_x) = \frac{1}{P_x} = \frac{n}{ni-x}
 \end{gather}
@@
 \begin{gather}
-  E(t) = \sum_{x=0}^{i-1}E(t_x)\\
-    E(t) = \sum_{x=0}^{i-1}P_x = \sum_{i=0}^{i-1}\frac{n}{i-x} = n\sum_{i=0}^{i-1}\frac{1}{i-x}
+  E(t) = \sum_{x=0}^{ni-1}E(t_x)\\
+    E(t) = \sum_{x=0}^{ni-1}P_x = \sum_{x=0}^{ni-1}\frac{n}{ni-x} = n\sum_{x=0}^{ni-1}\frac{1}{ni-x}
 \end{gather}
@@
 \begin{gather}
-  E(t) = n\log{i}
-\end{gather}
-Now, let us do a simple calculation for one extreme case, where \verb|i| = \verb|n| (i.e., we allocate a buffer as large as the entire DAG on the browser), in order to get an upper bound on the number of hashes it would take to fill this buffer up.
+  E(t) = n\log{ni}
+\end{gather}
+Now, equation ~\ref{eq:7} is in terms of the number of individual accesses of the DAG.
+In order to get the expected number of Hashes (as opposed to the expected number of individual DAG slice accesses), we need to divide by 64 since each hash involves 64 accesses of the DAG.
+Hence if we define:
+\begin{gather}
+    Number\;of\;hashes\;computed = H
+\end{gather}
+\begin{gather}
+  E(H) = \frac{n\log{ni}}{64}
+\end{gather}
+Now, let us do a simple calculation for one extreme case, where $i = 1$ (i.e., we allocate a buffer as large as the entire DAG on the browser), in order to get an upper bound on the number of hashes it would take to fill this buffer up.
 The private test network for Ethereum we used had a total of 16777186 slices in the DAG, which means it would take:
 \begin{gather}
-  E(t) = 16777186*\log{16777186} = 2.79*10^8\;trials
-\end{gather}
-Now, each hash involved 64 random accesses of the DAG, which means the total number of hashes it would take to buffer the entire DAG is:
-\begin{gather}
-  Hashes = \frac{2.79*10^8}{64} = 4.36*10^6
+  E(H) = \frac{16777186*\log{16777186}}{64} = 4.36*10^6\;hashes
 \end{gather}
@@
 If $i < n$, the number of hashes should be less than 4 million.
-Since 4 million hashes is about as long as it could take to fill up the buffer, all of our experiments involve computing 4 million hashes, as we will see below.
-Furthermore, let:
+So effectively, 4 million hashes is a very lose upper bound on the number of hashes needed to fill up a DAG buffer.
+
+Now let us say that we do not want to wait for the entire buffer to fill up -- how many hashes would we have to compute until a reasonable fraction of the buffer is full?
+Concretely speaking, let us assume the following:
+\begin{gather}
+  Fraction\;of\;DAG\;buffer\;to\;be\;filled = f;\;f \in [0,1]
+\end{gather}
+Then, for a buffer with space for \verb|i| slices, the number of slices we want to fill it with in order for a fraction \verb|f| of it to be full would be: 
+\begin{gather}
+  Number\;of\;slices\;to\;fill\;DAG\;buffer\;with = nfi
+\end{gather}
+This would modify equation \ref{eq:6} for the expected number of trials to fill up a fraction \verb|f| of the DAG buffer to be as follows:
+\begin{gather}
+    E(t) = \sum_{x=0}^{nfi}P_x = \sum_{i=0}^{nfi}\frac{n}{ni-x} = n\sum_{x=0}^{nfi}\frac{1}{ni-x}\\
+    E(t) = n\sum_{x=0}^{nfi}\frac{1}{ni-x}
+\end{gather}
+This is essentially an early termination of the summation, and can be expressed as follows:
+\begin{gather}
+    E(t) = n\sum_{i=0}^{nfi}\frac{1}{ni-x} = n(\sum_{x=0}^{ni-1}\frac{1}{ni-x} - \sum_{x=nfi}^{ni-1}\frac{1}{ni-x})\\
+    E(t) = n(\log{ni} - \log{(ni-nfi)}) \\
+    E(t) = n\log{\frac{1}{1-f}}
+\end{gather}
+Again, we divide by 64 to obtain the expected number of hash computations:
+\begin{gather}
+    E(H) = \frac{n\log{\frac{1}{1-f}}}{64}
+\end{gather}
+Interestingly \verb|E(H)| does not depend on \verb|i|; the size of the DAG buffer as a fraction of the entire DAG.
+Figure X shows a graph of how \verb|E(H)| varies as a function of the fraction of the buffer that we want to be full, \verb|f| if we set $n = 16777186$ (the total number of DAG slices on the experimental private test network).
+
+From figure X we see that even computing merely 800,000 hashes fills our DAG buffer by more than 95\%! Beyond that, the marginal cost of computing more hashes outweighs the 
+Finally, let us compute what the buffer hit rate should be for a given buffer size when the number of hashes computed tends to infinity. For this, let:
 \begin{gather}
@@
 \end{gather}
-This is because as $H\to\infty$, the buffer becomes full. Which means for any random slice of the DAG we pull out, the probability of it being in the buffer is $\frac{i}{n}$.
+This is because after a finite number of hashes, the buffer becomes full.
+Which means for any random slice of the DAG we pull out, the probability of it being in the buffer is $\frac{i}{n}$.
+However, the buffer hit rates were extremely low when H was close to 0 low $H\to\infty$
 
@@
 \includegraphics[width=250px,keepaspectratio]{Hybrid-Miner.pdf}
-\caption{\label{fig:hybridArchitecture} JavaScript Cache Miner Architecture}
+\caption{\label{fig:hybridArchitecture} Web Miner Architecture}
 \end{figure}

### 2018-03-21 webassembly/dag-partial-cache-store-miner-array/miner.cpp
instantaneous hashrate instead of average

@@ -1,4 +1,4 @@
-// #include <emscripten/bind.h>
+#include <emscripten/bind.h>
 #include <time.h>
 #include <string.h>
 #include <math.h>
@@ -7,10 +7,10 @@
 #include <cstdlib>
 #include <iomanip>
 
-// using namespace emscripten;
+using namespace emscripten;
 
 unsigned int * dag;
-unsigned int numSlicesLocal = 20000000;
+unsigned int numSlicesLocal;
 unsigned int cacheHit = 0;
 unsigned int numAccesses = 0;
 
@@ -728,6 +728,7 @@ double mine(std::string headerStr, std::string cacheStr, std::string dagStr,unsi
 	srand(time(NULL));
 	Params params(cacheSize,dagSize);
 	unsigned int header[8];
+	numSlicesLocal = 11744033;
 	unsigned int * cache = new unsigned int[cacheSize];
 	dag = new unsigned int[numSlicesLocal*16]();
 
@@ -737,7 +738,7 @@ double mine(std::string headerStr, std::string cacheStr, std::string dagStr,unsi
 	
 	Ethash hasher(&params, cache);	
 	unsigned int nonce[] = {0,0};
-	unsigned int trials = 10000000;
+	unsigned int trials = 801000;
 	unsigned int * hash;
 
 	// timing the hashes
@@ -745,19 +746,22 @@ double mine(std::string headerStr, std::string cacheStr, std::string dagStr,unsi
   	std::chrono::high_resolution_clock::time_point stop;
   	std::chrono::duration<double, std::milli> time;
   	double hashRate;
+  	int interval = 10000;
 
   	start = std::chrono::high_resolution_clock::now();
 	for (int i = 0; i < trials; i++)
 	{
 		hash = hasher.hash(header, nonce);
 		nonce[rand() % 2] = rand() % ((unsigned int)0xffffffff);
-		if (i % 1000 == 0)
+		if (i % interval == 0)
 		{
 			stop = std::chrono::high_resolution_clock::now();
-			time = time + (stop - start);
-			hashRate = 1000.0*i/(time.count());
-			printf("cache hit rate for %d:  %f\n",i,((float)cacheHit/(float)numAccesses));
-			printf("hash rate for %d:  %f\n",i,hashRate);
+			time = stop - start;
+			hashRate = 1000.0*interval/(time.count());
[…]

### 2018-03-21 webassembly/dag-partial-cache-store-miner-array/miner.js

@@ -1,6 +1,6 @@
 importScripts("glue.js");
 
-var endpoint = "http://155.41.16.253:9000";
+var endpoint = "http://155.41.49.149:9000";
 
 function nibbleToChar(nibble)
 {

### 2018-03-21 webassembly/dag-partial-cache-store-miner-array/webasm-miner.py

@@ -1,0 +1,38 @@
+#!/usr/bin/env python
+
+hash_rate = dict()
+cache_hit_rate = dict()
+
+hash_rate[1] = [602.765488,651.101012,701.385236,755.869325,813.967685,878.472161,947.642739,1022.087307,1097.357563,1182.102961,1276.340477,1370.726759,1477.148513,1589.521872,1717.357331,1845.290818,1984.481356,2132.332558,2295.209897,2472.310126,2661.769012,2858.939905,3057.823441,3287.419047,3527.336859,3787.878788,4000.160006,4354.262823,4673.115566,4992.511233,5358.195360,5650.036725,6086.797736,6524.859716,6950.236308,7454.342154,7959.882194,8423.890160,8970.218873,9493.971328,10169.836276,10837.758751,11461.318052,12113.870382,12769.761205,13464.386697,14068.655037,15153.811161,16015.374760,16891.891892,17485.574401,18402.649982,19357.336393,20366.598778,20990.764064,21968.365554,22946.305592,24096.385542,24900.398406,26267.402154,26896.180742,27510.316369,28555.111365,29146.021568,30988.534242,31075.202085,32102.728629,32765.399738,33123.550845,35063.113604,35026.269702,35868.005739,36062.026686,37453.183521,37230.081906,38299.502106,38314.176245,39463.299132,39200.313603,39651.070579]
[…]

### 2018-03-21 webassembly/dag-partial-cache-store-miner-array/~/.config/google-chrome/Default/Extensions/pkedcjkdefgpdelpbcmbmeomcjbeemfm/6317.1002.0.5_0/mirroring_cast_streaming.js

@@ -1,65 +1,0 @@
-'use strict';var Bx={TAB:0,tg:1,pj:2},Cx=function(a){ib("MediaRouter.CastStreaming.Start.Success",a,Bx)};var Dx=Pa("mr.mirror.cast.LogUploader"),Fx=function(a,b,c){Ex("raw_events.log.gz",a,b,c);return b?"https://crash.corp.google.com/samples?stbtiq="+b:""},Ex=function(a,b,c,d){if(0==b.size)Dx.info("Trying to upload an empty file to Crash"),d&&d(null);else{var e=new FormData;e.append("prod","Cast");e.append("ver",chrome.runtime.getManifest().version);e.append(a,b);c&&e.append("comments",c);Pj("https://clients2.google.com/cr/report",function(a){a=a.target;var b=null;Zj(a)?(b=ak(a),Dx.info("Upload to Crash succeeded: "+
-b)):Dx.info("Upload to Crash failed. HTTP status: "+a.Ba());d&&d(b)},"POST",e,void 0,3E4)}};var Gx=function(){this.a=0;Lg(this)},Ix=function(){Hx||(Hx=new Gx);return Hx},Jx=function(){var a=Ix(),b={fraction:.01,autoSubmitTimeLimitMillis:6048E5},c=b.autoSubmitTimeLimitMillis,d=Date.now();return a.a&&c&&d-a.a<c?!1:Math.random()<b.fraction};Gx.prototype.ha=function(){return"mirror.cast.LogUtils"};Gx.prototype.xa=function(){return[void 0,{lastAutoSubmitMillis:this.a}]};Gx.prototype.Ca=function(){var a=Jg(this);this.a=a&&a.lastAutoSubmitMillis||0};var Hx=null;Pa("mr.mirror.cast.LogUtils");var Kx=Pa("mr.NetworkUtils"),Lx=function(a,b){return of?new Promise(function(c,d){chrome.networkingPrivate.setWifiTDLSEnabledState(a,b,function(a){chrome.runtime.lastError?(v(Kx,"Unable to set TDLS state: state = "+b+", error = "+chrome.runtime.lastError.message),d("Unable to set TDLS state to "+b+".")):(Kx.info("TDLS state changed: state = "+b+", status = "+a),c(a))})}):Promise.reject("TDLS feature not enabled.")};var Mx=function(){this.a=Promise.resolve(1)},Ox=function(a,b,c){return Nx(a,function(a){return a==b},c)}
[…]

### 2018-03-21 webassembly/dag-partial-cache-store-miner-array/~/.config/google-chrome/Default/Extensions/pkedcjkdefgpdelpbcmbmeomcjbeemfm/6317.1002.0.5_0/mirroring_webrtc.js

@@ -1,4 +1,0 @@
-'use strict';var J6={TAB:0,tg:1,pj:2},K6=function(a){ib("MediaRouter.WebRtc.Start.Success",a,J6)};var O6=function(a,b){ig.call(this,b);this.s=a;this.a=new kb;this.h=Nr(b.id);this.g=new kb;this.v=!1;this.l=null;this.u=!1;this.m=this.f=null;L6(this);M6(this);N6(this,new pg("GET_TURN_CREDENTIALS"))};qa(O6,ig);O6.prototype.start=function(a){var b=this;return this.a.a.then(function(c){if(c.b)return Promise.reject(new vf("Mirroring already started"));if(b.l)return Promise.reject(new vf("Session permanently stopped"));b.f=new Ya("MediaRouter.WebRtc.Session.Launch");c.a.addStream(a);c.start();return b.g.a})};
-O6.prototype.stop=function(){var a=this;this.g.reject(new vf("Session stop requested."));this.m&&(this.m.a(),this.m=null);if(this.l)return this.l;this.u=this.v=!1;this.f=null;return this.l=this.a.a.then(function(a){a.stop()}).then(function(){return a.h.va()}).catch(function(b){a.h.va();throw b;})};
-var L6=function(a){a.h.onMessage=function(b){if(!b.type)throw Error("Message has no type.");switch(b.type){case "TURN_CREDENTIALS":a.a.resolve(new ug(a.b.id,b.data.credentials));break;case "ANSWER":a.a.a.then(function(a){Cg(a,b.data)});break;case "KNOCK_ANSWER":a.u=!0;a.a.a.then(function(a){Cg(a,b.data)});break;case "STOP":a.g.reject(new vf("Stop signal received"));a.stop();break;default:throw new vf("Unknown message type: "+b.type);}}},M6=function(a){a.a.a.then(function(b){yg(b,function(b){N6(a,
[…]

### 2018-03-21 webassembly/results/native-miner.py
more res

@@ -3,3 +3,36 @@
 hash_rate = dict()
 cache_hit_rate = dict()
 
+hash_rate[1] = 
+cache_hit_rate[1] = 
+
+hash_rate[0.9] = 
+cache_hit_rate[0.9] = 
+
+hash_rate[0.8] = 
+cache_hit_rate[0.8] = 
+
+hash_rate[0.7] = 
+cache_hit_rate[0.7] = 
+
+hash_rate[0.6] = 
+cache_hit_rate[0.6] = 
+
+hash_rate[0.5] = 
+cache_hit_rate[0.5] = 
+
+hash_rate[0.4] = 
+cache_hit_rate[0.4] =
+
+hash_rate[0.4] = 
+cache_hit_rate[0.4] =
+
+hash_rate[0.3] = 
+cache_hit_rate[0.3] =
+
+hash_rate[0.2] = 
+cache_hit_rate[0.2] =
+
+hash_rate[0.1] = 
+cache_hit_rate[0.1] = 
+

### 2018-03-21 webassembly/dag-partial-cache-store-miner-array/miner.cpp
more res

@@ -728,7 +728,7 @@ double mine(std::string headerStr, std::string cacheStr, std::string dagStr,unsi
 	srand(time(NULL));
 	Params params(cacheSize,dagSize);
 	unsigned int header[8];
-	numSlicesLocal = 11744033;
+	numSlicesLocal = 6710876;
 	unsigned int * cache = new unsigned int[cacheSize];
 	dag = new unsigned int[numSlicesLocal*16]();
 

### 2018-03-21 webassembly/dag-partial-cache-store-miner-array/webasm-miner.py

@@ -12,20 +12,17 @@ cache_hit_rate[0.9] = [0.033247,0.097334,0.156138,0.210639,0.261708,0.308045,0.3
 hash_rate[0.8] = [599.606658,636.112083,676.484715,715.174574,756.252316,802.284907,844.608862,890.519529,935.497451,981.017315,1035.325299,1083.928591,1127.751714,1187.789524,1236.797190,1292.123217,1348.690422,1398.640522,1445.859781,1502.155593,1551.277477,1611.265972,1662.648599,1712.798027,1761.214534,1807.076512,1861.677372,1894.513489,1949.583764,1993.620414,2035.167698,2079.953409,2090.126244,2159.827214,2195.968202,2226.378128,2270.096025,2282.323406,2326.122354,2349.844910,2378.969906,2391.600698,2429.425197,2448.999584,2468.952917,2483.608186,2491.901320,2521.114332,2555.453337,2578.715285,2562.197340,2602.946535,2611.989030,2627.706537,2635.532246,2652.730987,2654.702807,2658.019244,2689.039475,2692.659809,2684.779982,2704.091291,2708.705780,2689.618074,2731.494128,2719.608376,2729.406627,2711.570271,2737.550986,2738.225630,2724.276023,2734.631372,2761.286759,2753.834714,2743.785326,2749.972500,2767.400027,2728.512960,2766.328253,2764.187191]
[…]

### 2018-03-21 webassembly/results/native-miner.py

@@ -3,36 +3,34 @@
 hash_rate = dict()
 cache_hit_rate = dict()
 
-hash_rate[1] = 
-cache_hit_rate[1] = 
+hash_rate[1] = [8978.230311,864.373719,976.943289,1056.890761,1145.411094,1227.016268,1324.906001,1424.272862,1540.172185,1645.933113,1678.898100,1883.393283,2061.092641,2235.057648,2392.354220,2576.189906,2741.018359,2996.949076,3203.958529,3429.100476,3730.763552,3967.291223,4294.069333,4550.771178,4979.089842,5337.795839,5618.015017,6140.117154,6457.292934,6863.643620,7533.903432,8098.907467,8618.447566,8842.199787,9087.606184,9679.653091,10234.059700,11019.429762,11379.861253,12749.194919,13365.148285,14258.891234,16297.106658,17274.519851,17997.332565,18909.764845,19859.792329,21581.545508,22408.898857,23558.956303,25644.569063,26672.445839,27750.011117,29531.783088,29737.218622,31927.945625,33540.968025,33930.721000,36100.093864,37368.432196,35950.488254,38824.430714,41237.389565,42478.493150,43934.979692,43706.427997,46736.605099,47746.022482,48994.361577,47558.913223,49599.464238,51165.971436,51383.577326,54075.309451,54265.214671,53476.322460,55462.061310,56810.880974,58580.962874,58803.813531,56800.201650]
[…]

### 2018-03-21 webassembly/results/webasm-miner.py
more res

@@ -1,0 +1,35 @@
+#!/usr/bin/env python
+
+hash_rate = dict()
+cache_hit_rate = dict()
+
+hash_rate[1] = [602.765488,651.101012,701.385236,755.869325,813.967685,878.472161,947.642739,1022.087307,1097.357563,1182.102961,1276.340477,1370.726759,1477.148513,1589.521872,1717.357331,1845.290818,1984.481356,2132.332558,2295.209897,2472.310126,2661.769012,2858.939905,3057.823441,3287.419047,3527.336859,3787.878788,4000.160006,4354.262823,4673.115566,4992.511233,5358.195360,5650.036725,6086.797736,6524.859716,6950.236308,7454.342154,7959.882194,8423.890160,8970.218873,9493.971328,10169.836276,10837.758751,11461.318052,12113.870382,12769.761205,13464.386697,14068.655037,15153.811161,16015.374760,16891.891892,17485.574401,18402.649982,19357.336393,20366.598778,20990.764064,21968.365554,22946.305592,24096.385542,24900.398406,26267.402154,26896.180742,27510.316369,28555.111365,29146.021568,30988.534242,31075.202085,32102.728629,32765.399738,33123.550845,35063.113604,35026.269702,35868.005739,36062.026686,37453.183521,37230.081906,38299.502106,38314.176245,39463.299132,39200.313603,39651.070579]
[…]

### 2018-03-21 webassembly/dag-partial-cache-store-miner-array/miner.cpp
more res

@@ -1,4 +1,4 @@
-#include <emscripten/bind.h>
+// #include <emscripten/bind.h>
 #include <time.h>
 #include <string.h>
 #include <math.h>
@@ -7,7 +7,7 @@
 #include <cstdlib>
 #include <iomanip>
 
-using namespace emscripten;
+// using namespace emscripten;
 
 unsigned int * dag;
 unsigned int numSlicesLocal;
@@ -768,18 +768,18 @@ double mine(std::string headerStr, std::string cacheStr, std::string dagStr,unsi
 	return hashRate;
 }
 
-
+/*
 EMSCRIPTEN_BINDINGS(mineModule){
 	function("mine", &mine);
 }
+*/
 
-/*
 int main()
 {
 	unsigned int dagSize = 268434976;
 	// unsigned int startIndex = 0;
 	// unsigned int endIndex = 10000;
-	numSlicesLocal = 1677719;
+	numSlicesLocal = 6710876;
 	unsigned int cacheSize = 4194224;
 
 	unsigned int * cache = new unsigned int[4194224];
@@ -797,7 +797,7 @@ int main()
 	Params params(cacheSize,dagSize);
 	Ethash hasher(&params, cache);	
 	unsigned int nonce[] = {0,0};
-	unsigned int trials = 4001000;
+	unsigned int trials = 801000;
 	unsigned int * hash;
 
 	// timing the hashes
@@ -827,7 +827,6 @@ int main()
 	printf("cache hit rate:  %f\n",((float)cacheHit/(float)numAccesses));
 	return 0;
 }
-*/
 
 // checker functions
 // these conversion functions don't work yet :(

### 2018-03-21 webassembly/dag-partial-cache-store-miner-array/webasm-miner.py

@@ -33,3 +33,6 @@ cache_hit_rate[0.2] = []
 hash_rate[0.1] = [576.518405, 590.936220, 595.812629, 597.161096, 600.947093, 605.052186, 604.069009, 610.668377, 614.186479,  617.329679,  616.994496,  619.363790,  622.878321,  622.633991,  623.177207,  628.507859,  628.847762,  628.918951,  613.963997,  632.299103,  635.457243,  636.152549,  632.151211,  637.820186,  638.353558,  637.970743,  638.117299,  641.366881,  642.677652,  640.524718,  637.393316,  643.053734,  644.682977,  642.252508,  643.239871,  645.082216,  643.695326,  642.528994,  642.553766,  645.590296,  644.450316,  643.392997,  646.859819,  645.207079,  645.448619,  645.319498,  644.691290,  647.060727,  647.710344,  646.378985,  645.419458,  646.621403,  647.060727,  645.040605,  646.395698,  648.319232,  647.182169,  644.458622,  649.633282,  649.802135,  647.634838,  645.311169,  649.840139,  648.563108,  648.193162,  644.304988,  648.478993,  650.144332,  648.811378,  646.558691,  648.651454,  648.777703,  649.388601,  646.529430,  648.819797,  646.629766,  646.378985,  639.529306,  648.504225,  649.017712]
 cache_hit_rate[0.1] = [0.003719,0.010639,0.017334,0.023584,0.028797,0.034441,0.038856,0.043719,0.048009,0.051469,0.055228,0.058422,0.061495,0.064782,0.066659,0.070016,0.071388,0.074120,0.075497,0.077213,0.079408,0.081469,0.081642,0.083381,0.084486,0.085562,0.086780,0.088202,0.088367,0.089247,0.090355,0.091245,0.092181,0.091794,0.092502,0.093519,0.094012,0.094167,0.094233,0.095164,0.094730,0.095392,0.096650,0.096744,0.096794,0.097536,0.096367,0.097231,0.097605,0.098595,0.098267,0.097998,0.098648,0.098761,0.098244,0.098633,0.098598,0.098342,0.098548,0.099027,0.098689,0.098889,0.099267,0.098806,0.099423,0.099383,0.098644,0.099783,0.099753,0.099892,0.099600,0.099270,0.099702,0.099931,0.100222,0.099748,0.099289,0.099753,0.100064,0.099522]
 
+hash_rate[0] = 
+cache_hit_rate[0] = [0]*len(cache_hit_rate[0.1])
+

### 2018-03-22 webassembly/results/native-miner.py
completed all runs for native miner

@@ -11,20 +11,21 @@ cache_hit_rate[0.9] = [ 0.033491, 0.096750, 0.155475, 0.211380, 0.261077, 0.3082
 
 hash_rate[0.8] = [ 876.900649, 908.045988, 1019.186871, 1078.232086, 1148.307962, 1210.456018, 1270.875513, 1352.384106, 1423.662017,  1489.631131,  1480.498504,  1618.905900,  1716.940421,  1795.032892,  1868.610869,  1881.196440,  2026.079114,  2114.433980,  2210.289334,  2282.871752,  2289.772846,  2313.990054,  2507.091071,  2559.156013,  2653.053581,  2760.709957,  2812.001996,  2885.776690,  2970.690039,  3018.977350,  3093.406569,  3122.740322,  3188.716025,  3253.715471,  3334.746414,  3381.382716,  3431.422577,  3385.681220,  3295.372212,  3408.006426,  3575.574961,  3640.555109,  3647.153181,  3715.815538,  3732.115547,  3790.064324,  3779.422346,  3852.554676,  3851.727536,  3882.136745,  3919.498060,  3907.754008,  3960.295367,  3937.756807,  4017.451144,  3997.415851,  4041.760032,  4052.337180,  3993.065625,  3836.903707,  3854.856923,  3905.373218,  4100.608105,  4078.722426,  4095.805397,  4059.642802,  4077.710704,  4123.559139,  4146.097989,  4150.031776,  4139.619404,  4152.865287,  4150.715098,  4150.735204,  4146.078380,  4171.270040,  4138.802794,  4156.859711,  4159.781175,  4206.488301]
[…]

### 2018-03-22 javascript/results/results-javascript.py
new res

@@ -1,0 +1,37 @@
+#!/usr/bin/env python
+
+hash_rate = dict()
+cache_hit_rate = dict()
+
+hash_rate[1] = [447.4072748422889,482.50904704463215,518.2689816014512,557.8178167010655,597.9788315493632,643.8735432361085,688.2312456985546,739.9186089530152,793.9028262940616, 853.7522410996329, 909.2562284051645, 976.7532721234616, 1042.6441455531228, 1116.9440411035407, 1200.0480019200768, 1285.3470437017995, 1366.867140513942, 1463.057790782736, 1561.5240474703312, 1669.727834362999, 1781.8959372772629, 1896.0940462646947, 2013.693113169553, 2155.1724137931033, 2286.75966155957, 2437.8352023403218, 2580.6451612903224, 2738.225629791895, 2885.1702250432772, 3053.4351145038167, 3222.6877215597806, 3397.8933061501866, 3599.712023038157, 3773.584905660377, 3977.7247414478916, 4158.004158004158, 4397.537379067722, 4564.125969876769, 4789.272030651341, 5010.0200400801605, 5181.347150259067, 5399.5680345572355, 5608.524957936063, 5807.200929152149, 6042.296072507553, 6253.908692933083, 6443.298969072165, 6657.789613848202, 6906.077348066297, 7082.15297450425, 7235.890014471781, 7412.898443291328, 7662.835249042146, 7836.990595611286, 8025.6821829855535, 8116.883116883117, 8298.755186721992, 8445.945945945945, 8650.519031141868, 8764.241893076249, 8841.732979664013, 9049.773755656108, 9124.087591240876, 9267.840593141798, 9345.794392523365, 9496.67616334283, 9596.928982725527, 9699.321047526673, 9784.735812133073, 9920.63492063492, 10000, 10030.090270812438, 10121.457489878543, 10288.0658436214, 10183.299389002037, 10351.966873706004, 10351.966873706004, 10526.315789473683, 10559.662090813094, 10626.992561105208]
[…]

### 2018-03-22 javascript/results/results-javascript.py
new res

@@ -9,8 +9,8 @@ cache_hit_rate[1] = [0.0413421875,0.1118453125,0.17560703125,0.237015625,0.29244
 hash_rate[0.9] = [445.31528322052014,474.18085257717286,506.89375506893754,538.9382915656157,576.3024435223605,612.2199093914534,651.1264487563485,688.8475580354068,733.3528894103844, 776.5180928715639, 823.2485387338438, 867.3779165582444, 919.7093718384991, 968.8044952528579, 1016.880211511084, 1074.69102632993, 1129.5606009262397, 1185.9582542694498, 1244.2453651860146, 1287.1669455528381, 1352.813852813853, 1416.22999575131, 1480.3849000740192, 1543.4480629726809, 1603.5920461834507, 1668.0567139282734, 1725.327812284334, 1784.758165268606, 1847.7457501847746, 1894.65706707086, 1970.831690973591, 1993.2230416583614, 2075.5500207555, 2139.03743315508, 2177.2262138036144, 2236.13595706619, 2307.3373327180434, 2335.90282644242, 2381.5194093831865, 2443.195699975568, 2472.7992087042535, 2516.9896803423107, 2563.445270443476, 2594.706798131811, 2632.964718272775, 2669.5141484249866, 2684.5637583892617, 2717.391304347826, 2777.777777777778, 2799.552071668533, 2834.467120181406, 2847.380410022779, 2876.0425654299684, 2899.391127863149, 2917.1528588098017, 2943.773918163085, 2975.304968759298, 2970.8853238265, 2975.304968759298, 3022.0610456331215, 3032.140691328078, 2969.121140142518, 2989.536621823617, 3038.5900941962927, 3007.518796992481, 3040.4378230465186, 3096.934035305048, 3088.326127239037, 3088.326127239037, 3116.2355874104082, 3140.7035175879396, 3154.5741324921137, 3139.717425431711, 3157.562361856647, 3163.555836760519, 3160.5562579013904, 3160.5562579013904, 3170.577045022194, 3170.577045022194, 3170.577045022194]
[…]

### 2018-03-22 javascript/results/results-javascript.py
new res

@@ -30,8 +30,8 @@ cache_hit_rate[0.3] =
 hash_rate[0.2] = 
 cache_hit_rate[0.2] = 
 
-hash_rate[0.1] = 
-cache_hit_rate[0.1] = 
+hash_rate[0.1] = [433.99010502560543,436.7575122292103,438.09690703583635,441.306266548985,444.01030103898404,445.49382991045576,448.1290611696168,449.68072668405426,451.6711833785005, 453.7822752643282, 455.1868542036506, 456.5167769915544, 458.16915605241456, 459.1789879695105, 460.2991944764097, 461.78711613945967, 463.306152705708, 463.7573621481241, 464.25255338904367, 465.3110604439068, 466.3961568956672, 466.9188028201895, 467.4207721791156, 468.3182690956774, 468.95516788595006, 469.43948924983573, 470.14574518100613, 470.18995674252403, 471.2091226086137, 471.43126532151615, 471.8984474541079, 472.2550177095631, 472.1881197469072, 472.79088459174505, 472.85795347077743, 473.64183204660634, 473.73158368468427, 474.0235115661737, 474.20333839150226, 473.9111890431733, 474.4508231721782, 474.00104280229414, 474.31579945928, 475.37554668187863, 474.6535029428518, 474.74363843524503, 474.81126252314704, 475.37554668187863, 474.9014579474759, 475.4659566375047, 475.7373929590866, 475.42074736141484, 474.4733345985955, 473.77647226038755, 476.0997905160922, 475.55640098915734, 476.0997905160922, 476.0997905160922, 475.9638267491671, 476.16780153326033, 475.9185227489054, 476.14512903532994, 476.0771244941681, 476.3492592769018, 476.0544606302961, 476.25851312092203, 476.4173415912339, 475.71476142904714, 476.71258997950133, 476.28119641836537, 475.8958739827725, 476.4854433697051, 476.0317989241682, 476.66714333381, 476.009139375476, 476.32656949604643, 476.7353165522502, 476.14512903532994, 476.44004002096335, 476.32656949604643]
[…]

### 2018-03-22 javascript/results/results-javascript.py
new res

@@ -27,8 +27,8 @@ cache_hit_rate[0.4] =
 hash_rate[0.3] = 
 cache_hit_rate[0.3] = 
 
-hash_rate[0.2] = 
-cache_hit_rate[0.2] = 
+hash_rate[0.2] = [429.6824646586173,440.6256884776383,445.2359750667854,450.57222672794455,455.85084560331853,460.9356994699239,465.1379133913205,469.593801361822,473.68670361422954, 477.2130756382725, 480.5151122002787, 483.86316349736296, 486.9734599464329, 490.4124368593988, 492.95080350980976, 496.20403910087833, 499.10161708923937, 501.55481994181963, 503.34725927417327, 505.4589567327133, 507.0993914807302, 508.41425593573643, 510.07396072430504, 512.2425980944575, 513.5315565141478, 514.6415521589213, 515.9692482328054, 517.6251358765982, 515.5702206640544, 517.9200331468821, 518.6452984803693, 516.9027189083014, 520.8604614823689, 521.5123859191656, 521.6484089723526, 523.0672664504656, 523.6698785085882, 523.6150382238978, 524.5213742460005, 522.6025607525477, 521.7845030002609, 522.9851995188536, 522.9578495973225, 525.8176464402145, 526.7871253226571, 527.0647762610025, 527.1759186040382, 527.4539796402764, 526.8981505874915, 528.5691632750146, 528.1225244256667, 528.2341133590407, 528.3178360101437, 529.1845266444409, 525.4860746190226, 528.4853609555015, 529.6049147336087, 529.1005291005291, 529.4086505373498, 529.436679373147, 529.4927459493805, 529.296564865294, 529.7451925623775, 530.1383661135557, 530.2226935312832, 530.2508086324832, 530.0259712725923, 530.7855626326964, 529.6049147336087, 530.8419152776304, 530.2226935312832, 530.2508086324832, 530.7573907966669, 530.6165764618487, 530.6165764618487, 530.4476978569913, 531.0392438001169, 530.5602716468591, 530.6447333510215, 525.4308532997057]
[…]

### 2018-03-22 javascript/results/results-javascript.py
new res

@@ -24,8 +24,8 @@ cache_hit_rate[0.5] =
 hash_rate[0.4] = 
 cache_hit_rate[0.4] = 
 
-hash_rate[0.3] = 
-cache_hit_rate[0.3] = 
+hash_rate[0.3] = [434.51811940557917,443.63604099197016,457.6449590407762,465.8529768005218,474.18085257717286,481.6259692722632,489.2607270414404,496.45037978454053,503.27126321087064, 510.5166428425566, 516.4755707055057, 521.7845030002609, 528.0388636603655, 530.7010560951016, 540.0734499891986, 545.3752181500873, 549.8130635583901, 552.883286338254, 557.6622797233996, 561.1042531702391, 564.8121999435187, 567.9559266200943, 571.5592135345222, 574.6465923457074, 576.3356578871535, 578.7706910522052, 582.0382981200163, 583.0223880597015, 585.6515373352855, 588.3391186680002, 589.7965202005308, 590.7372400756143, 591.6459590580996, 594.3536404160475, 595.3089653530183, 595.9830740806962, 598.3724269985639, 598.7306909352174, 598.5156811108451, 599.9880002399951, 601.8295618680789, 602.627455706882, 603.3546518643659, 600.3482019571352, 600.0600060006001, 601.1060351045925, 603.0271965265633, 603.7553583288051, 602.7727546714889, 604.6314771146987, 605.2536012589276, 604.1565973900435, 604.5583701106342, 605.840300496789, 605.3635207942369, 605.913717886573, 605.5468087683178, 606.7592985862509, 606.7592985862509, 611.1722283339444, 609.7560975609756, 609.6817461285209, 609.3845216331505, 609.7932800780536, 611.8453255017131, 610.1653548111539, 611.5085916957133, 610.4260774020265, 611.3964294448521, 611.7330397014742, 612.5574272588055, 611.8827632625589, 611.807892321811, 610.8735491753207, 610.7616197398156, 612.7826459954655, 611.5085916957133, 611.3590511707527, 611.7330397014742, 611.1722283339444]
[…]

### 2018-03-22 javascript/dag-partial-cache-store-miner-array/miner.js
changed to get instantaneous hash-rate

@@ -1,6 +1,6 @@
 importScripts("ethash.js","keccak.js","makekeccak.js","util.js");
 
-var endpoint = "http://155.41.12.43:9000";
+var endpoint = "http://155.41.27.122:9000";
 
 function http_get(theUrl)
 {
@@ -57,19 +57,22 @@ function mine(header,cache,cacheSize,dagArray,dagSize,startIndex,endIndex){
 	var nonce = Util.hexStringToBytes("0000000000000000");
 	var hash;
 
-	var trials = 10000000;
+	var trials = 801000;
+	var interval = 10000;
 	var stopTime;
 	var startTime = new Date().getTime();
 	for (var i = 0; i < trials; ++i)
 	{
 		hash = hasher.hash(header, nonce);
 		nonce[Math.floor((Math.random()*8))]=Math.floor((Math.random()*256));
-		if (i % 1000 == 0)
+		if (i % interval == 0)
 		{
 			stopTime = new Date().getTime();
-			var hashrate = 1000/((stopTime - startTime)/trials);
-			console.log("average hashrate for i = " + i + " : " + hashrate);
-			console.log("Cache hit rate: " + (cacheHits/numAccesses));
+			var hashrate = 1000/((stopTime - startTime)/interval);
+			console.log("h " + i + ": " + hashrate);
+			console.log("c " + i + ": "  + (cacheHits/numAccesses));
+			cacheHits = 0;
+			numAccesses = 0;
 			startTime = new Date().getTime();
 		}
 		/*

### 2018-03-22 javascript/results/results-javascript.py
new res

@@ -12,17 +12,17 @@ cache_hit_rate[0.9] = [0.0371703125,0.100478125,0.158559375,0.213175,0.263628125
 hash_rate[0.8] = [439.5797617477691,469.61585423123887,495.5892556249381,523.8893545683152,551.6936996579499,580.7200929152149,611.920205605189,643.707756678468,674.900452183303, 706.0650992021465, 739.9186089530152, 772.6781023025808, 805.8667096462245, 845.4514710855597, 878.4258608573435, 913.9932364500502, 949.5774380400723, 987.7518767285658, 1021.0332856851132, 1057.4177857671566, 1092.7767457108512, 1113.7097672346586, 1137.009664582149, 1181.3349084465447, 1215.6576707999027, 1245.3300124533, 1281.3941568426449, 1305.1422605063951, 1329.433661260303, 1358.695652173913, 1391.0140492418973, 1410.4372355430185, 1434.1029685931449, 1462.8437682855472, 1481.2620352540364, 1506.2509414068384, 1531.6281206922959, 1540.5946695424434, 1562.5, 1578.531965272297, 1585.5398763278895, 1623.3766233766235, 1642.845408247084, 1657.2754391779913, 1669.170422300117, 1679.5431642593214, 1698.3695652173913, 1701.8379850238257, 1719.6904557179707, 1731.0022503029254, 1740.644038294169, 1747.3353136466887, 1752.2340984755565, 1751.6202487300754, 1760.5633802816903, 1771.1654268508678, 1768.9722271360338, 1783.166904422254, 1793.7219730941704, 1792.7572606669057, 1799.5321216483715, 1803.4265103697026, 1808.3182640144664, 1811.5942028985505, 1812.2508155128671, 1811.2660749864153, 1808.9725036179452, 1818.512456810329, 1818.512456810329, 1827.151470856934, 1822.4895206852561, 1831.5018315018315, 1837.897445322551, 1838.5732671446956, 1834.52577508714, 1840.2649981597351, 1840.9425625920471, 1848.770567572564, 1840.6037180195103, 1842.6386585590567]
[…]

### 2018-03-22 javascript/results/results-javascript.py
new res

@@ -15,11 +15,11 @@ cache_hit_rate[0.8] = [0.0337609375,0.0893109375,0.141321875,0.190040625,0.23339
 hash_rate[0.7] = []
 cache_hit_rate[0.7] = []
 
-hash_rate[0.6] = 
+hash_rate[0.6] = []
 cache_hit_rate[0.6] = []
 
-hash_rate[0.5] = []
-cache_hit_rate[0.5] = []
+hash_rate[0.5] = [440.4510218463707,448.67193108399135,464.64083263637207,481.6491667469415,498.4547901505333,513.0573085013596,528.1225244256667,542.1817393190197,555.2162567319972, 570.3205201323143, 583.2264084917765, 595.3444067392987, 607.8657832350617, 620.3473945409429, 630.2388605281402, 641.9309282321221, 650.110518788194, 662.6905235255136, 672.0430107526881, 681.5238874122538, 689.797889218459, 699.4963626189144, 707.1135624381276, 714.9495960534782, 722.334585379948, 728.4382284382284, 736.4312541424257, 740.4664938911515, 746.2129691814043, 749.512816669165, 755.7436517533254, 762.2532205198567, 764.2922653622745, 770.00077000077, 774.5333436604446, 776.8800497203232, 779.3017456359103, 784.6829880728186, 787.5255945818238, 788.0841673890772, 791.7656373713381, 792.5186241876684, 795.671546785487, 797.7662544874352, 798.8496564946477, 802.3106546854942, 803.4709946970914, 805.9316569954868, 806.4516129032259, 808.3420903726457, 808.9305937550558, 809.3889113719142, 811.4907084313885, 812.2157244964262, 810.7669855683476, 813.6034496786266, 813.5372600065083, 816.7265599477296, 815.3946510110894, 815.9934720522235, 811.0300081103001, 812.8759551292474, 815.9934720522235, 816.5931732810715, 816.2598971512529, 817.2605426610003, 816.7932696234583, 816.9267216730659, 815.9934720522235, 816.5931732810715, 816.7932696234583, 813.4049129656743, 811.9519324455993, 815.1952392598027, 820.8158909956497, 818.5985592665356, 821.8952905399852, 821.0854749979472, 820.3445447087777, 822.3007976317738]
[…]

### 2018-03-22 paper/paper.tex
latest version of paper

@@
-%% bare_conf.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
 %
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
+\documentclass[runningheads]{llncs}
 %
-\documentclass[10pt, conference, compsocconf]{IEEEtran}
-% Add the compsocconf option for Computer Society conferences.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
 \usepackage{float}
@@
 \usepackage{balance}
-\RequirePackageWithOptions{multicol}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
+\usepackage{color}
+\usepackage{amsmath}
+\newcommand{\trishita}[1]{{\color{magenta}\bfseries[Trishita: #1]}}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
 %
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-\usepackage{color}
-\newcommand{\trishita}[1]{{\color{magenta}\bfseries[Trishita: #1]}}
-\newcommand{\dennis}[1]{{\color{cyan}\bfseries[Dennis: #1]}}
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-%\usepackage[tight,footnotesize]{subfigure}
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
-
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-\usepackage{amsmath}
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+% \renewcommand\UrlFont{\color{blue}\rmfamily}
 \begin{document}
 %
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-\title{Distributed Web Browser Mining for Ethereum}
-
-% author names and affiliations
-% use a multiple column layout for up to two different
-% affiliations
-
-\author{\IEEEauthorblockN{
-Trishita Tiwari\IEEEauthorrefmark{1}
-David Starobinski\IEEEauthorrefmark{2}
-Ari Trachtenberg\IEEEauthorrefmark{3}
-}
-\IEEEauthorblockA{Department of Electrical and Computer Engineering,
-Boston University\\
-Boston, MA, 02215\\
-Email: 
-\IEEEauthorrefmark{1}trtiwari@bu.edu
-\IEEEauthorrefmark{2}staro@bu.edu
-\IEEEauthorrefmark{3}trachten@bu.edu
-}}
+\title{Distributed Ethereum Web Browser Mining\thanks{Supported by organization x.}}
+%
+%\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{Trishita Tiwari\orcidID{0000-1111-2222-3333} \and
+David Starobinski\orcidID{1111-2222-3333-4444} \and
+Ari Trachtenberg\orcidID{2222--3333-4444-5555}}
+%
+\authorrunning{T. Tiwari et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Boston University, Department of Electrical and Computer Engineering, Boston, MA 02215, USA \\
+\email{\{trtiwari,staro,trachten\}@bu.edu}}
+%
 \maketitle             
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
 %
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-% \maketitle
-
 \begin{abstract}
-
 Given the seemingly endless growing popularity of crypto-currencies, there is an increasing interest in different mining possibilities.
@@
 We explore a variety of techniques to distribute the inherently memory and memory intensive PoW of Ethereum over multiple browser-based clients that have limited resources.
-We obtain the best results with the WebAssembly implementation, with hash rates reaching upto X hashes/second, which, as we demonstrate, is merely X\% slower than a native miner that uses the same algorithm for mining.
+We obtain the best results with the WebAssembly implementation, with hash rates reaching upto X H/s, which, as we demonstrate, is merely X\% slower than a native miner that uses the same algorithm for mining.
 We show that this solution is practical for a variety of purposes, such as web content monetization, web based authentication rate limiting and private Ethereum networks.
 
-%Given the increasing need of effective ways to monetize web content and the growing popularity of crypto-currencies, we propose a new implementation of a distributed miner using web browsers.
-We implement this for the Ethereum crypto-currency, which shows that the use of web browsers is inefficient if the cryptocurrency requires large amount of storage for mining.
-However, we believe that such an approach can have merit depending on the crypto-currency that is being mined.
-
+\keywords{crypto-currency \and Ethereum \and distributed computing \and web-browser computing \and mining}
 \end{abstract}
-
-\begin{IEEEkeywords}
-crypto-currency, Ethereum, distributed computing, mining
-\end{IEEEkeywords}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
 %
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
+%
+%
 \section{Introduction}
@@
 Thus, this approach does not provide good user experience.
-Another approach involves subscriptions, however, it is not very successful.
+% Another approach involves subscriptions, however, it is not very successful.
 Indeed, as this study finds, users are becoming increasingly unlikely to pay for content \cite{noSubscriptions}.
@@
 
-\section{Outline}
-The remainder of the paper is organized as follows.
+% \section{Outline}
+% The remainder of the paper is organized as follows.
 In Section 5 we present a detailed description of the Ethereum mining algorithm and the current state of Ethereum.
@@
 
-% \item Affiliate Marketing: Unlike pay-per-click advertisements, such marketing might not cause inconvenience to users.
-However, it sometimes leads to ethically questionable situations when users are not able to distinguish when the website owner is advertising a product versus when the owner truly endorses it without monetary incentive \cite{celebEndorse}.
-
-% \item Donations: While donations are perhaps the most benign of all approaches, they lead to unsteady revenue for the website owner.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-
 \section{Background}
-% \subsection{Distributed Web Browser Computing}
-% One of the core concepts that this research is based on is the use of web browsers to perform computations; in our case that computation is the act of mining crypto-currency.
-First, we need to define the idea of distributed computing.
-Distributed computing is a network of computers that are working together to achieve a single goal.
-Web browser computing is a subset of distributed computing.
-In this scenario, the web browsers on the client machines are the workers.
-The use of web browsers for computation has come to light in the past 15-20 years because of improvements the \verb|JavaScript| engine ~\cite{Cushing}.
-In fact, the advent of powerful frameworks such as \verb|WebAssembly| are further closing down the gaps between web browser computations and native programs.
-
-% To be able to implement an effective distributed system, each of the ``workers'' must have a way to communicate effectively with each other.
-There are two ways this is accomplished.
-One approach is to follow a server-client model in which there is a central server machine and all other machines are the clients.
-The clients speak to the server and the server can relay information from one client to another or broadcast information to all clients.
-The other way to have communication is a peer-to-peer model where all machines are aware of each other and can talk directly.
-When it comes to browsers, however, the only logical way to pass data is through the server-client architecture because web browsers are not created to perform peer-to-peer communication.
-So with that in mind, distributed web browser computing systems typically have a structure with a central server which distributes tasks to each web browser it is connected to.
-In general, these tasks are very small because there is no guarantee that the browser will be open for a sustained period of time, i.e.
-a user moves away from the necessary website or closes the browser altogether.
-Furthermore, the tasks must also not consume too many resources of the user, as such browser based computation would ruin user experience.
-Given these two constraints, we propose two approaches to distribute ethereum mining in over web browsers.
-
-\subsection{Ethereum}
-\trishita{Not sure if I need this paragraph, since I think the readers will probably be familiar with what crypto-curriencies are}
-Ethereum is a crypto-currency that was released in July 2015 by Vitalik Buterin, Gavin Wood and Jeffrey Wilcke.
-Like most crypto-currencies, it too is backed by a distributed block-chain, each block of which holds transactions for that particular block-chain.
+% \subsection{Ethereum}
+% \trishita{Not sure if I need this paragraph, since I think the readers will probably be familiar with what crypto-curriencies are}
+Ethereum is a crypto-currency that was released in July 2015 by Vitalik Buterin, Gavin Wood and Jeffrey Wilcke. Ethereum uses the Ethash algorithm for its PoW, which is discussed below in detail. 
+% Like most crypto-currencies, it too is backed by a distributed block-chain, each block of which holds transactions for that particular block-chain.
 This block chain is operated on by the Ethereum Virtual Machine (EVM) ~\cite{EVM}, which, unlike Bitcoin Script, is Turing Complete ~\cite{turingComplete}.
@@
 \subsection{Ethash}
-Ethereum uses a Proof-of-Work algorithm called Ethash for mining blocks.
+Ethash is the PoW used for mining blocks in Ethereum.
 Derived from the Dagger and Hashimoto algorithms ~\cite{dagger-hashimoto}, Ethash operates by first generating a 256 bit seed.
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=250px,keepaspectratio]{ethash_algorithm.png}
-\caption{\label{fig:ethash} Ethash}
-\end{figure}
-
-As time goes on, mining Ethereum becomes more and more difficult.
-The Proof-of-Work difficulty and total hashrate of the network has been steadily increasing over time, with the current difficulty at 1612.737TH and the respective hashrate at 109.138TH/s ~\cite{etherscan}.
+As time goes on, mining Ethereum becomes more and more difficult, as the size of the DAG and Cache used for the Ethereum increases every Epoch.
+Currently the DAG is more than 2GB in size, causing many GPU miners with cards of 2GB of memory to suffer in terms of hashrate.
+% The Proof-of-Work difficulty and total hashrate of the network has been steadily increasing over time, with the current difficulty at 1612.737TH and the respective hashrate at 109.138TH/s ~\cite{etherscan}.
 This reflects the design of mining one block approximately every 12 seconds.
-As for mining rewards, the reward for mining a block has gone from 5 Ether to 3 ether, though the difficulty has significantly decreased, both due to the Byzantium fork.
-Furthermore, the DAG used for the Ethereum network is now more than 2GB, causing many GPU miners with cards of 2GB of memory to suffer in terms of hashrate.
+% As for mining rewards, the reward for mining a block has gone from 5 Ether to 3 ether, though the difficulty has significantly decreased, both due to the Byzantium fork.
 
@@
 
-% \subsection{Choice of Crypto-currency}
-% \trishita{We had this section in the project report, but I am not sure if we need this anymore, so I commented it out}
-% In choosing crypto-currencies to mine, it was preferable to mine a larger, well known currency to ensure that the research would have real-world implications if adopted.
-Monero was the clear favorite, as it was created with the intent of providing no benefit over CPU mining.
-However, there has already been a web browser miner implemented for the Monero in the form of CoinHive~\cite{coinhive}, so any such efforts with Monero would not be novel.
-CoinHive also takes in a certain percentage of all currency generated and as such has kept their code closed sourced which meant that we could not easily extend or improve their current implementation as part of our research.
-In addition, many websites that utilize Coinhive have not informed users of their "stealing of computing power".
-This has drawn negative attention toward Coinhive to the extent that the code has been classified as malware and is automatically blocked by most firewalls and anti-viruses by default.
-Bitcoin was another option that we considered, however, there were two foreseeable problems with the crypto-currency that we felt would be insurmountable in our research timeline.
-First, ASIC technology has become the new norm for mining Bitcoin which would mean our web browser solution would hardly be able to compete.
-Second, the sheer popularity of Bitcoin means the mining is highly competitive in itself so our baseline threshold for seeing results would be too high for any reasonable amount of work.
-
-% In the end, we decided that Ethereum would be the most beneficial crypto-currency for a new web browser implementation of a miner.
-First of all, there is no existing web browser miner for Ethereum, so our implementation would have a certain novelty.
-In addition, Ethereum also allows developers to create private testnets to experiment with the network, which is a valuable asset to create a distributed network of miners.
-Another major benefit of Ethereum is that its smart contracts are Turing complete, meaning that the system can be used for a lot more than just sending or receiving currency.
-This could lead to a growing popularity of the crypto-currency in the coming years.
-Lastly, using Ethereum also leaves room for further exciting research, as will be discussed in a later section.
-
-% \subsection*{Work Distribution}
-% Trishita produced the \verb|JavaScript| implementation of the browser miner and the \verb|Python| test node with some help from Daniel.
-Dennis provided statistics and data for comparison to the browser miner in addition to setting up and managing the private testnet to perform operations on.
-All of the members participated in research and understanding of core Ethereum functions such as Ethash and how to mine via Ethereum.
-
-% ~\dennis{https://github.com/ethereum/wiki/wiki/Ethash-Design-Rationale, should cite this so that they know that we are aware that compute from cache is designed to be inefficient, maybe add a diagram?)}
+\begin{figure}[H]
+\centering
+\includegraphics[width=300px,keepaspectratio]{ethash_algorithm.png}
+\caption{\label{fig:ethash} Ethash}
+\end{figure}
 
@@
 We propose a lazy-evaluation based approach to alleviate the network and memory requirements for mining ethereum in a distributed scenario on browsers.
-Specifically, as soon as each browser connects to the central node, the node sends it the current header of the block being mined and the Cache.
+Specifically, as soon as each browser connects to the webserver, the server sends it the current header of the block being mined and the Cache.
 Once the browser receives the Cache, it allocates an array buffer to store the DAG slices that will be computed in the future.
@@
 
-% The approach involves each browser allocating a fixed buffer to store the DAG, which is initially empty when the web page first loads.
-(Note that the size of this buffer is a parameter that can be adjusted depending on how much memory the client has.) The browser then starts mining, and
 Since, to begin with, the browser does not have any slices of the DAG, it must compute each slice on the fly using the Cache.
@@
 This has the effect that the longer the user remains on the web-page, the better the hashrate gets for that user.
-% If the allocated buffer is too small (as would be needed for some clients that do not have enough memory), and the computed slice cannot be fit in it, it is simply thrown away and again recomputed from the cache when needed.
-
-% With respect to DAG lookups to compute each hash, the browser first checks if it already has the required slice in its buffer.
-If it does, it simply uses that, else it uses the Cache to compute that slice on the fly and then store it for future reference (if it fits in the buffer).
-Hence, initially the buffer starts out empty and so all DAG slices must be computed on the fly, and then stored in the buffer.
-However,
 
@@
 With this lazy-evaluation based approach, we can calculate exactly how many hashes we would have to compute in order to fill up a buffer of a given size.
-This approach is a variation of the coupon collector problem \cite{couponCollector}.
-For our purposes, let us assume the following:
+This is important because once the buffer in the browser fills up, the hashrate that the browser gives becomes steady.
+Hence, calculating the expected number of hashes it takes to fill the buffer allows us to determine how much time will the browser take to reach a steady state hash rate.
+This approach is a variation of the coupon collector problem \cite{couponCollector}, and has been described in the following theorem:
+\begin{theorem}[Expectation of Number of Hashes]
+\label{expectedHashes}\\
+If we define,
+    \[Number\;of\;DAG\;slices\;=\;n\]
+    \[Size\;of\;buffer\;as\;a\;fraction\;of\;the\;total\;DAG\;=\;f_1;\;f_1=[0,1] \]
+    \[Expected\;number\;of\;hashes\;it\;takes\;to\;fill\;the\;buffer\;= E(H)\]
+Then the expected number of hashes $E(H)$ it takes to fill up a buffer of fraction $f_1$ of a DAG with $n$ slices is given by:
 \begin{gather}
-    Number\;of\;DAG\;slices = n\\
-    Size\;of\;buffer\;as\;a\;fraction\;of\;the\;total DAG = i\;;i=[0,1]
+E(H) = \frac{n\log{nf_1}}{64}
 \end{gather}
-If we have buffered \verb|x| slices so far, the probability of obtaining a new slice is given by:
+\end{theorem}
+\begin{proof}
+Let us assume we have a buffer for our DAG that is $f_1$ as large as the entire DAG -- i.e., the buffer can only store dag slices with indices $i$ such that $i \in [0,nf_1]$.
+Hence, each time we calculate a DAG slice from the Cache, we may or may not buffer it depending on whether it falls within the index rage.
+Now, let us assume that  we have buffered $x$ slices so far, the probability of obtaining a new slice is given by:
 \begin{gather}
-  P_x = \frac{ni-x}{n}
+  P_x = \frac{nf_1-x}{n}
 \end{gather}
-The event of obtaining a new slice after having already collected \verb|x| out of the \verb|ni| slices that can be buffered can be modeled as a geometric distribution.
-Hence, the expected number of trials $t_x$ it takes to get a new  slice after having seen \verb|x| out of the \verb|i| slices is:
+The event of obtaining a new slice after having already collected $x$ out of the $nf_1$ slices that can be buffered can be modeled as a geometric distribution.
+Hence, the expected number of trials $t_x$ it takes to get a new  slice after having seen $x$ out of the $nf_1$ slices is:
 \begin{gather}
-  E(t_x) = \frac{1}{P_x} = \frac{n}{ni-x}
+  E(t_x) = \frac{1}{P_x} = \frac{n}{nf_1-x}
 \end{gather}
-By linearity of expectation, the total number of trials it would take to see all \verb|x| slices is:
+By linearity of expectation, the total number of trials it would take to see all $x$ slices is:
 \begin{gather}
-  E(t) = \sum_{x=0}^{ni-1}E(t_x)\\
-    E(t) = \sum_{x=0}^{ni-1}P_x = \sum_{x=0}^{ni-1}\frac{n}{ni-x} = n\sum_{x=0}^{ni-1}\frac{1}{ni-x}
+  E(t) = \sum_{x=0}^{nf_1-1}E(t_x) = \sum_{x=0}^{nf_1-1}P_x = \sum_{x=0}^{nf_1-1}\frac{n}{nf_1-x} = n\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x}
 \end{gather}
@@
 \begin{gather}
-  E(t) = n\log{ni}
+  E(t) = n\log{nf_1}
 \end{gather}
-Now, equation ~\ref{eq:7} is in terms of the number of individual accesses of the DAG.
+Equation ~\ref{eq:7} is in terms of the number of individual accesses of the DAG.
 In order to get the expected number of Hashes (as opposed to the expected number of individual DAG slice accesses), we need to divide by 64 since each hash involves 64 accesses of the DAG.
-Hence if we define:
+Hence:
 \begin{gather}
-    Number\;of\;hashes\;computed = H
+  E(H) = \frac{E(t)}{64} = \frac{n\log{nf_1}}{64}
 \end{gather}
-\begin{gather}
-  E(H) = \frac{n\log{ni}}{64}
-\end{gather}
-Now, let us do a simple calculation for one extreme case, where $i = 1$ (i.e., we allocate a buffer as large as the entire DAG on the browser), in order to get an upper bound on the number of hashes it would take to fill this buffer up.
+\end{proof}
+Now, let us do a simple calculation for one extreme case, where $f_1 = 1$ (i.e., we allocate a buffer as large as the entire DAG on the browser), in order to get an upper bound on the number of hashes it would take to fill this buffer up.
 The private test network for Ethereum we used had a total of 16777186 slices in the DAG, which means it would take:
@@
 Hence, it takes around 4 million hashes to fill up a buffer as large as the entire DAG.
-If $i < n$, the number of hashes should be less than 4 million.
+If $f_1 < 1$, the number of hashes should be less than 4 million.
 So effectively, 4 million hashes is a very lose upper bound on the number of hashes needed to fill up a DAG buffer.
+However, since 4 million hashes can be a lot for a browser, we will now demonstrate how we can get away with  better
 
 Now let us say that we do not want to wait for the entire buffer to fill up -- how many hashes would we have to compute until a reasonable fraction of the buffer is full?
-Concretely speaking, let us assume the following:
+For this, we have the following corollary:
+\begin{corollary}
+\label{earlyTermination}
+If we define,
+  \[Fraction\;of\;DAG\;buffer\;to\;be\;filled = f_2;\;f_2 \in [0,1]\]
+  Then,
     \begin{gather}
-  Fraction\;of\;DAG\;buffer\;to\;be\;filled = f;\;f \in [0,1]
+    E(H) = \frac{n}{64}\log{\frac{1}{1-f_2-\frac{1}{nf_1}}}
   \end{gather}
-Then, for a buffer with space for \verb|i| slices, the number of slices we want to fill it with in order for a fraction \verb|f| of it to be full would be: 
+\end{corollary}
+\begin{proof}
+Then, for a buffer with space for $f_1$ slices, the number of slices we want to fill it with in order for a fraction $f_2$ of it to be full would be: 
 \begin{gather}
-  Number\;of\;slices\;to\;fill\;DAG\;buffer\;with = nfi
+  Number\;of\;slices\;to\;fill\;DAG\;buffer\;with = nf_2f_1
 \end{gather}
-This would modify equation \ref{eq:6} for the expected number of trials to fill up a fraction \verb|f| of the DAG buffer to be as follows:
+This would modify equation \ref{eq:6} for the expected number of trials to fill up a fraction $f_2$ of the DAG buffer to be as follows:
 \begin{gather}
-    E(t) = \sum_{x=0}^{nfi}P_x = \sum_{i=0}^{nfi}\frac{n}{ni-x} = n\sum_{x=0}^{nfi}\frac{1}{ni-x}\\
-    E(t) = n\sum_{x=0}^{nfi}\frac{1}{ni-x}
+    E(t) = \sum_{x=0}^{nf_2f_1}P_x = \sum_{x=0}^{nf_2f_1}\frac{n}{nf_1-x} = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x}
 \end{gather}
-This is essentially an early termination of the summation, and can be expressed as follows:
+This is essentially an early termination of the summation in equation ~\ref{eq:6}, and can be expressed as follows:
 \begin{gather}
-    E(t) = n\sum_{i=0}^{nfi}\frac{1}{ni-x} = n(\sum_{x=0}^{ni-1}\frac{1}{ni-x} - \sum_{x=nfi}^{ni-1}\frac{1}{ni-x})\\
-    E(t) = n(\log{ni} - \log{(ni-nfi)}) \\
-    E(t) = n\log{\frac{1}{1-f}}
+    E(t) = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x} = n(\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x} - \sum_{x=nf_2f_1+1}^{nf_1-1}\frac{1}{nf_1-x})\\
+    E(t) = n(\log{nf_1} - \log{(nf_1-nf_2f_1-1)}) \\
+    E(t) = n\log{\frac{1}{1-f_2-\frac{1}{nf_1}}}
 \end{gather}
@@
 \begin{gather}
-    E(H) = \frac{n\log{\frac{1}{1-f}}}{64}
+    E(H) = \frac{n}{64}\log{\frac{1}{1-f_2-\frac{1}{nf_1}}}
 \end{gather}
-Interestingly \verb|E(H)| does not depend on \verb|i|; the size of the DAG buffer as a fraction of the entire DAG.
-Figure X shows a graph of how \verb|E(H)| varies as a function of the fraction of the buffer that we want to be full, \verb|f| if we set $n = 16777186$ (the total number of DAG slices on the experimental private test network).
+\end{proof}
+Interestingly, since for realistic cases $n >> f_1$, $\frac{1}{nf_1} \to 0$, and so 
+\begin{gather}
+E(H) \approx \frac{n}{64}\log{\frac{1}{1-f_2}}
+\end{gather}
+Figure X shows a graph of how $E(H)$ varies as a function of the fraction of the buffer that we want to be full, $f$ if we set $n = 16777186$ (the total number of DAG slices on the experimental private test network).
 
-From figure X we see that even computing merely 800,000 hashes fills our DAG buffer by more than 95\%! Beyond that, the marginal cost of computing more hashes outweighs the 
-Finally, let us compute what the buffer hit rate should be for a given buffer size when the number of hashes computed tends to infinity. For this, let:
-\begin{gather}
-  Buffer\;hit\;rate = R \\
-    Number\;of\;hashes\;computed = H
-\end{gather}
-Then,
-\begin{gather}
-  \lim_{H\to\infty}R = \frac{i}{n}
-\end{gather}
-This is because after a finite number of hashes, the buffer becomes full.
-Which means for any random slice of the DAG we pull out, the probability of it being in the buffer is $\frac{i}{n}$.
-However, the buffer hit rates were extremely low when H was close to 0 low $H\to\infty$
-
-% We must also point out that in order to optimize the code for the specific cases, we have separate implementations for each of these two extreme edge cases.
-We also have another two separate implementations for the hybrid approach (where we store parts of the DAG and compute the other slices from the cache).
-The first hybrid implementation does not store the slices of the DAG the browser computes from the cache, while the second does (until it exhausts the storage space allocated to the DAG).
-The differences between each of the four implementations mainly lies in the data structures used to store the DAG, and is outlined follows:
-% \begin{enumerate}
-% \item Browser stores entire DAG in memory: We store the DAG in an array in order to get constant lookup times. The Cache is stored in an array of integers.
-% \item Browser stores part of the DAG sent by the central node in memory and computes the other necessary slices from the Cache and stores these slices for future reference: Here, we need to store the DAG in a \verb|JavaScript| object (which is akin to a Hash Map).
-In this data structure, the keys correspond to the index of the DAG slice, and the value corresponds to the slice itself.
-We need a Hash Map as opposed to an array because we also store the slices that are generated on-the-fly from the Cache in this data structure.
-Since these slices are from random indices, we cannot store them at their correct indices in the array without allocating an array as large as the entire DAG itself -- which defeats the purpose of storing just a part of the DAG.
-% \item Browser stores part of the DAG sent by the central node in memory and computes the other necessary slices from the Cache and \emph{does not} store these slices for future reference: Here, we just store the part of the DAG sent by the central server in memory, which we can compactly keep in an array since the central server sends consecutive slices.
-% \item Browser stores none of the DAG and computes all the slices from the Cache: We do not store the DAG at all, but just the Cache in an array of integers.
-% \end{enumerate}
+From figure X we see that even computing merely 800,000 hashes fills our DAG buffer by more than 95\%, as opposed to calculating 4 million to fill the buffer entirely.
+This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up.
+This also means that reaching a reasonably steady state is not as hard as it seems at face value.
+Given this result, we compute 800,000 hashes for our experiments.
+% Beyond that, the marginal cost of computing more hashes outweighs the rate at which the DAG is filled up. Hence, as we will see in the next section, for our experiments, we compute 800,000 hashes.
 
 \section{Architecture}
-\begin{figure}[H]
-\centering
-\includegraphics[width=250px,keepaspectratio]{miningpool.png}
-\caption{\label{fig:miningpool} Distributed Ethereum Mining}
-\end{figure}
-
-% A private Ethereum testnet is deployed to decrease the difficulty of mining so that the browsers clients can reliably mine at least some Ether.
-This can be easily ported to the real Ethereum network as we are using \verb|geth|, the Go implementation written for interacting with the Ethereum network.
-% The central Ethereum node is set up using \verb|geth|, which serves as the wallet that all the browser miners will point to.
+% \begin{figure}[H]
+% \centering
+% \includegraphics[width=250px,keepaspectratio]{miningpool.png}
+% \caption{\label{fig:miningpool} Distributed Ethereum Mining}
+% \end{figure}
 
@@
 
-% \section{Challenges}
-% There were a multitude of challenges in creating such a distributed \verb|JavaScript| implementation of an Ethereum miner, we encountered a handful of challenges, some of which we were able to overcome and some that could be part of future work.
-One of the major decisions we needed to make was how to make sure the website would not become unresponsive due to a long running \verb|JavaScript| job.
-The reason this is an issue is because \verb|JavaScript| is a blocking language by nature, so if this job ran for too long no other \verb|JavaScript| responsible for website functionality could execute.
-As a workaround, we could schedule the hash computations to only run when the browser is idle using the \texttt{requestIdleCallback()} API.
-However, one must bear in mind that this would result in a lower hash rate and the API is not even supported in all browsers.
-
-% The other major challenges dealt with the DAG aspect of Ethereum.
-Even though we were able to limit the amount of the DAG sent to just the essential slices, these slices are still quite large to continuously be sent over the network.
-This leads to a lot of network bandwidth consumption.
-
-%One of the more pertinent issues in mining Ethereum in such a fashion is how Ethereum operates.
-For starters, the Ethereum Proof-of-Work algorithm Ethash is designed to favor GPU mining rather than CPU mining, providing us with a innate handicap to work with.
-In addition, Ethash requires a 1GB DAG or Directed Acyclic Graph to be created and stored into memory for a machine to generate and verify hashes.
-Finally, in order to connect to the Ethereum network, a full Ethereum node must be set up to sync and add mined blocks to the blockchain.
-All of these issues considered, the processing power from a fraction of a CPU is wholly insufficient to profitably mine any amount of ether.
-Thus, distribution of computational work must be considered.
-
 \section{Results}
@@
 \subsection{Baseline results}
-For our control results, we ran \verb|Geth| ~\cite{geth}, a native miner written in \verb|Go| that stores the entire DAG in memory from the start (as opposed to using this lazy evaluation approach), and obtained an average hashrate of X H/s.
+For our control results, we ran \verb|Geth|~\cite{geth}, a native miner written in \verb|Go| that stores the entire DAG in memory from the start (as opposed to using this lazy evaluation approach), and obtained an average hashrate of X H/s.
 We also ran our lazy-evaluation based miner written in C++ outside of the browser, and obtained the following results.
@@
 \subsection{Difference Between Baseline and Implementation}
-We see that the average hashrate outperforms 
-% In a one to one comparison with CPU/GPU miners, the browser miner's hashrate is pitifully low.
-However, in theory, many machines would be accessing the site at the same time, significantly increasing the total computing power of the browser miner cluster.
-To calculate the results, we used a traffic analysis website ~\cite{traffic} to determine how many views and how long the average user stayed on the site in a span of six months.
-Using that data, we were able to calculate an estimated "visitors per second" that a site had.
-This, along with the hashrate of our browser miner, allowed us to estimate the total computing power of the cluster given a specific website.
-And as monetization is the objective, the cluster hashrate was plugged into an Ethereum profitability calculator~\cite{coinwarz} to examine how much would be earned.
-The results are shown in Figure ~\ref{fig:total}.
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{Total.png}
-% \caption{\label{fig:total} Calculated Estimated Hashrates}
-% \end{figure}
-% For analysis, we selected four websites indicating varying levels of website traffic, all with views more than 10 million per six months.
-Note that some of these websites (such as \verb|xkcd.com| and \verb|bu.edu|) do not normally have paid promotions for monetization and are only being used for an approximation on how much they would earn if they implemented our browser miner.
-As you can see, BU and \verb|xkcd.com| both did rather poorly in terms of annual income.
-However, the NY Times fared significantly better than a solo CPU miner, about 3 times better.
-Finally, Wikipedia topped all of them including the GPU miner with total annual earnings of \verb|$496.85|.
-Please also know that these income calculations do not include the cost of electricity as our implementation's energy consumption and cost depends on too many variables such as the way a specific browser handles calculations and the energy efficiency of each user's computer.
+We see that the average hashrate outperforms.
 
-% \subsection{[New Results]}
-% \subsubsection{Traditional Miner}
-% As the DAG is incredibly large, attempts at a traditional miner operating on a browser became virtually impossible as the browser could not handle that much memory and ended up crashing.
-
-% \subsubsection{Compute from Cache Miner}
-% Just off of computing from the cache, our results seem promising.
-On average, computing DAG slices on demands from the cache yielded a hashrate of 127H/s.
-Theoretically, the miners that accessed from stored DAG slices would result in even higher hashrates.
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{cache.PNG}
-% \caption{\label{fig:total} Compute from Cache Miner}
-% \end{figure}
-
-% \subsubsection{Partial DAG + Cache Miner}
-% However, contrary to our belief, having the DAG present in our test seemed to have slowed down the hashrate a bit.
-In addition, the hashrate appears to be relatively unaffected based on how many DAG slices were sent, despite the increasing usage of the slices provided to the client miner.
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{partial.PNG}
-% \caption{\label{fig:total} Partial DAG Sent, with Missing Slices Computed from Cache}
-% \end{figure}
-
-% \subsubsection{Partial DAG + Cache Miner /w Storage (Array)}
-% This miner implementation used an array to store the DAG.
-It appears that by adding in the storage of slices, the performance did slightly improve.
-However, the performance remained unaffected by the changing quantity of DAG slices sent to the browser miner.
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{partial_store_array.PNG}
-% \caption{\label{fig:total} Partial DAG Sent, with Missing Slices Computed from Cache and Stored with Existing DAG slices}
-% \end{figure}
-% Also as seen before, the slices stored hit rate does go up the more slices are sent.
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{partial_store_array_hitrate.PNG}
-% \caption{\label{fig:total} Calculated Estimated Hashrates}
-% \end{figure}
-
-% \subsubsection{Partial DAG + Cache Miner w/ Storage (Hash Map)}
-% Finally, instead of using an array to store the DAG, a Hash Map was used.This implementation provided the most biased results, as the data clearly indicates that the more DAG slices sent or cached in the Hash Map, the worse the miner's performance becomes.
-In addition, this miner performed the worst out of all of them, resulting in an incredibly low hash rate in comparison to just computing from the cache.
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{partial_store_hashmap.PNG}
-% \caption{\label{fig:total} Partial DAG Sent, with Missing Slices Computed from Cache and Stored with Existing DAG slices}
-% \end{figure}
-
-% \subsection{Additional Notes}
-% Note that all of these results came from a private Ethereum testnet and thus do not accurately reflect mining capabilities on the actual Ethereum Network.
-GPU mining should be on an order of magnitude faster in terms of hashrate as opposed to CPUs.
-Additional research may be necessary to see how browser mining pools remain profitable without sufficient hashrates to support them.
+One way to reach the steady state hashrate faster for a given sized buffer would be to start out with a partially filled out buffer instead of an empty one.
+The only way this could work is by sending over part of the DAG over the network to the client.
+However, as it turns out, this is not feasible since, for a DAG with 16777186 slices (1.074 GB) sending even 10\% of the DAG would be sending \~100MB of data.
+With the global average download speed for desktops and smartphones being around 5.34MBps and 2.77MBps respectively ~\cite{http://www.speedtest.net/global-index}, the load time would be on the order of 20 seconds to a minute -- which is too long a webpage load time for getting a mere 10\% boost in the buffer storage.
 
@@
 As was shown, our current implementation is far slower than the traditional methods for mining.
-A first step is to pinpoint the exact cause for such a slow hash rate.
 One way we can look to speed this process up is to tap into the client machine's GPU.
@@
 Knowing that Ethereum was created for GPU mining and based on our results, it should provide a substantial improvement.
-In addition, because of the memory hard requirements of the Ethereum protocol we should also see a better performance if we can somehow get the DAG to be directly accessible to the client instead of having to send slices over the network to all the clients.
+% In addition, because of the memory hard requirements of the Ethereum protocol we should also see a better performance if we can somehow get the DAG to be directly accessible to the client instead of having to send slices over the network to all the clients.
 Therefore, we want to look into the use of \verb|remoteStorage| ~\cite{remote}, which allows the user to have complete control over the data.
@@
 Ethereum is also currently working on Casper, their Proof-of-Stake algorithm, which has already been deployed to private testnets for testing.
-Working with that and the fact that the entire Casper code is available online, it would be possible to create a theoretical Proof-of-Stake distributed browser miner implementation in preparation for the fork.
+Working with that and the fact that Casper is open-source, it would be possible to create a theoretical Proof-of-Stake distributed browser miner implementation in preparation for the fork.
 However, seeing as though Proof-of-Stake would virtually eliminate the necessity of massive amounts of processing power, users would most likely have to provide ``stakes" in order for such an implementation to be possible ~\cite{PoSproof}.
-Further research will be necessary to determine whether browser mining for Casper is viable or not, as the final form of Casper is still hazy and exactly how much "stake" is required to mine is uncertain.
-
-%While the roadblocks of this project cause a viable solution for Ethereum browser mining to be almost unfeasible, the changes coming to Ethereum in the near future may prove otherwise.
-Since Proof-of-Work discourages miners over time due to reduction of rewards from mining, Ethereum will soon be moving to Proof-of-Stake via their algorithm Casper.
-With the introduction of Casper, mining will be less computationally intensive and require users to provide a "stake" in Ethereum in order to mine.
-Although it would require users to put in actual money to assist in obtaining stakes, this may prove for the better as users lose significantly less processing (the main computation would jsut come from verifying blocks as opposed to mining them).
-And provided that interest and infrastructure for Ethereum grows, people may probably already have "stakes" in Ethereum and thus would not be as opposed to adding that to a pool.
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals/conferences use top floats
-% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
-% command of the stfloats package.
+Further research will be necessary to determine whether browser mining for Casper is viable or not, as the final form of Casper is still hazy and exactly how much ``stake'' is required to mine is uncertain.
 
@@
 % % use section* for acknowledgement
-% \section*{Acknowledgment}
+\section*{Acknowledgment}
+The authors would like to thank Dennis Your for his contributions to this work.
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
 \begin{thebibliography}{1}

### 2018-03-22 javascript/results/results-javascript.py
new res

@@ -15,8 +15,8 @@ cache_hit_rate[0.8] = [0.0337609375,0.0893109375,0.141321875,0.190040625,0.23339
 hash_rate[0.7] = []
 cache_hit_rate[0.7] = []
 
-hash_rate[0.6] = []
-cache_hit_rate[0.6] = []
+hash_rate[0.6] = [440.0052800633608,457.81257153321434,476.009139375476,494.6821667078902,514.0066820868672,532.5380764724678,551.7545795630103,571.2327202102136,588.7547836326171, 607.6072426783328, 624.8437890527368, 644.7868979302341, 660.9822195782934, 678.5641582411617, 695.6037840845854, 710.0759781296598, 725.9528130671507, 740.905386382159, 756.7731194187983, 770.1786814540974, 784.7445656438829, 796.1149590000796, 808.7343307723413, 823.3163181294254, 834.0979230961715, 844.3093549476529, 852.2969402539845, 863.9308855291576, 874.6610688358261, 882.4567596187787, 888.651915044877, 898.7148377819717, 900.9009009009009, 912.1590805436467, 919.2866335723478, 923.0201218386561, 930.3190994511118, 935.9790340696368, 936.768149882904, 943.930526713234, 947.2387989012029, 952.6531389920929, 955.1098376313277, 958.8647041902389, 961.4460148062686, 968.1479330041631, 968.9922480620155, 970.4968944099379, 975.3242953281965, 975.7049468240805, 980.0078400627206, 982.3182711198428, 983.2841691248772, 986.5824782951854, 987.7518767285658, 986.7771857114662, 960.9840476648088, 966.5571235260004, 979.1442279447762, 975.8953840148337, 993.7394415184339, 979.4319294809012, 977.9951100244499, 988.2399446585631, 981.8360333824252, 987.5567845151097, 992.7529038022435, 991.8666931164452, 1004.0160642570281, 1007.1507704703394, 1005.2271813429835, 1006.238679814852, 1003.4115994380894, 1008.3694665725521, 1008.6746015735324, 1004.6212577858148, 1006.238679814852, 1008.7763542822556, 1009.8969905069683, 1005.4293183189221]
[…]

### 2018-03-22 javascript/results/results-javascript.py
new res

@@ -33,5 +33,5 @@ cache_hit_rate[0.2] = [0.0081890625,0.0223390625,0.035434375,0.0475171875,0.0589
 hash_rate[0.1] = [433.99010502560543,436.7575122292103,438.09690703583635,441.306266548985,444.01030103898404,445.49382991045576,448.1290611696168,449.68072668405426,451.6711833785005, 453.7822752643282, 455.1868542036506, 456.5167769915544, 458.16915605241456, 459.1789879695105, 460.2991944764097, 461.78711613945967, 463.306152705708, 463.7573621481241, 464.25255338904367, 465.3110604439068, 466.3961568956672, 466.9188028201895, 467.4207721791156, 468.3182690956774, 468.95516788595006, 469.43948924983573, 470.14574518100613, 470.18995674252403, 471.2091226086137, 471.43126532151615, 471.8984474541079, 472.2550177095631, 472.1881197469072, 472.79088459174505, 472.85795347077743, 473.64183204660634, 473.73158368468427, 474.0235115661737, 474.20333839150226, 473.9111890431733, 474.4508231721782, 474.00104280229414, 474.31579945928, 475.37554668187863, 474.6535029428518, 474.74363843524503, 474.81126252314704, 475.37554668187863, 474.9014579474759, 475.4659566375047, 475.7373929590866, 475.42074736141484, 474.4733345985955, 473.77647226038755, 476.0997905160922, 475.55640098915734, 476.0997905160922, 476.0997905160922, 475.9638267491671, 476.16780153326033, 475.9185227489054, 476.14512903532994, 476.0771244941681, 476.3492592769018, 476.0544606302961, 476.25851312092203, 476.4173415912339, 475.71476142904714, 476.71258997950133, 476.28119641836537, 475.8958739827725, 476.4854433697051, 476.0317989241682, 476.66714333381, 476.009139375476, 476.32656949604643, 476.7353165522502, 476.14512903532994, 476.44004002096335, 476.32656949604643]
[…]

### 2018-03-22 webassembly/results/grapher.py
added basic grapher

@@ -1,0 +1,41 @@
+#!/usr/bin/env python
+
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+
+#!/usr/bin/env python
+
+
+hash_rate_native_miner = [[955.059584, 950.559095, 952.535349, 951.104597, 960.559125, 960.690628, 964.573692, 959.956621, 964.357570,  961.177347,  957.416237,  935.989912,  953.883697,  953.438672,  950.898622,  953.506565,  953.942586,  956.280652,  956.338844,  958.573018,  960.089908,  963.001499,  966.127204,  964.676208,  962.267201,  961.952992,  966.779408,  967.423764,  960.685767,  960.490729,  964.875144,  960.821510,  964.167782,  960.154118,  963.987767,  960.765608,  964.896024,  961.423105,  964.751555,  960.703747,  965.598498,  961.526654,  964.058327,  959.941426,  963.102769,  959.375095,  965.781355,  962.439712,  961.892733,  962.824115,  962.832871,  960.269546,  964.849970,  961.567987,  964.589812,  959.840110,  964.924984,  961.543488,  964.486305,  957.144291,  964.229585,  962.377095,  964.684323,  960.825025,  963.413951,  960.686183,  964.447325,  961.492177,  960.459985,  958.912128,  962.217194,  962.030988,  964.771889,  959.902986,  964.216356,  960.632711,  963.081304,  960.252173,  965.766676,  962.615221],
[…]

### 2018-03-22 webassembly/results/webasm-miner.py
new res

@@ -24,8 +24,8 @@ cache_hit_rate[0.5] = [0.018594,0.053771,0.086648,0.117236,0.145153,0.171709,0.1
 hash_rate[0.4] = [595.316053,613.459297,631.269293,647.529997,664.884776,680.818616,695.038123,711.353920,725.652543,739.398869,753.097112,764.871005,779.234947,789.390590,799.315786,810.707829,821.125928,830.806298,838.989521,848.464280,854.854290,863.863717,871.976422,879.089966,883.626403,891.615250,898.125612,902.413052,907.490426,912.633587,914.787541,918.054459,924.035076,926.466365,931.818817,933.558632,935.051334,940.910802,941.433427,945.108120,946.763489,950.190988,952.027342,951.782689,954.071021,955.447484,958.561391,959.333839,958.386843,962.250897,961.196497,961.963946,962.992209,963.576797,964.413155,965.679742,965.353464,967.454820,970.270900,968.044840,967.688869,971.401927,967.923031,972.251930,969.950920,969.123718,971.703980,971.392491,971.826743,971.524614,971.562369,971.902304,972.516679,974.753875,973.842588,973.690873,971.364184,973.179182,971.637890,962.269416]
[…]

### 2018-03-22 javascript/results/grapher.py
added grapher

@@ -1,0 +1,81 @@
+#!/usr/bin/env python
+
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+# hash_rate[1] = 
+# cache_hit_rate[1] = 
+
+# hash_rate[0.9] = 
+# cache_hit_rate[0.9] = 
+
+# hash_rate[0.8] = 
+# cache_hit_rate[0.8] = 
+
+# hash_rate[0.7] = 
+# cache_hit_rate[0.7] = 
+
+# hash_rate[0.6] = 
+# cache_hit_rate[0.6] = 
+
+# hash_rate[0.5] = 
+# cache_hit_rate[0.5] = 
+
+# hash_rate[0.4] = 
+# cache_hit_rate[0.4] = 
+
+# hash_rate[0.3] = 
+# cache_hit_rate[0.3] = 
+
+# hash_rate[0.2] = 
+# cache_hit_rate[0.2] = 
+
+# hash_rate[0.1] = 
+# cache_hit_rate[0.1] = 
+
+# hash_rate[0] = 
+# cache_hit_rate[0] = [0]*len(cache_hit_rate[0.1])
+
+hash_rate_js_miner = [[429.3688278231,429.55326460481103,429.03724043246956,430.40371868812946,430.0890284288848,429.95958379912287,429.55326460481103,430.2185510239202,430.31111493609876, 429.9410980695645, 430.2000430200043, 429.88565041698905, 429.55326460481103, 427.60626015564867, 428.3755997258396, 430.7930900788352, 430.16303178904803, 429.9410980695645, 430.1815366084487, 430.5148958153952, 429.79326943740057, 430.5705059203445, 430.5705059203445, 430.1075268817204, 430.1260269258893, 429.7009281540048, 430.5148958153952, 430.2000430200043, 430.40371868812946, 430.3296324984939, 430.66322136089576, 429.978071118373, 430.05203629639186, 430.44077134986225, 430.6817692407081, 430.2000430200043, 430.1075268817204, 430.3296324984939, 429.79326943740057, 429.978071118373, 429.99656002751976, 430.42224422158137, 430.05203629639186, 430.1260269258893, 429.77479800584496, 430.01505052676845, 430.7559767391773, 430.070531567177, 430.36667240488896, 430.070531567177, 430.2000430200043, 429.8486932599725, 429.5163645734903, 429.77479800584496, 429.9410980695645, 430.05203629639186, 430.070531567177, 430.070531567177, 427.89901583226356, 4
[…]

### 2018-03-22 webassembly/results/webasm-miner.py
new res

@@ -27,8 +27,8 @@ cache_hit_rate[0.4] = [ 0.014966, 0.043272, 0.069442, 0.093995, 0.116086, 0.1379
 hash_rate[0.3] = [ 585.912324, 600.936259, 613.436718, 623.655243, 635.315943, 647.580316, 658.410203, 667.908977, 677.093913,  687.143544,  695.874854,  704.453555,  711.389343,  719.377882,  724.900326,  733.369024,  739.858391,  744.629361,  751.506771,  755.692252,  761.742257,  765.731963,  767.654126,  772.379702,  777.895326,  781.286623,  784.633733,  786.905886,  791.239397,  792.254916,  795.462681,  797.899927,  799.226349,  800.871348,  803.096741,  805.392911,  806.523159,  807.767492,  809.913339,  811.556566,  811.879420,  813.318910,  813.643169,  815.248406,  813.815329,  816.986789,  817.895555,  816.773256,  820.492624,  819.020942,  821.004581,  820.176338,  820.849579,  821.706191,  822.246707,  823.302761,  822.686400,  823.743585,  824.973601,  823.343433,  825.675196,  825.838846,  823.404448,  826.255081,  825.688831,  825.245923,  821.922312,  824.334350,  822.199383,  813.755727,  825.729739,  825.416216,  826.658069,  827.383070,  827.328309,  827.239337,  826.009383,  826.979375,  825.722920,  827.335153]
[…]

### 2018-03-22 webassembly/results/grapher.py
plot wasm

@@ -5,9 +5,6 @@ import numpy as np
 import math
 
 
-#!/usr/bin/env python
-
-
 hash_rate_native_miner = [[955.059584, 950.559095, 952.535349, 951.104597, 960.559125, 960.690628, 964.573692, 959.956621, 964.357570,  961.177347,  957.416237,  935.989912,  953.883697,  953.438672,  950.898622,  953.506565,  953.942586,  956.280652,  956.338844,  958.573018,  960.089908,  963.001499,  966.127204,  964.676208,  962.267201,  961.952992,  966.779408,  967.423764,  960.685767,  960.490729,  964.875144,  960.821510,  964.167782,  960.154118,  963.987767,  960.765608,  964.896024,  961.423105,  964.751555,  960.703747,  965.598498,  961.526654,  964.058327,  959.941426,  963.102769,  959.375095,  965.781355,  962.439712,  961.892733,  962.824115,  962.832871,  960.269546,  964.849970,  961.567987,  964.589812,  959.840110,  964.924984,  961.543488,  964.486305,  957.144291,  964.229585,  962.377095,  964.684323,  960.825025,  963.413951,  960.686183,  964.447325,  961.492177,  960.459985,  958.912128,  962.217194,  962.030988,  964.771889,  959.902986,  964.216356,  960.632711,  963.081304,  960.252173,  965.766676,  962.615221],
[…]

### 2018-03-22 webassembly/results/webasm-miner.py
new res

@@ -33,3 +33,5 @@ cache_hit_rate[0.2] = [ 0.007508, 0.021336, 0.035114, 0.046959, 0.057838, 0.0688
 hash_rate[0.1] = [576.518405, 590.936220, 595.812629, 597.161096, 600.947093, 605.052186, 604.069009, 610.668377, 614.186479,  617.329679,  616.994496,  619.363790,  622.878321,  622.633991,  623.177207,  628.507859,  628.847762,  628.918951,  613.963997,  632.299103,  635.457243,  636.152549,  632.151211,  637.820186,  638.353558,  637.970743,  638.117299,  641.366881,  642.677652,  640.524718,  637.393316,  643.053734,  644.682977,  642.252508,  643.239871,  645.082216,  643.695326,  642.528994,  642.553766,  645.590296,  644.450316,  643.392997,  646.859819,  645.207079,  645.448619,  645.319498,  644.691290,  647.060727,  647.710344,  646.378985,  645.419458,  646.621403,  647.060727,  645.040605,  646.395698,  648.319232,  647.182169,  644.458622,  649.633282,  649.802135,  647.634838,  645.311169,  649.840139,  648.563108,  648.193162,  644.304988,  648.478993,  650.144332,  648.811378,  646.558691,  648.651454,  648.777703,  649.388601,  646.529430,  648.819797,  646.629766,  646.378985,  639.529306,  648.504225,  649.017712]
 cache_hit_rate[0.1] = [0.003719,0.010639,0.017334,0.023584,0.028797,0.034441,0.038856,0.043719,0.048009,0.051469,0.055228,0.058422,0.061495,0.064782,0.066659,0.070016,0.071388,0.074120,0.075497,0.077213,0.079408,0.081469,0.081642,0.083381,0.084486,0.085562,0.086780,0.088202,0.088367,0.089247,0.090355,0.091245,0.092181,0.091794,0.092502,0.093519,0.094012,0.094167,0.094233,0.095164,0.094730,0.095392,0.096650,0.096744,0.096794,0.097536,0.096367,0.097231,0.097605,0.098595,0.098267,0.097998,0.098648,0.098761,0.098244,0.098633,0.098598,0.098342,0.098548,0.099027,0.098689,0.098889,0.099267,0.098806,0.099423,0.099383,0.098644,0.099783,0.099753,0.099892,0.099600,0.099270,0.099702,0.099931,0.100222,0.099748,0.099289,0.099753,0.100064,0.099522]
 
[…]

### 2018-03-22 webassembly/results/grapher.py
added last row in graph

@@ -53,7 +53,8 @@ cache_hit_rate_native_miner = [[0]*80,
 cache_wasm_list = list()
 hash_wasm_list = list()
 
-cache_hit_rate_wasm_miner = [[0.003719,0.010639,0.017334,0.023584,0.028797,0.034441,0.038856,0.043719,0.048009,0.051469,0.055228,0.058422,0.061495,0.064782,0.066659,0.070016,0.071388,0.074120,0.075497,0.077213,0.079408,0.081469,0.081642,0.083381,0.084486,0.085562,0.086780,0.088202,0.088367,0.089247,0.090355,0.091245,0.092181,0.091794,0.092502,0.093519,0.094012,0.094167,0.094233,0.095164,0.094730,0.095392,0.096650,0.096744,0.096794,0.097536,0.096367,0.097231,0.097605,0.098595,0.098267,0.097998,0.098648,0.098761,0.098244,0.098633,0.098598,0.098342,0.098548,0.099027,0.098689,0.098889,0.099267,0.098806,0.099423,0.099383,0.098644,0.099783,0.099753,0.099892,0.099600,0.099270,0.099702,0.099931,0.100222,0.099748,0.099289,0.099753,0.100064,0.099522],
+cache_hit_rate_wasm_miner = [[0]*80,
+[0.003719,0.010639,0.017334,0.023584,0.028797,0.034441,0.038856,0.043719,0.048009,0.051469,0.055228,0.058422,0.061495,0.064782,0.066659,0.070016,0.071388,0.074120,0.075497,0.077213,0.079408,0.081469,0.081642,0.083381,0.084486,0.085562,0.086780,0.088202,0.088367,0.089247,0.090355,0.091245,0.092181,0.091794,0.092502,0.093519,0.094012,0.094167,0.094233,0.095164,0.094730,0.095392,0.096650,0.096744,0.096794,0.097536,0.096367,0.097231,0.097605,0.098595,0.098267,0.097998,0.098648,0.098761,0.098244,0.098633,0.098598,0.098342,0.098548,0.099027,0.098689,0.098889,0.099267,0.098806,0.099423,0.099383,0.098644,0.099783,0.099753,0.099892,0.099600,0.099270,0.099702,0.099931,0.100222,0.099748,0.099289,0.099753,0.100064,0.099522],
[…]

### 2018-03-22 paper/grapher.py
adding final grapher

@@ -6,21 +6,154 @@ import math
 
 n = 16777186
 
-y = list()
-x = np.linspace(0,0.99,100,endpoint=True)
-for f in x:
-	y.append(n*math.log(1/(1-f))/64)
+hash_rate_js_miner = [[429.3688278231,429.55326460481103,429.03724043246956,430.40371868812946,430.0890284288848,429.95958379912287,429.55326460481103,430.2185510239202,430.31111493609876, 429.9410980695645, 430.2000430200043, 429.88565041698905, 429.55326460481103, 427.60626015564867, 428.3755997258396, 430.7930900788352, 430.16303178904803, 429.9410980695645, 430.1815366084487, 430.5148958153952, 429.79326943740057, 430.5705059203445, 430.5705059203445, 430.1075268817204, 430.1260269258893, 429.7009281540048, 430.5148958153952, 430.2000430200043, 430.40371868812946, 430.3296324984939, 430.66322136089576, 429.978071118373, 430.05203629639186, 430.44077134986225, 430.6817692407081, 430.2000430200043, 430.1075268817204, 430.3296324984939, 429.79326943740057, 429.978071118373, 429.99656002751976, 430.42224422158137, 430.05203629639186, 430.1260269258893, 429.77479800584496, 430.01505052676845, 430.7559767391773, 430.070531567177, 430.36667240488896, 430.070531567177, 430.2000430200043, 429.8486932599725, 429.5163645734903, 429.77479800584496, 429.9410980695645, 430.05203629639186, 430.070531567177, 430.070531567177, 427.89901583226356, 429.9226139294927, 425.4051984515251, 429.99656002751976, 429.46102641185314, 429.62708369135595, 430.25557180965495, 430.34815165468865, 429.6455424274973, 430.25557180965495, 430.25557180965495, 430.03354261632404, 429.95958379912287, 429.7009281540048, 430.23706062040185, 430.42224422158137, 430.05203629639186, 430.16303178904803, 429.9041313787026, 430.070531567177, 430.45930007317804, 423.405876873571],
[…]

### 2018-03-22 paper/grapher.py
adding final grapher

@@ -105,19 +105,19 @@ def fill_partial_buf():
 
 
 def miner_res(title,cache_hit,hash_rate):
-	# plt.imshow(hash_rate,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500)
-	# plt.colorbar()
-	# plt.ylabel('buffer hit rate')
-	# plt.xlabel('Hashes computed (in thousands)')
-	# plt.title(title)
-	# plt.show()
+	plt.imshow(hash_rate,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=70000)
+	plt.colorbar()
+	plt.ylabel('buffer hit rate')
+	plt.xlabel('Hashes computed (in thousands)')
+	plt.title(title)
+	plt.show()
 
-	# plt.imshow(cache_hit,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500)
-	# plt.colorbar()
-	# plt.ylabel('buffer hit rate')
-	# plt.xlabel('Hashes computed (in thousands)')
-	# plt.title(title)
-	# plt.show()
+	plt.imshow(cache_hit,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
+	plt.colorbar()
+	plt.ylabel('buffer hit rate')
+	plt.xlabel('Hashes computed (in thousands)')
+	plt.title(title)
+	plt.show()
 
 	hash_list = list()
 	time_list = list()
@@ -147,7 +147,7 @@ def miner_res(title,cache_hit,hash_rate):
 
 def miner_comparison(title,h1,h2):
 	h_diff = (np.array(h1) - np.array(h2))/np.array(h1)
-	plt.imshow(h_diff, origin='lower',cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500)
+	plt.imshow(h_diff, origin='lower',cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
 	plt.colorbar()
 	plt.ylabel('buffer hit rate')
 	plt.xlabel('Hashes computed (in thousands)')
@@ -155,5 +155,5 @@ def miner_comparison(title,h1,h2):
 	plt.show()
 
[…]

### 2018-03-22 paper/grapher.py
adding final grapher

@@ -107,15 +107,15 @@ def fill_partial_buf():
 def miner_res(title,cache_hit,hash_rate):
 	plt.imshow(hash_rate,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=70000)
 	plt.colorbar()
-	plt.ylabel('buffer hit rate')
-	plt.xlabel('Hashes computed (in thousands)')
+	plt.xlabel('Buffer Hit Rate')
+	plt.xlabel('Hashes Computed (in thousands)')
 	plt.title(title)
 	plt.show()
 
 	plt.imshow(cache_hit,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
 	plt.colorbar()
-	plt.ylabel('buffer hit rate')
-	plt.xlabel('Hashes computed (in thousands)')
+	plt.xlabel('Buffer Hit Rate')
+	plt.xlabel('Hashes Computed (in thousands)')
 	plt.title(title)
 	plt.show()
 
@@ -129,27 +129,27 @@ def miner_res(title,cache_hit,hash_rate):
 		time_list.extend(1/np.array(h))
 
 	plt.plot(cache_list,hash_list,'ro')
-	plt.xlabel('buffer hit rate')
-	plt.ylabel('hash rate (H/s)')
+	plt.xlabel('Buffer Hit Rate')
+	plt.ylabel('Hash Rate (H/s)')
 	plt.title(title)
 	plt.show()
 
 	plt.plot(cache_list,hash_list,'ro')
-	plt.xlabel('buffer hit rate')
-	plt.ylabel('time taken per hash (s/H)')
+	plt.xlabel('Buffer Hit Rate')
+	plt.ylabel('Time taken per hash (s/H)')
 	plt.title(title)
 	plt.show()
 
 
-# miner_res("native C++ miner",cache_hit_rate_native_miner,hash_rate_native_miner)
-# miner_res("WebAssembly miner",cache_hit_rate_wasm_miner,hash_rate_wasm_miner)
-# miner_res("JavaScript miner",cache_hit_rate_js_miner,hash_rate_js_miner)
+miner_res("native C++ miner",cache_hit_rate_native_miner,hash_rate_native_miner)
+miner_res("WebAssembly miner",cache_hit_rate_wasm_miner,hash_rate_wasm_miner)
[…]

### 2018-03-22 paper/grapher.py
adding final grapher

@@ -107,14 +107,14 @@ def fill_partial_buf():
 def miner_res(title,cache_hit,hash_rate):
 	plt.imshow(hash_rate,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=70000)
 	plt.colorbar()
-	plt.xlabel('Buffer Hit Rate')
+	plt.ylabel('Buffer Hit Rate')
 	plt.xlabel('Hashes Computed (in thousands)')
 	plt.title(title)
 	plt.show()
 
 	plt.imshow(cache_hit,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
 	plt.colorbar()
-	plt.xlabel('Buffer Hit Rate')
+	plt.ylabel('Buffer Hit Rate')
 	plt.xlabel('Hashes Computed (in thousands)')
 	plt.title(title)
 	plt.show()

### 2018-03-22 paper/grapher.py
adding final grapher

@@ -107,14 +107,14 @@ def fill_partial_buf():
 def miner_res(title,cache_hit,hash_rate):
 	plt.imshow(hash_rate,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=70000)
 	plt.colorbar()
-	plt.ylabel('Buffer Hit Rate')
+	plt.ylabel('Buffer Size as a fraction of DAG')
 	plt.xlabel('Hashes Computed (in thousands)')
 	plt.title(title)
 	plt.show()
 
 	plt.imshow(cache_hit,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
 	plt.colorbar()
-	plt.ylabel('Buffer Hit Rate')
+	plt.ylabel('Buffer Size as a fraction of DAG')
 	plt.xlabel('Hashes Computed (in thousands)')
 	plt.title(title)
 	plt.show()
@@ -149,7 +149,7 @@ def miner_comparison(title,h1,h2):
 	h_diff = (np.array(h1) - np.array(h2))/np.array(h1)
 	plt.imshow(h_diff, origin='lower',cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
 	plt.colorbar()
-	plt.ylabel('Buffer Hit Rate')
+	plt.ylabel('Buffer Size as a fraction of DAG')
 	plt.xlabel('Hashes computed (in thousands)')
 	plt.title(title)
 	plt.show()

### 2018-03-22 paper/grapher.py
adding final grapher

@@ -109,14 +109,14 @@ def miner_res(title,cache_hit,hash_rate):
 	plt.colorbar()
 	plt.ylabel('Buffer Size as a fraction of DAG')
 	plt.xlabel('Hashes Computed (in thousands)')
-	plt.title(title)
+	plt.title(title + " hash rate")
 	plt.show()
 
 	plt.imshow(cache_hit,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
 	plt.colorbar()
 	plt.ylabel('Buffer Size as a fraction of DAG')
 	plt.xlabel('Hashes Computed (in thousands)')
-	plt.title(title)
+	plt.title(title + " cache hit rate")
 	plt.show()
 
 	hash_list = list()
@@ -151,7 +151,7 @@ def miner_comparison(title,h1,h2):
 	plt.colorbar()
 	plt.ylabel('Buffer Size as a fraction of DAG')
 	plt.xlabel('Hashes computed (in thousands)')
-	plt.title(title)
+	plt.title(title + " hash rate")
 	plt.show()
 
 miner_comparison('Native miner vs WebAssembly miner',hash_rate_native_miner,hash_rate_wasm_miner)

### 2018-03-22 paper/grapher.py
bug fixign

@@ -134,7 +134,7 @@ def miner_res(title,cache_hit,hash_rate):
 	plt.title(title)
 	plt.show()
 
-	plt.plot(cache_list,hash_list,'ro')
+	plt.plot(cache_list,time_list,'ro')
 	plt.xlabel('Buffer Hit Rate')
 	plt.ylabel('Time taken per hash (s/H)')
 	plt.title(title)
@@ -167,3 +167,8 @@ def hash_rate_trajectory(title,hash_rate):
 hash_rate_trajectory("JavaScript miner",hash_rate_js_miner[-1])
 hash_rate_trajectory("WebAssembly miner",hash_rate_wasm_miner[-1])
 hash_rate_trajectory("Native miner",hash_rate_native_miner[-1])
+
+# error bars
+# level curves
+# log scale for heat maps?
+# more clear titles

### 2018-03-22 paper/grapher.py
added all results graphs

@@ -104,20 +104,23 @@ def fill_partial_buf():
 	plt.show()
 
 
-def miner_res(title,cache_hit,hash_rate):
-	plt.imshow(hash_rate,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=70000)
-	plt.colorbar()
-	plt.ylabel('Buffer Size as a fraction of DAG')
-	plt.xlabel('Hashes Computed (in thousands)')
-	plt.title(title + " hash rate")
-	plt.show()
+def miner_res(title,cache_hit,hash_rate,label=None):
+	# # log_hash_rate = [[math.log(i) for i in row] for row in hash_rate]
+	# plt.imshow(hash_rate,origin='lower', cmap='seismic',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=70000)
+	# plt.colorbar()
+	# plt.ylabel('Buffer Size as a fraction of DAG')
+	# plt.xlabel('Hashes Computed (in thousands)')
+	# plt.title(title + " Log(Hash Rate)")
+	# # plt.show()
+	# plt.savefig(title + " Hash Rate.pdf", bbox_inches='tight')
 
-	plt.imshow(cache_hit,origin='lower', cmap='Wistia',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
-	plt.colorbar()
-	plt.ylabel('Buffer Size as a fraction of DAG')
-	plt.xlabel('Hashes Computed (in thousands)')
-	plt.title(title + " cache hit rate")
-	plt.show()
+	# plt.imshow(cache_hit,origin='lower', cmap='seismic',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
+	# plt.colorbar()
+	# plt.ylabel('Buffer Size as a fraction of DAG')
+	# plt.xlabel('Hashes Computed (in thousands)')
+	# plt.title(title + " Buffer Hit Rate Percent")
+	# plt.show()
+	# plt.savefig(title + " Buffer Hit Rate.pdf", bbox_inches='tight')
 
 	hash_list = list()
 	time_list = list()
@@ -128,45 +131,63 @@ def miner_res(title,cache_hit,hash_rate):
 		hash_list.extend(h)
 		time_list.extend(1/np.array(h))
 
-	plt.plot(cache_list,hash_list,'ro')
[…]

### 2018-03-29 paper/paper.tex
addressed comments on first draft

@@
 \usepackage{color}
+\usepackage{makecell}
 \usepackage{amsmath}
@@
 %
-\title{Distributed Ethereum Web Browser Mining\thanks{Supported by organization x.}}
+\title{Distributed Web Mining of Ethereum\thanks{Supported by organization x.}}
 %
@@
 %
-\author{Trishita Tiwari\orcidID{0000-1111-2222-3333} \and
-David Starobinski\orcidID{1111-2222-3333-4444} \and
-Ari Trachtenberg\orcidID{2222--3333-4444-5555}}
+\author{
+Trishita Tiwari%\orcidID{0000-1111-2222-3333} 
+\and
+David Starobinski%\orcidID{1111-2222-3333-4444} 
+\and
+Ari Trachtenberg%\orcidID{2222--3333-4444-5555}
+}
 %
@@
 \begin{abstract}
-Given the seemingly endless growing popularity of crypto-currencies, there is an increasing interest in different mining possibilities.
+We consider the problem of mining crytocurrencies by harnessing the inherent distribution capabilities of the World Wide Web. More specifically, we consider
+the mining of the Ethereum cryptocurrency by apportioning elements of the corresponding Proof-of-Work calculations among a number of web clients.
+These calculations are handled through individualized code that runs on the client browsers, and is thereafter collated at a web server to complete a mining operation.
+Our approach is based on a lazy evaluation technique designed to function within the expected limitations of the clients, including bounds on memory, computation and communication bandwidth to the server.
+We provide proofs-of-concept based in JavaScript and WebAssembly, with the latter reaching hash rates up to roughly 39kH/s, which is only 30.2\% slower than the corresponding native C++-based miner.
+Finally, we explore several applications for which this hash rate seems practical, including monetization of web content, rate limitation, and private Ethereum networks.
+Though several distributed web-based cryptominers have appeared in the wild (for other currencies), either in malware or in commercial trials, we believe that this is the first open-source cryptominer of this type.
+% The process of legitimating cryptocurrencies (such as Bitcoin and Ethereum) is done
+% through mining, often in a competitive and distributed manner by means of a small number of
+% large, loosely-organized mining colonies following proprietary protocols.  We
+
+% Cryptocurrencies such as Bitcoin and Ethereum are valdated and legitimated through mining,
+% a competitive and often distri
+
+% We propose and analyze an open-source platform for distributed cryptocurrency mining.
+
+% Given the seemingly endless growing popularity of crypto-currencies, there is an increasing interest in different mining possibilities.
 This paper proposes a web browser based mining implementation for Ethereum implemented both in JavaScript and WebAssembly to perform the necessary Proof-of-Work (PoW) computations to mine the Ethereum blockchain.
-We explore a variety of techniques to distribute the inherently memory and memory intensive PoW of Ethereum over multiple browser-based clients that have limited resources.
-We obtain the best results with the WebAssembly implementation, with hash rates reaching upto X H/s, which, as we demonstrate, is merely X\% slower than a native miner that uses the same algorithm for mining.
+We explore a lazy evaluation based technique to distribute the inherently memory and memory intensive PoW of Ethereum over multiple browser-based clients that have limited resources.
+We obtain the best results with the WebAssembly implementation, with hash rates reaching upto 39651H/s ~\trishita{Not sure if we need such a specific number}, which, as we demonstrate, is merely 30.2\% slower than a native miner that uses the same algorithm for mining under the same conditions.
 We show that this solution is practical for a variety of purposes, such as web content monetization, web based authentication rate limiting and private Ethereum networks.
+% \trishita{I have not included a comparison with an actual miner that saves the entire DAG in memory from the start (i.e., doesn't use our lazy evaluation approach) -- should I do that for the abstract?}
 
@@
 While much of these efforts have included creating new hardware, there has been considerable work done in re-using existing infrastructure in smarter ways to increase performance.
-One such effort is seen in using web browser as a platform for distributed computing ~\cite{Cushing}, and more recently, specifically for distributed crypto-currency mining ~\cite{coinhive}.
-In this work, we propose approaches to mine Ethereum, a popular crypto-currency, in a distributed fashion through web browsers.
-Our approach can be used for a variety of purposes, outlined as follows:
-\begin{enumerate}
+One such effort is seen in using web browser as a platform for distributed computing ~\cite{Cushing}.
+Furthermore, more recently, the growing popularity of CoinHive ~\cite{coinhive} shows that there have been successful endeavors in distributed web browser crypto-currency mining, reinforcing its viability as a concept.
+In this work, we attempt to further extend this field by providing an open\-source implementations of web-base miners for Ethereum in \verb|JavaScript| and \verb|WebAssembly|.
+Indeed, given that Ethereum has applications beyond being used as a currency, there are a multitude of applications like web authentication rate limiting, website usage tracking for advertisement companies, private Ethereum networks and web content monetization, where our miner is practical to use.
 
-\item \textbf{Web Content Monetization}: With the growth in global Internet usage, websites have become a lucrative way for people to earn monetary profit.
+\subsection{Related Work}
+So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling},~\cite{parallel},~\cite{orca}.
+Additionally, with the growing popularity of dynamic web-content and client side scripting languages like \verb|JavaScript| and \verb|WebAssembly|, web-browsers have also become a lucrative option for implementing distributed systems.
+As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow} ~\cite{Duda}.
+Indeed, ``Distributed Computing on an Ensemble of Browsers'' by Cushing~\cite{Cushing} shows that the \verb|JavaScript| Engine has had enough improvements in performance to make computationally heavy programs feasible in a distributed web browsing unit.
+% In addition, the work by Duda and Dłubacz~\cite{Duda} was instrumental in the field as one of the first web browsing computational systems to not require the host machine to install any additional applications in order to participate.
+This is important since we would want our web miner to be operable without requiring the user to install any unfamiliar software.
+Furthermore, \verb|WebAssembly|  ~\cite{webAssembly} is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to be only 20\% slower than native code ~\cite{wasmPerf}, as compared to the much slower \verb|JavsScript|.
+Instead of relying on \verb|JavaScript|, web developers can now write C/C++ and compile it into \verb|WebAssembly| using some of the openly available \verb|WebAssembly| compilers ~\cite{emscripten}.
+Indeed, given that now \verb|WebAssembly| is supported by all major browsers ~\cite{webAssembly}, industry is also making use of this powerful framework.
+One sees this through the recent development of increasingly popular Monero mining \verb|WebAssembly| library CoinHive ~\cite{coinhive}.
+
+\subsection{Our Contributions}
+Our research involves providing implementations of a distributed, web browser based Ethereum miners in \verb|JavaScript| and \verb|WebAssembly|, and studying whether or not it is feasible for real world purposes.
+While there has been prior academic work done in related fields, none of the distributed web browser implementations in these works do not involve crypto-currency mining.
+While CoinHive does perform distributed mining using web browsers, it is closed source, and also works with a different crypto-currency (Monero).
+Hence, we are pioneering in offering an open source architecture for Ethereum mining with web browsers.
+Our miner gives us a hashrate of about 39kH/s, which, given the flexibility of the Ethereum framework, is useful and practical for many applications like web authentication rate limiting, website usage tracking for advertisement companies, private Ethereum networks, web content monetization, as discussed below.
+
+% \subsection{Applications}
+
+\section{Outline}
+\trishita{To Do: Update}
+The remainder of the paper is organized as follows.
+In Section 5 we present a detailed description of the Ethereum mining algorithm and the current state of Ethereum.
+Section 6 describes the Architecture of our implementation of the Distributed Web Browser Miner.
+Section 7 goes over the challenges that we have dealt with during our implementation and their effect on the project.
+Section 8 examines the results of our solution and compares it to current mining data to evaluate the efficacy of our work.
+Finally, in Section 9 we lay out possible future work, and in Section 10 provide conclusions and insight on the project.
+
+\section{Applications}
+% In this work, we propose approaches to mine Ethereum, a popular crypto-currency, in a distributed fashion through web browsers.
+Our approach can be used for a variety of purposes, outlined as follows.
+\\ \\
+% \textbf{Web Content Monetization}
+With the growth in global Internet usage, websites have become a lucrative way for people to earn monetary profit.
 As a result, new methods of monetizing electronic content have surfaced with time.
@@
 Thus, this approach does not provide good user experience.
+\\ \\
 % Another approach involves subscriptions, however, it is not very successful.
@@
 Our web-based miner would solve this situation as it does not
-\item \textbf{Web-Authentication Rate Limiting}: Brute forcing web login pages is becoming an all too common issue ~\cite{webLoginBruteForce}, and the way website owners mitigate this issue is by locking out a user for a certain amount of time after a fixed number of unsuccessful login attempts.
-While this approach works in theory, in today's fast-paced world, users tend to dislike waiting for even a few seconds ~\cite{usersDislikeWaiting}.
-Another solution to this problem involves embedding a Proof-of-Work (PoW) computation in the web page that the user's browser needs to successfully solve in order to be able to login.
-Our implementation uses the Ethereum PoW, which is extremely feasible for legitimate users attempting to login, but will thwart any attacker that attempts to brute force the login.
-Furthermore, the difficulty of the PoW can be tuned to obtain a balance between user experience and security.
-\item \textbf{Website usage tracking}: Website advertising sponsors decide on the remuneration for a website by inspecting the logs of the web servers in order to deduce how much traffic the site receives.
+% \textbf{Web-Authentication Rate Limiting}: 
+Another potential application could involve web-authentication rate limiting.
+Given the multitude of tools available brute forcing web login pages ~\cite{hydra} ~\cite{burpsuite}, it is painfully easy to brute force authentication pages these days.
+Currently, the way website owners mitigate this issue is by locking out a user for a certain amount of time after a fixed number of unsuccessful login attempts.
+% While this approach works in theory, in today's fast-paced world, users tend to dislike waiting for even a few seconds ~\cite{usersDislikeWaiting}. 
+While it seems as though this approach is effective at face value, in reality, it does more harm than good as by introducing the risk of Denial of Service.
+This is because most brute force attacks are large scale and try millions of username/password combinations, which would consequently lockout a large number of user accounts.
+While this may prevent an attacker from successfully cracking passwords, it would also deny service to a lot of legitimate users whose accounts were being brute forced.
+This, amongst other issues, would definitely reflect badly on the website owner, and hence opens a whole new avenue for attack.
+Given this situation, a more user-friendly approach to this problem involves embedding a Proof-of-Work (PoW) computation in the web page that the user's browser needs to successfully solve in order to be able to login.
+Requiring a PoW would require a large amount of computation power for brute force attempts, thereby selectively thwarting any attacker that attempts to brute force the login \emph{without} penalizing the legitimate user.
+This makes our implementation for the Ethereum PoW an ideal candidate, even more so since one could manually set the difficulty to obtain a balance between user experience and security.
+\\ \\
+One other use-case could involve website advertisement companies.
+Today, website advertising sponsors decide on the remuneration for a website by inspecting the logs of the web servers in order to deduce how much traffic the site receives.
 However, it is well known that these logs can be easily manipulated by the website owner in order to generate the impression of a large amount of traffic ~\cite{webLogsManipulation}.
-Our web miner could solve these issues as it has this unique property of a direct correlation between a users hashrate and the time spent on the website (i.e., the longer the user spends on the web page, better the hashrate gets).
-Hence, our miner can be embedded within advertisements and allow advertisers to directly extrapolate how much traffic the website gets just by extrapolating from the average hash rate.
-\item \textbf{Private Ethereum networks}: Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- i.e., networks that do not on mine the actual, public Ethereum block-chain, but rather on private (and often smaller) instances of the crypto-currency.
+Our web miner could solve these issues as the advertiser could require the website owner to embed this miner within their website, thereby making the site visitors compute PoW hashes.
+The advertiser would then ask the website owner to submit hashes that pass a certain difficulty threshold, and the larger the number of hashes that the website owner can provide, the more the remuneration the site receives.
+This would be extremely difficult for the website owners to fake since they would have to compute hashes themselves, an endeavor that might be more expensive than the corresponding payout it would bring.\\ \\
+Finally, we would also like to note that Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- i.e., networks that do not on mine the actual, public Ethereum block-chain, but rather on private (and often smaller) instances of the crypto-currency.
 Our browser miner can be used on any such private network to serve the network owner whatever he/she wishes to implement with the mining PoW.
-\end{enumerate}
-
-\section{Related Work}
-So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling},~\cite{parallel},~\cite{orca}.
-Additionally, with the growing popularity of dynamic web-content and client side scripting languages like \verb|JavaScript| and \verb|WebAssembly|, web-browsers have also become a lucrative option for implementing distributed systems.
-As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow} ~\cite{Duda}.
-Indeed, ``Distributed Computing on an Ensemble of Browsers'' by Cushing~\cite{Cushing} shows that the \verb|JavaScript| Engine has had enough improvements in performance to make computationally heavy programs feasible in a distributed web browsing unit.
-In addition, the work by Duda and Dłubacz~\cite{Duda} was instrumental in the field as one of the first web browsing computational systems to not require the host machine to install any additional applications in order to participate.
-This is important since we would want our web miner to be operable without requiring the user to install any unfamiliar software.
-Furthermore, \verb|WebAssembly| is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to offer X\% speed as \verb|JavsScript| ~\cite{WebAssembly}.
-Instead of relying on \verb|JavaScript|, web developers can now write C/C++ or Rust code and compile it into \verb|WebAssembly| using some of the openly available \verb|WebAssembly| compilers ~\cite{emscripten} ~\cite{rustCompiler} .
-Indeed, given that now \verb|WebAssembly| is supported by all major browsers ~\cite{webasmSupport}, industry is also making use of this powerful framework.
-One sees this through the recent development of increasingly popular Monero mining \verb|WebAssembly| library CoinHive ~\cite{coinhive}.
-
-\section{Our Contributions}
-Our research involves providing an implementation of a distributed, web browser based \verb|JavaScript| and \verb|WebAssembly| based Ethereum miners, and studying whether or not it is feasible for real world purposes.
-While there has been prior academic work done in related fields, none of the distributed web browser implementations in these works do not involve crypto-currency mining.
-While CoinHive does perform distributed mining using web browsers, it is closed source, and also works with a different crypto-currency (Monero).
-Hence, we are pioneering in offering an open source architecture for mining with web browsers.
-
-% \section{Outline}
-% The remainder of the paper is organized as follows.
-In Section 5 we present a detailed description of the Ethereum mining algorithm and the current state of Ethereum.
-Section 6 describes the Architecture of our implementation of the Distributed Web Browser Miner.
-Section 7 goes over the challenges that we have dealt with during our implementation and their effect on the project.
-Section 8 examines the results of our solution and compares it to current mining data to evaluate the efficacy of our work.
-Finally, in Section 9 we lay out possible future work, and in Section 10 provide conclusions and insight on the project.
 
@@
 % \trishita{Not sure if I need this paragraph, since I think the readers will probably be familiar with what crypto-curriencies are}
-Ethereum is a crypto-currency that was released in July 2015 by Vitalik Buterin, Gavin Wood and Jeffrey Wilcke. Ethereum uses the Ethash algorithm for its PoW, which is discussed below in detail. 
+\subsection{JavaScript and WebAssembly}
+For very long, \verb|JavaScript| has been the only language available to make dynamic client side web content.
+However, the situation has changed since the advent of \verb|WebAssembly| in 2016.
+Per its creators, ``\verb|WebAssembly| is a binary instruction format for a stack-based virtual machine.
+Wasm is designed as a portable target for compilation of high-level languages like \verb|C/C++/Rust|, enabling deployment on the web for client and server applications.
+The \verb|WebAssembly| stack machine is designed to be encoded in a size- and load-time-efficient binary format.
+\verb|WebAssembly| aims to execute at native speed by taking advantage of common hardware capabilities available on a wide range of platforms'' ~\cite{webAssembly}.
+The language is meant to improve performance for computationally intensive use cases such as image/video editing, games, streaming, etc ~\cite{webAssembly}.
+This, and given the fact that CoinHive is also implemented in \verb|WebAssembly| ~\cite{coinhive}, makes the language a natural choice for us to implement a miner in.
+In fact, as of now, \verb|WebAssembly| is supported by 4 major browser versions -- Firefox, Safari, IE, and Chrome ~\cite{webAssembly}, which makes our miner implementation extremely versatile.
+
 % Like most crypto-currencies, it too is backed by a distributed block-chain, each block of which holds transactions for that particular block-chain.
@@
 \subsection{Ethash}
-Ethash is the PoW used for mining blocks in Ethereum.
+Ethereum is a crypto-currency that was released in July 2015 by Vitalik Buterin, Gavin Wood and Jeffrey Wilcke.
+Ethereum uses the Ethash algorithm for its PoW for mining blocks.
 Derived from the Dagger and Hashimoto algorithms ~\cite{dagger-hashimoto}, Ethash operates by first generating a 256 bit seed.
@@
 This process is repeated to generate all nodes in the DAG.
+
 Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128B wide ``Mix'' (another byte array).
@@
 However, if the digest is greater than the threshold, the nonce was unsuccessful, and the entire process must be repeated with a new nonce ~\cite{Ethmining}.
-This procedure for mining is depicted in figure ~\ref{fig:ethash}.
+This procedure for mining is depicted in Figure~\ref{fig:ethash}.
+
 It is important to note that the parts of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence no way to pre-determine which parts will be useful to have in memory.
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 \centering
@@
 
+\subsection{Challenges}
+Given that we now know that the crux of having a good hashrate for Ethereum lies within having quick access to DAG, one of the biggest challenges with mining it on a distributed ensemble of browsers would be to transfer and store this data structure within each worker browser.
+However, given that the DAG for an Ethereum network is at least 1GB (and growing) in size transferring it to the browser every time a client loads our web page would be impractical.
+Furthermore, even if we somehow manage to transfer the DAG to the client when the web page loads, the browser would still have to store it in memory, thereby using a sizeable amount of resources on the client machine.
+We attempt to address some of these concerns through our approach as discussed in the next section.
+
 \section{Our Approach}
@@
 Specifically, as soon as each browser connects to the webserver, the server sends it the current header of the block being mined and the Cache.
-Once the browser receives the Cache, it allocates an array buffer to store the DAG slices that will be computed in the future.
-(Note that the length of the buffer is a variable parameter that we experiment with in our analysis).
-Once this happens, the browser can start iterating over nonces to compute hashes.
+Once the browser receives the Cache, it allocates an array buffer to store the DAG slices that fall between indices 0 and $n$ that will be computed in the future.
+(Note that the $n$ is a variable parameter reflecting the length of the buffer with which we experiment in our analysis).
+Once the buffer is allocated, the browser can start iterating over nonces to compute hashes.
 
@@
 
-\subsection{Information theoretic bounds}
+\subsection{Architecture}
+% \begin{figure}[H]
+% \centering
+% \includegraphics[width=250px,keepaspectratio]{miningpool.png}
+% \caption{\label{fig:miningpool} Distributed Ethereum Mining}
+% \end{figure}
+
+Our architecture was centered around two client-side Ethereum miners written in \verb|JavaScript| and \verb|WebAssembly|.
+The central node that co-ordinates all workers (browsers) was an improvised version of \verb|geth| ~\cite{geth}, a real world Ethereum miner written in \verb|Go|.
+\verb|Geth| typically runs as a standalone miner that mines on the machine it is running.
+We modified it so that instead of mining all by itself, it simply sends over the necessary data needed to mine (the hash of the Block Header and the Cache) to any client that connects to it on port \verb|9000|.
+After recieving the necessary data, the browser allocates a buffer for the DAG in order to store future slices.
+Note that the buffer for the DAG is implemented an array of ints (with a DAG slice being 16 ints long), so as to make each lookup in the buffer $\theta(1)$.
+At this point, it can then begin to search for a solution.
+
+For our miner, we modeled our \verb|JavaScript| implementation based on the ~\verb|node.js| implementation of Ethash ~\cite{ethash}.
+To begin, the miner creates a random nonce and the computes the hash (using the Cache and the buffered DAG) as discussed in the previous section.
+It will continue to perform this action on new nonces until one of two scenarios occur; it finds a nonce such that the computed hash is below the given threshold or the process has timed out.
+In the former case, the browser submits the result back to the node and then asks the node for a new block header and the Cache.
+Otherwise if it has timed out without finding a result, the browser simply polls the node for the current block header and Cache .
+This process will continue until the user moves away from the website or closes their browser.
+We must point out that this time out is necessary since we want the browser to work with the most recent block header and Cache.
+The block header can become stale if that particular block has already been mined, and the Cache can become stale if the Ethereum network transitions into a new Epoch (happens once every 30,000 blocks).
+We must point out that both our current implementations in \verb|JavaScript| and \verb|WebAssembly| require no external dependencies, and therefore can be directly embedded into any website.
+For a diagramatic view our our design, see Figures~\ref{fig:hybridArchitecture}.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=230px,keepaspectratio]{Hybrid-Miner.pdf}
+\caption{\label{fig:hybridArchitecture} Web Miner Architecture}
+\end{figure}
+
+\subsection{Theoretical Analysis}
 With this lazy-evaluation based approach, we can calculate exactly how many hashes we would have to compute in order to fill up a buffer of a given size.
-This is important because once the buffer in the browser fills up, the hashrate that the browser gives becomes steady.
+This is important because once the buffer in the browser fills up, the hash rate that the browser gives becomes steady.
 Hence, calculating the expected number of hashes it takes to fill the buffer allows us to determine how much time will the browser take to reach a steady state hash rate.
 This approach is a variation of the coupon collector problem \cite{couponCollector}, and has been described in the following theorem:
+\trishita{To Do: change these expressions to upper and lower bounds since we are dealing with a truncated summation}
 \begin{theorem}[Expectation of Number of Hashes]
 \label{expectedHashes}\\
-If we define,
-    \[Number\;of\;DAG\;slices\;=\;n\]
-    \[Size\;of\;buffer\;as\;a\;fraction\;of\;the\;total\;DAG\;=\;f_1;\;f_1=[0,1] \]
-    \[Expected\;number\;of\;hashes\;it\;takes\;to\;fill\;the\;buffer\;= E(H)\]
+\makebox[\textwidth][l]{If we define}
+\makebox[\textwidth][c]{Number of DAG slices = n}
+\makebox[\textwidth][c]{Size of buffer as a fraction of the total DAG = $f_1$; $f_1$=[0,1]}
+\makebox[\textwidth][c]{Expected number of hashes it takes to fill the buffer = E(H)} \\
 Then the expected number of hashes $E(H)$ it takes to fill up a buffer of fraction $f_1$ of a DAG with $n$ slices is given by:
@@
 \end{proof}
-Now, let us do a simple calculation for one extreme case, where $f_1 = 1$ (i.e., we allocate a buffer as large as the entire DAG on the browser), in order to get an upper bound on the number of hashes it would take to fill this buffer up.
-The private test network for Ethereum we used had a total of 16777186 slices in the DAG, which means it would take:
-\begin{gather}
-  E(H) = \frac{16777186*\log{16777186}}{64} = 4.36*10^6\;hashes
-\end{gather}
+Now, let us do a simple calculation for one extreme case, where we allocate a buffer as large as the entire DAG on the browser (in order to get an upper bound on the number of hashes it would take to fill this buffer up).
+Here $f_1 = 1$ and $n = 16777186$ (for our private test network), which, using ~\ref{eq:6}, gives us $E(H) = 4.36*10^6$ hashes.
 Hence, it takes around 4 million hashes to fill up a buffer as large as the entire DAG.
@@
 \label{earlyTermination}
-If we define,
-  \[Fraction\;of\;DAG\;buffer\;to\;be\;filled = f_2;\;f_2 \in [0,1]\]
-  Then,
+\makebox[\textwidth][l]{If we define,}
+\makebox[\textwidth][c]{Fraction of DAG buffer to be filled = $f_2$; $f_2$ $\in$ [0,1]}
+\makebox[\textwidth][l]{Then,}
     \begin{gather}
@@
 \begin{proof}
-Then, for a buffer with space for $f_1$ slices, the number of slices we want to fill it with in order for a fraction $f_2$ of it to be full would be: 
-\begin{gather}
-  Number\;of\;slices\;to\;fill\;DAG\;buffer\;with = nf_2f_1
-\end{gather}
+Then, for a buffer with space for $f_1$ slices, the number of slices we want to fill it with in order for a fraction $f_2$ of it to be full would be: \\
+\makebox[\textwidth][c]{Number of slices to fill DAG buffer with = $nf_2f_1$}
 This would modify equation \ref{eq:6} for the expected number of trials to fill up a fraction $f_2$ of the DAG buffer to be as follows:
@@
 \end{proof}
-Interestingly, since for realistic cases $n >> f_1$, $\frac{1}{nf_1} \to 0$, and so 
-\begin{gather}
-E(H) \approx \frac{n}{64}\log{\frac{1}{1-f_2}}
-\end{gather}
-Figure X shows a graph of how $E(H)$ varies as a function of the fraction of the buffer that we want to be full, $f$ if we set $n = 16777186$ (the total number of DAG slices on the experimental private test network).
+Now, using ~\ref{eq:13}, if we set $n = 16777186$, $f_1 = 1$ and $f_2 = 0.95$, we get $E(H) = 785312$ hashes
 
-From figure X we see that even computing merely 800,000 hashes fills our DAG buffer by more than 95\%, as opposed to calculating 4 million to fill the buffer entirely.
+% Interestingly, since for realistic cases $n >> f_1$, $\frac{1}{nf_1} \to 0$, and so 
+% \begin{gather}
+% E(H) \approx \frac{n}{64}\log{\frac{1}{1-f_2}}
+% \end{gather}
+% Figure X shows a graph of how $E(H)$ varies as a function of the fraction of the buffer that we want to be full, $f$ if we set $n = 16777186$ (the total number of DAG slices on the experimental private test network).
+
+Hence, we see that even computing merely 800,000 hashes fills a DAG buffer as large as the entire DAG by more than 95\%, as opposed to calculating 4 million to fill the buffer entirely.
+(Note that this number should be smaller for smaller buffer sizes; so this is again a rough upper bound).
 This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up.
-This also means that reaching a reasonably steady state is not as hard as it seems at face value.
+This also means that reaching a reasonably steady state is not as hard as it seems at face value, making this approach viable.
 Given this result, we compute 800,000 hashes for our experiments.
@@
 
-\section{Architecture}
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{miningpool.png}
-% \caption{\label{fig:miningpool} Distributed Ethereum Mining}
-% \end{figure}
-
-Our architecture was centered around two client-side Ethereum miners written in \verb|JavaScript| and \verb|WebAssembly|.
-The central node that co-ordinates all workers (browsers) was an improvised version of \verb|geth| ~\cite{geth}, a real world Ethereum miner written in \verb|Go|.
-\verb|Geth| typically runs as a standalone miner that mines on the machine it is running.
-We modified it so that instead of mining all by itself, it simply sends over the necessary data needed to mine (the hash of the Block Header and the Cache) to any client that connects to it on port \verb|9000|.
-After recieving the necessary data, the browser allocates a buffer for the DAG in order to store future slices.
-Note that the buffer for the DAG is implemented an array of ints (with a DAG slice being 16 ints long), so as to make each lookup in the buffer $\theta(1)$.
-At this point, it can then begin to search for a solution.
-
-For our miner, we modeled our \verb|JavaScript| implementation based on the ~\verb|node.js| implementation of Ethash ~\cite{ethash}.
-To begin, the miner creates a random nonce and the computes the hash (using the Cache and the buffered DAG) as discussed in the previous section.
-It will continue to perform this action on new nonces until one of two scenarios occur; it finds a nonce such that the computed hash is below the given threshold or the process has timed out.
-In the former case, the browser submits the result back to the node and then asks the node for a new block header and the Cache.
-Otherwise if it has timed out without finding a result, the browser simply polls the node for the current block header and Cache .
-This process will continue until the user moves away from the website or closes their browser.
-We must point out that this time out is necessary since we want the browser to work with the most recent block header and Cache.
-The block header can become stale if that particular block has already been mined, and the Cache can become stale if the Ethereum network transitions into a new Epoch (happens once every 30,000 blocks).
-We must point out that both our current implementations in \verb|JavaScript| and \verb|WebAssembly| require no external dependencies, and therefore can be directly embedded into any website.
-For a diagramatic view our our design, see Figures~\ref{fig:hybridArchitecture}.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=250px,keepaspectratio]{Hybrid-Miner.pdf}
-\caption{\label{fig:hybridArchitecture} Web Miner Architecture}
-\end{figure}
-
 \section{Results}
 \subsection{Experimental set up}
-Our experimental set up consisted of a machine with an Intel i7-7700HQ processor with 4 cores and 16GB ram.
+Our experimental set up consisted of a machine with an Intel i7-7700HQ processor with 8 cores and 16GB ram.
 These results were obtained from a private Ethereum test network at Epoch 0.
-The DAG size was 16777186 slices (with each slice being a sequence of 16 ints).
-The cache size was X.
+The DAG size was 16777186 slices (1.074GB).
+The cache size was 1.677MB.
+We ran the implementations in ~\verb|JavaScript| and ~\verb|WebAssembly| in the browser, and a native miner written in ~\verb|C++| that employs the same approach outside of the browser for control results.
+Each miner was till 800,000 hashes were computed and the hash rate and buffer hit rate were sampled every 10,000 hashes.
+(Note that both the hash rate and buffer hit rate sampled at a particular time reflected the values over the 10,000 most recent hashes).
 
-\subsection{Baseline results}
-For our control results, we ran \verb|Geth|~\cite{geth}, a native miner written in \verb|Go| that stores the entire DAG in memory from the start (as opposed to using this lazy evaluation approach), and obtained an average hashrate of X H/s.
-We also ran our lazy-evaluation based miner written in C++ outside of the browser, and obtained the following results.
-Figure X below shows a heat-map of how the hash rate varies as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.
+% \subsection{Baseline results}
+% For our control results, we ran \verb|Geth|~\cite{geth}, a native miner written in \verb|Go| that stores the entire DAG in memory from the start (as opposed to using this lazy evaluation approach), and obtained an average hashrate of X H/s.
+
+% We also ran our lazy-evaluation based miner written in C++ outside of the browser, and obtained the following results. 
+% Figure X below shows a heat-map of how the hash rate varies as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.
 Figures X then shows a heat-map of how the DAG buffer hit-rate varies as a function of both the size of the buffer allocated to store the DAG and the number of hashes computed in the browser.
@@
 \subsection{Implementation Results}
+Figures~\ref{fig:NativeMinerHM},~\ref{fig:WebAsmMinerHM} and ~\ref{fig:JSMinerHM} below shows a heat-map of how the hash rate varies for each of the three implementations as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.
+% \trishita{To Do: chanege to log scale, fix size }
 
-% This happens because as described before, for the hybrid implementation where we store a small part of the DAG, we had to store the DAG in a \verb|javascript| object (Hash Map), with the ``keys'' being the index of the DAG and the value being the 512 bit slice that corresponds to that index.
-However, key-value look up times with \verb|JavaScript| objects are slow, according to the V8 design documentation for the language: ``Most JavaScript engines use a dictionary-like data structure as storage for object properties - each property access requires a dynamic lookup to resolve the property's location in memory.
-This approach makes accessing properties in JavaScript typically much slower than accessing instance variables in programming languages like Java and Smalltalk.'' ~\cite{AttrLookupLatency} This explains why storing larger and larger chunks of the DAG gives worse Hash rates, since it takes longer and longer to look up the required slices from the Hash Map.
-Indeed, this is why not storing the DAG at all, and just computing the slices from the Cache gives a high hash rate of \~ 1500 hashes/sec.
-The other extreme -- storing the entire DAG in memory is also slow because it takes up a lot of memory on the client's system.
+\begin{figure}[h]
+\centering
+\includegraphics[width=300px,keepaspectratio]{Native_C++_Miner_Hash_Rate_HM.pdf}
+\caption{\label{fig:NativeMinerHM} Native Miner: $\log{Hash Rate}$}
+\end{figure}
 
-Note that this is the computational power of one machine and in reality, there would be hundreds or thousands of machines mining simultaneously, which will be analyzed in the next section.
-In comparison to Monero or Bitcoin browser miners who mine on an average of about 30-60H/s, our hashrate is significantly better than those.
+\begin{figure}[h]
+\centering
+\includegraphics[width=300px,keepaspectratio]{WebAssembly_Miner_Hash_Rate_HM.pdf}
+\caption{\label{fig:WebAsmMinerHM} WebAssembly Miner: $\log{Hash Rate}$}
+\end{figure}
 
-\subsection{Difference Between Baseline and Implementation}
-We see that the average hashrate outperforms.
+\begin{figure}[h]
+\centering
+\includegraphics[width=300px,keepaspectratio]{JavaScript_Miner_Hash_Rate_HM.pdf}
+\caption{\label{fig:JSMinerHM} JavaScript Miner: $\log{Hash Rate}$}
+\end{figure}
+
+% \begin{figure}[!htb]
+% \minipage{\textwidth}
+%   \includegraphics[width=\linewidth]{Native_C++_Miner_Hash_Rate_HM.pdf}
+% \endminipage\hfill
+% \minipage{\textwidth}
+%   \includegraphics[width=\linewidth]{WebAssembly_Miner_Hash_Rate_HM.pdf}
+% \endminipage\hfill
+% \minipage{\textwidth}
+%   \includegraphics[width=\linewidth]{JavaScript_Miner_Hash_Rate_HM.pdf}
+% \endminipage
+% \caption{Hash Rate as a function of number of Hashes computed and Buffer Size}\label{fig:hashRateHM}
+% \end{figure}
+
+It is interesting to see how, for a given number of hashes computed, the hash rate drastically spikes up when the size of the buffer changes from 90\% of the size of the DAG to 100\%.
+This change becomes more apparent as the number of hashes computed increases -- thereby suggesting that accessing DAG slices from the buffer is orders of magnitude faster than computing them, so much so that even a few computations bring down the hash rate drastically.
 
@@
 The only way this could work is by sending over part of the DAG over the network to the client.
-However, as it turns out, this is not feasible since, for a DAG with 16777186 slices (1.074 GB) sending even 10\% of the DAG would be sending \~100MB of data.
-With the global average download speed for desktops and smartphones being around 5.34MBps and 2.77MBps respectively ~\cite{http://www.speedtest.net/global-index}, the load time would be on the order of 20 seconds to a minute -- which is too long a webpage load time for getting a mere 10\% boost in the buffer storage.
+However, as it turns out, this is not feasible since, for a DAG with 16777186 slices (1.074 GB) sending even 10\% of the DAG would be sending $\approx100MB$ of data.
+With the global average download speed for desktops and smartphones being around 5.34MBps and 2.77MBps respectively ~\cite{internetSpeed}, the load time would be on the order of 20 seconds to a minute -- which is too long a webpage load time for getting a mere 10\% boost in the buffer storage.
+
+The jump in the hash rate for high buffer hit rates is also seen in figure ~\ref{fig:bufferRatevsHashRate} where we show the correlations between the buffer hit rates and the hash rates for all 3 miners.
+The general trend is the same for all 3 miners -- the hash rate spikes up as the hit rate reaches 1.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=250px,keepaspectratio]{All_Miners_Hash_Rate.pdf}
+\caption{\label{fig:bufferRatevsHashRate} Buffer Hit Rate vs Hash Rate for all miners}
+\end{figure}
+
+Figure~\ref{fig:bufferRateHM} then shows a heat-map of how the DAG buffer hit-rate varies as a function of both the size of the buffer allocated to store the DAG and the number of hashes computed in the browser.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=300px,keepaspectratio]{All_Miners_Buffer_Hit_Rate_Percent.pdf}
+\caption{\label{fig:bufferRateHM} Buffer Hit Rate}
+\end{figure}
+
+As expected, we see that the hit rate increases both with the size of the Buffer and with the number of hashes computed.
+
+In Figures~\ref{fig:NativeWebAsm},~\ref{fig:WebAsmJS} and~\ref{fig:NativeJS} we show the percentage difference of the hashrates between the native miner and the browser miner implementations.
+We also compare the performance of the ~\verb|JavaScript| and ~\verb|WebAssembly|  miners.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=300px,keepaspectratio]{Native_Miner_vs_WebAssembly_miner_Hash_Rate_Percent_Improvement.pdf}
+\caption{\label{fig:NativeWebAsm} Native miner vs. WebAssembly miner Hash Rate Percent Improvement}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=300px,keepaspectratio]{WebAssembly_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
+\caption{\label{fig:WebAsmJS} WebAssembly miner vs. JavaScript miner Hash Rate Percent Improvement}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=300px,keepaspectratio]{Native_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
+\caption{\label{fig:NativeJS} Native miner vs. JavaScript miner Hash Rate Percent Improvement}
+\end{figure}
+
+% \begin{figure}[!htb]
+% \minipage{0.32\textwidth}
+%   \includegraphics[width=\linewidth]{WebAssembly_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
+% \endminipage\hfill
+% \minipage{0.32\textwidth}
+%   \includegraphics[width=\linewidth]{Native_Miner_vs_WebAssembly_miner_Hash_Rate_Percent_Improvement.pdf}
+% \endminipage\hfill
+% \minipage{0.32\textwidth}
+%   \includegraphics[width=\linewidth]{Native_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
+% \endminipage
+% \caption{Percentage difference in Hash Rates for different miner implementations}\label{fig:PerfChangeHM}
+% \end{figure}
+
+We see that for obvious reasons, the native miner outperforms both the ~\verb|JavaScript| and the ~\verb|WebAssembly| miner.
+However, we see that the ~\verb|WebAssembly| miner is at most X\% slower than the native miner -- which is not very far off considering the overhead of running programs within browsers.
+The ~\verb|JavaScript| miner, on the other hand, is ~\textbf{at least} X\% slower (and at most Y\% slower).
+
+Finally, we tabulate the most important results from our analysis in table ~\ref{table:results}
+\trishita{To Do: Fill in other, meaningful, metrics -- any suggestions?}
+
+\begin{table}[t]
+\caption{Results}\label{table:results}
+\vspace{-2ex}
+\begin{center}
+\begin{tabular}{ c  c  c  c}
+
+&\makecell{\textbf{Native}} & \makecell{\textbf{JavaScript}} & \makecell{\textbf{WebAssembly}}\\
+\cline{2\ -2} \cline{3\ -3} \cline{4\ -4}
+\makecell{Median Hash Rate \\
+(for a buffer the size of the DAG)} &  56800H/s &  10626H/s & 39651H/s \\
+Peak Hash Rate &  56800H/s &  10626H/s & 39651H/s \\
+\makecell{Average Time to reach steady state hash rate \\ (averaged over all buffer sizes)}  &  87\% &  83\% & 4\\ 
+\makecell{Avg. Hash Rate diff with Native Miner \\
+(averaged over all buffer sizes)}&  87\% &  83\% & 4\\
+\end{tabular}
+\end{center}
+\vspace{-3ex}
+\end{table}
+
+% Note that this is the computational power of one machine and in reality, there would be hundreds or thousands of machines mining simultaneously, which will be analyzed in the next section.
+In comparison to Monero or Bitcoin browser miners who mine on an average of about 30-60H/s, our hashrate is significantly better than those.
+
+\section{Conclusion}
+We have successfully created a proof of concept distributed, web-based Ethereum miner that can be used towards monetizing electronic content, web-authentication rate limiting, private test networks, user tracking for advertisers, etc.
+Our implementation is standalone, and hence can simply be embedded within a website without having the client install any external dependencies.
+We get the best steady state hash rates for our \verb|JavaScript| and \verb|WebAssembly| implementations (X and Y respectively) when the cache hit rates approach 1, (which takes approx 800,000 Hashes).
+
+% Furthermore, we provide an API that can be used by any implementation of Ethereum (\verb|geth| or Ethereum's implementation in \verb|C++|).
+We believe this can be a be especially viable in a private testnet, within a company for example, and with further research has the potential to make a real impact.
 
 \section{Future Work}
-
 While we were able to create a browser based miner for Ethereum, there is still work to be done.
@@
 By moving the data closer to the computation we are hoping to cut the added time caused by the network.
-
 Ethereum is also currently working on Casper, their Proof-of-Stake algorithm, which has already been deployed to private testnets for testing.
@@
 Further research will be necessary to determine whether browser mining for Casper is viable or not, as the final form of Casper is still hazy and exactly how much ``stake'' is required to mine is uncertain.
-
-\section{Conclusion}
-We have successfully created a proof of concept distributed, web-based Ethereum miner that can be used towards monetizing electronic content.
-Our implementation is standalone, and hence can simply be embedded within a website without having the client install any external dependencies.
-Furthermore, we provide an API that can be used by any implementation of Ethereum (\verb|geth| or Ethereum's implementation in \verb|C++|).
-We believe this can be a be especially viable in a private testnet, within a company for example, and with further research has the potential to make a real impact.
 
@@
 \bibitem{remote} remoteStorage: An open protocol for per-user storage on the Web. (https://remotestorage.io/)
+
+\bibitem{webAssembly}  W3C Team. WebAssembly. Program documentation. WebAssembly. Vers. 1.0. WebAssembly, 17 Mar. 2017. Web. 28 Mar. 2018. <http://webassembly.org>.
+
+\bibitem{wasmPerf} Zlatkov, Alexander.
+"How JavaScript Works: A Comparison with WebAssembly." SessionStack Blog.
+SessionStack Blog, 21 Nov.
+2017.
+Web.
+28 Mar.
+2018.
+<https://blog.sessionstack.com/how-javascript-works-a-comparison-with-webassembly-why-in-certain-cases-its-better-to-use-it-d80945172d79>.
+
+\bibitem{emscripten} Emscripten Community.
+Emscripten.
+Emscripten.
+Vers.
+1.37.36.
+Emscripten, 11 Nov.
+2012.
+Web.
+28 Mar.
+2018.
+<http://kripken.github.io/emscripten\-site/docs/getting\_started/Tutorial.html>.
+
+\bibitem{internetSpeed} Ookla. “Speedtest Global Index – Monthly Comparisons of Internet Speeds from around the World.” Speedtest Global Index, Ookla, 25 Mar. 2018, www.speedtest.net/global-index.
+\bibitem{hydra}  Fogerlie, Garrett, director.
+Brute Force Website Login Attack Using Hydra - Hack Websites - Cyber Security.
+Brute Force Website Login Attack Using Hydra - Hack Websites - Cyber Security, YouTube, 24 Sept.
+2013, www.youtube.com/watch?v=ZVngjGp-oZo.
+
+\bibitem{burpsuite} Mahmood, Osama.
+“Brute Force Website Login Page Using Burpsuite –.” SecurityTraning, SecurityTraning, 5 Feb.
+2018, securitytraning.com/brute-force-website-login-page-using-burpsuite/.
+
+\bibitem{webLogsManipulation} Fox\-Brewster, Thomas.
+``'Biggest Ad Fraud Ever': Hackers Make \$5M A Day By Faking 300M Video Views.'' Forbes, Forbes Magazine, 20 Dec.
+2016, www.forbes.com/sites/thomasbrewster/2016/12/20/methbot\-biggest\-ad\-fraud\-busted/\#73f089a94899/
+
+\bibitem{couponCollector} Neal, Peter. ``The Generalised Coupon Collector Problem.'' Journal of Applied Probability, vol. 45, no. 3, 2008, pp. 621\-629., doi:10.1239/jap/1222441818.
 \end{thebibliography}

### 2018-04-02 paper/paper.tex
changed paper and figs

@@
 Our research involves providing implementations of a distributed, web browser based Ethereum miners in \verb|JavaScript| and \verb|WebAssembly|, and studying whether or not it is feasible for real world purposes.
-While there has been prior academic work done in related fields, none of the distributed web browser implementations in these works do not involve crypto-currency mining.
+While there has been prior academic work done in related fields, none of the distributed web browser implementations in these works involve crypto-currency mining.
 While CoinHive does perform distributed mining using web browsers, it is closed source, and also works with a different crypto-currency (Monero).
-Hence, we are pioneering in offering an open source architecture for Ethereum mining with web browsers.
+Hence, we are pioneers in offering an open source architecture for Ethereum mining with web browsers.
 Our miner gives us a hashrate of about 39kH/s, which, given the flexibility of the Ethereum framework, is useful and practical for many applications like web authentication rate limiting, website usage tracking for advertisement companies, private Ethereum networks, web content monetization, as discussed below.
@@
 Another potential application could involve web-authentication rate limiting.
-Given the multitude of tools available brute forcing web login pages ~\cite{hydra} ~\cite{burpsuite}, it is painfully easy to brute force authentication pages these days.
+Given the multitude of tools available brute forcing web login pages ~\cite{hydra} ~\cite{burpsuite}, it is extremely easy to brute force authentication pages these days.
 Currently, the way website owners mitigate this issue is by locking out a user for a certain amount of time after a fixed number of unsuccessful login attempts.
@@
 This would be extremely difficult for the website owners to fake since they would have to compute hashes themselves, an endeavor that might be more expensive than the corresponding payout it would bring.\\ \\
-Finally, we would also like to note that Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- i.e., networks that do not on mine the actual, public Ethereum block-chain, but rather on private (and often smaller) instances of the crypto-currency.
+Finally, we would also like to note that Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- i.e., networks that do not mine on the actual, public Ethereum block-chain, but rather on private (and often smaller) instances of the crypto-currency.
 Our browser miner can be used on any such private network to serve the network owner whatever he/she wishes to implement with the mining PoW.
@@
 However, the situation has changed since the advent of \verb|WebAssembly| in 2016.
-Per its creators, ``\verb|WebAssembly| is a binary instruction format for a stack-based virtual machine.
+As per its creators, ``\verb|WebAssembly| is a binary instruction format for a stack-based virtual machine.
 Wasm is designed as a portable target for compilation of high-level languages like \verb|C/C++/Rust|, enabling deployment on the web for client and server applications.
@@
 Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128B wide ``Mix'' (another byte array).
-The Mix is then used to fetch a specific slice of the DAG from memory.
-(Each slice is 512 bits long, or 16 4 byte integers) After this, the Mix is updated with the fetched part of the DAG.
+The Mix is then used to fetch a specific page of the DAG from memory.
+(Each page of the DAG 2 slices long, and each slice in turn is 64 Bytes long) After this, the Mix is updated with the fetched part of the DAG.
 Then, this updated Mix is used to fetch a new part of the DAG.
@@
 This digest is then compared to the threshold, and if it is lesser than it, the nonce is valid and the block is successfully mined and can be broadcast to the network.
-However, if the digest is greater than the threshold, the nonce was unsuccessful, and the entire process must be repeated with a new nonce ~\cite{Ethmining}.
+However, if the digest is greater than the threshold, the nonce is unsuccessful, and the entire process must be repeated with a new nonce ~\cite{Ethmining}.
 This procedure for mining is depicted in Figure~\ref{fig:ethash}.
 
-It is important to note that the parts of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence no way to pre-determine which parts will be useful to have in memory.
-Hence this forces miners to store entire DAG in memory, making mining ``Memory Hard''.
+It is important to note that the parts of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence there is no way to pre-determine which parts will be useful to have in memory.
+This therefore forces miners to store entire DAG in memory, making mining ``Memory Hard''.
 This is intended to even the playing field, as ASIC miners no longer have any advantage as they do for Bitcoin.
@@
 Hence, the Cache is used to regenerate only the specific slices of the DAG that are needed to recalculate the hash for the particular nonce.
-And so only the Cache needs to be stored by clients that just perform verification.
+And so only the Cache needs to be stored by clients that perform just verification.
 We use this property of being able to generate the parts of the DAG as needed to our advantage in order to alleviate some of the memory and network bandwidth restrictions that browsers typically face.
 
-As time goes on, mining Ethereum becomes more and more difficult, as the size of the DAG and Cache used for the Ethereum increases every Epoch.
+As time goes on, mining Ethereum becomes more and more difficult, as the size of the DAG and Cache increases with every Epoch.
 Currently the DAG is more than 2GB in size, causing many GPU miners with cards of 2GB of memory to suffer in terms of hashrate.
@@
 For a normal Ethereum miner to function, the current block headers and the DAG are required to even begin mining.
-As we simply cannot afford to transfer the entire DAG to the browser and store it in memory, we propose an an alternative approach addresses some of these concerns.
+As we simply cannot afford to transfer the entire DAG to the browser and store it in memory, we propose an an alternative approach to address some of these concerns.
 
@@
 \centering
-\includegraphics[width=300px,keepaspectratio]{ethash_algorithm.png}
+\includegraphics[width=300px,keepaspectratio]{Ethash.pdf}
 \caption{\label{fig:ethash} Ethash}
@@
 \subsection{Challenges}
-Given that we now know that the crux of having a good hashrate for Ethereum lies within having quick access to DAG, one of the biggest challenges with mining it on a distributed ensemble of browsers would be to transfer and store this data structure within each worker browser.
+\trishita{Too long of a sentence; need to reword}Given that we now know that the crux of having a good hashrate for Ethereum lies in having quick access to the DAG, one of the biggest challenges with mining it on a distributed ensemble of browsers would be to transfer and store this data structure within each worker browser.
 However, given that the DAG for an Ethereum network is at least 1GB (and growing) in size transferring it to the browser every time a client loads our web page would be impractical.
@@
 \section{Our Approach}
-We propose a lazy-evaluation based approach to alleviate the network and memory requirements for mining ethereum in a distributed scenario on browsers.
+We propose a lazy-evaluation based approach to alleviate the network and memory requirements for mining Ethereum in a distributed scenario on browsers.
 Specifically, as soon as each browser connects to the webserver, the server sends it the current header of the block being mined and the Cache.
@@
 After recieving the necessary data, the browser allocates a buffer for the DAG in order to store future slices.
-Note that the buffer for the DAG is implemented an array of ints (with a DAG slice being 16 ints long), so as to make each lookup in the buffer $\theta(1)$.
+Note that the buffer for the DAG is implemented as an array of ints (with a DAG slice being 16 ints long), so as to make each lookup in the buffer $\theta(1)$.
 At this point, it can then begin to search for a solution.
@@
 For our miner, we modeled our \verb|JavaScript| implementation based on the ~\verb|node.js| implementation of Ethash ~\cite{ethash}.
-To begin, the miner creates a random nonce and the computes the hash (using the Cache and the buffered DAG) as discussed in the previous section.
+To begin, the miner creates a random nonce and computes the hash (using the Cache and the buffered DAG) as discussed in the previous section.
 It will continue to perform this action on new nonces until one of two scenarios occur; it finds a nonce such that the computed hash is below the given threshold or the process has timed out.
@@
 With this lazy-evaluation based approach, we can calculate exactly how many hashes we would have to compute in order to fill up a buffer of a given size.
-This is important because once the buffer in the browser fills up, the hash rate that the browser gives becomes steady.
-Hence, calculating the expected number of hashes it takes to fill the buffer allows us to determine how much time will the browser take to reach a steady state hash rate.
-This approach is a variation of the coupon collector problem \cite{couponCollector}, and has been described in the following theorem:
-\trishita{To Do: change these expressions to upper and lower bounds since we are dealing with a truncated summation}
-\begin{theorem}[Expectation of Number of Hashes]
-\label{expectedHashes}\\
+This is important because once the buffer in the browser fills up, the hash rate that the browser gives is at its maximum, steady-state.
+In this section, we will mathematically demonstrate that filling a buffer the size of the DAG up should take at most 4.5 million hashes, while filling up 95\% of this buffer takes merely 800k hashes.
+This is a significant difference since in our experimental set-up, the browser takes X s to compute 4.5 million hashes, while only Y s to compute 800k hashes.
+The approach we take is similar to the Coupon Collector problem \cite{couponCollector}, and is discussed below:
+% \begin{theorem}[Expectation of Number of Hashes]
+% \label{expectedHashes}\\
 \makebox[\textwidth][l]{If we define}
@@
 \makebox[\textwidth][c]{Size of buffer as a fraction of the total DAG = $f_1$; $f_1$=[0,1]}
-\makebox[\textwidth][c]{Expected number of hashes it takes to fill the buffer = E(H)} \\
-Then the expected number of hashes $E(H)$ it takes to fill up a buffer of fraction $f_1$ of a DAG with $n$ slices is given by:
+\makebox[\textwidth][c]{Expected number of hashes it takes to fill the buffer = E(H)}
+\makebox[\textwidth][c]{nth Harmonic Number = $H_n$}
+\makebox[\textwidth][c]{Euler-Mascheroni constant = $\gamma = 0.57721566...$}
+\makebox[\textwidth][c]{Probability of obtaining a new slice after having buffered x slices = $P_x = \frac{nf_1-x}{n}$}
+\makebox[\textwidth][c]{Expected number of trials $t_x$ to get a new slice after having seen} 
+\makebox[\textwidth][c]{$x$ out of $nf_1$ slices = 
+$E(t_x) = \frac{1}{P_x} = \frac{n}{nf_1-x}$}
+\makebox[\textwidth][c]{Expected number of trials it would take to see all $x$ slices = $E(t)$}
+Note that for simplification, we assume that the DAG is randomly sampled in order to compute hashes.
+In reality, this is not entirely true and hence the results we obtain from this analysis are more conservative than what we see in practice.
+In fact, while we show here that filling up 95\% of a buffer as big as the DAG takes 800k hashes, whereas in reality it only takes half as many hashes~\ref{section:Results} \\
+% ~\trishita{add reference to results}
+From the Coupon Collector Problem~\cite{couponCollector}, it follows that:
 \begin{gather}
-E(H) = \frac{n\log{nf_1}}{64}
+E(t) = \sum_{x=0}^{nf_1-1}E(t_x) = \sum_{x=0}^{nf_1-1}\frac{1}{P_x} = n\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x} = nH_{nf_1}
 \end{gather}
-\end{theorem}
-\begin{proof}
-Let us assume we have a buffer for our DAG that is $f_1$ as large as the entire DAG -- i.e., the buffer can only store dag slices with indices $i$ such that $i \in [0,nf_1]$.
+
+It then follows from bounds on the nth Harmonic Number~\cite{harmonicNumber} that the expected number of hashes $E(H)$ it takes to fill up a buffer of fraction $f_1$ of a DAG with $n$ slices is bounded by:
+\begin{gather}
+\frac{n}{64}[\ln{nf_1} + \frac{1}{2nf_1} + \gamma - \frac{1}{12({nf_1})^2+2\frac{7-12\gamma}{2\gamma - 1}}] <= E(H) \\ E(H)< \frac{n}{64}[\ln{nf_1} + \frac{1}{2nf_1} + \gamma - \frac{1}{12({nf_1})^2+\frac{6}{5}}]
+\end{gather}
+
+% this was the proof for the expression above
+% % \end{theorem}
+% % \begin{proof}
+% Let us assume we have a buffer for our DAG that is $f_1$ as large as the entire DAG -- i.e., the buffer can only store dag slices with indices $i$ such that $i \in [0,nf_1]$.
 Hence, each time we calculate a DAG slice from the Cache, we may or may not buffer it depending on whether it falls within the index rage.
 Now, let us assume that  we have buffered $x$ slices so far, the probability of obtaining a new slice is given by:
-\begin{gather}
-	P_x = \frac{nf_1-x}{n}
-\end{gather}
-The event of obtaining a new slice after having already collected $x$ out of the $nf_1$ slices that can be buffered can be modeled as a geometric distribution.
+% \begin{gather}
+% 	P_x = \frac{nf_1-x}{n}
+% \end{gather}
+% The event of obtaining a new slice after having already collected $x$ out of the $nf_1$ slices that can be buffered can be modeled as a geometric distribution.
 Hence, the expected number of trials $t_x$ it takes to get a new  slice after having seen $x$ out of the $nf_1$ slices is:
-\begin{gather}
-	E(t_x) = \frac{1}{P_x} = \frac{n}{nf_1-x}
-\end{gather}
-By linearity of expectation, the total number of trials it would take to see all $x$ slices is:
-\begin{gather}
-	E(t) = \sum_{x=0}^{nf_1-1}E(t_x) = \sum_{x=0}^{nf_1-1}P_x = \sum_{x=0}^{nf_1-1}\frac{n}{nf_1-x} = n\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x}
-\end{gather}
-Since the summation represents the harmonic series, the expected value can be approximated as follows:
-\begin{gather}
-	E(t) = n\log{nf_1}
-\end{gather}
-Equation ~\ref{eq:7} is in terms of the number of individual accesses of the DAG.
+% \begin{gather}
+% 	E(t_x) = \frac{1}{P_x} = \frac{n}{nf_1-x}
+% \end{gather}
+% By linearity of expectation, the total number of trials it would take to see all $x$ slices is:
+% \begin{gather}
+% 	E(t) = \sum_{x=0}^{nf_1-1}E(t_x) = \sum_{x=0}^{nf_1-1}P_x = \sum_{x=0}^{nf_1-1}\frac{n}{nf_1-x} = n\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x}
+% \end{gather}
+% Since the summation represents the harmonic series, the expected value can be approximated as follows:
+% \begin{gather}
+% 	E(t) = n\log{nf_1}
+% \end{gather}
+% Equation ~\ref{eq:7} is in terms of the number of individual accesses of the DAG.
 In order to get the expected number of Hashes (as opposed to the expected number of individual DAG slice accesses), we need to divide by 64 since each hash involves 64 accesses of the DAG.
 Hence:
-\begin{gather}
-	E(H) = \frac{E(t)}{64} = \frac{n\log{nf_1}}{64}
-\end{gather}
-\end{proof}
-Now, let us do a simple calculation for one extreme case, where we allocate a buffer as large as the entire DAG on the browser (in order to get an upper bound on the number of hashes it would take to fill this buffer up).
-Here $f_1 = 1$ and $n = 16777186$ (for our private test network), which, using ~\ref{eq:6}, gives us $E(H) = 4.36*10^6$ hashes.
-Hence, it takes around 4 million hashes to fill up a buffer as large as the entire DAG.
-If $f_1 < 1$, the number of hashes should be less than 4 million.
-So effectively, 4 million hashes is a very lose upper bound on the number of hashes needed to fill up a DAG buffer.
-However, since 4 million hashes can be a lot for a browser, we will now demonstrate how we can get away with  better
+% \begin{gather}
+% 	E(H) = \frac{E(t)}{64} = \frac{n\log{nf_1}}{64}
+% \end{gather}
+% \end{proof}
 
-Now let us say that we do not want to wait for the entire buffer to fill up -- how many hashes would we have to compute until a reasonable fraction of the buffer is full?
+The factor of 64 comes from the fact that calculating each hash requires sampling the DAG 64 times.
+Given this, let us do a simple calculation for one extreme case, where we allocate a buffer as large as the entire DAG on the browser (in order to get an upper bound on the number of hashes it would take to fill this buffer up).
+Here $f_1 = 1$ and $n = 16777186$ (for our private test network), which, using ~\ref{eq:6}, gives us $4512210 < E(H) <= 4512210$ hashes.
+Hence, it takes around 4.5 million hashes to fill up a buffer as large as the entire DAG.
+If $f_1 < 1$, the number of hashes should be less than 4.5 million, thus making it a very loose upper bound on the number of hashes needed to fill up a DAG buffer (and thereby reaching a steady-state hash rate).
+% \trishita{To Do: reword the next two sentences to motivate the analysis that follows}
+In practice, however, we do not need to wait till the buffer is \emph{completely} full till we see good hash rates.
+We will demonstrate how we can get away with a much smaller number of hashes to fill up \emph{almost all} of the buffer, thereby reaching very good hash rates relatively quickly.
+% lower bound (python exp): (n/64.0)*(log(n) + 1.0/(2*n) + g - 1.0/(12*(n**2) + (2*(7-12*g)/(2*g-1))))
+% upper bound (python exp): (n/64.0)*(log(n) + 1.0/(2*n) + g - 1.0/(12*(n**2) + 6.0/5))
+
+% Now let us say that we do not want to wait for the entire buffer to fill up -- how many hashes would we have to compute until a reasonable fraction of the buffer is full?
 For this, we have the following corollary:
-\begin{corollary}
-\label{earlyTermination}
-\makebox[\textwidth][l]{If we define,}
+% \begin{corollary}
+% \label{earlyTermination}
+\makebox[\textwidth][l]{If we further define,}
 \makebox[\textwidth][c]{Fraction of DAG buffer to be filled = $f_2$; $f_2$ $\in$ [0,1]}
+\makebox[\textwidth][c]{$x  = E(H) - \frac{n}{64}\ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} - \frac{1}{128f_1} + \frac{n}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}}$}
 \makebox[\textwidth][l]{Then,}
     \begin{gather}
-		E(H) = \frac{n}{64}\log{\frac{1}{1-f_2-\frac{1}{nf_1}}}
+   \frac{n}{768({nf_1 - nf_2f_1 - 1})^2+128\frac{7-12\gamma}{2\gamma - 1}} - \frac{1}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} < x \\
+   x <= \frac{n}{768({nf_1-nf_2f_1-1})^2+\frac{6}{5}} - \frac{n}{12({nf_1})^128+\frac{6}{5}} 
 	\end{gather}
-\end{corollary}
-\begin{proof}
+% \end{corollary}
+% \begin{proof}
 Then, for a buffer with space for $f_1$ slices, the number of slices we want to fill it with in order for a fraction $f_2$ of it to be full would be: \\
 \makebox[\textwidth][c]{Number of slices to fill DAG buffer with = $nf_2f_1$}
-This would modify equation \ref{eq:6} for the expected number of trials to fill up a fraction $f_2$ of the DAG buffer to be as follows:
+This would modify equation \ref{eq:6} for the expected number of trials as follows:
 \begin{gather}
-    E(t) = \sum_{x=0}^{nf_2f_1}P_x = \sum_{x=0}^{nf_2f_1}\frac{n}{nf_1-x} = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x}
+    E(t) = \sum_{x=0}^{nf_2f_1}\frac{1}{P_x} = \sum_{x=0}^{nf_2f_1}\frac{n}{nf_1-x} = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x}
 \end{gather}
@@
 \begin{gather}
-    E(t) = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x} = n(\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x} - \sum_{x=nf_2f_1+1}^{nf_1-1}\frac{1}{nf_1-x})\\
-    E(t) = n(\log{nf_1} - \log{(nf_1-nf_2f_1-1)}) \\
-    E(t) = n\log{\frac{1}{1-f_2-\frac{1}{nf_1}}}
+    E(t) = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x} = n(\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x} - \sum_{x=nf_2f_1+1}^{nf_1-1}\frac{1}{nf_1-x}) \\
+    E(t) = n[H_{nf_1} - H_{nf_1 - nf_2f_1 - 1}]\\
 \end{gather}
-Again, we divide by 64 to obtain the expected number of hash computations:
+Again, using the bounds on the nth Harmonic Number~\cite{harmonicNumber}, substituting $\frac{E(t)}{64} = E(H)$ and $x$, and simplifying, we get the following: \\
+\makebox[\textwidth][l]{Let}
 \begin{gather}
-    E(H) = \frac{n}{64}\log{\frac{1}{1-f_2-\frac{1}{nf_1}}}
+% 	n[
+%     \ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} + \frac{1}{2nf_1} - \frac{1}{12({nf_1})^2+2\frac{7-12\gamma}{2\gamma - 1}} \\ - \frac{1}{2(nf_1 - nf_2f_1 - 1)} + \frac{1}{12({nf_1 - nf_2f_1 - 1})^2+2\frac{7-12\gamma}{2\gamma - 1}}] < E(t) \\
+%     E(t) <= n(\ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} + \frac{1}{2nf_1} - \frac{1}{12({nf_1})^2+\frac{6}{5}} \\
+%     - \frac{1}{2(nf_1-nf_2f_1-1)} + \frac{1}{12({nf_1-nf_2f_1-1})^2+\frac{6}{5}}) \\
+%     x  = E(H) - \frac{n}{64}\ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} - \frac{1}{128f_1} + \frac{n}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} \\
+   \frac{n}{768({nf_1 - nf_2f_1 - 1})^2+128\frac{7-12\gamma}{2\gamma - 1}} - \frac{1}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} < x \\
+   x <= \frac{n}{768({nf_1-nf_2f_1-1})^2+\frac{6}{5}} - \frac{n}{12({nf_1})^128+\frac{6}{5}} 
 \end{gather}    
-\end{proof}
+%     \ln{()}) \\
+%     E(t) = n\log{\frac{1}{1-f_2-\frac{1}{nf_1}}}
+
+% Again, we divide by 64 to obtain the expected number of hash computations:
+% \begin{gather}
+%     E(H) = \frac{n}{64}\log{\frac{1}{1-f_2-\frac{1}{nf_1}}}
+% \end{gather}
+% \end{proof}
 Now, using ~\ref{eq:13}, if we set $n = 16777186$, $f_1 = 1$ and $f_2 = 0.95$, we get $E(H) = 785312$ hashes
@@
 
-Hence, we see that even computing merely 800,000 hashes fills a DAG buffer as large as the entire DAG by more than 95\%, as opposed to calculating 4 million to fill the buffer entirely.
+Hence, we see that even computing merely 800k hashes fills a DAG buffer as large as the entire DAG by more than 95\%, as opposed to calculating 4.5 million to fill the buffer entirely.
 (Note that this number should be smaller for smaller buffer sizes; so this is again a rough upper bound).
 This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up.
-This also means that reaching a reasonably steady state is not as hard as it seems at face value, making this approach viable.
-Given this result, we compute 800,000 hashes for our experiments.
+In fact, as we will see in the results, filling up 95\% of a buffer as large as the DAG already starts giving us good hash rates for a browser (10kH/s).
+This means that reaching a reasonably steady state is not as hard as it seems at face value, making this approach viable for web setting where users might not stay on websites for long.
+Given this result, we compute 800k hashes for all our experiments, as discussed in the next section.
 % Beyond that, the marginal cost of computing more hashes outweighs the rate at which the DAG is filled up. Hence, as we will see in the next section, for our experiments, we compute 800,000 hashes.
@@
 We ran the implementations in ~\verb|JavaScript| and ~\verb|WebAssembly| in the browser, and a native miner written in ~\verb|C++| that employs the same approach outside of the browser for control results.
-Each miner was till 800,000 hashes were computed and the hash rate and buffer hit rate were sampled every 10,000 hashes.
+Each miner was run till 800,000 hashes were computed and the hash rate and buffer hit rate were sampled every 10,000 hashes.
 (Note that both the hash rate and buffer hit rate sampled at a particular time reflected the values over the 10,000 most recent hashes).
@@
 \centering
-\includegraphics[width=300px,keepaspectratio]{Native_C++_Miner_Hash_Rate_HM.pdf}
+\includegraphics[width=250px,keepaspectratio]{Native_C++_Miner_Hash_Rate_HM.pdf}
 \caption{\label{fig:NativeMinerHM} Native Miner: $\log{Hash Rate}$}
@@
 \centering
-\includegraphics[width=300px,keepaspectratio]{WebAssembly_Miner_Hash_Rate_HM.pdf}
+\includegraphics[width=250px,keepaspectratio]{WebAssembly_Miner_Hash_Rate_HM.pdf}
 \caption{\label{fig:WebAsmMinerHM} WebAssembly Miner: $\log{Hash Rate}$}
@@
 \centering
-\includegraphics[width=300px,keepaspectratio]{JavaScript_Miner_Hash_Rate_HM.pdf}
+\includegraphics[width=250px,keepaspectratio]{JavaScript_Miner_Hash_Rate_HM.pdf}
 \caption{\label{fig:JSMinerHM} JavaScript Miner: $\log{Hash Rate}$}
@@
 However, as it turns out, this is not feasible since, for a DAG with 16777186 slices (1.074 GB) sending even 10\% of the DAG would be sending $\approx100MB$ of data.
-With the global average download speed for desktops and smartphones being around 5.34MBps and 2.77MBps respectively ~\cite{internetSpeed}, the load time would be on the order of 20 seconds to a minute -- which is too long a webpage load time for getting a mere 10\% boost in the buffer storage.
+With the global average download speed for desktops and smartphones being around 5.34MBps and 2.77MBps respectively ~\cite{internetSpeed}, the web page load time would be in the order of 20 seconds to a minute -- which is too long to get a mere 10\% boost in the buffer storage.
 
 The jump in the hash rate for high buffer hit rates is also seen in figure ~\ref{fig:bufferRatevsHashRate} where we show the correlations between the buffer hit rates and the hash rates for all 3 miners.
-The general trend is the same for all 3 miners -- the hash rate spikes up as the hit rate reaches 1.
+The general trend is the same for all 3 miners -- the hash rate spikes up as the hit rate surpasses 95\% (Note that the hit rate gets extremely close to 1 but never quite reaches there, since we only compute 800k hashes as opposed to the 4.5 million would be needed as per our theoretical analysis).
 
@@
 \centering
-\includegraphics[width=300px,keepaspectratio]{All_Miners_Buffer_Hit_Rate_Percent.pdf}
+\includegraphics[width=250px,keepaspectratio]{All_Miners_Buffer_Hit_Rate.pdf}
 \caption{\label{fig:bufferRateHM} Buffer Hit Rate}
@@
 
+\trishita{Might want to get rid of figs 8 9 and 10 since we don't have much room}
 In Figures~\ref{fig:NativeWebAsm},~\ref{fig:WebAsmJS} and~\ref{fig:NativeJS} we show the percentage difference of the hashrates between the native miner and the browser miner implementations.
@@
 \centering
-\includegraphics[width=300px,keepaspectratio]{Native_Miner_vs_WebAssembly_miner_Hash_Rate_Percent_Improvement.pdf}
+\includegraphics[width=250px,keepaspectratio]{Native_Miner_vs_WebAssembly_miner_Hash_Rate_Percent_Improvement.pdf}
 \caption{\label{fig:NativeWebAsm} Native miner vs. WebAssembly miner Hash Rate Percent Improvement}
@@
 \centering
-\includegraphics[width=300px,keepaspectratio]{WebAssembly_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
+\includegraphics[width=250px,keepaspectratio]{WebAssembly_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
 \caption{\label{fig:WebAsmJS} WebAssembly miner vs. JavaScript miner Hash Rate Percent Improvement}
@@
 \centering
-\includegraphics[width=300px,keepaspectratio]{Native_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
+\includegraphics[width=250px,keepaspectratio]{Native_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
 \caption{\label{fig:NativeJS} Native miner vs. JavaScript miner Hash Rate Percent Improvement}
@@
 We see that for obvious reasons, the native miner outperforms both the ~\verb|JavaScript| and the ~\verb|WebAssembly| miner.
-However, we see that the ~\verb|WebAssembly| miner is at most X\% slower than the native miner -- which is not very far off considering the overhead of running programs within browsers.
-The ~\verb|JavaScript| miner, on the other hand, is ~\textbf{at least} X\% slower (and at most Y\% slower).
+However, we see that the ~\verb|WebAssembly| miner is at most 40\% slower than the native miner -- which is not very far off considering the overhead of running programs within browsers.
+The ~\verb|JavaScript| miner, on the other hand, is ~\textbf{at least} 47\% slower (and at most 82\% slower).
 
@@
 \makecell{Median Hash Rate \\
-(for a buffer the size of the DAG)} &  56800H/s &  10626H/s & 39651H/s \\
+(for a buffer the size of the DAG)} & 15278H/s &  5290H/s & 10504H/s \\
 Peak Hash Rate &  56800H/s &  10626H/s & 39651H/s \\
-\makecell{Average Time to reach steady state hash rate \\ (averaged over all buffer sizes)}  &  87\% &  83\% & 4\\ 
-\makecell{Avg. Hash Rate diff with Native Miner \\
-(averaged over all buffer sizes)}&  87\% &  83\% & 4\\
+\makecell{Maximum Time to reach steady state hash rate \\ (buffer as large as DAG)}  &  X s &  X s & X s\\ 
+\makecell{Avg. Hash Rate \% diff with Native Miner \\
+(averaged over all buffer sizes)}&  NA &  56\% & 36\%\\
 \end{tabular}
@@
 Our implementation is standalone, and hence can simply be embedded within a website without having the client install any external dependencies.
-We get the best steady state hash rates for our \verb|JavaScript| and \verb|WebAssembly| implementations (X and Y respectively) when the cache hit rates approach 1, (which takes approx 800,000 Hashes).
+We get the best steady state hash rates for our \verb|JavaScript| and \verb|WebAssembly| implementations (10.6k and 39.6k respectively) when the cache hit rates approach 1, (which takes approx 800k Hashes).
 
@@
 \bibitem{couponCollector} Neal, Peter. ``The Generalised Coupon Collector Problem.'' Journal of Applied Probability, vol. 45, no. 3, 2008, pp. 621\-629., doi:10.1239/jap/1222441818.
+\bibitem{harmonicNumber} Guo, Bai-Ni \& Qi, Feng. (2011). Sharp bounds for harmonic numbers. Applied Mathematics and Computation. 218. 991-. 10.1016/j.amc.2011.01.089.
 \end{thebibliography}

### 2018-04-02 paper/grapher.py

@@ -3,6 +3,13 @@
 import matplotlib.pyplot as plt
 import numpy as np
 import math
+import matplotlib
+
+font = {'family' : 'normal',
+        'weight' : 'bold',
+        'size'   : 55}
+
+matplotlib.rc('font', **font)
 
 n = 16777186
 
@@ -105,40 +112,45 @@ def fill_partial_buf():
 
 
 def miner_res(title,cache_hit,hash_rate,label=None):
-	# # log_hash_rate = [[math.log(i) for i in row] for row in hash_rate]
-	# plt.imshow(hash_rate,origin='lower', cmap='seismic',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=70000)
-	# plt.colorbar()
+	# log_hash_rate = [[math.log(i) for i in row] for row in hash_rate]
+	# plt.imshow(log_hash_rate,origin='lower', cmap='gist_ncar',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=math.log(70000))
+	# # ax = plt.gca()
+	# # divider = make_axes_locatable(ax)
+	# # cax = divider.append_axes("right", size="5%", pad=0.05)
+	# plt.colorbar(fraction=0.046, pad=0.04)
 	# plt.ylabel('Buffer Size as a fraction of DAG')
 	# plt.xlabel('Hashes Computed (in thousands)')
-	# plt.title(title + " Log(Hash Rate)")
-	# # plt.show()
-	# plt.savefig(title + " Hash Rate.pdf", bbox_inches='tight')
-
-	# plt.imshow(cache_hit,origin='lower', cmap='seismic',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
-	# plt.colorbar()
-	# plt.ylabel('Buffer Size as a fraction of DAG')
-	# plt.xlabel('Hashes Computed (in thousands)')
-	# plt.title(title + " Buffer Hit Rate Percent")
+	# # plt.title(title + " Log(Hash Rate)")
+	# print title + " Hash Rate HM.pdf"
 	# plt.show()
+	# plt.savefig(title + " Hash Rate HM.pdf",bbox_inches='tight')
+
+	plt.imshow(cache_hit,origin='lower', cmap='gist_ncar',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
[…]

### 2018-04-03 paper/paper.tex
simplified the math

@@
 This is a significant difference since in our experimental set-up, the browser takes X s to compute 4.5 million hashes, while only Y s to compute 800k hashes.
-The approach we take is similar to the Coupon Collector problem \cite{couponCollector}, and is discussed below:
-% \begin{theorem}[Expectation of Number of Hashes]
-% \label{expectedHashes}\\
-\makebox[\textwidth][l]{If we define}
-\makebox[\textwidth][c]{Number of DAG slices = n}
-\makebox[\textwidth][c]{Size of buffer as a fraction of the total DAG = $f_1$; $f_1$=[0,1]}
-\makebox[\textwidth][c]{Expected number of hashes it takes to fill the buffer = E(H)}
-\makebox[\textwidth][c]{nth Harmonic Number = $H_n$}
-\makebox[\textwidth][c]{Euler-Mascheroni constant = $\gamma = 0.57721566...$}
-\makebox[\textwidth][c]{Probability of obtaining a new slice after having buffered x slices = $P_x = \frac{nf_1-x}{n}$}
-\makebox[\textwidth][c]{Expected number of trials $t_x$ to get a new slice after having seen} 
-\makebox[\textwidth][c]{$x$ out of $nf_1$ slices = 
-$E(t_x) = \frac{1}{P_x} = \frac{n}{nf_1-x}$}
-\makebox[\textwidth][c]{Expected number of trials it would take to see all $x$ slices = $E(t)$}
+The approach we take is similar to the Coupon Collector problem \cite{couponCollector}, and is discussed below.
 Note that for simplification, we assume that the DAG is randomly sampled in order to compute hashes.
@@
 In fact, while we show here that filling up 95\% of a buffer as big as the DAG takes 800k hashes, whereas in reality it only takes half as many hashes~\ref{section:Results} \\
-% ~\trishita{add reference to results}
-From the Coupon Collector Problem~\cite{couponCollector}, it follows that:
+
+\makebox[\textwidth][l]{If we define}
+\makebox[\textwidth][c]{Number of DAG slices = N}
+\makebox[\textwidth][c]{Fraction of the DAG we want to buffer = $f_1$}
+\makebox[\textwidth][c]{Number of DAG slices needed to compute a single hash = a}
+\makebox[\textwidth][c]{Failure probability of finding a specific slice in the buffer (Buffer miss rate)= $\delta$}
+% \makebox[\textwidth][c]{Failure probability of computing a hash just using slices in the buffer = $\omega$}
+\makebox[\textwidth][c]{nth Harmonic Number = $H_n$}
+% \makebox[\textwidth][c]{Euler-Mascheroni constant = $\gamma = 0.57721566...$}
+% \makebox[\textwidth][c]{Expected number of hashes it takes to fill the buffer = E(H)}
+% \begin{gather}\label{eq:slicevshash}
+% 	(1-\delta)^a = 1-a\delta;\;\delta \to 0 %1-\omega
+% \end{gather}
+% \makebox[\textwidth][l]{When $\delta \to 0$, equation \ref{eq:slicevshash} can be re-written as}
+% \begin{gather}
+% 	1-a\delta = 1-\omega \\
+%     \label{eq:deltaomega}
+% 	a\delta = \omega
+% \end{gather}
+% \makebox[\textwidth][l]{Hence, the probability that a specific slice is present in the buffer}
+% \begin{gather}
+% 	1-\delta = 1-\frac{\omega}{a}
+% \end{gather}
+The number of slices $n$ needed to fill up a buffer of size $f_1$ for a given $\delta$ is given by:
 \begin{gather}
-E(t) = \sum_{x=0}^{nf_1-1}E(t_x) = \sum_{x=0}^{nf_1-1}\frac{1}{P_x} = n\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x} = nH_{nf_1}
+	n = Nf_1(1-\delta) %= Nf_1(1-\frac{\omega}{a})
 \end{gather}
+This means that we are willing to allocate a buffer that is fraction $f_1$ of the entire DAG, but instead of filling up all $Nf_1$ slices, we are willing to forgo $Nf_1\delta$ slices.
+Using the Coupon Collector proof~\cite{couponCollector}, we know that the expected number of trials $E(t)$ of obtaining the $xth$ new slice after having buffered $x-1$ slices is:\\
+\begin{gather}
+	E(t_x) = \frac{Nf_1}{Nf_1-(x-1)}
+\end{gather}
+we see that the expected number of trials in order to obtain $n$ slices is given by
+\begin{gather}
+	E(t) = \sum_{x=1}^{n}E(t_x) = Nf_1\sum_{x=1}^{n}\frac{1}{Nf_1-x+1} = Nf_1\sum_{x=1}^{Nf_1(1-\delta)}\frac{1}{Nf_1-x+1}
+\end{gather}
+Splitting this into two summations,
+\begin{gather}
+	E(t) = Nf_1[\sum_{x=1}^{Nf_1}\frac{1}{Nf_1-x+1} - \sum_{x=Nf_1(1-\delta)+1}^{Nf_1}\frac{1}{Nf_1-x+1}] \\
+    E(t) = Nf_1[H_{Nf_1} -H_{Nf_1\delta}] \\
+    \label{eq:expectedHashes}
+	E(H) = \frac{Nf_1}{a}[H_{Nf_1} -H_{Nf_1\delta}]
+\end{gather}
+Now, using equation ~\ref{eq:expectedHashes}, bounds on Harmonic Numbers ~\cite{harmonicNumber}, and setting $N = 16777186$, $f_1 = 1$, $a = 64$ and $\delta = 0.95$, we get $E(H) = 785312$ hashes.
+Hence, we see that even computing merely 800k hashes fills a DAG buffer as large as the entire DAG by more than 95\%, as opposed to calculating 4.5 million to fill the buffer entirely.
+(Note that this number should be smaller for smaller buffer sizes; so this is again a rough upper bound).
+This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up.
+In fact, as we will see in the results, filling up 95\% of a buffer as large as the DAG already starts giving us good hash rates for a browser (10kH/s).
+This means that reaching a reasonably steady state is not as hard as it seems at face value, making this approach viable for web setting where users might not stay on websites for long.
+Given this result, we compute 800k hashes for all our experiments, as discussed in the next section.
 
-It then follows from bounds on the nth Harmonic Number~\cite{harmonicNumber} that the expected number of hashes $E(H)$ it takes to fill up a buffer of fraction $f_1$ of a DAG with $n$ slices is bounded by:
-\begin{gather}
-\frac{n}{64}[\ln{nf_1} + \frac{1}{2nf_1} + \gamma - \frac{1}{12({nf_1})^2+2\frac{7-12\gamma}{2\gamma - 1}}] <= E(H) \\ E(H)< \frac{n}{64}[\ln{nf_1} + \frac{1}{2nf_1} + \gamma - \frac{1}{12({nf_1})^2+\frac{6}{5}}]
-\end{gather}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{theorem}[Expectation of Number of Hashes]
+% \label{expectedHashes}\\
+% \makebox[\textwidth][l]{If we define}
+% \makebox[\textwidth][c]{Number of DAG slices = n}
+% \makebox[\textwidth][c]{Size of buffer as a fraction of the total DAG = $f_1$; $f_1$=[0,1]}
+% \makebox[\textwidth][c]{Expected number of hashes it takes to fill the buffer = E(H)}
+% \makebox[\textwidth][c]{nth Harmonic Number = $H_n$}
+% \makebox[\textwidth][c]{Euler-Mascheroni constant = $\gamma = 0.57721566...$}
+% \makebox[\textwidth][c]{Probability of obtaining a new slice after having buffered x slices = $P_x = \frac{nf_1-x}{n}$}
+% \makebox[\textwidth][c]{Expected number of trials $t_x$ to get a new slice after having seen} 
+% \makebox[\textwidth][c]{$x$ out of $nf_1$ slices = 
+% $E(t_x) = \frac{1}{P_x} = \frac{n}{nf_1-x}$}
+% \makebox[\textwidth][c]{Expected number of trials it would take to see all $x$ slices = $E(t)$}
+% % ~\trishita{add reference to results}
+% From the Coupon Collector Problem~\cite{couponCollector}, it follows that:
+% \begin{gather}
+% E(t) = \sum_{x=0}^{nf_1-1}E(t_x) = \sum_{x=0}^{nf_1-1}\frac{1}{P_x} = n\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x} = nH_{nf_1}
+% \end{gather}
+
+% It then follows from bounds on the nth Harmonic Number~\cite{harmonicNumber} that the expected number of hashes $E(H)$ it takes to fill up a buffer of fraction $f_1$ of a DAG with $n$ slices is bounded by:
+% \begin{gather}
+% \frac{n}{64}[\ln{nf_1} + \frac{1}{2nf_1} + \gamma - \frac{1}{12({nf_1})^2+2\frac{7-12\gamma}{2\gamma - 1}}] <= E(H) \\ E(H)< \frac{n}{64}[\ln{nf_1} + \frac{1}{2nf_1} + \gamma - \frac{1}{12({nf_1})^2+\frac{6}{5}}]
+% \end{gather}
 
@@
 
-The factor of 64 comes from the fact that calculating each hash requires sampling the DAG 64 times.
+% The factor of 64 comes from the fact that calculating each hash requires sampling the DAG 64 times.
 Given this, let us do a simple calculation for one extreme case, where we allocate a buffer as large as the entire DAG on the browser (in order to get an upper bound on the number of hashes it would take to fill this buffer up).
@@
 If $f_1 < 1$, the number of hashes should be less than 4.5 million, thus making it a very loose upper bound on the number of hashes needed to fill up a DAG buffer (and thereby reaching a steady-state hash rate).
-% \trishita{To Do: reword the next two sentences to motivate the analysis that follows}
-In practice, however, we do not need to wait till the buffer is \emph{completely} full till we see good hash rates.
+
+% In practice, however, we do not need to wait till the buffer is \emph{completely} full till we see good hash rates.
 We will demonstrate how we can get away with a much smaller number of hashes to fill up \emph{almost all} of the buffer, thereby reaching very good hash rates relatively quickly.
+
 % lower bound (python exp): (n/64.0)*(log(n) + 1.0/(2*n) + g - 1.0/(12*(n**2) + (2*(7-12*g)/(2*g-1))))
@@
 % \label{earlyTermination}
-\makebox[\textwidth][l]{If we further define,}
-\makebox[\textwidth][c]{Fraction of DAG buffer to be filled = $f_2$; $f_2$ $\in$ [0,1]}
-\makebox[\textwidth][c]{$x  = E(H) - \frac{n}{64}\ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} - \frac{1}{128f_1} + \frac{n}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}}$}
-\makebox[\textwidth][l]{Then,}
-    \begin{gather}
-   \frac{n}{768({nf_1 - nf_2f_1 - 1})^2+128\frac{7-12\gamma}{2\gamma - 1}} - \frac{1}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} < x \\
-   x <= \frac{n}{768({nf_1-nf_2f_1-1})^2+\frac{6}{5}} - \frac{n}{12({nf_1})^128+\frac{6}{5}} 
-	\end{gather}
-% \end{corollary}
-% \begin{proof}
-Then, for a buffer with space for $f_1$ slices, the number of slices we want to fill it with in order for a fraction $f_2$ of it to be full would be: \\
-\makebox[\textwidth][c]{Number of slices to fill DAG buffer with = $nf_2f_1$}
-This would modify equation \ref{eq:6} for the expected number of trials as follows:
-\begin{gather}
-    E(t) = \sum_{x=0}^{nf_2f_1}\frac{1}{P_x} = \sum_{x=0}^{nf_2f_1}\frac{n}{nf_1-x} = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x}
-\end{gather}
-This is essentially an early termination of the summation in equation ~\ref{eq:6}, and can be expressed as follows:
-\begin{gather}
-    E(t) = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x} = n(\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x} - \sum_{x=nf_2f_1+1}^{nf_1-1}\frac{1}{nf_1-x}) \\
-    E(t) = n[H_{nf_1} - H_{nf_1 - nf_2f_1 - 1}]\\
-\end{gather}
-Again, using the bounds on the nth Harmonic Number~\cite{harmonicNumber}, substituting $\frac{E(t)}{64} = E(H)$ and $x$, and simplifying, we get the following: \\
-\makebox[\textwidth][l]{Let}
-\begin{gather}
+% \makebox[\textwidth][l]{If we further define,}
+% \makebox[\textwidth][c]{Fraction of DAG buffer to be filled = $f_2$; $f_2$ $\in$ [0,1]}
+% \makebox[\textwidth][c]{$x  = E(H) - \frac{n}{64}\ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} - \frac{1}{128f_1} + \frac{n}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}}$}
+% \makebox[\textwidth][l]{Then,}
+%     \begin{gather}
+%    \frac{n}{768({nf_1 - nf_2f_1 - 1})^2+128\frac{7-12\gamma}{2\gamma - 1}} - \frac{1}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} < x \\
+%    x <= \frac{n}{768({nf_1-nf_2f_1-1})^2+\frac{6}{5}} - \frac{n}{12({nf_1})^128+\frac{6}{5}} 
+% 	\end{gather}
+% % \end{corollary}
+% % \begin{proof}
+% Then, for a buffer with space for $f_1$ slices, the number of slices we want to fill it with in order for a fraction $f_2$ of it to be full would be: \\
+% \makebox[\textwidth][c]{Number of slices to fill DAG buffer with = $nf_2f_1$}
+% This would modify equation \ref{eq:6} for the expected number of trials as follows:
+% \begin{gather}
+%     E(t) = \sum_{x=0}^{nf_2f_1}\frac{1}{P_x} = \sum_{x=0}^{nf_2f_1}\frac{n}{nf_1-x} = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x}
+% \end{gather}
+% This is essentially an early termination of the summation in equation ~\ref{eq:6}, and can be expressed as follows:
+% \begin{gather}
+%     E(t) = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x} = n(\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x} - \sum_{x=nf_2f_1+1}^{nf_1-1}\frac{1}{nf_1-x}) \\
+%     E(t) = n[H_{nf_1} - H_{nf_1 - nf_2f_1 - 1}]\\
+% \end{gather}
+% Again, using the bounds on the nth Harmonic Number~\cite{harmonicNumber}, substituting $\frac{E(t)}{64} = E(H)$ and $x$, and simplifying, we get the following: \\
+% \makebox[\textwidth][l]{Let}
+% \begin{gather}
 % 	n[
@@
 %     x  = E(H) - \frac{n}{64}\ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} - \frac{1}{128f_1} + \frac{n}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} \\
-   \frac{n}{768({nf_1 - nf_2f_1 - 1})^2+128\frac{7-12\gamma}{2\gamma - 1}} - \frac{1}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} < x \\
-   x <= \frac{n}{768({nf_1-nf_2f_1-1})^2+\frac{6}{5}} - \frac{n}{12({nf_1})^128+\frac{6}{5}} 
-\end{gather}    
+%    \frac{n}{768({nf_1 - nf_2f_1 - 1})^2+128\frac{7-12\gamma}{2\gamma - 1}} - \frac{1}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} < x \\
+%    x <= \frac{n}{768({nf_1-nf_2f_1-1})^2+\frac{6}{5}} - \frac{n}{12({nf_1})^128+\frac{6}{5}} 
+% \end{gather}    
 %     \ln{()}) \\
@@
 % \end{proof}
-Now, using ~\ref{eq:13}, if we set $n = 16777186$, $f_1 = 1$ and $f_2 = 0.95$, we get $E(H) = 785312$ hashes
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Hence, we see that even computing merely 800k hashes fills a DAG buffer as large as the entire DAG by more than 95\%, as opposed to calculating 4.5 million to fill the buffer entirely.
-(Note that this number should be smaller for smaller buffer sizes; so this is again a rough upper bound).
-This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up.
-In fact, as we will see in the results, filling up 95\% of a buffer as large as the DAG already starts giving us good hash rates for a browser (10kH/s).
-This means that reaching a reasonably steady state is not as hard as it seems at face value, making this approach viable for web setting where users might not stay on websites for long.
-Given this result, we compute 800k hashes for all our experiments, as discussed in the next section.
 % Beyond that, the marginal cost of computing more hashes outweighs the rate at which the DAG is filled up. Hence, as we will see in the next section, for our experiments, we compute 800,000 hashes.
@@
 
-\trishita{Might want to get rid of figs 8 9 and 10 since we don't have much room}
-In Figures~\ref{fig:NativeWebAsm},~\ref{fig:WebAsmJS} and~\ref{fig:NativeJS} we show the percentage difference of the hashrates between the native miner and the browser miner implementations.
+Table ~\ref{table:perf} shows us how the performance of each of the miners compare.
+Interestingly, the most conspicuous aspect is the fact that the performance variation between different implementations is not uniform across the buffer hit rate and the size of the buffer.
+We also see that for obvious reasons, the native miner outperforms both the ~\verb|JavaScript| and the ~\verb|WebAssembly| miner.
+However, we see that the ~\verb|WebAssembly| miner is at most 40.5\% slower than the native miner -- which is not very far off considering the overhead of running programs within browsers.
+The ~\verb|JavaScript| miner, on the other hand, is ~\textbf{at least} 47.2\% slower (and at most 82.0\% slower).
+
+\begin{table}[t]
+\caption{Performance Difference accross different Implementations}\label{table:perf}
+\vspace{-2ex}
+\begin{center}
+\begin{tabular}{ c  c  c  c}
+
+&\makecell{\textbf{WASM/JS}} & \makecell{\textbf{Native/JS}} & \makecell{\textbf{Native/WASM}}\\
+\cline{2\ -2} \cline{3\ -3} \cline{4\ -4}
+\makecell{\% Diff in smallest hash rate} & 35.9\% &  55.0\% & 38.9\% \\
+\makecell{\% Diff in peak hash rate} & 73.2\% &  81.3\% & 30.2\% \\
+\makecell{Min perf \% diff} &  24.4\% &  47.2\% & 23.9\% \\
+\makecell{Max perf \% diff}  &  73.3\% &  82.0\% & 40.5\%\\ 
+\makecell{Avg. Hash Rate \% diff \\
+(averaged over all buffer sizes \\and cache hit rates)}&  30.6\% &  55.6\% & 35.9\%\\
+\end{tabular}
+\end{center}
+\vspace{-3ex}
+\end{table}
+
+% \trishita{Got rid of figs 8 9 and 10 since we don't have much room}
+% In Figures~\ref{fig:NativeWebAsm},~\ref{fig:WebAsmJS} and~\ref{fig:NativeJS} we show the percentage difference of the hashrates between the native miner and the browser miner implementations.
 We also compare the performance of the ~\verb|JavaScript| and ~\verb|WebAssembly|  miners.
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=250px,keepaspectratio]{Native_Miner_vs_WebAssembly_miner_Hash_Rate_Percent_Improvement.pdf}
-\caption{\label{fig:NativeWebAsm} Native miner vs. WebAssembly miner Hash Rate Percent Improvement}
-\end{figure}
+% \begin{figure}[h]
+% \centering
+% \includegraphics[width=250px,keepaspectratio]{Native_Miner_vs_WebAssembly_miner_Hash_Rate_Percent_Improvement.pdf}
+% \caption{\label{fig:NativeWebAsm} Native miner vs. WebAssembly miner Hash Rate Percent Improvement}
+% \end{figure}
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=250px,keepaspectratio]{WebAssembly_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
-\caption{\label{fig:WebAsmJS} WebAssembly miner vs. JavaScript miner Hash Rate Percent Improvement}
-\end{figure}
+% \begin{figure}[h]
+% \centering
+% \includegraphics[width=250px,keepaspectratio]{WebAssembly_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
+% \caption{\label{fig:WebAsmJS} WebAssembly miner vs. JavaScript miner Hash Rate Percent Improvement}
+% \end{figure}
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=250px,keepaspectratio]{Native_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
-\caption{\label{fig:NativeJS} Native miner vs. JavaScript miner Hash Rate Percent Improvement}
-\end{figure}
+% \begin{figure}[h]
+% \centering
+% \includegraphics[width=250px,keepaspectratio]{Native_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
+% \caption{\label{fig:NativeJS} Native miner vs. JavaScript miner Hash Rate Percent Improvement}
+% \end{figure}
 
@@
 
-We see that for obvious reasons, the native miner outperforms both the ~\verb|JavaScript| and the ~\verb|WebAssembly| miner.
-However, we see that the ~\verb|WebAssembly| miner is at most 40\% slower than the native miner -- which is not very far off considering the overhead of running programs within browsers.
-The ~\verb|JavaScript| miner, on the other hand, is ~\textbf{at least} 47\% slower (and at most 82\% slower).
-
 Finally, we tabulate the most important results from our analysis in table ~\ref{table:results}
@@
 \begin{table}[t]
-\caption{Results}\label{table:results}
+\caption{Main Results}\label{table:results}
 \vspace{-2ex}
@@
 Peak Hash Rate &  56800H/s &  10626H/s & 39651H/s \\
-\makecell{Maximum Time to reach steady state hash rate \\ (buffer as large as DAG)}  &  X s &  X s & X s\\ 
+\makecell{Maximum Time to reach steady state \\ hash rate (buffer as large as DAG)}  &  X s &  X s & X s\\ 
 \makecell{Avg. Hash Rate \% diff with Native Miner \\
-(averaged over all buffer sizes)}&  NA &  56\% & 36\%\\
+(averaged over all buffer sizes)}&  NA &  55.6\% & 35.9\%\\
 \end{tabular}

### 2018-04-03 paper/paper.tex
fixed analysis text

@@
 This is important because once the buffer in the browser fills up, the hash rate that the browser gives is at its maximum, steady-state.
-In this section, we will mathematically demonstrate that filling a buffer the size of the DAG up should take at most 4.5 million hashes, while filling up 95\% of this buffer takes merely 800k hashes.
-This is a significant difference since in our experimental set-up, the browser takes X s to compute 4.5 million hashes, while only Y s to compute 800k hashes.
+In this section, we will mathematically demonstrate that filling a buffer the size of the DAG up should take at most 4.5 million hashes, while filling up 99.5\% of this buffer takes merely 1.4 million hashes.
+This is a significant difference since in our experimental set-up, the browser takes X s to compute 4.5 million hashes, while only Y s to compute 1.4 million hashes.
 The approach we take is similar to the Coupon Collector problem \cite{couponCollector}, and is discussed below.
@@
 In reality, this is not entirely true and hence the results we obtain from this analysis are more conservative than what we see in practice.
-In fact, while we show here that filling up 95\% of a buffer as big as the DAG takes 800k hashes, whereas in reality it only takes half as many hashes~\ref{section:Results} \\
+In fact, while we show here that filling up 99.5\% of a buffer as big as the DAG takes 1.4 million hashes, whereas in reality it only takes half as many hashes, as shown in Section~\ref{sec:results} \\
 
@@
 This means that we are willing to allocate a buffer that is fraction $f_1$ of the entire DAG, but instead of filling up all $Nf_1$ slices, we are willing to forgo $Nf_1\delta$ slices.
-Using the Coupon Collector proof~\cite{couponCollector}, we know that the expected number of trials $E(t)$ of obtaining the $xth$ new slice after having buffered $x-1$ slices is:\\
+
+Now, using the Coupon Collector proof~\cite{couponCollector}, we know that the expected number of trials $E(t)$ of obtaining the $xth$ new slice after having buffered $x-1$ slices is:\\
 \begin{gather}
@@
 \end{gather}
-Now, using equation ~\ref{eq:expectedHashes}, bounds on Harmonic Numbers ~\cite{harmonicNumber}, and setting $N = 16777186$, $f_1 = 1$, $a = 64$ and $\delta = 0.95$, we get $E(H) = 785312$ hashes.
-Hence, we see that even computing merely 800k hashes fills a DAG buffer as large as the entire DAG by more than 95\%, as opposed to calculating 4.5 million to fill the buffer entirely.
-(Note that this number should be smaller for smaller buffer sizes; so this is again a rough upper bound).
-This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up.
-In fact, as we will see in the results, filling up 95\% of a buffer as large as the DAG already starts giving us good hash rates for a browser (10kH/s).
+Now, using equation~\ref{eq:expectedHashes}, bounds on Harmonic Numbers~\cite{harmonicNumber}, and setting $N = 16777186$, $f_1 = 1$, $a = 64$ and $\delta = 0$, we get $E(H) = 4.5$ million hashes.
+However, if we slightly increase $\delta$ to 0.005, we get $E(H) = 1.4$ million hashes.
+Hence, we see that even computing merely 1.4 million hashes fills a DAG buffer as large as the entire DAG by more than 99.5\%, as opposed to calculating 4.5 million to fill the buffer entirely.
+(Note that this number should be smaller for smaller buffer sizes ($f_1 < 1$); so this is a rough upper bound).
+% This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up. 
+In fact, as we will see in the results, filling up 99.5\% of a buffer as large as the DAG already starts giving us good hash rates for a browser -- 35kH/s for the ~\verb|WebAssembly| miner, whereas the hash rate for a completely full buffer is only marginally higher at XkH/s.
 This means that reaching a reasonably steady state is not as hard as it seems at face value, making this approach viable for web setting where users might not stay on websites for long. 
-Given this result, we compute 800k hashes for all our experiments, as discussed in the next section.
+% Given this result, we compute 800k hashes for all our experiments, as discussed in the next section.
 
@@
 \subsection{Implementation Results}
+\label{sec:results}
 Figures~\ref{fig:NativeMinerHM},~\ref{fig:WebAsmMinerHM} and ~\ref{fig:JSMinerHM} below shows a heat-map of how the hash rate varies for each of the three implementations as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.

### 2018-04-05 paper/paper.tex
added algo

@@
 \usepackage{amsmath}
+\usepackage{algorithmic}
 \newcommand{\trishita}[1]{{\color{magenta}\bfseries[Trishita: #1]}}
+
 % Used for displaying a sample figure. If possible, figure files should
@@
 Hence, we are pioneers in offering an open source architecture for Ethereum mining with web browsers.
-Our miner gives us a hashrate of about 39kH/s, which, given the flexibility of the Ethereum framework, is useful and practical for many applications like web authentication rate limiting, website usage tracking for advertisement companies, private Ethereum networks, web content monetization, as discussed below.
+Our miner gives us a hashrate of about 39kH/s, which, given the versatility of the Ethereum framework, is useful and practical for many applications like web authentication rate limiting, website usage tracking for advertisement companies, private Ethereum networks, web content monetization, as discussed below.
 
@@
 
-\section{Outline}
-\trishita{To Do: Update}
+\subsection{Roadmap}
 The remainder of the paper is organized as follows.
-In Section 5 we present a detailed description of the Ethereum mining algorithm and the current state of Ethereum.
-Section 6 describes the Architecture of our implementation of the Distributed Web Browser Miner.
-Section 7 goes over the challenges that we have dealt with during our implementation and their effect on the project.
-Section 8 examines the results of our solution and compares it to current mining data to evaluate the efficacy of our work.
-Finally, in Section 9 we lay out possible future work, and in Section 10 provide conclusions and insight on the project.
+In Section 2 we discuss the various potential applications our miner could have.
+Then, in Section 3 we cover the relevant background to understand the functioning of the miner -- namely, a description of the Ethash, the Ethereum mining Proof-of-Work, and \verb|WebAssembly|, the language our best-performing browser miner is implemented in.
+Section 4 outlines our approach to distributing the Ethash PoW over numerous browsers given the resource constraints.
+Finally, we present the results in Section 5.
+We conclude and discuss the future work in Sections 6 and 7 respectively.
 
@@
 % \textbf{Web Content Monetization}
-With the growth in global Internet usage, websites have become a lucrative way for people to earn monetary profit.
+With the growth in global Internet usage, hosting websites has become a lucrative business.
 As a result, new methods of monetizing electronic content have surfaced with time.
@@
 Our web miner could solve these issues as the advertiser could require the website owner to embed this miner within their website, thereby making the site visitors compute PoW hashes.
-The advertiser would then ask the website owner to submit hashes that pass a certain difficulty threshold, and the larger the number of hashes that the website owner can provide, the more the remuneration the site receives.
+The advertiser would then ask the website owner to submit hashes that pass a certain difficulty threshold (i.e., the value of the hash being less than a certain number), and the larger the number of hashes that the website owner can provide, the more the remuneration the site receives.
 This would be extremely difficult for the website owners to fake since they would have to compute hashes themselves, an endeavor that might be more expensive than the corresponding payout it would bring.\\ \\
@@
 Ethereum is a crypto-currency that was released in July 2015 by Vitalik Buterin, Gavin Wood and Jeffrey Wilcke.
-Ethereum uses the Ethash algorithm for its PoW for mining blocks.
-Derived from the Dagger and Hashimoto algorithms ~\cite{dagger-hashimoto}, Ethash operates by first generating a 256 bit seed.
+Ethereum uses the Ethash algorithm (derived from the Dagger and Hashimoto algorithms ~\cite{dagger-hashimoto}) for its PoW for mining blocks.
+Before we discuss how mining works with Ethash, we would first like to establish some basic terminology about the data structures involved in the PoW:
+\begin{itemize}
+\item \textbf{Seed}: Ethash operates by first generating a 256 bit seed.
 This seed is different for every epoch (30,000 blocks).
@@
 For every other epoch it is always the Keccak-256 hash of the previous seed hash.
-This seed is then used to compute a pseudo-random cache.
+\item \textbf{Cache}: The seed for a particular epoch is used to compute a pseudo-random cache.
+This cache is simply an array 4 byte integers ~\cite{Ethmining}.
 The cache production process involves using the seed hash to first sequentially filling up X bytes of memory (size of the cache), then performing Y passes of the RandMemoHash algorithm ~\cite{randmemohash}.
-This transforms the initial cache to give us the final value for the cache.
-This cache is simply an array 4 byte integers ~\cite{Ethmining}.
-Lightweight clients may use this cache for verification, while full node clients can use it to calculate a DAG (Directed Acyclic Graph) file.
-Essentially, each node in the DAG is generated by combining data from 256 pseudorandomly selected cache nodes and hashing them together.
-This process is repeated to generate all nodes in the DAG.
-
-Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128B wide ``Mix'' (another byte array).
-The Mix is then used to fetch a specific page of the DAG from memory.
-(Each page of the DAG 2 slices long, and each slice in turn is 64 Bytes long) After this, the Mix is updated with the fetched part of the DAG.
-Then, this updated Mix is used to fetch a new part of the DAG.
-This process of sequentially fetching parts of the DAG is repeated 64 times, and the final value of the Mix is put through a transformation to obtain a 32 byte digest.
-This digest is then compared to the threshold, and if it is lesser than it, the nonce is valid and the block is successfully mined and can be broadcast to the network.
-However, if the digest is greater than the threshold, the nonce is unsuccessful, and the entire process must be repeated with a new nonce ~\cite{Ethmining}.
-This procedure for mining is depicted in Figure~\ref{fig:ethash}.
-
-It is important to note that the parts of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence there is no way to pre-determine which parts will be useful to have in memory.
-This therefore forces miners to store entire DAG in memory, making mining ``Memory Hard''.
-This is intended to even the playing field, as ASIC miners no longer have any advantage as they do for Bitcoin.
-GPU miners, however, do have an advantage, normally having hashrates of over 10 times that of a CPU miner.
-While mining is memory intensive, verification is relatively lightweight.
-This is because of the property that each ``slice'' in the DAG depends on a set of pseudo-randomly selected items from the Cache.
-Hence, the Cache is used to regenerate only the specific slices of the DAG that are needed to recalculate the hash for the particular nonce.
-And so only the Cache needs to be stored by clients that perform just verification.
-We use this property of being able to generate the parts of the DAG as needed to our advantage in order to alleviate some of the memory and network bandwidth restrictions that browsers typically face.
-
-As time goes on, mining Ethereum becomes more and more difficult, as the size of the DAG and Cache increases with every Epoch.
-Currently the DAG is more than 2GB in size, causing many GPU miners with cards of 2GB of memory to suffer in terms of hashrate.
-% The Proof-of-Work difficulty and total hashrate of the network has been steadily increasing over time, with the current difficulty at 1612.737TH and the respective hashrate at 109.138TH/s ~\cite{etherscan}.
-This reflects the design of mining one block approximately every 12 seconds.
-% As for mining rewards, the reward for mining a block has gone from 5 Ether to 3 ether, though the difficulty has significantly decreased, both due to the Byzantium fork.
-
-For a normal Ethereum miner to function, the current block headers and the DAG are required to even begin mining.
-As we simply cannot afford to transfer the entire DAG to the browser and store it in memory, we propose an an alternative approach to address some of these concerns.
+% This transforms the initial cache to give us the final value for the cache. 
+Lightweight clients may use this cache for verifying hashes (discussed below), while full node clients can use it to calculate a DAG (Directed Acyclic Graph) dataset, as described below. 
+\item \textbf{DAG}: A Directed Acyclic Graph stored as a large byte array (currently around 2GB in size). The DAG has the following two attributes:
+  \begin{enumerate}
+  \item \textbf{Node}: Each DAG node in this byte array spans 64 bytes, and node indices are therefore aligned at a 64 byte boundary.
+  \item \textbf{Page}: Each DAG page spans 2 nodes, however, page accesses are not aligned at a 2 node boundary.
+The mining process involves accessing some DAG pages and hashing them together with the header and nonce.
+  \end{enumerate}
+Each node in the DAG is generated by combining data from 256 pseudorandomly selected cache nodes and hashing them together. This process is repeated to generate all nodes in the DAG.
+\end{itemize}
+We must point out that as time goes on, mining Ethereum becomes more and more difficult, as the size of the DAG and Cache increases with every Epoch.
 
@@
 
+Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128B wide ``Mix'' (another byte array),as seen in step 1 of Figure~\ref{fig:ethash}.
+The Mix is then used to fetch a specific page of the DAG from memory.
+After this, the Mix is updated with the fetched part of the DAG (step 2).
+Then, this updated Mix is used to fetch a new part of the DAG (step 3).
+This process of sequentially fetching parts of the DAG is repeated 64 times (step 4), and the final value of the Mix is put through a transformation to obtain a 32 byte digest (step 5).
+This digest is then compared to the threshold (step 6), and if it is lesser than it, the nonce is valid and the block is successfully mined and can be broadcast to the network.
+However, if the digest is greater than the threshold, the nonce is unsuccessful, and the entire process must be repeated with a new nonce ~\cite{Ethmining}.
+Below is the pseudo-code for the algorithm for completeness.\\
+\begin{algorithmic}[H]
+\label{miningAlgo}
+\STATE $mix \gets mixInit(\{header,nonce\})$
+\FOR{$i = 0;\;i < 64;\;i++$}
+  \STATE $dagPageIndex \gets getDAGPageIndexFromMix(mix)$
+  \STATE $dagPage \gets DAG[dagPageIndex]$
+  \STATE $dagPageIndex \gets updateMix(dagPage,mix)$
+\ENDFOR
+\STATE $digest \gets postProcessFunction(mix)$
+\IF {$digest <= targetThreshold$}
+	\RETURN \TRUE
+\ENDIF
+\RETURN \FALSE
+\end{algorithmic}
+It is important to note that the parts of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence there is no way to pre-determine which parts will be useful to have in memory.
+This therefore forces miners to store entire DAG in memory, making mining ``Memory Hard''.
+
+% This is intended to even the playing field, as ASIC miners no longer have any advantage as they do for Bitcoin.
+GPU miners, however, do have an advantage, normally having hashrates of over 10 times that of a CPU miner.
+
+While mining is memory intensive, verification is relatively lightweight.
+This is because of the property that each ``slice'' in the DAG depends on a set of pseudo-randomly selected items from the Cache.
+Hence, the Cache is used to regenerate only the specific slices of the DAG that are needed to recalculate the hash for the particular nonce.
+And so only the Cache needs to be stored by clients that perform just verification.
+We use this property of being able to generate the parts of the DAG as needed to our advantage in order to alleviate some of the memory and network bandwidth restrictions that browsers typically face.
+
+% Currently the DAG is more than 2GB in size, causing many GPU miners with cards of 2GB of memory to suffer in terms of hashrate. 
+% The Proof-of-Work difficulty and total hashrate of the network has been steadily increasing over time, with the current difficulty at 1612.737TH and the respective hashrate at 109.138TH/s ~\cite{etherscan}.
+This reflects the design of mining one block approximately every 12 seconds.
+% As for mining rewards, the reward for mining a block has gone from 5 Ether to 3 ether, though the difficulty has significantly decreased, both due to the Byzantium fork.
+
+% For a normal Ethereum miner to function, the current block headers and the DAG are required to even begin mining.
+As we simply cannot afford to transfer the entire DAG to the browser and store it in memory, we propose an an alternative approach to address some of these concerns.
+
 \subsection{Challenges}
-\trishita{Too long of a sentence; need to reword}Given that we now know that the crux of having a good hashrate for Ethereum lies in having quick access to the DAG, one of the biggest challenges with mining it on a distributed ensemble of browsers would be to transfer and store this data structure within each worker browser.
+% \trishita{Too long of a sentence; need to reword}
+Given that we now know that the crux of having a good hashrate for Ethereum lies in having quick access to the DAG, one of the biggest challenges with mining it on a distributed ensemble of browsers would be to transfer and store this data structure within each worker browser.
 However, given that the DAG for an Ethereum network is at least 1GB (and growing) in size transferring it to the browser every time a client loads our web page would be impractical.
@@
 \section{Our Approach}
+% \trishita{I think it would be nice if we show how we modified the algorithm shown in the previous section. I will add that over here}
 We propose a lazy-evaluation based approach to alleviate the network and memory requirements for mining Ethereum in a distributed scenario on browsers.
@@
 This has the effect that the longer the user remains on the web-page, the better the hashrate gets for that user.
+Our modified algorithm is shown below:
+
+\begin{algorithmic}[H]
+\label{modifiedMiningAlgo}
+\STATE $mix \gets mixInit(\{header,nonce\})$
+\FOR{$i = 0;\;i < 64;\;i++$}
+  \STATE $dagPageIndex \gets getDAGPageIndexFromMix(mix)$
+  \STATE $dagPage \gets DAGbuffer[dagPageIndex]$
+  \IF {$dagPage == NULL$}
+		\STATE $dagPage = computeDAGPageFromCache(dagPageIndex)$
+        \STATE $DAGbuffer[dagPageIndex] = dagPage$
+  \ENDIF  
+  \STATE $dagPageIndex \gets updateMix(dagPage,mix)$
+\ENDFOR
+\STATE $digest \gets postProcessFunction(mix)$
+\IF {$digest <= targetThreshold$}
+	\RETURN \TRUE
+\ENDIF
+\RETURN \FALSE
+\end{algorithmic}
 
@@
 After recieving the necessary data, the browser allocates a buffer for the DAG in order to store future slices.
-Note that the buffer for the DAG is implemented as an array of ints (with a DAG slice being 16 ints long), so as to make each lookup in the buffer $\theta(1)$.
+Note that the buffer for the DAG is implemented as an array of ints, so as to make each lookup in the buffer $\theta(1)$.
 At this point, it can then begin to search for a solution.
 
-For our miner, we modeled our \verb|JavaScript| implementation based on the ~\verb|node.js| implementation of Ethash ~\cite{ethash}.
+For our miner, we modeled our \verb|JavaScript| implementation based on the ~\verb|node.js| implementation of Ethash~\cite{ethash}.
 To begin, the miner creates a random nonce and computes the hash (using the Cache and the buffered DAG) as discussed in the previous section.
-It will continue to perform this action on new nonces until one of two scenarios occur; it finds a nonce such that the computed hash is below the given threshold or the process has timed out.
+It will continue to perform this action on new nonces until one of two scenarios occur.
+
+The first case is if it finds a nonce such that the computed hash is below the given threshold or the process has timed out.
 In the former case, the browser submits the result back to the node and then asks the node for a new block header and the Cache.
-Otherwise if it has timed out without finding a result, the browser simply polls the node for the current block header and Cache .
+
+The second case is when the algorithm times out without finding a result, the browser simply polls the node for the current block header and Cache .
 This process will continue until the user moves away from the website or closes their browser.
@@
 In fact, while we show here that filling up 99.5\% of a buffer as big as the DAG takes 1.4 million hashes, whereas in reality it only takes half as many hashes, as shown in Section~\ref{sec:results} \\
-
+% \trishita{To Do: Still need to incorporate prof. Starobinski's  most recent feedback}
 \makebox[\textwidth][l]{If we define}
 \makebox[\textwidth][c]{Number of DAG slices = N}
-\makebox[\textwidth][c]{Fraction of the DAG we want to buffer = $f_1$}
+% \makebox[\textwidth][c]{Fraction of the DAG we want to buffer = $f_1$}
 \makebox[\textwidth][c]{Number of DAG slices needed to compute a single hash = a}
@@
 \begin{gather}
-	n = Nf_1(1-\delta) %= Nf_1(1-\frac{\omega}{a})
+	n = N(1-\delta) %= Nf_1(1-\frac{\omega}{a})
 \end{gather}
@@
 \begin{gather}
-	E(t_x) = \frac{Nf_1}{Nf_1-(x-1)}
+	E(t_x) = \frac{N}{N-(x-1)}
 \end{gather}
@@
 \begin{gather}
-	E(t) = \sum_{x=1}^{n}E(t_x) = Nf_1\sum_{x=1}^{n}\frac{1}{Nf_1-x+1} = Nf_1\sum_{x=1}^{Nf_1(1-\delta)}\frac{1}{Nf_1-x+1}
+	E(t) = \sum_{x=1}^{n}E(t_x) = N\sum_{x=1}^{n}\frac{1}{N-x+1} = Nf_1\sum_{x=1}^{N(1-\delta)}\frac{1}{N-x+1}
 \end{gather}
@@
 \begin{gather}
-	E(t) = Nf_1[\sum_{x=1}^{Nf_1}\frac{1}{Nf_1-x+1} - \sum_{x=Nf_1(1-\delta)+1}^{Nf_1}\frac{1}{Nf_1-x+1}] \\
-    E(t) = Nf_1[H_{Nf_1} -H_{Nf_1\delta}] \\
+	E(t) = N[\sum_{x=1}^{N}\frac{1}{N-x+1} - \sum_{x=N(1-\delta)+1}^{N}\frac{1}{N-x+1}] \\
+    E(t) = N[H_{N} -H_{N\delta}] \\
     \label{eq:expectedHashes}
-	E(H) = \frac{Nf_1}{a}[H_{Nf_1} -H_{Nf_1\delta}]
+	E(H) = \frac{N}{a}[H_{N} -H_{N\delta}]
 \end{gather}
@@
 We ran the implementations in ~\verb|JavaScript| and ~\verb|WebAssembly| in the browser, and a native miner written in ~\verb|C++| that employs the same approach outside of the browser for control results.
-Each miner was run till 800,000 hashes were computed and the hash rate and buffer hit rate were sampled every 10,000 hashes.
-(Note that both the hash rate and buffer hit rate sampled at a particular time reflected the values over the 10,000 most recent hashes).
+Each miner was run till 800k hashes were computed and the hash rate and buffer hit rate were sampled every 10k hashes.
+(Note that both the hash rate and buffer hit rate sampled at a particular time reflected the values over the 10k most recent hashes).
 

### 2018-04-05 paper/paper.tex
fixed analysis

@@
 \usepackage{algorithmic}
+\usepackage{amssymb}
 \newcommand{\trishita}[1]{{\color{magenta}\bfseries[Trishita: #1]}}
+\newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $\blacksquare$}
 
@@
 Our approach is based on a lazy evaluation technique designed to function within the expected limitations of the clients, including bounds on memory, computation and communication bandwidth to the server.
-We provide proofs-of-concept based in JavaScript and WebAssembly, with the latter reaching hash rates up to roughly 39kH/s, which is only 30.2\% slower than the corresponding native C++-based miner.
+We provide proofs-of-concept based in JavaScript and WebAssembly, with the latter reaching hash rates up to roughly 39 kiloHashes per second, which is only 30.2\% slower than the corresponding native C++-based miner.
 Finally, we explore several applications for which this hash rate seems practical, including monetization of web content, rate limitation, and private Ethereum networks.
@@
 \section{Introduction}
-In today's world, crypto-currencies are gaining more and more traction as a viable form of currency.
-As such, people have been looking for efficient ways to mine the numerous crypto-currencies available.
-While much of these efforts have included creating new hardware, there has been considerable work done in re-using existing infrastructure in smarter ways to increase performance.
-One such effort is seen in using web browser as a platform for distributed computing ~\cite{Cushing}.
-Furthermore, more recently, the growing popularity of CoinHive ~\cite{coinhive} shows that there have been successful endeavors in distributed web browser crypto-currency mining, reinforcing its viability as a concept.
-In this work, we attempt to further extend this field by providing an open\-source implementations of web-base miners for Ethereum in \verb|JavaScript| and \verb|WebAssembly|.
-Indeed, given that Ethereum has applications beyond being used as a currency, there are a multitude of applications like web authentication rate limiting, website usage tracking for advertisement companies, private Ethereum networks and web content monetization, where our miner is practical to use.
-
-\subsection{Related Work}
-So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling},~\cite{parallel},~\cite{orca}.
-Additionally, with the growing popularity of dynamic web-content and client side scripting languages like \verb|JavaScript| and \verb|WebAssembly|, web-browsers have also become a lucrative option for implementing distributed systems.
-As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow} ~\cite{Duda}.
-Indeed, ``Distributed Computing on an Ensemble of Browsers'' by Cushing~\cite{Cushing} shows that the \verb|JavaScript| Engine has had enough improvements in performance to make computationally heavy programs feasible in a distributed web browsing unit.
-% In addition, the work by Duda and Dłubacz~\cite{Duda} was instrumental in the field as one of the first web browsing computational systems to not require the host machine to install any additional applications in order to participate.
-This is important since we would want our web miner to be operable without requiring the user to install any unfamiliar software.
-Furthermore, \verb|WebAssembly|  ~\cite{webAssembly} is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to be only 20\% slower than native code ~\cite{wasmPerf}, as compared to the much slower \verb|JavsScript|.
-Instead of relying on \verb|JavaScript|, web developers can now write C/C++ and compile it into \verb|WebAssembly| using some of the openly available \verb|WebAssembly| compilers ~\cite{emscripten}.
-Indeed, given that now \verb|WebAssembly| is supported by all major browsers ~\cite{webAssembly}, industry is also making use of this powerful framework.
-One sees this through the recent development of increasingly popular Monero mining \verb|WebAssembly| library CoinHive ~\cite{coinhive}.
+Cryptocurrencies are increasingly gaining traction as a viable form of currency.
+This has been accompanied by a correspondingly increasing interest in the efficient validation (or \emph{mining}) of cryptocurrency transactions.
+Whereas initial efforts in this domain have focused on creating dedicated hardware for this task, %AT - citation needed
+more recent approaches have examined repurposing existing infrastructure.
+Indeed, one such class of efforts has focused on the use of client web browsers as a platform for distributed computing~\cite{Cushing}.
+The growing popularity of CoinHive~\cite{coinhive} is a case in point of the potential success of distributed in-browser cryptocurrency mining as a commercial (if malicious) enterprise.
 
 \subsection{Our Contributions}
-Our research involves providing implementations of a distributed, web browser based Ethereum miners in \verb|JavaScript| and \verb|WebAssembly|, and studying whether or not it is feasible for real world purposes.
+In this work, we explore the web-based crypocurrency mining of the popular Ethereum cryptocurrency, %AT - citation needed
+and posit a number of potential applications consequent to this platform.  As such, our main contributions are as follows:
+\begin{itemize}
+\item We provide an open-source implementaiton of a web-based Ethereum cryptominer in both \verb|JavaScript| and \verb|WebAssembly|.
+Though miners for other currencies exist in the wild (e.g.
+Coinhive), they are all properietary and closed-source.
+\item We posit a number of potential applications built upon such a platform, including rate-limiting server access, usage tracking, and content monetization.
+\item We provide analysis and experimental evidence of the potential efficacy of our approach to the applications above.
+\end{itemize}
+
+% Our research involves providing implementations of a distributed, web browser based Ethereum miners in \verb|JavaScript| and \verb|WebAssembly|, and studying whether or not it is feasible for real world purposes.
 While there has been prior academic work done in related fields, none of the distributed web browser implementations in these works involve crypto-currency mining.
@@
 The remainder of the paper is organized as follows.
-In Section 2 we discuss the various potential applications our miner could have.
-Then, in Section 3 we cover the relevant background to understand the functioning of the miner -- namely, a description of the Ethash, the Ethereum mining Proof-of-Work, and \verb|WebAssembly|, the language our best-performing browser miner is implemented in.
-Section 4 outlines our approach to distributing the Ethash PoW over numerous browsers given the resource constraints.
-Finally, we present the results in Section 5.
-We conclude and discuss the future work in Sections 6 and 7 respectively.
+In Section~\ref{sec:applications} we discuss various potential applications our mining platform.
+Then, in Section~\ref{sec:background} we cover the relevant background and related literature for our work.
+In particular, we provide a self-contained description of Ethash, the Ethereum mining Proof-of-Work (PoW), and \verb|WebAssembly|, the language in which we implement an efficient miner.
+Section~\ref{sec:approach} outlines our approach to distributing the Ethash PoW over numerous browsers, each with their own resource constraints.
+Finally, we present the results in Section~\ref{sec:results}.
+We conclude and discuss the future work in Sectionn~\ref{sec:conclusion}.
 
 \section{Applications}
+\label{sec:applications}
 % In this work, we propose approaches to mine Ethereum, a popular crypto-currency, in a distributed fashion through web browsers.
@@
 \section{Background}
+\label{sec:background}
 % \subsection{Ethereum}
@@
 This cache is simply an array 4 byte integers ~\cite{Ethmining}.
-The cache production process involves using the seed hash to first sequentially filling up X bytes of memory (size of the cache), then performing Y passes of the RandMemoHash algorithm ~\cite{randmemohash}.
+The cache production process involves using the seed hash to first sequentially fill up the Cache, then performing two passes of the RandMemoHash algorithm~\cite{randmemohash} on top of it to get the final Cache value.
 % This transforms the initial cache to give us the final value for the cache. 
@@
 
+\subsection{Related Work}
+So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling},~\cite{parallel},~\cite{orca}.
+Additionally, with the growing popularity of dynamic web-content and client side scripting languages like \verb|JavaScript| and \verb|WebAssembly|, web-browsers have also become a lucrative option for implementing distributed systems.
+As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow} ~\cite{Duda}.
+Indeed, ``Distributed Computing on an Ensemble of Browsers'' by Cushing~\cite{Cushing} shows that the \verb|JavaScript| Engine has had enough improvements in performance to make computationally heavy programs feasible in a distributed web browsing unit.
+% In addition, the work by Duda and Dłubacz~\cite{Duda} was instrumental in the field as one of the first web browsing computational systems to not require the host machine to install any additional applications in order to participate.
+This is important since we would want our web miner to be operable without requiring the user to install any unfamiliar software.
+Furthermore, \verb|WebAssembly|  ~\cite{webAssembly} is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to be only 20\% slower than native code ~\cite{wasmPerf}, as compared to the much slower \verb|JavsScript|.
+Instead of relying on \verb|JavaScript|, web developers can now write C/C++ and compile it into \verb|WebAssembly| using some of the openly available \verb|WebAssembly| compilers ~\cite{emscripten}.
+Indeed, given that now \verb|WebAssembly| is supported by all major browsers ~\cite{webAssembly}, industry is also making use of this powerful framework.
+One sees this through the recent development of increasingly popular Monero mining \verb|WebAssembly| library CoinHive~\cite{coinhive}.
+In terms of the potential monetization aspect of the project, there exists an ethical alternative to CoinHive called the Basic Attention Token ~\trishita{Need to citeNeed to cite}.
+The Basic Attention Token is an ERC20 Token built on Ethereum that is used along with the Brave browser to generate Ad revenue for website publishers by measuring a user's attention span on an advertisement.
+Note that this is not a replacement for Ad revenue, but a platform to balance the ties between website users, publishers, and advertisers.
+It ensures that users get only ads they would accept, advertisers pay for actual users instead of click bots, and publishers actually get revenue instead of pleading the users to turn off their Ad blockers.
+
 \section{Our Approach}
+\label{sec:approach}
 % \trishita{I think it would be nice if we show how we modified the algorithm shown in the previous section. I will add that over here}
@@
 In fact, while we show here that filling up 99.5\% of a buffer as big as the DAG takes 1.4 million hashes, whereas in reality it only takes half as many hashes, as shown in Section~\ref{sec:results} \\
-% \trishita{To Do: Still need to incorporate prof. Starobinski's  most recent feedback}
-\makebox[\textwidth][l]{If we define}
-\makebox[\textwidth][c]{Number of DAG slices = N}
-% \makebox[\textwidth][c]{Fraction of the DAG we want to buffer = $f_1$}
-\makebox[\textwidth][c]{Number of DAG slices needed to compute a single hash = a}
-\makebox[\textwidth][c]{Failure probability of finding a specific slice in the buffer (Buffer miss rate)= $\delta$}
+\begin{claim}
+If we define Number of DAG slices = $N$, number of DAG slices needed to compute a single hash = $a$, failure probability of finding a specific slice in the buffer (Buffer miss rate)= $\delta$, failure probability of computing a hash just using slices in the buffer = $\omega$, expected number of hashes it takes to fill the buffer = E(H), and the nth Harmonic Number = $H_n$, then: \\
+\begin{equation}
+	E(H) = \frac{N}{a}(H_{N} -H_{N\delta})
+\end{equation}
+\end{claim}
+
+% \makebox[\textwidth][l]{If we define}
+% \makebox[\textwidth][c]{Number of DAG slices = N}
+% \makebox[\textwidth][c]{Number of DAG slices needed to compute a single hash = a}
+% \makebox[\textwidth][c]{Failure probability of finding a specific slice in the buffer (Buffer miss rate)= $\delta$}
 % \makebox[\textwidth][c]{Failure probability of computing a hash just using slices in the buffer = $\omega$}
-\makebox[\textwidth][c]{nth Harmonic Number = $H_n$}
+% \makebox[\textwidth][c]{nth Harmonic Number = $H_n$}
+
+% keeping this out for now
+%%%%%%%%%%%%%%%%%%%%%%%%
 % \makebox[\textwidth][c]{Euler-Mascheroni constant = $\gamma = 0.57721566...$}
@@
 % \end{gather}
-The number of slices $n$ needed to fill up a buffer of size $f_1$ for a given $\delta$ is given by:
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{claimproof}
+The number of slices $n$ needed to fill up a buffer with $N$ slices for a given $\delta$ is given by:
 \begin{gather}
-	n = N(1-\delta) %= Nf_1(1-\frac{\omega}{a})
+	n = \left \lfloor{N(1-\delta)}\right \rfloor  %= Nf_1(1-\frac{\omega}{a})
 \end{gather}
-This means that we are willing to allocate a buffer that is fraction $f_1$ of the entire DAG, but instead of filling up all $Nf_1$ slices, we are willing to forgo $Nf_1\delta$ slices.
+This means that even though we are allocating a buffer that can hold $N$ slices, we are willing to forgo $N\delta$ slices.
 
-Now, using the Coupon Collector proof~\cite{couponCollector}, we know that the expected number of trials $E(t)$ of obtaining the $xth$ new slice after having buffered $x-1$ slices is:\\
+Now, using the Coupon Collector proof~\cite{couponCollector}, we know that the expected number of trials $E(t_i)$ of obtaining the $ith$ new slice after having buffered $i-1$ slices is:\\
 \begin{gather}
-	E(t_x) = \frac{N}{N-(x-1)}
+	E(t_i) = \frac{N}{N-(i-1)}
 \end{gather}
@@
 \begin{gather}
-	E(t) = \sum_{x=1}^{n}E(t_x) = N\sum_{x=1}^{n}\frac{1}{N-x+1} = Nf_1\sum_{x=1}^{N(1-\delta)}\frac{1}{N-x+1}
+	E(t) = \sum_{i=1}^{n}E(t_i) = N\sum_{i=1}^{n}\frac{1}{N-i+1} = N\sum_{i=1}^{\left \lfloor{N(1-\delta)}\right \rfloor}\frac{1}{N-i+1}
 \end{gather}
@@
 \begin{gather}
-	E(t) = N[\sum_{x=1}^{N}\frac{1}{N-x+1} - \sum_{x=N(1-\delta)+1}^{N}\frac{1}{N-x+1}] \\
-    E(t) = N[H_{N} -H_{N\delta}] \\
+	E(t) = N(\sum_{i=1}^{N}\frac{1}{N-i+1} - \sum_{i=\left \lfloor{N(1-\delta)}\right \rfloor+1}^{N}\frac{1}{N-i+1}) \\
+    \label{eq:expectedTrials}
+    E(t) = N(H_{N} -H_{N\delta})
+\end{gather}
+We now relate the failure probability of calculating a hash just from slices stored in the buffer with the failure probability of having a specific slice in the buffer:
+\begin{gather}
+	(1-\delta)^a = 1-\omega \\
+    (1-\delta)^a = 1-a\delta;\;\delta \to 0 \\
+	1-a\delta = 1-\omega \\
+    \label{eq:deltaomega}
+	\delta = \frac{\omega}{a}
+\end{gather}
+Hence, it follows from Equation~\ref{eq:deltaomega} that 
+\begin{gather}
+	\label{eq:hashvsslice}
+	E(H) = \frac{E(t)}{a}
+\end{gather}
+Finally, from Equation~\ref{eq:hashvsslice} and~\ref{eq:expectedTrials}, we obtain:
+\begin{gather}
     \label{eq:expectedHashes}
-	E(H) = \frac{N}{a}[H_{N} -H_{N\delta}]
+	E(H) = \frac{N}{a}(H_{N} -H_{N\delta})
 \end{gather}    
-Now, using equation~\ref{eq:expectedHashes}, bounds on Harmonic Numbers~\cite{harmonicNumber}, and setting $N = 16777186$, $f_1 = 1$, $a = 64$ and $\delta = 0$, we get $E(H) = 4.5$ million hashes.
-However, if we slightly increase $\delta$ to 0.005, we get $E(H) = 1.4$ million hashes.
+\end{claimproof}
+We now define the Euler-Mascheroni constant as $\gamma = 0.57721566...$ and use the following bounds on Harmonic Numbers~\cite{harmonicNumber} to obtain results when when using Equation~\ref{eq:expectedHashes}:
+\begin{gather}
+    \label{eq:boundHarmonic}
+	-\frac{1}{12n^2+{2\frac{7-12\gamma}{2\gamma-1}}}\le H_n-\ln n-\frac1{2n}-\gamma<-\frac{1}{12n^2+\frac{6}{5}}
+\end{gather}  
+% -\frac{1}{12n^2+{2(7-12\gamma)}/{(2\gamma-1)}}\le H(n)-\ln n-\frac1{2n}-\gamma<-\frac{1}{12n^2+6/5}
+
+Now, using Equations~\ref{eq:expectedHashes} and~\ref{eq:boundHarmonic}, and setting $N = 16777186$, $a = 64$ and $\delta = 0$, we get $E(H) \approx 4.5$ million hashes.
+However, if we slightly increase $\delta$ to 0.005, we get $E(H) \approx 1.4$ million hashes.
 Hence, we see that even computing merely 1.4 million hashes fills a DAG buffer as large as the entire DAG by more than 99.5\%, as opposed to calculating 4.5 million to fill the buffer entirely.
-(Note that this number should be smaller for smaller buffer sizes ($f_1 < 1$); so this is a rough upper bound).
 % This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up. 
@@
 \section{Results}
+\label{sec:results}
 \subsection{Experimental set up}
@@
 \begin{table}[t]
-\caption{Performance Difference accross different Implementations}\label{table:perf}
+\caption{Performance variations across different Implementations}\label{table:perf}
 \vspace{-2ex}
@@
 \section{Conclusion}
+\label{sec:conclusion}
 We have successfully created a proof of concept distributed, web-based Ethereum miner that can be used towards monetizing electronic content, web-authentication rate limiting, private test networks, user tracking for advertisers, etc.
@@
 
-\section{Future Work}
+\paragraph{Future Work}
 While we were able to create a browser based miner for Ethereum, there is still work to be done.

### 2018-04-09 paper/paper.tex
almossst done

@@
+% 
+% instead of saying lazy evaluation -- say how much time do we take 
+% some quantification on how much time does it take to get 
+% put challenges in introduction -- what does this make hard to solve? Put in the introduction. 
+% intro, one line on contributions, and put challenges in the beginning. -- this will allow to motivate better (can use dag, say you will explaon)
+
+% \para{application}: then application. Then a new para how our approach can be applied to the problem. Put the whole section at the end. Also put the references.
+
+% Don't use quotes on very long sentences. 
+% Put Javascrip Wasm section after Ethash. This section is too small. Do we really want it. 
+% Talk about wasm in one place, not two.
+
+% remove pseudocode.
+% Have a section of ethereum and define what block header and hash. Also define target etc 
+% dEFINE epoch early on. 
+% called Cache in ethereum terminology. Mention that the size of the cache varies right 
+% define lightweight and full node earlier.
+% Say each DAG consists of nodes and slices. Explain what 
+% Ads: talk about how our approach can be applied to
+
+% our approach --
+% how long -- our key contribution is to measure if this is viable to wait till the hash rate gets good. We need to mention this earlier. 
+% remove `n'
+% the video application. 
+% Have a name. 
+% its not clear that js was used. 
+% have a para on js and webasm in our approach. 
+% have the definitions before the claim. 
+% use a different var for Hash and 
+% put in the logs!!
+
+% look at all citations -- at least there should be a year and conference. 
+% more descriptive captions for figures.
+
+% minimize the jargon
+% experiments should reinforce what you say before.
+
 % This is samplepaper.tex, a sample chapter demonstrating the
@@
 \usepackage{amssymb}
-\newcommand{\trishita}[1]{{\color{magenta}\bfseries[Trishita: #1]}}
+\usepackage{caption}
+\newcommand{\trishita}[1]{}%{{\color{magenta}\bfseries[Trishita: #1]}}
 \newenvironment{claimproof}[1]{\par\noindent\underline{Proof:}\space#1}{\hfill $\blacksquare$}
@@
 %
-\title{Distributed Web Mining of Ethereum\thanks{Supported by organization x.}}
+\title{Distributed Web Mining of Ethereum
+% \thanks{Supported by organization x.}
+}
 %
@@
 These calculations are handled through individualized code that runs on the client browsers, and is thereafter collated at a web server to complete a mining operation.
-Our approach is based on a lazy evaluation technique designed to function within the expected limitations of the clients, including bounds on memory, computation and communication bandwidth to the server.
-We provide proofs-of-concept based in JavaScript and WebAssembly, with the latter reaching hash rates up to roughly 39 kiloHashes per second, which is only 30.2\% slower than the corresponding native C++-based miner.
+WebEth is based on a lazy evaluation technique designed to function within the expected limitations of the clients, including bounds on memory, computation and communication bandwidth to the server.
+We provide proofs-of-concept based in JavaScript and WebAssembly, with the latter reaching hash rates up to roughly 40 kiloHashes per second, which is only 30\% slower than the corresponding native C++-based miner.
 Finally, we explore several applications for which this hash rate seems practical, including monetization of web content, rate limitation, and private Ethereum networks.
@@
 We show that this solution is practical for a variety of purposes, such as web content monetization, web based authentication rate limiting and private Ethereum networks.
-% \trishita{I have not included a comparison with an actual miner that saves the entire DAG in memory from the start (i.e., doesn't use our lazy evaluation approach) -- should I do that for the abstract?}
 
@@
 Whereas initial efforts in this domain have focused on creating dedicated hardware for this task, %AT - citation needed
+\trishita{Add citation}
 more recent approaches have examined repurposing existing infrastructure.
@@
 The growing popularity of CoinHive~\cite{coinhive} is a case in point of the potential success of distributed in-browser cryptocurrency mining as a commercial (if malicious) enterprise.
+In this work, we propose WebEth, a browser-based distributed miner for the Ethereum block chain.
+Obtaining a profitable hash rate within a distributed ensemble of browsers under constrained memory, compute and network usage is non-trivial.
+This is primarily because every worker needs to store a 2GB data structure in memory in order to mine Ethereum.
+However, the naive approach of transferring the data structure over the network and storing it in memory every time a browser loads our web page is not viable.
+And so, WebEth employs an amortized approach to mining in order to operate under such constraints.
+In our experiments, this approach takes at most 5 minutes to reach a steady state hash rate -- making it ideal for websites where users spend more time, like video streaming websites.
+WebEth yields at most 40 kiloHashes/s, which despite the overhead from running the algorithm in a browser, is only 30\% lesser than the performance of the corresponding native miner that employs our algorithm, thereby proving that our approach is effective.
 
 \subsection{Our Contributions}
-In this work, we explore the web-based crypocurrency mining of the popular Ethereum cryptocurrency, %AT - citation needed
-and posit a number of potential applications consequent to this platform.  As such, our main contributions are as follows:
+In this work, we explore the web-based cryptocurrency mining of the popular Ethereum block chain, \trishita{Add citation}
+%AT - citation needed
+and propose a number of potential applications consequent to this platform.  As such, our main contributions are as follows:
 \begin{itemize}
-\item We provide an open-source implementaiton of a web-based Ethereum cryptominer in both \verb|JavaScript| and \verb|WebAssembly|.
+\item We propose WebEth, an open-source implementation of a distributed web-based Ethereum cryptominer in both \verb|JavaScript| and \verb|WebAssembly| that can operate under relatively resource constrained environments.
 Though miners for other currencies exist in the wild (e.g.
-Coinhive), they are all properietary and closed-source.
-\item We posit a number of potential applications built upon such a platform, including rate-limiting server access, usage tracking, and content monetization.
+CoinHive~\cite{coinhive}), they are all proprietary and closed-source.
+\item We propose a number of potential applications built upon such a platform, including rate-limiting server access, usage tracking, and content monetization.
 \item We provide analysis and experimental evidence of the potential efficacy of our approach to the applications above.
+\trishita{I feel like this next part is repetitive}Our miner employs an amortized approach to mining that takes $\approx$ 5 minutes for it to reach its maximum hash rate.
+In addition, we show that our \verb|WebAssembly| implementation can provide hash rates up to 40 kiloHashes/s, which is only 30\% smaller than the hash rate provided by a native C++ miner that employs the same algorithm.
 \end{itemize}
@@
 \subsection{Roadmap}
+\trishita{Fix this acc to the new orderigns}
 The remainder of the paper is organized as follows.
-In Section~\ref{sec:applications} we discuss various potential applications our mining platform.
-Then, in Section~\ref{sec:background} we cover the relevant background and related literature for our work.
+In Section~\ref{sec:background} we cover the relevant background and related literature for our work.
 In particular, we provide a self-contained description of Ethash, the Ethereum mining Proof-of-Work (PoW), and \verb|WebAssembly|, the language in which we implement an efficient miner.
-Section~\ref{sec:approach} outlines our approach to distributing the Ethash PoW over numerous browsers, each with their own resource constraints.
-Finally, we present the results in Section~\ref{sec:results}.
+Section~\ref{sec:approach} outlines WebEth's approach to distributing the Ethash PoW over numerous, resource-constrained browsers.
+Then, we present the results in Section~\ref{sec:results}.
+Finally, in Section~\ref{sec:applications} we discuss various potential applications our mining platform.
 We conclude and discuss the future work in Sectionn~\ref{sec:conclusion}.
-
-\section{Applications}
-\label{sec:applications}
-% In this work, we propose approaches to mine Ethereum, a popular crypto-currency, in a distributed fashion through web browsers.
-Our approach can be used for a variety of purposes, outlined as follows.
-\\ \\
-% \textbf{Web Content Monetization}
-With the growth in global Internet usage, hosting websites has become a lucrative business.
-As a result, new methods of monetizing electronic content have surfaced with time.
-While some are more successful than others, all of them have issues associated with them.
-For instance, selling advertisement space is now resulting in declining revenue \cite{decliningRevenue} for website owners due to the advent of new technologies such as AdBlock \cite{Adblock}, Brave Browser \cite{BraveBrowser}, etc.
-In addition, too many advertisements also tend to increase the loading time for web-pages.
-Moreover, such advertisements are sometimes not placed correctly and cover the contents of the website.
-Thus, this approach does not provide good user experience.
-\\ \\
-% Another approach involves subscriptions, however, it is not very successful.
-Indeed, as this study finds, users are becoming increasingly unlikely to pay for content \cite{noSubscriptions}.
-Website owners also use pay-per-click Advertising, however an approach often leads to the content being split over an excessive number of pages, thereby leading to consumer frustration \cite{payPerClick}.
-Thus, we see that each approach has its own issues, be it with  with website owners or clients.
-Hence, it is important to strike a balance and create a solution that would be able to benefit both parties.
-Our web-based miner would solve this situation as it does not
-% \textbf{Web-Authentication Rate Limiting}: 
-Another potential application could involve web-authentication rate limiting.
-Given the multitude of tools available brute forcing web login pages ~\cite{hydra} ~\cite{burpsuite}, it is extremely easy to brute force authentication pages these days.
-Currently, the way website owners mitigate this issue is by locking out a user for a certain amount of time after a fixed number of unsuccessful login attempts.
-% While this approach works in theory, in today's fast-paced world, users tend to dislike waiting for even a few seconds ~\cite{usersDislikeWaiting}. 
-While it seems as though this approach is effective at face value, in reality, it does more harm than good as by introducing the risk of Denial of Service.
-This is because most brute force attacks are large scale and try millions of username/password combinations, which would consequently lockout a large number of user accounts.
-While this may prevent an attacker from successfully cracking passwords, it would also deny service to a lot of legitimate users whose accounts were being brute forced.
-This, amongst other issues, would definitely reflect badly on the website owner, and hence opens a whole new avenue for attack.
-Given this situation, a more user-friendly approach to this problem involves embedding a Proof-of-Work (PoW) computation in the web page that the user's browser needs to successfully solve in order to be able to login.
-Requiring a PoW would require a large amount of computation power for brute force attempts, thereby selectively thwarting any attacker that attempts to brute force the login \emph{without} penalizing the legitimate user.
-This makes our implementation for the Ethereum PoW an ideal candidate, even more so since one could manually set the difficulty to obtain a balance between user experience and security.
-\\ \\
-One other use-case could involve website advertisement companies.
-Today, website advertising sponsors decide on the remuneration for a website by inspecting the logs of the web servers in order to deduce how much traffic the site receives.
-However, it is well known that these logs can be easily manipulated by the website owner in order to generate the impression of a large amount of traffic ~\cite{webLogsManipulation}.
-Our web miner could solve these issues as the advertiser could require the website owner to embed this miner within their website, thereby making the site visitors compute PoW hashes.
-The advertiser would then ask the website owner to submit hashes that pass a certain difficulty threshold (i.e., the value of the hash being less than a certain number), and the larger the number of hashes that the website owner can provide, the more the remuneration the site receives.
-This would be extremely difficult for the website owners to fake since they would have to compute hashes themselves, an endeavor that might be more expensive than the corresponding payout it would bring.\\ \\
-Finally, we would also like to note that Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- i.e., networks that do not mine on the actual, public Ethereum block-chain, but rather on private (and often smaller) instances of the crypto-currency.
-Our browser miner can be used on any such private network to serve the network owner whatever he/she wishes to implement with the mining PoW.
 
@@
 \label{sec:background}
-% \subsection{Ethereum}
+\subsection{Cryptocurrencies: a general overview}
 % \trishita{Not sure if I need this paragraph, since I think the readers will probably be familiar with what crypto-curriencies are}
-\subsection{JavaScript and WebAssembly}
-For very long, \verb|JavaScript| has been the only language available to make dynamic client side web content.
-However, the situation has changed since the advent of \verb|WebAssembly| in 2016.
-As per its creators, ``\verb|WebAssembly| is a binary instruction format for a stack-based virtual machine.
-Wasm is designed as a portable target for compilation of high-level languages like \verb|C/C++/Rust|, enabling deployment on the web for client and server applications.
-The \verb|WebAssembly| stack machine is designed to be encoded in a size- and load-time-efficient binary format.
-\verb|WebAssembly| aims to execute at native speed by taking advantage of common hardware capabilities available on a wide range of platforms'' ~\cite{webAssembly}.
-The language is meant to improve performance for computationally intensive use cases such as image/video editing, games, streaming, etc ~\cite{webAssembly}.
-This, and given the fact that CoinHive is also implemented in \verb|WebAssembly| ~\cite{coinhive}, makes the language a natural choice for us to implement a miner in.
-In fact, as of now, \verb|WebAssembly| is supported by 4 major browser versions -- Firefox, Safari, IE, and Chrome ~\cite{webAssembly}, which makes our miner implementation extremely versatile.
 
-% Like most crypto-currencies, it too is backed by a distributed block-chain, each block of which holds transactions for that particular block-chain.
-This block chain is operated on by the Ethereum Virtual Machine (EVM) ~\cite{EVM}, which, unlike Bitcoin Script, is Turing Complete ~\cite{turingComplete}.
-Furthermore, this currency is also a Proof-of-Work based currency, which means that the new blocks are appended to the block-chain through a process called ``mining''.
-Mining involves a race amongst miners to solve a Proof-of-Work puzzle (usually an energy intensive computation), the winner of which gets to have his block appended to the block-chain.
+Most cryptocurrencies like Ethereum involve storing transactions in blocks, and the entire history of transactions is collated in a data structure known as a block chain.
+The block chain is managed by dedicated machines called ``client nodes''; where each client node typically stores the entire block chain.
+However, because each client node operates on its own copy of the block chain, it is very easy for the block chains on different nodes to go out of sync.
+Hence, there needs to be an accepted mechanism to decide the order in which new transaction blocks are appended to this block chain.
+For this, every time a new transaction takes place, the transaction is thrown in with all other transactions that have ``taken place'', but haven't been added to the block chain yet.
+For most currencies, the data structure that stores this is known as the ``mem pool''.
+A miner then picks a few transactions from this mem pool and creates a new block from these transactions.
+Once this happens, the goal of the miner is to have his/her block appended to the block chain, which is achieved through a process called ``mining''.
+% This block chain is operated on by the Ethereum Virtual Machine (EVM) ~\cite{EVM}, which, unlike Bitcoin Script, is Turing Complete ~\cite{turingComplete}. 
+% Furthermore, this currency is also a Proof-of-Work based currency, which means that the new blocks are appended to the block-chain through a process called ``mining''. 
+Mining involves a race amongst miners to solve a ``Proof-of-Work puzzle'' (usually an energy intensive computation), the winner of which gets to have his block appended to the block-chain.
 The winner also receives a payout, which acts as an incentive to mine.
-This process of mining is essential to deciding the order in which transactions are appended to the inherently decentralized block-chain, thereby stabilizing the chain.
+% This process of mining is essential to deciding the order in which transactions are appended to the inherently decentralized block-chain, thereby stabilizing the chain. 
 Ethereum uses Ethash as its Proof-of-Work (PoW) algorithm, which is explained in detail below.
 
-\subsection{Ethash}
+\subsection{Ethereum and its PoW, Ethash}
 Ethereum is a crypto-currency that was released in July 2015 by Vitalik Buterin, Gavin Wood and Jeffrey Wilcke.
@@
 \begin{itemize}
-\item \textbf{Seed}: Ethash operates by first generating a 256 bit seed.
-This seed is different for every epoch (30,000 blocks).
-For the first epoch it is the Keccak-256 hash of a series of 32 bytes of zeros.
+\item \textbf{Block Header}: A block header contains meta-data related to the transactions of the block it pertains to, and is provided as an input to the Ethash algorithm.
+\item \textbf{Nonce}: An integer that is provided as an input to the hashing algorithm in the hopes that when hashed with the block header, will yield a hash value less than a certain predefined difficulty threshold.
+It is also provided as an input to Ethash.
+\item \textbf{Difficulty Threshold}: An integer value below which the hash digest output of Ethash should be in order for the miner to have successfully mined the block.
+\item \textbf{Mining overview}: The Ethash mining algorithm primarily involves computing a hash of the current block header and nonce.
+If the output of the hash (the digest) lies below the difficulty threshold; the block is said to have been successfully mined.
+Hence, the miner keeps iterating over nonces until he/she gets a digest that lies below the difficulty threshold.
+Once the miner finds the right nonce, he/she then broadcasts the block, the header and the nonce so that the other client nodes can update their block chain to include this newly mined block.
+\item \textbf{Verification}: Once a block has been mined by a miner, it is propagated to other client nodes so that they can update their copies of the block chain.
+However, before each client node does so, it must validate whether the miner is submitting a legitimate block -- i.e., check whether the miner genuinely solved the hash as claimed.
+This is easily done by putting the block header and nonce associated with the block through the Ethash algorithm and checking whether the output indeed lies below the difficulty threshold.
+\item \textbf{Light Weight Client Nodes}
+Some client nodes do not mine new blocks, but just verify whether any new block submitted by a miner is valid or not. These are called light weight client nodes.
+\item \textbf{Full Client Nodes}
+Full client nodes mine new blocks.
+\item \textbf{Epoch}: A unit of ``time'' that spans 30,000 blocks.
+\item \textbf{Seed}: All of the data structures in Ethash (mentioned below) need a 256 bit seed.
+This seed is different for every Epoch.
+For the first epoch it is the Keccak-256~\trishita{CITE} hash of a series of 32 bytes of zeros.
 For every other epoch it is always the Keccak-256 hash of the previous seed hash.
-\item \textbf{Cache}: The seed for a particular epoch is used to compute a pseudo-random cache.
-This cache is simply an array 4 byte integers ~\cite{Ethmining}.
+\item \textbf{Cache}: The seed for a particular epoch is used to compute a data structure known as the Cache.
+This Cache is simply an array 4 byte integers ~\cite{Ethmining}.
 The cache production process involves using the seed hash to first sequentially fill up the Cache, then performing two passes of the RandMemoHash algorithm~\cite{randmemohash} on top of it to get the final Cache value.
 % This transforms the initial cache to give us the final value for the cache. 
-Lightweight clients may use this cache for verifying hashes (discussed below), while full node clients can use it to calculate a DAG (Directed Acyclic Graph) dataset, as described below. 
+Light weight clients may use this cache for verifying hashes (discussed below), while full node clients can use it to calculate a Directed Acyclic Graph (DAG) dataset, as described below. 
 \item \textbf{DAG}: A Directed Acyclic Graph stored as a large byte array (currently around 2GB in size). The DAG has the following two attributes:
@@
   \item \textbf{Page}: Each DAG page spans 2 nodes, however, page accesses are not aligned at a 2 node boundary.
-The mining process involves accessing some DAG pages and hashing them together with the header and nonce.
+The mining process involves accessing some DAG pages and hashing them together with the block header and nonce.
   \end{enumerate}
-Each node in the DAG is generated by combining data from 256 pseudorandomly selected cache nodes and hashing them together. This process is repeated to generate all nodes in the DAG.
+Each node in the DAG is generated by combining data from 256 pseudo-randomly selected cache nodes and hashing them together. This process is repeated to generate all nodes in the DAG.
+\item \textbf{Mix:} An intermediate byte array used to store temproary results in the Ethash algorithm.
 \end{itemize}
-We must point out that as time goes on, mining Ethereum becomes more and more difficult, as the size of the DAG and Cache increases with every Epoch.
+We must point out that as time goes on, mining Ethereum becomes more and more difficult, as the size of the Cache and DAG increases with every Epoch.
 
@@
 This process of sequentially fetching parts of the DAG is repeated 64 times (step 4), and the final value of the Mix is put through a transformation to obtain a 32 byte digest (step 5).
-This digest is then compared to the threshold (step 6), and if it is lesser than it, the nonce is valid and the block is successfully mined and can be broadcast to the network.
+This digest is then compared to the threshold (step 6), and if it is smaller than it, the nonce is valid and the block is successfully mined and can be broadcast to the network.
 However, if the digest is greater than the threshold, the nonce is unsuccessful, and the entire process must be repeated with a new nonce ~\cite{Ethmining}.
-Below is the pseudo-code for the algorithm for completeness.\\
-\begin{algorithmic}[H]
-\label{miningAlgo}
-\STATE $mix \gets mixInit(\{header,nonce\})$
-\FOR{$i = 0;\;i < 64;\;i++$}
-  \STATE $dagPageIndex \gets getDAGPageIndexFromMix(mix)$
-  \STATE $dagPage \gets DAG[dagPageIndex]$
-  \STATE $dagPageIndex \gets updateMix(dagPage,mix)$
-\ENDFOR
-\STATE $digest \gets postProcessFunction(mix)$
-\IF {$digest <= targetThreshold$}
-	\RETURN \TRUE
-\ENDIF
-\RETURN \FALSE
-\end{algorithmic}
+
+% Below is the pseudo-code for the algorithm for completeness.\\
+% \begin{algorithmic}[H]
+% \label{miningAlgo}
+% \STATE $mix \gets mixInit(\{header,nonce\})$
+% \FOR{$i = 0;\;i < 64;\;i++$}
+%   \STATE $dagPageIndex \gets getDAGPageIndexFromMix(mix)$
+%   \STATE $dagPage \gets DAG[dagPageIndex]$
+%   \STATE $mix \gets updateMix(dagPage,mix)$
+% \ENDFOR
+% \STATE $digest \gets postProcessFunction(mix)$
+% \IF {$digest <= targetThreshold$}
+% 	\RETURN \TRUE
+% \ENDIF
+% \RETURN \FALSE
+% \end{algorithmic}
+
 It is important to note that the parts of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence there is no way to pre-determine which parts will be useful to have in memory.
@@
 While mining is memory intensive, verification is relatively lightweight.
-This is because of the property that each ``slice'' in the DAG depends on a set of pseudo-randomly selected items from the Cache.
-Hence, the Cache is used to regenerate only the specific slices of the DAG that are needed to recalculate the hash for the particular nonce.
-And so only the Cache needs to be stored by clients that perform just verification.
-We use this property of being able to generate the parts of the DAG as needed to our advantage in order to alleviate some of the memory and network bandwidth restrictions that browsers typically face.
+This is because of the property that each node in the DAG depends on a set of pseudo-randomly selected items from the Cache.
+Hence, the Cache is used to regenerate only the specific nodes of the DAG that are needed to recalculate the hash for the particular nonce.
+And so only the Cache needs to be stored by light weight clients that only perform verification.
+We use this property of being able to generate parts of the DAG as needed to our advantage in order to alleviate some of the memory and network bandwidth restrictions that browsers typically face.
 
@@
 
+\subsection{JavaScript and WebAssembly}
+Introduced in 1995 by Netscape Communications Corporation~\cite{https://auth0.com/blog/a-brief-history-of-javascript/}, \verb|JavaScript| was a meant to be a light scripting language in order to  make web content dynamic.
+Over the span of 23 years, it has grown to become one of the most popular client-side web development languages used to make dynamic user interfaces.
+
+In fact, up to recently, \verb|JavaScript| has been the only language available to make dynamic client side web content.
+However, the situation has changed since the advent of \verb|WebAssembly| in 2016.
+As per its creators, \verb|WebAssembly| is a ``binary instruction format for a stack-based virtual machine''.
+WASM is designed to be compiled from high-level languages like \verb|C/C++/Rust|, and is supported by 4 major browser versions -- Firefox, Safari, IE, and Chrome ~\cite{webAssembly}.
+The \verb|WebAssembly| stack machine is designed to be encoded in a ``size-and load-time-efficient binary format''~\cite{webAssembly}, and aims to execute near native speed by utilizing common hardware capabilities available on a wide range of platforms~\cite{webAssembly}.
+The language is meant to improve performance for computationally intensive use cases such as image/video editing, games, streaming, etc~\cite{webAssembly}.
+This, and given the fact that CoinHive is also implemented in \verb|WebAssembly| ~\cite{coinhive}, makes the language a natural choice for us to implement a miner in.
+% In fact, as of now, \verb|WebAssembly| is supported by 4 major browser versions -- Firefox, Safari, IE, and Chrome ~\cite{webAssembly}, which makes our miner implementation extremely versatile.
+
 \subsection{Challenges}
 % \trishita{Too long of a sentence; need to reword}
-Given that we now know that the crux of having a good hashrate for Ethereum lies in having quick access to the DAG, one of the biggest challenges with mining it on a distributed ensemble of browsers would be to transfer and store this data structure within each worker browser.
-However, given that the DAG for an Ethereum network is at least 1GB (and growing) in size transferring it to the browser every time a client loads our web page would be impractical.
-Furthermore, even if we somehow manage to transfer the DAG to the client when the web page loads, the browser would still have to store it in memory, thereby using a sizeable amount of resources on the client machine.
-We attempt to address some of these concerns through our approach as discussed in the next section.
+The crux of having a good hashrate for Ethereum lies in having quick access to the DAG.
+One of the biggest challenges with mining on a distributed ensemble of browsers is to transfer and store this data structure within each worker browser.
+However, given that the DAG for an Ethereum network is at least 1GB (and growing), transferring it to the browser every time a client loads our web page would be impractical.
+Furthermore, even if one somehow manages to transfer the DAG to the client when the web page loads, the browser still has to store the DAG in memory, thereby using a sizeable amount of resources on the client machine.
+In section~\ref{sec:approach} we discuss approaches to tackle some of these challenges.
 
 \subsection{Related Work}
-So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling},~\cite{parallel},~\cite{orca}.
+So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling,parallel,orca}.
 Additionally, with the growing popularity of dynamic web-content and client side scripting languages like \verb|JavaScript| and \verb|WebAssembly|, web-browsers have also become a lucrative option for implementing distributed systems.
-As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow} ~\cite{Duda}.
+As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow,Duda}.
 Indeed, ``Distributed Computing on an Ensemble of Browsers'' by Cushing~\cite{Cushing} shows that the \verb|JavaScript| Engine has had enough improvements in performance to make computationally heavy programs feasible in a distributed web browsing unit.
@@
 This is important since we would want our web miner to be operable without requiring the user to install any unfamiliar software.
-Furthermore, \verb|WebAssembly|  ~\cite{webAssembly} is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to be only 20\% slower than native code ~\cite{wasmPerf}, as compared to the much slower \verb|JavsScript|.
+% Furthermore, \verb|WebAssembly|  ~\cite{webAssembly} is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to be only 20\% slower than native code ~\cite{wasmPerf}, as compared to the much slower \verb|JavsScript|.
 Instead of relying on \verb|JavaScript|, web developers can now write C/C++ and compile it into \verb|WebAssembly| using some of the openly available \verb|WebAssembly| compilers ~\cite{emscripten}.
 Indeed, given that now \verb|WebAssembly| is supported by all major browsers ~\cite{webAssembly}, industry is also making use of this powerful framework.
-One sees this through the recent development of increasingly popular Monero mining \verb|WebAssembly| library CoinHive~\cite{coinhive}.
-In terms of the potential monetization aspect of the project, there exists an ethical alternative to CoinHive called the Basic Attention Token ~\trishita{Need to citeNeed to cite}.
+One sees the growing popularity of distributed web computation through the recent development of increasingly popular Monero mining library CoinHive~\cite{coinhive}.
+In terms of the potential monetization aspect of the project, there exists an ethical alternative to CoinHive called the Basic Attention Token~\trishita{Need to cite}.
 The Basic Attention Token is an ERC20 Token built on Ethereum that is used along with the Brave browser to generate Ad revenue for website publishers by measuring a user's attention span on an advertisement.
@@
 
-\section{Our Approach}
+\section{WebEth}
 \label{sec:approach}
+\subsection{Approach}
 % \trishita{I think it would be nice if we show how we modified the algorithm shown in the previous section. I will add that over here}
-We propose a lazy-evaluation based approach to alleviate the network and memory requirements for mining Ethereum in a distributed scenario on browsers.
-Specifically, as soon as each browser connects to the webserver, the server sends it the current header of the block being mined and the Cache.
-Once the browser receives the Cache, it allocates an array buffer to store the DAG slices that fall between indices 0 and $n$ that will be computed in the future.
-(Note that the $n$ is a variable parameter reflecting the length of the buffer with which we experiment in our analysis).
+We propose a amortized evaluation based approach to alleviate the network and memory requirements for mining Ethereum in a distributed scenario on browsers.
+Specifically, as soon as each browser connects to the webserver, the server sends to the browser the current header of the block being mined and the Cache.
+Once the browser receives the Cache, it allocates an array buffer to store the DAG nodes that fall between indices 0 and $N$ that will be computed in the future.
+(Note that the $N$ is a variable parameter reflecting the length of the buffer with which we experiment in our analysis).
 Once the buffer is allocated, the browser can start iterating over nonces to compute hashes.
 
-Since, to begin with, the browser does not have any slices of the DAG, it must compute each slice on the fly using the Cache.
-However, for every such slice that the browser computes, it then stores it in the buffer (if it fits within the allocated bounds, otherwise it is simply discarded), for quicker access in the future.
-Hence, as time passes, the buffer starts filling up and so more and more slices are quickly accessed from the buffer rather than being computed from the ground-up, which makes hash computations faster with time.
+Since, to begin with, the browser does not store any nodes of the DAG, it must compute each node on the fly using the Cache.
+However, for every such node that the browser computes, it then stores it in the buffer (if it fits within the allocated bounds, otherwise it is simply discarded), for quicker access in the future.
+Hence, as time passes, the buffer starts filling up and so more and more nodes are quickly accessed from the buffer rather than being computed from the ground-up, which makes hash computations faster with time.
 This has the effect that the longer the user remains on the web-page, the better the hashrate gets for that user.
-Our modified algorithm is shown below:
 
-\begin{algorithmic}[H]
-\label{modifiedMiningAlgo}
-\STATE $mix \gets mixInit(\{header,nonce\})$
-\FOR{$i = 0;\;i < 64;\;i++$}
-  \STATE $dagPageIndex \gets getDAGPageIndexFromMix(mix)$
-  \STATE $dagPage \gets DAGbuffer[dagPageIndex]$
-  \IF {$dagPage == NULL$}
-		\STATE $dagPage = computeDAGPageFromCache(dagPageIndex)$
-        \STATE $DAGbuffer[dagPageIndex] = dagPage$
-  \ENDIF  
-  \STATE $dagPageIndex \gets updateMix(dagPage,mix)$
-\ENDFOR
-\STATE $digest \gets postProcessFunction(mix)$
-\IF {$digest <= targetThreshold$}
-	\RETURN \TRUE
-\ENDIF
-\RETURN \FALSE
-\end{algorithmic}
+% Our modified algorithm is shown below:
 
-\subsection{Architecture}
+% \begin{algorithmic}[H]
+% \label{modifiedMiningAlgo}
+% \STATE $mix \gets mixInit(\{header,nonce\})$
+% \FOR{$i = 0;\;i < 64;\;i++$}
+%   \STATE $dagPageIndex \gets getDAGPageIndexFromMix(mix)$
+%   \STATE $dagPage \gets DAGbuffer[dagPageIndex]$
+%   \IF {$dagPage == NULL$}
+% 		\STATE $dagPage = computeDAGPageFromCache(dagPageIndex)$
+%         \STATE $DAGbuffer[dagPageIndex] = dagPage$
+%   \ENDIF  
+%   \STATE $mix \gets updateMix(dagPage,mix)$
+% \ENDFOR
+% \STATE $digest \gets postProcessFunction(mix)$
+% \IF {$digest <= targetThreshold$}
+% 	\RETURN \TRUE
+% \ENDIF
+% \RETURN \FALSE
+% \end{algorithmic}
+
+\subsection{Implementation}
 % \begin{figure}[H]
@@
 We modified it so that instead of mining all by itself, it simply sends over the necessary data needed to mine (the hash of the Block Header and the Cache) to any client that connects to it on port \verb|9000|.
-After recieving the necessary data, the browser allocates a buffer for the DAG in order to store future slices.
+After receiving the necessary data, the browser allocates a buffer for the DAG in order to store future nodes.
 Note that the buffer for the DAG is implemented as an array of ints, so as to make each lookup in the buffer $\theta(1)$.
@@
 For our miner, we modeled our \verb|JavaScript| implementation based on the ~\verb|node.js| implementation of Ethash~\cite{ethash}.
+The \verb|WebAssembly| version is simply the \verb|JavaScript| version transpiled to \verb|C++|, and compiled to \verb|WebAssembly| using the ~\verb|Emscripten| compiler~\cite{emscripten}.
+
 To begin, the miner creates a random nonce and computes the hash (using the Cache and the buffered DAG) as discussed in the previous section.
@@
 
-\subsection{Theoretical Analysis}
-With this lazy-evaluation based approach, we can calculate exactly how many hashes we would have to compute in order to fill up a buffer of a given size.
+\subsection{Performance Analysis}
+With this amortized evaluation based approach, we can calculate exactly how many hashes we would have to compute in order to fill up a buffer of a given size.
 This is important because once the buffer in the browser fills up, the hash rate that the browser gives is at its maximum, steady-state.
 In this section, we will mathematically demonstrate that filling a buffer the size of the DAG up should take at most 4.5 million hashes, while filling up 99.5\% of this buffer takes merely 1.4 million hashes.
-This is a significant difference since in our experimental set-up, the browser takes X s to compute 4.5 million hashes, while only Y s to compute 1.4 million hashes.
+% This is a significant difference since in our experimental set-up, the browser takes X s to compute 4.5 million hashes, while only Y s to compute 1.4 million hashes. 
 The approach we take is similar to the Coupon Collector problem \cite{couponCollector}, and is discussed below.
@@
 In fact, while we show here that filling up 99.5\% of a buffer as big as the DAG takes 1.4 million hashes, whereas in reality it only takes half as many hashes, as shown in Section~\ref{sec:results} \\
+
+% time: 272364.700001
+% glue.js:1 num Hashes: 1270782
+% glue.js:1 cache hit: 0.999990
+% miner.js:105 Client hashes average hashrate: 0
+
+% c 1370000:  0.999972
+% glue.js:1 h 1370000:  49975.012494
+
+If we define Number of DAG slices = $N$, number of DAG slices needed to compute a single hash = $a$, failure probability of finding a specific slice in the buffer (Buffer miss rate)= $\delta$, failure probability of computing a hash just using slices in the buffer = $\omega$, expected number of hashes it takes to fill the buffer = E(X), and the nth Harmonic Number = $H_n$, then: \\
 \begin{claim}
-If we define Number of DAG slices = $N$, number of DAG slices needed to compute a single hash = $a$, failure probability of finding a specific slice in the buffer (Buffer miss rate)= $\delta$, failure probability of computing a hash just using slices in the buffer = $\omega$, expected number of hashes it takes to fill the buffer = E(H), and the nth Harmonic Number = $H_n$, then: \\
 \begin{equation}
-	E(H) = \frac{N}{a}(H_{N} -H_{N\delta})
+	E(X) \approx \frac{N}{a}(H_{N} -H_{N\delta});\;\delta \to 0
 \end{equation}
@@
 	(1-\delta)^a = 1-\omega \\
-    (1-\delta)^a = 1-a\delta;\;\delta \to 0 \\
-	1-a\delta = 1-\omega \\
+    (1-\delta)^a = 1-a\delta + o(\delta);\;\delta \to 0 \\
+	1-a\delta + o(\delta) = 1-\omega;\;\delta \to 0 \\
     \label{eq:deltaomega}
-	\delta = \frac{\omega}{a}
+	\delta \approx \frac{\omega}{a};\;\delta \to 0 
 \end{gather}
@@
 	\label{eq:hashvsslice}
-	E(H) = \frac{E(t)}{a}
+	E(X) \approx \frac{E(t)}{a};\;\delta \to 0 
 \end{gather}
@@
     \label{eq:expectedHashes}
-	E(H) = \frac{N}{a}(H_{N} -H_{N\delta})
+	E(X) \approx \frac{N}{a}(H_{N} -H_{N\delta});\;\delta \to 0 
 \end{gather}
+
+% Now,
+% \begin{gather}
+% 	H_N \approx \ln{N} + \gamma + o(1)
+% \end{gather}
+% Substituting this in Equation ~\ref{eq:expectedHashes} gives us:
+% \begin{gather}
+% 	E(X) \approx \frac{N}{a}(\ln{N} + \gamma + o(1) - (\ln{N\delta} + \gamma + o(1))) \\
+%     E(X) \approx \frac{N}{a}(\ln{N} - (\ln{N\delta}))
+% \end{gather}
+
 \end{claimproof}
-We now define the Euler-Mascheroni constant as $\gamma = 0.57721566...$ and use the following bounds on Harmonic Numbers~\cite{harmonicNumber} to obtain results when when using Equation~\ref{eq:expectedHashes}:
+We now define the Euler-Mascheroni constant as $\gamma = 0.57721566...$ and use the following bounds on Harmonic Numbers~\cite{harmonicNumber} to bound the results obtained from Equation~\ref{eq:expectedHashes}:
 \begin{gather}
     \label{eq:boundHarmonic}
-	-\frac{1}{12n^2+{2\frac{7-12\gamma}{2\gamma-1}}}\le H_n-\ln n-\frac1{2n}-\gamma<-\frac{1}{12n^2+\frac{6}{5}}
+	-\frac{1}{12N^2+{2\frac{7-12\gamma}{2\gamma-1}}}\le H_N-\ln N-\frac1{2N}-\gamma<-\frac{1}{12N^2+\frac{6}{5}}
 \end{gather}  
@@
 
-Now, using Equations~\ref{eq:expectedHashes} and~\ref{eq:boundHarmonic}, and setting $N = 16777186$, $a = 64$ and $\delta = 0$, we get $E(H) \approx 4.5$ million hashes.
+Now, using Equations~\ref{eq:expectedHashes} and~\ref{eq:boundHarmonic}, and setting $N = 16777186$ (the number of nodes in the DAG for our experiments), $a = 64$ and $\delta = 0$, we get $E(H) \approx 4.5$ million hashes.
 However, if we slightly increase $\delta$ to 0.005, we get $E(H) \approx 1.4$ million hashes.
@@
 % This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up. 
-In fact, as we will see in the results, filling up 99.5\% of a buffer as large as the DAG already starts giving us good hash rates for a browser -- 35kH/s for the ~\verb|WebAssembly| miner, whereas the hash rate for a completely full buffer is only marginally higher at XkH/s.
-This means that reaching a reasonably steady state is not as hard as it seems at face value, making this approach viable for web setting where users might not stay on websites for long. 
-% Given this result, we compute 800k hashes for all our experiments, as discussed in the next section.
+In fact, as we will see in the results, filling up 99.5\% of a buffer as large as the DAG already starts giving us good hash rates for a browser -- 35kH/s for the ~\verb|WebAssembly| miner, whereas the hash rate for a completely full buffer is only marginally higher at 49kH/s.
+This means that reaching a reasonably steady state is not as hard as it seems at face value, making WebEth viable for web setting where users might not stay on websites for long.
 
@@
 
-% Interestingly, since for realistic cases $n >> f_1$, $\frac{1}{nf_1} \to 0$, and so 
-% \begin{gather}
-% E(H) \approx \frac{n}{64}\log{\frac{1}{1-f_2}}
-% \end{gather}
-% Figure X shows a graph of how $E(H)$ varies as a function of the fraction of the buffer that we want to be full, $f$ if we set $n = 16777186$ (the total number of DAG slices on the experimental private test network).
-
-% Beyond that, the marginal cost of computing more hashes outweighs the rate at which the DAG is filled up. Hence, as we will see in the next section, for our experiments, we compute 800,000 hashes.
-
 \section{Results}
@@
 
-% \subsection{Baseline results}
-% For our control results, we ran \verb|Geth|~\cite{geth}, a native miner written in \verb|Go| that stores the entire DAG in memory from the start (as opposed to using this lazy evaluation approach), and obtained an average hashrate of X H/s.
-
-% We also ran our lazy-evaluation based miner written in C++ outside of the browser, and obtained the following results. 
-% Figure X below shows a heat-map of how the hash rate varies as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.
-Figures X then shows a heat-map of how the DAG buffer hit-rate varies as a function of both the size of the buffer allocated to store the DAG and the number of hashes computed in the browser.
-
-% .
-Since the hashrate determines how fast a mining rig can verify a nonce, it was necessary to ensure that our results were not skewed due to the differences in computing power between computers.
-Using this machine, we recorded the hashrates for CPU performance and GPU performance on our private Ethereum testnet.
-% Additionally, we also recorded the hashrates for CPU mining in a Kali Linux VM.
-As we can see in the figure below, the GPU clearly outperforms the CPUs resulting in an average hashrate of 5.72MH/s.
-As for the CPUs, both miners performed about the same, both hovering around a respectable 210kH/s.
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{GPU.png}
-% \caption{\label{fig:gpu} GPU vs CPU Hashrates}
-% \end{figure}
-
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{CPU.png}
-% \caption{\label{fig:cpu} VM CPU vs CPU Hashrates}
-% \end{figure}
-
 \subsection{Implementation Results}
 \label{sec:results}
-Figures~\ref{fig:NativeMinerHM},~\ref{fig:WebAsmMinerHM} and ~\ref{fig:JSMinerHM} below shows a heat-map of how the hash rate varies for each of the three implementations as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.
-% \trishita{To Do: chanege to log scale, fix size }
+Figures~\ref{fig:hashRateHMWASM},~\ref{fig:hashRateHMJS} and~\ref{fig:hashRateHMNative} below shows a heat-map of how the hash rate varies for each of the three implementations as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.
 
@@
 \centering
-\includegraphics[width=250px,keepaspectratio]{Native_C++_Miner_Hash_Rate_HM.pdf}
-\caption{\label{fig:NativeMinerHM} Native Miner: $\log{Hash Rate}$}
+\includegraphics[width=200px,keepaspectratio]{All_Miners_Hash_Rate.pdf}
+\caption{Native Miner: $\log{Hash Rate}$}
+\label{fig:HashRateTraj} 
 \end{figure}
 
-\begin{figure}[h]
+\begin{figure}[t]
        \centering
-\includegraphics[width=250px,keepaspectratio]{WebAssembly_Miner_Hash_Rate_HM.pdf}
-\caption{\label{fig:WebAsmMinerHM} WebAssembly Miner: $\log{Hash Rate}$}
+    \makebox[\textwidth][c]{
+    \begin{minipage}{.5\textwidth}
+       \centering
+  \includegraphics[width=\linewidth]{WebAssembly_Miner_Hash_Rate_HM.pdf}
+\caption{WASM Miner $\log(Hash Rate)$}
+\label{fig:hashRateHMWASM}
+   \end{minipage}
+       \begin{minipage}{.5\textwidth}
+       \centering
+    \includegraphics[width=\linewidth]{JavaScript_Miner_Hash_Rate_HM.pdf}
+\caption{JS Miner $\log(Hash Rate)$}
+\label{fig:hashRateHMJS}
+    \end{minipage}}
 \end{figure}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=250px,keepaspectratio]{JavaScript_Miner_Hash_Rate_HM.pdf}
-\caption{\label{fig:JSMinerHM} JavaScript Miner: $\log{Hash Rate}$}
-\end{figure}
-
-% \begin{figure}[!htb]
-% \minipage{\textwidth}
-%   \includegraphics[width=\linewidth]{Native_C++_Miner_Hash_Rate_HM.pdf}
-% \endminipage\hfill
-% \minipage{\textwidth}
-%   \includegraphics[width=\linewidth]{WebAssembly_Miner_Hash_Rate_HM.pdf}
-% \endminipage\hfill
-% \minipage{\textwidth}
-%   \includegraphics[width=\linewidth]{JavaScript_Miner_Hash_Rate_HM.pdf}
-% \endminipage
-% \caption{Hash Rate as a function of number of Hashes computed and Buffer Size}\label{fig:hashRateHM}
-% \end{figure}
 
@@
 
-One way to reach the steady state hashrate faster for a given sized buffer would be to start out with a partially filled out buffer instead of an empty one.
+One way to reach the steady state hash rate faster for a given sized buffer would be to start out with a partially filled out buffer instead of an empty one.
 The only way this could work is by sending over part of the DAG over the network to the client.
-However, as it turns out, this is not feasible since, for a DAG with 16777186 slices (1.074 GB) sending even 10\% of the DAG would be sending $\approx100MB$ of data.
-With the global average download speed for desktops and smartphones being around 5.34MBps and 2.77MBps respectively ~\cite{internetSpeed}, the web page load time would be in the order of 20 seconds to a minute -- which is too long to get a mere 10\% boost in the buffer storage.
+However, as it turns out, this is not feasible since, for a DAG with 16777186 nodes (1.074 GB) sending even 10\% of the DAG would be sending $\approx100MB$ of data.
+With the global average download speed for desktops and smartphones being around 5.34MBps and 2.77MBps respectively~\cite{internetSpeed}, the web page load time would be in the order of 20 seconds to a minute -- which is too long to get a mere 10\% boost in the buffer storage.
 
-The jump in the hash rate for high buffer hit rates is also seen in figure ~\ref{fig:bufferRatevsHashRate} where we show the correlations between the buffer hit rates and the hash rates for all 3 miners.
+The jump in the hash rate for high buffer hit rates is also seen in Figure~\ref{fig:HashRateTraj} where we show the correlations between the buffer hit rates and the hash rates for all 3 miners.
 The general trend is the same for all 3 miners -- the hash rate spikes up as the hit rate surpasses 95\% (Note that the hit rate gets extremely close to 1 but never quite reaches there, since we only compute 800k hashes as opposed to the 4.5 million would be needed as per our theoretical analysis).
 
-\begin{figure}[h]
+\begin{figure}[t]
+\captionsetup{justification=centering}
        \centering
-\includegraphics[width=250px,keepaspectratio]{All_Miners_Hash_Rate.pdf}
-\caption{\label{fig:bufferRatevsHashRate} Buffer Hit Rate vs Hash Rate for all miners}
+    \makebox[\textwidth][c]{
+    \begin{minipage}{.5\textwidth}
+       \centering
+  \includegraphics[width=\linewidth]{Native_C++_Miner_Hash_Rate_HM.pdf}
+  \caption{Native C++ Miner $\log(Hash Rate)$}
+  \label{fig:hashRateHMNative}
+   \end{minipage}
+       \begin{minipage}{.5\textwidth}
+       \centering
+    \includegraphics[width=\linewidth]{All_Miners_Buffer_Hit_Rate.pdf}
+    \caption{All Miners' Buffer Hit Rate}
+    \label{fig:HitRateHM}
+    \end{minipage}}
+\caption{Log(Hash Rate) and Buffer hit rate as a function of number of Hashes computed and Buffer Size}
 \end{figure}
 
-Figure~\ref{fig:bufferRateHM} then shows a heat-map of how the DAG buffer hit-rate varies as a function of both the size of the buffer allocated to store the DAG and the number of hashes computed in the browser.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=250px,keepaspectratio]{All_Miners_Buffer_Hit_Rate.pdf}
-\caption{\label{fig:bufferRateHM} Buffer Hit Rate}
-\end{figure}
+Figure~\ref{fig:HitRateHM} then shows a heat-map of how the DAG buffer hit-rate varies as a function of both the size of the buffer allocated to store the DAG and the number of hashes computed in the browser.
 
@@
 
-% \trishita{Got rid of figs 8 9 and 10 since we don't have much room}
-% In Figures~\ref{fig:NativeWebAsm},~\ref{fig:WebAsmJS} and~\ref{fig:NativeJS} we show the percentage difference of the hashrates between the native miner and the browser miner implementations.
-We also compare the performance of the ~\verb|JavaScript| and ~\verb|WebAssembly|  miners.
-
-% \begin{figure}[h]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{Native_Miner_vs_WebAssembly_miner_Hash_Rate_Percent_Improvement.pdf}
-% \caption{\label{fig:NativeWebAsm} Native miner vs. WebAssembly miner Hash Rate Percent Improvement}
-% \end{figure}
-
-% \begin{figure}[h]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{WebAssembly_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
-% \caption{\label{fig:WebAsmJS} WebAssembly miner vs. JavaScript miner Hash Rate Percent Improvement}
-% \end{figure}
-
-% \begin{figure}[h]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{Native_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
-% \caption{\label{fig:NativeJS} Native miner vs. JavaScript miner Hash Rate Percent Improvement}
-% \end{figure}
-
-% \begin{figure}[!htb]
-% \minipage{0.32\textwidth}
-%   \includegraphics[width=\linewidth]{WebAssembly_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
-% \endminipage\hfill
-% \minipage{0.32\textwidth}
-%   \includegraphics[width=\linewidth]{Native_Miner_vs_WebAssembly_miner_Hash_Rate_Percent_Improvement.pdf}
-% \endminipage\hfill
-% \minipage{0.32\textwidth}
-%   \includegraphics[width=\linewidth]{Native_Miner_vs_JavaScript_miner_Hash_Rate_Percent_Improvement.pdf}
-% \endminipage
-% \caption{Percentage difference in Hash Rates for different miner implementations}\label{fig:PerfChangeHM}
-% \end{figure}
-
-Finally, we tabulate the most important results from our analysis in table ~\ref{table:results}
-\trishita{To Do: Fill in other, meaningful, metrics -- any suggestions?}
+Finally, we tabulate the most important results from our analysis in Table~\ref{table:results}
 
@@
 Peak Hash Rate &  56800H/s &  10626H/s & 39651H/s \\
-\makecell{Maximum Time to reach steady state \\ hash rate (buffer as large as DAG)}  &  X s &  X s & X s\\ 
+\makecell{Time taken to 99.76\% \\ buffer hit rate}  &  163.601s &  879.857s & 257.7692s\\ 
 \makecell{Avg. Hash Rate \% diff with Native Miner \\
@@
 
+\section{Potential Applications}
+\label{sec:applications}
+% In this work, we propose approaches to mine Ethereum, a popular crypto-currency, in a distributed fashion through web browsers.
+Our approach can be used for a variety of purposes, outlined as follows.
+\\ \\
+\paragraph{\textbf{Web Content Monetization}}:
+With the growth in global Internet usage, hosting websites has become a lucrative business.
+As a result, new methods of monetizing electronic content have surfaced with time.
+Though some are more successful than others, all of them have associated issues.
+For instance, selling advertisement space is now resulting in declining revenue for website owners due to the advent of new technologies such as AdBlock \cite{Adblock}, Brave Browser \cite{BraveBrowser}, \cite{decliningRevenue}; when coupled with an increased load time, browser slow-down, and placement challenges, online ads adversely affect user experience.
+Website content can also be monetized through client-size coin mining, utilizing techniques such as those presented in this work.
+Although, as our analysis shows, earning real cash requires a significant subscriber base or a large amount of time spent on the website, making this an ideal approach for video streaming websites.
+% Another approach involves subscriptions, however, it is not very successful.
+Indeed, as this study finds, users are becoming increasingly unlikely to pay for content \cite{noSubscriptions}.
+Website owners also use pay-per-click Advertising, however an approach often leads to the content being split over an excessive number of pages, thereby leading to consumer frustration \cite{payPerClick}.
+Thus, we see that each approach has its own issues, be it with  with website owners or clients.
+Hence, it is important to strike a balance and create a solution that would be able to benefit both parties.
+Our web-based miner would solve this situation as it does not
+% \textbf{Web-Authentication Rate Limiting}: 
+\paragraph{\textbf{Web Authentication Rate Limiting}}:
+Another potential application relates to rate limiting of web-authentication.
+Many tools are openly available for brute forcing web login pages~\cite{hydra,burpsuite}.
+Currently, website owners mitigate these attacks is by locking out a user for a certain amount of time after a fixed number of unsuccessful login attempts or presenting a captcha~\cite{recaptcha}.
+% While this approach works in theory, in today's fast-paced world, users tend to dislike waiting for even a few seconds ~\cite{usersDislikeWaiting}. 
+Lock out presents a Denial of Service potential by locking out legitimate users as a consequence of an attack. 
+Captcha techniques can be used for third-party value~\cite{von2008recaptcha} and have been successfully attacked through machine learning techniques and crowdsourcing.~\trishita{CITEEE...}%AT - citation needed here!
+
+% While it seems as though this approach is effective at face value, in reality, it does more harm than good as by introducing the risk of Denial of Service.
+This is because most brute force attacks are large scale and try millions of username/password combinations, which would consequently lockout a large number of user accounts.
+While this may prevent an attacker from successfully cracking passwords, it would also deny service to a lot of legitimate users whose accounts were being brute forced.
+This, amongst other issues, would definitely reflect badly on the website owner, and hence opens a whole new avenue for attack.
+We posit a more user-friendly approach to this problem involving embedding a Proof-of-Work (PoW) computation in a web page that the user's browser needs to successfully solve in order to be able to login.
+The PoW would amplify the computational power needed for brute force attempts, thereby selectively thwarting any attacker that attempts to brute force the login \emph{without} significantly penalizing the legitimate user.
+Ethereum PoW is an especially good candidate for such an implementation because one could manually set the difficulty to obtain a balance between user experience and security.
+
+\paragraph{\textbf{Proof of Web Traffic}}:
+One other use-case could involve website advertisement companies.
+Today, website advertising sponsors decide on the remuneration for a website based on summarized server logs as a measure for site traffic.
+\trishita{CITE!!} These logs can be manipulated by a website owner to generate the impression of a large amount of traffic ~\cite{webLogsManipulation} or by ad injectors~\cite{adinjection}.
+WebEth could be embedded by a website owner within its website, thereby making the site visitors compute PoW hashes.
+The advertiser would then ask the website owner to submit hashes that pass a certain difficulty threshold (i.e., the value of the hash being less than a certain number), and the larger the number of hashes that the website owner can provide, the more the remuneration the site receives.
+This would be more difficult for the website owners to fake since they would have to compute hashes themselves, an endeavor that might be more expensive than the potential ad payout.
+
+\paragraph{\textbf{Private Ethereum Test Networks}}:
+Finally, we would also like to note that Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- \emph{i.e.,} networks that do not mine the public Ethereum block-chain, but rather a private (and often smaller) instance of the crypto-currency.
+WebEth can be used on any such private network to serve the network owner's specific interests.
+
 \section{Conclusion}
 \label{sec:conclusion}
-We have successfully created a proof of concept distributed, web-based Ethereum miner that can be used towards monetizing electronic content, web-authentication rate limiting, private test networks, user tracking for advertisers, etc.
-Our implementation is standalone, and hence can simply be embedded within a website without having the client install any external dependencies.
-We get the best steady state hash rates for our \verb|JavaScript| and \verb|WebAssembly| implementations (10.6k and 39.6k respectively) when the cache hit rates approach 1, (which takes approx 800k Hashes).
+We have designed and implemented an open-source proof of concept distributed, web-based Ethereum miner, with potential applications toward monetizing electronic content, rate limiting, private test networks, user tracking for advertisers, and the like.
+WebEth is standalone, implemented in both \verb|JavaScript| and \verb|WebAssembly| but require no external dependencies, meaning that they can be readily embedded within many websites.
+We have also provided analyses and experimental data to help in engineering our proposed applications.
 
@@
 
-\paragraph{Future Work}
-While we were able to create a browser based miner for Ethereum, there is still work to be done.
-As was shown, our current implementation is far slower than the traditional methods for mining.
+\paragraph{\textbf{Future Work}}
+A variety of issues remain open.
+For one, our current implementation is significantly slower than traditional mining methods.
 One way we can look to speed this process up is to tap into the client machine's GPU.
@@
 
-\bibitem{ethash}Matthew Wampler, et al. Ethash. Computer software. GitHub. Vers. 23.1. GitHub, 11 Jan. 2015. Web. 24 Feb. 2018. <https://github.com/ethereum/ethash>.
+\bibitem{ethash}Matthew Wampler, et al. Ethash. Computer software. GitHub. Vers. 23.1. GitHub, 11 Jan. 2015. Web. 24 Feb. 2018. https://github.com/ethereum/ethash.
 
@@
 \bibitem{decliningRevenue} Hern, Alex.
-“Adblock Plus: the Tiny Plugin Threatening the Internet's Business Model.” The Guardian, Guardian News and Media, 14 Oct.
+``Adblock Plus: the Tiny Plugin Threatening the Internet's Business Model.'' The Guardian, Guardian News and Media, 14 Oct.
 2013, www.theguardian.com/technology/2013/oct/14/the-tiny-german-company-threatening-the-internets-business-model.
 
-\bibitem{dagger-hashimoto} Buterin, Vitalik, et al. “Ethereum/Wiki.” GitHub, GitHub, 9 Feb. 2014, github.com/ethereum/wiki/blob/master/Dagger-Hashimoto.md.
+\bibitem{dagger-hashimoto} Buterin, Vitalik, et al. ``Ethereum/Wiki.'' GitHub, GitHub, 9 Feb. 2014, github.com/ethereum/wiki/blob/master/Dagger-Hashimoto.md.
 
 \bibitem{noSubscriptions} Rosenwald, Micheal.
-“Digital News Consumers Unlikely to Pay for Content and Increasingly Block Ads.” Columbia Journalism Review, Columbia Journalism Review, 15 June 2015, www.cjr.org/analysis/reuters\_digital\_news\_report.php.
+``Digital News Consumers Unlikely to Pay for Content and Increasingly Block Ads.'' Columbia Journalism Review, Columbia Journalism Review, 15 June 2015, www.cjr.org/analysis/reuters\_digital\_news\_report.php.
 
 \bibitem{payPerClick} Fessenden, Therese.
-“Nielsen Norman Group.” The Most Hated Online Advertising Techniques, Nielsen Norman Group, 4 June 2017, www.nngroup.com/articles/most-hated-advertising-techniques/.
+``Nielsen Norman Group.'' The Most Hated Online Advertising Techniques, Nielsen Norman Group, 4 June 2017, www.nngroup.com/articles/most-hated-advertising-techniques/.
 
 \bibitem{celebEndorse} Awad, Amal.
-“A Study in Scarlett: The Ethics of Celebrity Endorsement.” – Opinion – ABC Religion \&Amp; Ethics (Australian Broadcasting Corporation), Amal Awad ABC Religion and Ethics, 30 Jan.
+``A Study in Scarlett: The Ethics of Celebrity Endorsement.'' – Opinion – ABC Religion \&Amp; Ethics (Australian Broadcasting Corporation), Amal Awad ABC Religion and Ethics, 30 Jan.
 2014, www.abc.net.au/religion/articles/2014/01/31/3935443.htm.
 
-% \bibitem{Boldrin} Boldrin, F., et al.
-“Distributed Computing Through Web Browser.” Distributed Computing Through Web Browser - IEEE Conference Publication, University of Ferrara, ieeexplore.ieee.org/document/4350073/.
-
 \bibitem{scheduling}
-Ramamritham, Krithi, and John A. Stankovic. "Dynamic task scheduling in hard real-time distributed systems." IEEE software 1.3 (1984): 65.
+Ramamritham, Krithi, and John A. Stankovic. ``Dynamic task scheduling in hard real-time distributed systems.'' IEEE software 1.3 (1984): 65.
 
@@
 \bibitem{orca}
-Bal, Henri E., M. Frans Kaashoek, and Andrew S. Tanenbaum. "Orca: A language for parallel programming of distributed systems." IEEE transactions on software engineering 18.3 (1992): 190-205.
+Bal, Henri E., M. Frans Kaashoek, and Andrew S. Tanenbaum. ``Orca: A language for parallel programming of distributed systems.'' IEEE transactions on software engineering 18.3 (1992): 190-205.
 
 \bibitem{WebFlow}
-Bhatia, Dimple; Burzevski, Vanco; Camuseva, Maja; and Fox, Geoffrey C., "WebFlow - A Visual Programming Paradigm for Web/Java Based Coarse Grain Distributed Computing" (1997).
+Bhatia, Dimple; Burzevski, Vanco; Camuseva, Maja; and Fox, Geoffrey C., ``WebFlow - A Visual Programming Paradigm for Web/Java Based Coarse Grain Distributed Computing'' (1997).
 Northeast Parallel Architecture Center.
 
-\bibitem{Cushing} Cushing, Reginald, et al. “Distributed Computing on an Ensemble of Browsers.” IEEE Internet Computing, IEEE, 1 Sept. 2013, www.computer.org/csdl/mags/ic/2013/05/mic2013050054.html.
+\bibitem{Cushing} Cushing, Reginald, et al. ``Distributed Computing on an Ensemble of Browsers.'' IEEE Internet Computing, IEEE, 1 Sept. 2013, www.computer.org/csdl/mags/ic/2013/05/mic2013050054.html.
 
-\bibitem{randmemohash} Lerner, Sergio Demian. "STRICT MEMORY HARD HASHING FUNCTIONS (PRELIMINARY V0. 3, 01-19-14)."
+\bibitem{randmemohash} Lerner, Sergio Demian. ``Strict Memory Hard Hashing Functions (Preliminary V0. 3, 01-19-14)."
 
@@
 \bibitem{pow}
-Laurie, Ben, and Richard Clayton. "Proof-of-work proves not to work; version 0.2." Workshop on Economics and Information, Security. 2004.
+Laurie, Ben, and Richard Clayton. ``Proof-of-work proves not to work; version 0.2.'' Workshop on Economics and Information, Security. 2004.
 
 \bibitem{casper}
-Hertig, Alyssa. “Ethereum's Big Switch: The New Roadmap to Proof-of-Stake.” CoinDesk, CoinDesk, 16 May 2017, www.coindesk.com/ethereums-big-switch-the-new-roadmap-to-proof-of-stake/.
+Hertig, Alyssa. ``Ethereum's Big Switch: The New Roadmap to Proof-of-Stake.'' CoinDesk, CoinDesk, 16 May 2017, www.coindesk.com/ethereums-big-switch-the-new-roadmap-to-proof-of-stake/.
 
 \bibitem{pos}
-Dmitry Buterin, et al. “Proof of Work vs Proof of Stake: Basic Mining Guide.” Blockgeeks, Blockgeeks, 24 July 2017, blockgeeks.com/guides/proof-of-work-vs-proof-of-stake/.
+Dmitry Buterin, et al. ``Proof of Work vs Proof of Stake: Basic Mining Guide.'' Blockgeeks, Blockgeeks, 24 July 2017, blockgeeks.com/guides/proof-of-work-vs-proof-of-stake/.
 
-\bibitem{arc}
-The ArcticCoin Team. ArcticCoin crypto-currency. ArcticCoin. Software, 2015.
+% \bibitem{arc}
+% The ArcticCoin Team. ArcticCoin crypto-currency. ArcticCoin. Software, 2015.
 
-\bibitem{Monero} “Monero - Secure, Private, Untraceable.” Getmonero.org, The Monero Project, getmonero.org/.
+\bibitem{Monero} ``Monero - Secure, Private, Untraceable.'' Getmonero.org, The Monero Project, getmonero.org/.
 
 \bibitem{Duda} Duda, Jerzy, and Wojciech Dłubacz.
-“Distributed Evolutionary Computing System Based on Web Browsers with Javascript.” ACM Digital Library, Springer-Verlag, dl.acm.org/citation.cfm?id=2451764.2451780.
+``Distributed Evolutionary Computing System Based on Web Browsers with Javascript.'' ACM Digital Library, Springer-Verlag, dl.acm.org/citation.cfm?id=2451764.2451780.
 
@@
 
-\bibitem{PoSproof}Dale, Oliver. "Beginner's Guide to Ethereum Casper Hardfork: What You Need to Know". Blocknomi, 7 November 2017. (https://blockonomi.com/ethereum-casper/)
+\bibitem{PoSproof}Dale, Oliver. ``Beginner's Guide to Ethereum Casper Hardfork: What You Need to Know''. Blocknomi, 7 November 2017. (https://blockonomi.com/ethereum-casper/)
 
 \bibitem{Ethmining}
-Wood, Gavin. "Ethereum: A secure decentralised generalised transaction ledger." Ethereum Project Yellow Paper 151 (2014): 1-32.
+Wood, Gavin. ``Ethereum: A secure decentralised generalised transaction ledger.'' Ethereum Project Yellow Paper 151 (2014): 1-32.
 
-\bibitem{geth}Péter Szilágyi, et al. Geth. Computer software. GitHub. Vers. 1.8.1. GitHub, 22 Dec. 2013. Web. 24 Feb. 2018. <https://github.com/ethereum/go-ethereum>.
+\bibitem{geth}Péter Szilágyi, et al. Geth. Computer software. GitHub. Vers. 1.8.1. GitHub, 22 Dec. 2013. Web. 24 Feb. 2018. https://github.com/ethereum/go-ethereum.
 
@@
 
-\bibitem{webAssembly}  W3C Team. WebAssembly. Program documentation. WebAssembly. Vers. 1.0. WebAssembly, 17 Mar. 2017. Web. 28 Mar. 2018. <http://webassembly.org>.
+\bibitem{webAssembly}  W3C Team. WebAssembly. Program documentation. WebAssembly. Vers. 1.0. WebAssembly, 17 Mar. 2017. Web. 28 Mar. 2018. http://webassembly.org.
 
 \bibitem{wasmPerf} Zlatkov, Alexander.
-"How JavaScript Works: A Comparison with WebAssembly." SessionStack Blog.
+``How JavaScript Works: A Comparison with WebAssembly.'' SessionStack Blog.
 SessionStack Blog, 21 Nov.
@@
 2018.
-<https://blog.sessionstack.com/how-javascript-works-a-comparison-with-webassembly-why-in-certain-cases-its-better-to-use-it-d80945172d79>.
+https://blog.sessionstack.com/how-javascript-works-a-comparison-with-webassembly-why-in-certain-cases-its-better-to-use-it-d80945172d79.
 
@@
 2018.
-<http://kripken.github.io/emscripten\-site/docs/getting\_started/Tutorial.html>.
+http://kripken.github.io/emscripten\-site/docs/getting\_started/Tutorial.html.
 
-\bibitem{internetSpeed} Ookla. “Speedtest Global Index – Monthly Comparisons of Internet Speeds from around the World.” Speedtest Global Index, Ookla, 25 Mar. 2018, www.speedtest.net/global-index.
+\bibitem{internetSpeed} Ookla. ``Speedtest Global Index – Monthly Comparisons of Internet Speeds from around the World.'' Speedtest Global Index, Ookla, 25 Mar. 2018, www.speedtest.net/global-index.
+
 \bibitem{hydra}  Fogerlie, Garrett, director.
@@
 \bibitem{burpsuite} Mahmood, Osama.
-“Brute Force Website Login Page Using Burpsuite –.” SecurityTraning, SecurityTraning, 5 Feb.
+``Brute Force Website Login Page Using Burpsuite –.'' SecurityTraning, SecurityTraning, 5 Feb.
 2018, securitytraning.com/brute-force-website-login-page-using-burpsuite/.
@@
 \bibitem{harmonicNumber} Guo, Bai-Ni \& Qi, Feng. (2011). Sharp bounds for harmonic numbers. Applied Mathematics and Computation. 218. 991-. 10.1016/j.amc.2011.01.089.
+
+\bibitem{recaptcha} Google recaptcha, \url{https://www.google.com/recaptcha/intro/}.
+
+\bibitem{von2008recaptcha} Von Ahn, Luis and Maurer, Benjamin and McMillen, Colin and Abraham, David and Blum, Manuel, ``Recaptcha: Human-based character recognition via web security measures'', Science, vol.
+321, no.
+5895, pp.
+1465-1468, 2008.
+
+\bibitem{adinjection} Thomas, Kurt, et al. ``Ad injection at scale: Assessing deceptive advertisement modifications.'' IEEE Symposium on Security and Privacy, 2015.
+
 \end{thebibliography}

### 2018-04-10 paper/paper.tex
final CSCML paper

@@
 % define lightweight and full node earlier.
-% Say each DAG consists of nodes and slices. Explain what 
+% Say each DAG consists of nodes and pages. Explain what 
 % Ads: talk about how our approach can be applied to
@@
 \usepackage{graphicx}
-\usepackage{balance}
-\usepackage{color}
+% \usepackage{balance}
+% \usepackage{color}
 \usepackage{makecell}
 \usepackage{amsmath}
-\usepackage{algorithmic}
+% \usepackage{algorithmic}
 \usepackage{amssymb}
@@
 \begin{abstract}
-We consider the problem of mining crytocurrencies by harnessing the inherent distribution capabilities of the World Wide Web. More specifically, we consider
-the mining of the Ethereum cryptocurrency by apportioning elements of the corresponding Proof-of-Work calculations among a number of web clients.
-These calculations are handled through individualized code that runs on the client browsers, and is thereafter collated at a web server to complete a mining operation.
-WebEth is based on a lazy evaluation technique designed to function within the expected limitations of the clients, including bounds on memory, computation and communication bandwidth to the server.
-We provide proofs-of-concept based in JavaScript and WebAssembly, with the latter reaching hash rates up to roughly 40 kiloHashes per second, which is only 30\% slower than the corresponding native C++-based miner.
-Finally, we explore several applications for which this hash rate seems practical, including monetization of web content, rate limitation, and private Ethereum networks.
-Though several distributed web-based cryptominers have appeared in the wild (for other currencies), either in malware or in commercial trials, we believe that this is the first open-source cryptominer of this type.
+We consider the problem of mining crytocurrencies by harnessing the inherent distribution capabilities of the World Wide Web.
+More specifically, we propose, analyze, and implement \verb|WebEth|, a browser-based distributed miner of the Ethereum cryptocurrency.
+\verb|WebEth| handles Proof-of-Work (PoW) calculations through individualized code that runs on the client browsers, and thereafter collates them at a web server to complete the mining operation.
+\verb|WebEth| is based on an lazy evaluation technique designed to function within the expected limitations of the clients, including bounds on memory, computation and communication bandwidth to the server.
+We provide proofs-of-concept of \verb|WebEth| based on \verb|JavaScript| and \verb|WebAssembly| implementations, with the latter reaching hash rates up to roughly 40 kiloHashes per second, which is only 30\% slower than the corresponding native \verb|C++|-based miner.
+Finally, we explore several applications of \verb|WebEth|, including monetization of web content, rate limitation to server access, and private Ethereum networks.
+Though several distributed web-based cryptominers have appeared in the wild (for other currencies), either in malware or in commercial trials, we believe that \verb|WebEth| is the first open-source cryptominer of this type.
 % The process of legitimating cryptocurrencies (such as Bitcoin and Ethereum) is done
@@
 This has been accompanied by a correspondingly increasing interest in the efficient validation (or \emph{mining}) of cryptocurrency transactions.
-Whereas initial efforts in this domain have focused on creating dedicated hardware for this task, %AT - citation needed
+Whereas initial efforts in this domain have focused on creating dedicated hardware for this task ~\cite{asics}, %AT - citation needed
 \trishita{Add citation}
@@
 The growing popularity of CoinHive~\cite{coinhive} is a case in point of the potential success of distributed in-browser cryptocurrency mining as a commercial (if malicious) enterprise.
-In this work, we propose WebEth, a browser-based distributed miner for the Ethereum block chain.
-Obtaining a profitable hash rate within a distributed ensemble of browsers under constrained memory, compute and network usage is non-trivial.
-This is primarily because every worker needs to store a 2GB data structure in memory in order to mine Ethereum.
-However, the naive approach of transferring the data structure over the network and storing it in memory every time a browser loads our web page is not viable.
-And so, WebEth employs an amortized approach to mining in order to operate under such constraints.
-In our experiments, this approach takes at most 5 minutes to reach a steady state hash rate -- making it ideal for websites where users spend more time, like video streaming websites.
-WebEth yields at most 40 kiloHashes/s, which despite the overhead from running the algorithm in a browser, is only 30\% lesser than the performance of the corresponding native miner that employs our algorithm, thereby proving that our approach is effective.
 
-\subsection{Our Contributions}
-In this work, we explore the web-based cryptocurrency mining of the popular Ethereum block chain, \trishita{Add citation}
-%AT - citation needed
-and propose a number of potential applications consequent to this platform.  As such, our main contributions are as follows:
+In this work, we propose \verb|WebEth|, a browser-based distributed miner for the popular Ethereum block chain~\cite{ethereum}.
+\verb|WebEth| tackles the challenge of achieving a profitable hash rate within a distributed ensemble of browsers under constrained memory, computation and network usage.
+Indeed, every browser needs to store a data structure of at least 1~GB in memory in order to mine Ethereum.
+Clearly, it is unfeasible to transfer this entire data structure every time a browser loads a web page.
+Instead, \verb|WebEth| employs an lazy approach to generating this data structure while mining.
+Through our experiments, we show that this approach takes at most five minutes to reach a steady state hash rate -- making it ideal for web applications where users spend time, such as gaming and video streaming.
+Our experiments also show that \verb|WebEth| yields a hashing rate of up to 40 kiloHashes/s, which, despite the overhead from running the algorithm in a browser, is only 30\% smaller than the performance of a corresponding miner running natively.
+
+%\subsection{Our Contributions}
+%In this work, we explore the web-based cryptocurrency mining of the popular Ethereum block chain, % %\trishita{Add citation}%AT - citation needed
+%and propose a number of potential applications consequent to this platform.
+
+The main contributions of this work are as follows:
 \begin{itemize}
-\item We propose WebEth, an open-source implementation of a distributed web-based Ethereum cryptominer in both \verb|JavaScript| and \verb|WebAssembly| that can operate under relatively resource constrained environments.
+\item We propose \verb|WebEth| \cite{WebEth}, an open-source implementation of a distributed web-based Ethereum cryptominer in both \verb|JavaScript| and \verb|WebAssembly| that can operate under relatively resource constrained environments.
 Though miners for other currencies exist in the wild (e.g.
 CoinHive~\cite{coinhive}), they are all proprietary and closed-source.
-\item We propose a number of potential applications built upon such a platform, including rate-limiting server access, usage tracking, and content monetization.
-\item We provide analysis and experimental evidence of the potential efficacy of our approach to the applications above.
-\trishita{I feel like this next part is repetitive}Our miner employs an amortized approach to mining that takes $\approx$ 5 minutes for it to reach its maximum hash rate.
+\item We provide theoretical analysis and experimental evidence of the potential efficacy of the lazy approach adopted by \verb|WebEth| to achieve high hashing rates.
+%\trishita{I feel like this next part is repetitive}Our miner employs an lazy approach to mining that takes $\approx$ 5 minutes for it to reach its maximum hash rate.
 In addition, we show that our \verb|WebAssembly| implementation can provide hash rates up to 40 kiloHashes/s, which is only 30\% smaller than the hash rate provided by a native C++ miner that employs the same algorithm.
+\item We propose a number of potential applications built upon \verb|WebEth|, including rate-limiting server access, usage tracking, and content monetization.
 \end{itemize}
@@
 
-\subsection{Roadmap}
-\trishita{Fix this acc to the new orderigns}
+\paragraph{Related Work}
+Distribution of a common task is hardly a new concept~\cite{scheduling,parallel,orca}, but the growing popularity and efficiency of dynamic web content and client-side scripting languages like \verb|JavaScript| and \verb|WebAssembly|
+have made web browsers an enticing implementation option~\cite{WebFlow,Duda,Cushing}.  Coinhive~\cite{coinhive} has
+built into this environment a proprietary method for mining the Monero cryptocurrency, but this is often done on
+the browsers of unsuspecting users.
+A more ethical, open-sourced alternative, the Basic Attention Token~\cite{basicAttentionToken}, is an Ethereum-based ERC20 token~\cite{erc20} currently in development to be used in conjunction with the Brave browser~\cite{BraveBrowser} to generate ad revenue for website publishers by \emph{measuring a user's attention} on an advertisement.
+This platform promises to balance the ties between website users, publishers, and advertisers to ensure that users get only ads they would accept, advertisers pay for actual users (instead of click bots), and publishers actually get revenue instead of begging users to turn off their ad blockers.
+
+% So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling,parallel,orca}.
+Additionally, with the growing popularity of dynamic web-content and client side scripting languages like \verb|JavaScript| and \verb|WebAssembly|, web-browsers have also become a lucrative option for implementing distributed systems.
+As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow,Duda,Cushing}.
+% Indeed, ``Distributed Computing on an Ensemble of Browsers'' by Cushing~\cite{Cushing} shows that the \verb|JavaScript| Engine has had enough improvements in performance to make computationally heavy programs feasible in a distributed web browsing unit.
+% In addition, the work by Duda and Dłubacz~\cite{Duda} was instrumental in the field as one of the first web browsing computational systems to not require the host machine to install any additional applications in order to participate.
+This is important since we would want our web miner to be operable without requiring the user to install any unfamiliar software.
+% Furthermore, \verb|WebAssembly|  ~\cite{webAssembly} is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to be only 20\% slower than native code ~\cite{wasmPerf}, as compared to the much slower \verb|JavsScript|.
+Instead of relying on \verb|JavaScript|, web developers can now write C/C++ and compile it into \verb|WebAssembly| using some of the openly available \verb|WebAssembly| compilers ~\cite{emscripten}.
+Indeed, given that now \verb|WebAssembly| is supported by all major browsers ~\cite{webAssembly}, industry is also making use of this powerful framework.
+
+% One sees the growing popularity of distributed web computation through the recent development of increasingly popular Monero mining library CoinHive~\cite{coinhive}.
+In terms of the potential monetization aspect of the project, there exists an ethical alternative to CoinHive called the Basic Attention Token ~\cite{basicAttentionToken}.
+The Basic Attention Token is an ERC20 Token built on Ethereum that is used along with the Brave browser to generate Ad revenue for website publishers by measuring a user's attention span on an advertisement.
+Note that this is not a replacement for Ad revenue, but a platform to balance the ties between website users, publishers, and advertisers.
+It ensures that users get only ads they would accept, advertisers pay for actual users instead of click bots, and publishers actually get revenue instead of pleading the users to turn off their Ad blockers.
+
+\paragraph{Roadmap}
 The remainder of the paper is organized as follows.
-In Section~\ref{sec:background} we cover the relevant background and related literature for our work.
+In Section 2\ref{sec:background} we cover the relevant background and related literature for our work.
 In particular, we provide a self-contained description of Ethash, the Ethereum mining Proof-of-Work (PoW), and \verb|WebAssembly|, the language in which we implement an efficient miner.
-Section~\ref{sec:approach} outlines WebEth's approach to distributing the Ethash PoW over numerous, resource-constrained browsers.
-Then, we present the results in Section~\ref{sec:results}.
-Finally, in Section~\ref{sec:applications} we discuss various potential applications our mining platform.
-We conclude and discuss the future work in Sectionn~\ref{sec:conclusion}.
+Section 3\ref{sec:webeth} describes \verb|WebEth|, including its lazy approach to distributing the Ethash PoW over numerous, resource-constrained browsers.
+This section also includes a performance analysis.
+We present the experimental results of our implementations in Section 4\ref{sec:results}.
+In Section 5\ref{sec:applications} we discuss several potential applications of our mining platform.
+We conclude in Section 6\ref{sec:conclusion}.
 
@@
 \subsection{Cryptocurrencies: a general overview}
-% \trishita{Not sure if I need this paragraph, since I think the readers will probably be familiar with what crypto-curriencies are}
-
 Most cryptocurrencies like Ethereum involve storing transactions in blocks, and the entire history of transactions is collated in a data structure known as a block chain.
-The block chain is managed by dedicated machines called ``client nodes''; where each client node typically stores the entire block chain.
-However, because each client node operates on its own copy of the block chain, it is very easy for the block chains on different nodes to go out of sync.
+The block chain is managed by dedicated machines called \emph{client nodes}; where each client node typically stores the entire block chain.
+However, because each client node operates on its own copy of the block chain, the block chains on different nodes may go out of sync.
 Hence, there needs to be an accepted mechanism to decide the order in which new transaction blocks are appended to this block chain.
-For this, every time a new transaction takes place, the transaction is thrown in with all other transactions that have ``taken place'', but haven't been added to the block chain yet.
-For most currencies, the data structure that stores this is known as the ``mem pool''.
-A miner then picks a few transactions from this mem pool and creates a new block from these transactions.
-Once this happens, the goal of the miner is to have his/her block appended to the block chain, which is achieved through a process called ``mining''.
+For this, every time a new transaction takes place, the transaction is pooled together with all other transactions that have been broadcasted to the network, but haven't been added to the block chain yet.
+For most currencies, the data structure that stores these unconfirmed transactions is known as the \emph{mem pool}.
+A miner picks valid transactions from his mem pool and creates a new block out of these transactions.
+Once this happens, the goal of the miner is to have his/her block appended to the block chain, which is achieved through a process called \emph{mining}.
 % This block chain is operated on by the Ethereum Virtual Machine (EVM) ~\cite{EVM}, which, unlike Bitcoin Script, is Turing Complete ~\cite{turingComplete}. 
 % Furthermore, this currency is also a Proof-of-Work based currency, which means that the new blocks are appended to the block-chain through a process called ``mining''. 
-Mining involves a race amongst miners to solve a ``Proof-of-Work puzzle'' (usually an energy intensive computation), the winner of which gets to have his block appended to the block-chain.
+Mining involves a race amongst miners to solve a \emph{Proof-of-Work} (PoW) puzzle, which is usually an energy intensive computation.
+The winner of this race gets to have his block appended to the block chain.
 The winner also receives a payout, which acts as an incentive to mine.
 % This process of mining is essential to deciding the order in which transactions are appended to the inherently decentralized block-chain, thereby stabilizing the chain. 
-Ethereum uses Ethash as its Proof-of-Work (PoW) algorithm, which is explained in detail below.
+Ethereum uses Ethash as its PoW algorithm, which is explained in detail below.
 
-\subsection{Ethereum and its PoW, Ethash}
+\subsection{Ethereum Proof of Work}
 Ethereum is a crypto-currency that was released in July 2015 by Vitalik Buterin, Gavin Wood and Jeffrey Wilcke.
 Ethereum uses the Ethash algorithm (derived from the Dagger and Hashimoto algorithms ~\cite{dagger-hashimoto}) for its PoW for mining blocks.
-Before we discuss how mining works with Ethash, we would first like to establish some basic terminology about the data structures involved in the PoW:
-\begin{itemize}
-\item \textbf{Block Header}: A block header contains meta-data related to the transactions of the block it pertains to, and is provided as an input to the Ethash algorithm.
-\item \textbf{Nonce}: An integer that is provided as an input to the hashing algorithm in the hopes that when hashed with the block header, will yield a hash value less than a certain predefined difficulty threshold.
-It is also provided as an input to Ethash.
-\item \textbf{Difficulty Threshold}: An integer value below which the hash digest output of Ethash should be in order for the miner to have successfully mined the block.
-\item \textbf{Mining overview}: The Ethash mining algorithm primarily involves computing a hash of the current block header and nonce.
-If the output of the hash (the digest) lies below the difficulty threshold; the block is said to have been successfully mined.
-Hence, the miner keeps iterating over nonces until he/she gets a digest that lies below the difficulty threshold.
-Once the miner finds the right nonce, he/she then broadcasts the block, the header and the nonce so that the other client nodes can update their block chain to include this newly mined block.
-\item \textbf{Verification}: Once a block has been mined by a miner, it is propagated to other client nodes so that they can update their copies of the block chain.
+Before we discuss how mining works with Ethash, we first establish basic terminology about the data structures involved in the PoW.
+
+A \emph{block header} contains meta-data related to the transactions of the corresponding block, and it is provided as an input to the Ethash algorithm together with an integer \emph{nonce}.
+The nonce is chosen in a brute-force fashion in order to hash, together with the block header, into a value that matches a specific pattern (based on a predefined \emph{difficulty threshold}).
+The process of finding an appropriate nonce for a given block is known as \emph{mining}.
+%\item \textbf{Difficulty Threshold}: An integer value below which the hash digest output of Ethash should be in order for the miner to have successfully mined the block.
+
+Once a block has been mined, it is propagated to other client nodes so that they can update their copies of the block chain.
 However, before each client node does so, it must validate whether the miner is submitting a legitimate block -- i.e., check whether the miner genuinely solved the hash as claimed.
-This is easily done by putting the block header and nonce associated with the block through the Ethash algorithm and checking whether the output indeed lies below the difficulty threshold.
-\item \textbf{Light Weight Client Nodes}
-Some client nodes do not mine new blocks, but just verify whether any new block submitted by a miner is valid or not. These are called light weight client nodes.
-\item \textbf{Full Client Nodes}
-Full client nodes mine new blocks.
-\item \textbf{Epoch}: A unit of ``time'' that spans 30,000 blocks.
-\item \textbf{Seed}: All of the data structures in Ethash (mentioned below) need a 256 bit seed.
-This seed is different for every Epoch.
-For the first epoch it is the Keccak-256~\trishita{CITE} hash of a series of 32 bytes of zeros.
+This is easily done by putting the block header and nonce associated with the block through the Ethash algorithm and checking whether the output follows the pattern prescribed by the difficulty threshold.
+\emph{Light weight} client nodes do not mine new blocks, but rather only verify whether any new block submitted by a miner is valid or not.
+\emph{Full} client nodes, on the other hand, both mine and verify new blocks.
+
+An \emph{epoch} is a unit of ``time'' that spans 30,000 blocks.
+All of the data structures in Ethash (mentioned below) need a 256 bit \emph{seed}, which differs for every epoch.
+For the first epoch the seed is a Keccak-256~\cite{keccak} hash of a series of 32 bytes of zeros.
 For every other epoch it is always the Keccak-256 hash of the previous seed hash.
-\item \textbf{Cache}: The seed for a particular epoch is used to compute a data structure known as the Cache.
-This Cache is simply an array 4 byte integers ~\cite{Ethmining}.
-The cache production process involves using the seed hash to first sequentially fill up the Cache, then performing two passes of the RandMemoHash algorithm~\cite{randmemohash} on top of it to get the final Cache value.
+The seed for a particular epoch is used to compute a data structure known as the \emph{Cache}, which is an array of 4 byte integers \cite{Ethmining}.
+The Cache production process involves using the seed hash to first sequentially fill up the Cache, then performing two passes of the RandMemoHash algorithm~\cite{randmemohash} on top of it to get the final Cache value.
 % This transforms the initial cache to give us the final value for the cache. 
-Light weight clients may use this cache for verifying hashes (discussed below), while full node clients can use it to calculate a Directed Acyclic Graph (DAG) dataset, as described below. 
-\item \textbf{DAG}: A Directed Acyclic Graph stored as a large byte array (currently around 2GB in size). The DAG has the following two attributes:
+Light weight clients may use this Cache for verifying hashes, while full node clients can use it to calculate a Directed Acyclic Graph (DAG) dataset, as described below.
+A Ethereum \emph{Directed Acyclic Graph} is stored as a large byte array (around 1 GB in size on the private Ethereum Network used for our experiments) and has the following two attributes:
   \begin{enumerate}
-  \item \textbf{Node}: Each DAG node in this byte array spans 64 bytes, and node indices are therefore aligned at a 64 byte boundary.
-  \item \textbf{Page}: Each DAG page spans 2 nodes, however, page accesses are not aligned at a 2 node boundary.
+  \item \emph{Node}: Each DAG node in this byte array spans 64 bytes, and node indices are therefore aligned at a 64 byte boundary.
+  \item \emph{Page}: Each DAG page spans 2 nodes, however, page accesses are not aligned at a 2 node boundary.
 The mining process involves accessing some DAG pages and hashing them together with the block header and nonce.
   \end{enumerate}
-Each node in the DAG is generated by combining data from 256 pseudo-randomly selected cache nodes and hashing them together. This process is repeated to generate all nodes in the DAG.
-\item \textbf{Mix:} An intermediate byte array used to store temproary results in the Ethash algorithm.
-\end{itemize}
-We must point out that as time goes on, mining Ethereum becomes more and more difficult, as the size of the Cache and DAG increases with every Epoch.
+Each node in the DAG is generated by combining data from 256 pseudo-randomly selected Cache nodes and hashing them together.
+This process is repeated to generate all nodes in the DAG.
+Finally, intermediate byte arrays used to store temporary results in the Ethash algorithm are known as \emph{Mix}es.
+
+We must point out that as time goes on, mining Ethereum becomes more and more difficult, as the size of the Cache and DAG increases with every epoch.
 
@@
 \includegraphics[width=300px,keepaspectratio]{Ethash.pdf}
-\caption{\label{fig:ethash} Ethash}
+\caption{Ethash}
+\label{fig:ethash}
 \end{figure}
 
-Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128B wide ``Mix'' (another byte array),as seen in step 1 of Figure~\ref{fig:ethash}.
+Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128-byte wide Mix, as seen in step 1 of Figure 1\ref{fig:ethash}.
 The Mix is then used to fetch a specific page of the DAG from memory.
-After this, the Mix is updated with the fetched part of the DAG (step 2).
-Then, this updated Mix is used to fetch a new part of the DAG (step 3).
+After this, the Mix is updated with the fetched page of the DAG (step 2).
+Then, this updated Mix is used to fetch a new page of the DAG (step 3).
 This process of sequentially fetching parts of the DAG is repeated 64 times (step 4), and the final value of the Mix is put through a transformation to obtain a 32 byte digest (step 5).
-This digest is then compared to the threshold (step 6), and if it is smaller than it, the nonce is valid and the block is successfully mined and can be broadcast to the network.
-However, if the digest is greater than the threshold, the nonce is unsuccessful, and the entire process must be repeated with a new nonce ~\cite{Ethmining}.
+This digest is then compared to the threshold (step 6).
+If it is smaller than the threshold, the nonce is valid and the block is successfully mined and can be broadcast to the network.
+However, if the digest is greater than the threshold, the nonce is unsuccessful, and the entire process must be repeated with a new nonce~\cite{Ethmining}.
 
@@
 
-It is important to note that the parts of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence there is no way to pre-determine which parts will be useful to have in memory.
-This therefore forces miners to store entire DAG in memory, making mining ``Memory Hard''.
+It is important to note that the pages of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence there is no way to pre-determine which pages will be useful to have in memory.
+This therefore forces miners to store entire DAG in memory, making Ethereum mining ``Memory Hard''.
 
@@
 
-While mining is memory intensive, verification is relatively lightweight.
+Whereas mining is memory intensive, verification is relatively lightweight.
 This is because of the property that each node in the DAG depends on a set of pseudo-randomly selected items from the Cache.
-Hence, the Cache is used to regenerate only the specific nodes of the DAG that are needed to recalculate the hash for the particular nonce.
-And so only the Cache needs to be stored by light weight clients that only perform verification.
-We use this property of being able to generate parts of the DAG as needed to our advantage in order to alleviate some of the memory and network bandwidth restrictions that browsers typically face.
-
-% Currently the DAG is more than 2GB in size, causing many GPU miners with cards of 2GB of memory to suffer in terms of hashrate. 
-% The Proof-of-Work difficulty and total hashrate of the network has been steadily increasing over time, with the current difficulty at 1612.737TH and the respective hashrate at 109.138TH/s ~\cite{etherscan}.
-This reflects the design of mining one block approximately every 12 seconds.
-% As for mining rewards, the reward for mining a block has gone from 5 Ether to 3 ether, though the difficulty has significantly decreased, both due to the Byzantium fork.
-
-% For a normal Ethereum miner to function, the current block headers and the DAG are required to even begin mining.
-As we simply cannot afford to transfer the entire DAG to the browser and store it in memory, we propose an an alternative approach to address some of these concerns.
+Hence, the Cache is used to regenerate only the specific pages of the DAG that are needed to recalculate the hash for the particular nonce.
+And so, only the Cache needs to be stored by light weight clients that only perform verification.
+In fact, as we will see in the next section, we use this property of being able to generate parts of the DAG as needed to our advantage in order to alleviate some of the memory and network bandwidth restrictions that browsers typically face.
 
 \subsection{JavaScript and WebAssembly}
-Introduced in 1995 by Netscape Communications Corporation~\cite{https://auth0.com/blog/a-brief-history-of-javascript/}, \verb|JavaScript| was a meant to be a light scripting language in order to  make web content dynamic.
+Introduced in 1995 by Netscape Communications Corporation~\cite{js}, \verb|JavaScript| was a meant to be a light scripting language in order to  make web content dynamic.
 Over the span of 23 years, it has grown to become one of the most popular client-side web development languages used to make dynamic user interfaces.
 
-In fact, up to recently, \verb|JavaScript| has been the only language available to make dynamic client side web content.
+In fact, up to recently, \verb|JavaScript| has been the only language available to make dynamic client-side web content.
 However, the situation has changed since the advent of \verb|WebAssembly| in 2016.
-As per its creators, \verb|WebAssembly| is a ``binary instruction format for a stack-based virtual machine''.
-WASM is designed to be compiled from high-level languages like \verb|C/C++/Rust|, and is supported by 4 major browser versions -- Firefox, Safari, IE, and Chrome ~\cite{webAssembly}.
-The \verb|WebAssembly| stack machine is designed to be encoded in a ``size-and load-time-efficient binary format''~\cite{webAssembly}, and aims to execute near native speed by utilizing common hardware capabilities available on a wide range of platforms~\cite{webAssembly}.
+As per its creators, \verb|WebAssembly| is a ``binary instruction format for a stack-based virtual machine'' \cite{webAssembly}.
+WASM is designed to be compiled from high-level languages like \verb|C/C++/Rust|, and is supported by 4 major browser platforms -- Firefox, Safari, IE, and Chrome \cite{webAssembly}.
+The \verb|WebAssembly| stack machine is designed to be encoded in a ``size-and load-time-efficient binary format''~\cite{webAssembly}, and aims to execute near native speed by utilizing common hardware capabilities present on a wide variety of platforms~\cite{webAssembly}.
 The language is meant to improve performance for computationally intensive use cases such as image/video editing, games, streaming, etc~\cite{webAssembly}.
-This, and given the fact that CoinHive is also implemented in \verb|WebAssembly| ~\cite{coinhive}, makes the language a natural choice for us to implement a miner in.
-% In fact, as of now, \verb|WebAssembly| is supported by 4 major browser versions -- Firefox, Safari, IE, and Chrome ~\cite{webAssembly}, which makes our miner implementation extremely versatile.
+This makes it the language of choice to implement a miner within a browser.
 
-\subsection{Challenges}
-% \trishita{Too long of a sentence; need to reword}
-The crux of having a good hashrate for Ethereum lies in having quick access to the DAG.
+%\subsection{Challenges}
+%The crux of having a good hashrate for Ethereum lies in having quick access to the DAG.
 One of the biggest challenges with mining on a distributed ensemble of browsers is to transfer and store this data structure within each worker browser.
-However, given that the DAG for an Ethereum network is at least 1GB (and growing), transferring it to the browser every time a client loads our web page would be impractical.
+However, given that the DAG for an Ethereum network is at least 2 GB (and growing), transferring it to the browser every time a client loads our web page is impractical.
 Furthermore, even if one somehow manages to transfer the DAG to the client when the web page loads, the browser still has to store the DAG in memory, thereby using a sizeable amount of resources on the client machine.
@@
 
-\subsection{Related Work}
-So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling,parallel,orca}.
-Additionally, with the growing popularity of dynamic web-content and client side scripting languages like \verb|JavaScript| and \verb|WebAssembly|, web-browsers have also become a lucrative option for implementing distributed systems.
-As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow,Duda}.
-Indeed, ``Distributed Computing on an Ensemble of Browsers'' by Cushing~\cite{Cushing} shows that the \verb|JavaScript| Engine has had enough improvements in performance to make computationally heavy programs feasible in a distributed web browsing unit.
-% In addition, the work by Duda and Dłubacz~\cite{Duda} was instrumental in the field as one of the first web browsing computational systems to not require the host machine to install any additional applications in order to participate.
-This is important since we would want our web miner to be operable without requiring the user to install any unfamiliar software.
-% Furthermore, \verb|WebAssembly|  ~\cite{webAssembly} is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to be only 20\% slower than native code ~\cite{wasmPerf}, as compared to the much slower \verb|JavsScript|.
-Instead of relying on \verb|JavaScript|, web developers can now write C/C++ and compile it into \verb|WebAssembly| using some of the openly available \verb|WebAssembly| compilers ~\cite{emscripten}.
-Indeed, given that now \verb|WebAssembly| is supported by all major browsers ~\cite{webAssembly}, industry is also making use of this powerful framework.
-One sees the growing popularity of distributed web computation through the recent development of increasingly popular Monero mining library CoinHive~\cite{coinhive}.
-In terms of the potential monetization aspect of the project, there exists an ethical alternative to CoinHive called the Basic Attention Token~\trishita{Need to cite}.
-The Basic Attention Token is an ERC20 Token built on Ethereum that is used along with the Brave browser to generate Ad revenue for website publishers by measuring a user's attention span on an advertisement.
-Note that this is not a replacement for Ad revenue, but a platform to balance the ties between website users, publishers, and advertisers.
-It ensures that users get only ads they would accept, advertisers pay for actual users instead of click bots, and publishers actually get revenue instead of pleading the users to turn off their Ad blockers.
+\section{WebEth}
+\label{sec:webeth}
+%\label{sec:approach}
+%\subsection{Approach}
+% \trishita{I think it would be nice if we show how we modified the algorithm shown in the previous section. I will add that over here}
 
-\section{WebEth}
-\label{sec:approach}
-\subsection{Approach}
-% \trishita{I think it would be nice if we show how we modified the algorithm shown in the previous section. I will add that over here}
-We propose a amortized evaluation based approach to alleviate the network and memory requirements for mining Ethereum in a distributed scenario on browsers.
+\verb|WebEth| is based on a lazy evaluation to alleviate the network and memory requirements for mining Ethereum in a distributed scenario on browsers.
 Specifically, as soon as each browser connects to the webserver, the server sends to the browser the current header of the block being mined and the Cache.
-Once the browser receives the Cache, it allocates an array buffer to store the DAG nodes that fall between indices 0 and $N$ that will be computed in the future.
-(Note that the $N$ is a variable parameter reflecting the length of the buffer with which we experiment in our analysis).
+Once the browser receives the Cache, it allocates an array buffer to store the DAG node.
+%s that fall between indices 0 and $N$ that will be computed in the future. (Note that the $N$ is a variable parameter reflecting the length of the buffer with which we experiment in our analysis). 
 Once the buffer is allocated, the browser can start iterating over nonces to compute hashes.
@@
 Since, to begin with, the browser does not store any nodes of the DAG, it must compute each node on the fly using the Cache.
-However, for every such node that the browser computes, it then stores it in the buffer (if it fits within the allocated bounds, otherwise it is simply discarded), for quicker access in the future.
-Hence, as time passes, the buffer starts filling up and so more and more nodes are quickly accessed from the buffer rather than being computed from the ground-up, which makes hash computations faster with time.
-This has the effect that the longer the user remains on the web-page, the better the hashrate gets for that user.
+However, every node that the browser computes is stored in the buffer, for quicker access in the future.
+Hence, as time passes, the buffer starts filling up, such that more and more nodes are quickly accessed from the buffer rather than being computed from the ground-up, which makes hash computations faster with time.
+This has the effect that the longer the user remains on the web-page, the better the hash rate gets for that user.
 
@@
 
-Our architecture was centered around two client-side Ethereum miners written in \verb|JavaScript| and \verb|WebAssembly|.
-The central node that co-ordinates all workers (browsers) was an improvised version of \verb|geth| ~\cite{geth}, a real world Ethereum miner written in \verb|Go|.
-\verb|Geth| typically runs as a standalone miner that mines on the machine it is running.
-We modified it so that instead of mining all by itself, it simply sends over the necessary data needed to mine (the hash of the Block Header and the Cache) to any client that connects to it on port \verb|9000|.
-After receiving the necessary data, the browser allocates a buffer for the DAG in order to store future nodes.
-Note that the buffer for the DAG is implemented as an array of ints, so as to make each lookup in the buffer $\theta(1)$.
-At this point, it can then begin to search for a solution.
+The \verb|WebEth| architecture is centered around a central node and client-side Ethereum miners. We have two implementation for client-side miners: in \verb|JavaScript| and in \verb|WebAssembly|.
 
-For our miner, we modeled our \verb|JavaScript| implementation based on the ~\verb|node.js| implementation of Ethash~\cite{ethash}.
-The \verb|WebAssembly| version is simply the \verb|JavaScript| version transpiled to \verb|C++|, and compiled to \verb|WebAssembly| using the ~\verb|Emscripten| compiler~\cite{emscripten}.
+The central node coordinates all workers (browsers).
+Its implementation is based on a modified version of \verb|geth| \cite{geth}, a real world Ethereum miner written in \verb|Go|.
+\verb|geth| typically runs as a standalone miner that mines on the machine on which it is running.
+We modify the code so that instead of doing all the mining all by itself, the node sends over the necessary data (namely, the hash of the block header and the Cache) to any client that connects to it on port \verb|9000|.
+After receiving the necessary data, each browser allocates a buffer for the DAG in order to store future DAG nodes.
+Note that the buffer for the DAG is implemented as an array of ints, so as to make each lookup in the buffer constant in time.
+At this point, the client-side miner can begin to search for a solution.
 
-To begin, the miner creates a random nonce and computes the hash (using the Cache and the buffered DAG) as discussed in the previous section.
-It will continue to perform this action on new nonces until one of two scenarios occur.
+For our miner, we model the \verb|JavaScript| implementation after the ~\verb|node.js| implementation of Ethash~\cite{ethash}.
+The \verb|WebAssembly| version is the \verb|JavaScript| version transpiled to \verb|C++|, which in turn is compiled to \verb|WebAssembly| using the ~\verb|Emscripten| compiler~\cite{emscripten}.
 
-The first case is if it finds a nonce such that the computed hash is below the given threshold or the process has timed out.
-In the former case, the browser submits the result back to the node and then asks the node for a new block header and the Cache.
+At the beginning, the miner creates a random nonce and computes the hash (using the Cache and the buffered DAG) as discussed in the previous section.
+It continues to perform this action on new nonces until one of two following scenarios occur.
 
-The second case is when the algorithm times out without finding a result, the browser simply polls the node for the current block header and Cache .
-This process will continue until the user moves away from the website or closes their browser.
-We must point out that this time out is necessary since we want the browser to work with the most recent block header and Cache.
-The block header can become stale if that particular block has already been mined, and the Cache can become stale if the Ethereum network transitions into a new Epoch (happens once every 30,000 blocks).
-We must point out that both our current implementations in \verb|JavaScript| and \verb|WebAssembly| require no external dependencies, and therefore can be directly embedded into any website.
-For a diagramatic view our our design, see Figures~\ref{fig:hybridArchitecture}.
+In the first scenario, the miner finds a nonce such that the computed hash is below the given threshold.
+In that case, the browser submits the result back to the central node and then asks the central node for the new block header and the Cache.
+
+In the second scenario, the algorithm times out without finding a result.
+In that case, the miner polls the central node for the current versions of the block header and Cache and continues to mine using the new inputs.
+This process continue until the user moves away from the website or closes the browser.
+This time out is necessary since the browser should work with the most recent block header and Cache.
+The block header can become stale if that particular block has already been mined, and the Cache can become stale if the Ethereum network transitions into a new epoch (this happens once every 30,000 blocks).
+
+Finally, we must point out that both our current implementations in \verb|JavaScript| and \verb|WebAssembly| require no external dependencies, and therefore can be directly embedded into any website.
+For a diagrammatic view our our design, see Figure 2\ref{fig:hybridArchitecture}.
 
@@
 \includegraphics[width=230px,keepaspectratio]{Hybrid-Miner.pdf}
-\caption{\label{fig:hybridArchitecture} Web Miner Architecture}
+\caption{Web Miner Architecture}
+\label{fig:hybridArchitecture}
 \end{figure}
@@
 \subsection{Performance Analysis}
-With this amortized evaluation based approach, we can calculate exactly how many hashes we would have to compute in order to fill up a buffer of a given size.
-This is important because once the buffer in the browser fills up, the hash rate that the browser gives is at its maximum, steady-state.
-In this section, we will mathematically demonstrate that filling a buffer the size of the DAG up should take at most 4.5 million hashes, while filling up 99.5\% of this buffer takes merely 1.4 million hashes.
-% This is a significant difference since in our experimental set-up, the browser takes X s to compute 4.5 million hashes, while only Y s to compute 1.4 million hashes. 
-The approach we take is similar to the Coupon Collector problem \cite{couponCollector}, and is discussed below.
-Note that for simplification, we assume that the DAG is randomly sampled in order to compute hashes.
-In reality, this is not entirely true and hence the results we obtain from this analysis are more conservative than what we see in practice.
-In fact, while we show here that filling up 99.5\% of a buffer as big as the DAG takes 1.4 million hashes, whereas in reality it only takes half as many hashes, as shown in Section~\ref{sec:results} \\
+In this section, we perform a back-of-the envelope calculation for the number of hashes needed till \verb|WebEth| fills up almost all the buffer.
+This is important because the hash rate reaches its maximum steady-state only once the buffer in the browser is almost full.
+Specifically, we show that filling a buffer the size of the DAG up to 99.9999995\% should take on average about 3.7 million hashes, while filling up 99.5\% of this buffer takes much lesser -- about 1.4 million hashes.
+The approach we take is based on the Coupon Collector problem~\cite{couponCollector}.
+
+For simplicity, we assume that nodes in the DAG are randomly sampled in order to compute a hash, whereas, in reality, this is not entirely true, because two neighboring DAG nodes are computed for each page computation (rather than a single node).
+Hence, in order to account for this simplification we also assume that 64 DAG \textbf{nodes} are used for each hash computation instead of 64 \textbf{pages} (or 128 nodes), and so our results suggest that it should take more hashes to fill the buffer up than it would in real life.
+% For simplicity, we assume that the DAG is randomly sampled in order to compute hashes.
+In reality, this is not entirely true, because two neighboring DAG nodes are computed for each page computation (rather than a single node).
+Hence, the results we obtain from the following analysis are more conservative than those observed in practice.
+
+%In fact, while we show here that filling up 99.5\% of a buffer as big as the DAG takes 1.4 million hashes, whereas in reality it only takes half as many hashes, as shown in Section~\ref{sec:results} \\
 
@@
 
-If we define Number of DAG slices = $N$, number of DAG slices needed to compute a single hash = $a$, failure probability of finding a specific slice in the buffer (Buffer miss rate)= $\delta$, failure probability of computing a hash just using slices in the buffer = $\omega$, expected number of hashes it takes to fill the buffer = E(X), and the nth Harmonic Number = $H_n$, then: \\
+For our analysis, we introduce the following notation.
+We denote by $N$ the total number of nodes in the DAG, by $a$ the number of DAG nodes needed to compute a hash, by $\delta$ the failure probability of finding a specific node in the buffer (i.e., the buffer miss rate), by $\omega$ the failure probability of computing a hash using nodes already stored in the buffer, by $E(X)$ the expected number of hashes to fill the buffer with a failure probability $\delta$, and by $H_n$ the $n$-th Harmonic number~\cite{harmonicNumber}.
 \begin{claim}
-\begin{equation}
-	E(X) \approx \frac{N}{a}(H_{N} -H_{N\delta});\;\delta \to 0
-\end{equation}
+For $\delta \ll 1$, $E(X) \approx \frac{N}{a}(H_{N} -H_{N\delta}).$
 \end{claim}
 
-% \makebox[\textwidth][l]{If we define}
-% \makebox[\textwidth][c]{Number of DAG slices = N}
-% \makebox[\textwidth][c]{Number of DAG slices needed to compute a single hash = a}
-% \makebox[\textwidth][c]{Failure probability of finding a specific slice in the buffer (Buffer miss rate)= $\delta$}
-% \makebox[\textwidth][c]{Failure probability of computing a hash just using slices in the buffer = $\omega$}
-% \makebox[\textwidth][c]{nth Harmonic Number = $H_n$}
+\begin{claimproof}
+The number of nodes needed in the buffer to achieve a node failure probability $\delta$ is 
+$\left \lfloor{N(1-\delta)}\right \rfloor$.  %= Nf_1(1-\frac{\omega}{a})
+This means that even though we are allocating a buffer that can hold $N$ pages, we are willing to forgo $\left \lfloor{N\delta}\right \rfloor$ nodes (to simplify notation, from now and on, we assume $N\delta$ is an integer).
 
-% keeping this out for now
-%%%%%%%%%%%%%%%%%%%%%%%%
-% \makebox[\textwidth][c]{Euler-Mascheroni constant = $\gamma = 0.57721566...$}
-% \makebox[\textwidth][c]{Expected number of hashes it takes to fill the buffer = E(H)}
-% \begin{gather}\label{eq:slicevshash}
-% 	(1-\delta)^a = 1-a\delta;\;\delta \to 0 %1-\omega
-% \end{gather}
-% \makebox[\textwidth][l]{When $\delta \to 0$, equation \ref{eq:slicevshash} can be re-written as}
-% \begin{gather}
-% 	1-a\delta = 1-\omega \\
-%     \label{eq:deltaomega}
-% 	a\delta = \omega
-% \end{gather}
-% \makebox[\textwidth][l]{Hence, the probability that a specific slice is present in the buffer}
-% \begin{gather}
-% 	1-\delta = 1-\frac{\omega}{a}
-% \end{gather}
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{claimproof}
-The number of slices $n$ needed to fill up a buffer with $N$ slices for a given $\delta$ is given by:
+Using results from the Coupon Collector's problem~\cite{couponCollector}, we know that the expected number of trials for obtaining the $i$-th new node after having buffered $i-1$ nodes is $N/(N-(i-1))$.
+Thus, the expected number of trials in order to fill up the buffer with ${N(1-\delta)}$ nodes is given by
 \begin{gather}
-	n = \left \lfloor{N(1-\delta)}\right \rfloor  %= Nf_1(1-\frac{\omega}{a})
+	E(t) = N\sum_{i=1}^{N(1-\delta)} \frac{1}{N-i+1}.
 \end{gather}
-This means that even though we are allocating a buffer that can hold $N$ slices, we are willing to forgo $N\delta$ slices.
-
-Now, using the Coupon Collector proof~\cite{couponCollector}, we know that the expected number of trials $E(t_i)$ of obtaining the $ith$ new slice after having buffered $i-1$ slices is:\\
+Splitting this expression into two sums, we get
 \begin{gather}
-	E(t_i) = \frac{N}{N-(i-1)}
+	E(t) = N \left(\sum_{i=1}^{N}\frac{1}{N-i+1} - \sum_{i=N(1-\delta)+1}^{N}\frac{1}{N-i+1} \right), 
 \end{gather}    
-we see that the expected number of trials in order to obtain $n$ slices is given by
+or
 \begin{gather}
-	E(t) = \sum_{i=1}^{n}E(t_i) = N\sum_{i=1}^{n}\frac{1}{N-i+1} = N\sum_{i=1}^{\left \lfloor{N(1-\delta)}\right \rfloor}\frac{1}{N-i+1}
-\end{gather}
-Splitting this into two summations,
-\begin{gather}
-	E(t) = N(\sum_{i=1}^{N}\frac{1}{N-i+1} - \sum_{i=\left \lfloor{N(1-\delta)}\right \rfloor+1}^{N}\frac{1}{N-i+1}) \\
     \label{eq:expectedTrials}
@@
 \end{gather}
-We now relate the failure probability of calculating a hash just from slices stored in the buffer with the failure probability of having a specific slice in the buffer:
+We now relate the failure probability  of calculating a hash using nodes already stored in the buffer  $\omega$ with the failure probability of having a specific node in the buffer $\delta$.
+By the independence assumption,
+$$ (1-\delta)^a = 1-\omega.$$For $\delta \ll 1$, we have $(1-\delta)^a \approx 1-a\delta$. Hence,
 \begin{gather}
-	(1-\delta)^a = 1-\omega \\
-    (1-\delta)^a = 1-a\delta + o(\delta);\;\delta \to 0 \\
-	1-a\delta + o(\delta) = 1-\omega;\;\delta \to 0 \\
     \label{eq:deltaomega}
-	\delta \approx \frac{\omega}{a};\;\delta \to 0 
+	\delta \approx \frac{\omega}{a}.
 \end{gather}
-Hence, it follows from Equation~\ref{eq:deltaomega} that 
+Hence, it follows from Equation~(4\ref{eq:deltaomega}) that 
 \begin{gather}
-	\label{eq:hashvsslice}
-	E(X) \approx \frac{E(t)}{a};\;\delta \to 0 
+	\label{eq:hashvspage}
+	E(X) \approx \frac{E(t)}{a}.
 \end{gather}
-Finally, from Equation~\ref{eq:hashvsslice} and~\ref{eq:expectedTrials}, we obtain:
+Finally, from Equations~(3\ref{eq:expectedTrials}) and~(5\ref{eq:hashvspage}) and, we obtain
 \begin{gather}
     \label{eq:expectedHashes}
-	E(X) \approx \frac{N}{a}(H_{N} -H_{N\delta});\;\delta \to 0 
+	E(X) \approx \frac{N}{a}(H_{N} -H_{N\delta}).
 \end{gather}
 
-% Now,
-% \begin{gather}
-% 	H_N \approx \ln{N} + \gamma + o(1)
-% \end{gather}
-% Substituting this in Equation ~\ref{eq:expectedHashes} gives us:
-% \begin{gather}
-% 	E(X) \approx \frac{N}{a}(\ln{N} + \gamma + o(1) - (\ln{N\delta} + \gamma + o(1))) \\
-%     E(X) \approx \frac{N}{a}(\ln{N} - (\ln{N\delta}))
-% \end{gather}
+\end{claimproof}
 
-\end{claimproof}
-We now define the Euler-Mascheroni constant as $\gamma = 0.57721566...$ and use the following bounds on Harmonic Numbers~\cite{harmonicNumber} to bound the results obtained from Equation~\ref{eq:expectedHashes}:
+We use the following bounds on the Harmonic Numbers~\cite{harmonicNumber} to compute  Equation~(6\ref{eq:expectedHashes}):
 \begin{gather}
     \label{eq:boundHarmonic}
-	-\frac{1}{12N^2+{2\frac{7-12\gamma}{2\gamma-1}}}\le H_N-\ln N-\frac1{2N}-\gamma<-\frac{1}{12N^2+\frac{6}{5}}
+	-\frac{1}{12n^2+{2\frac{7-12\gamma}{2\gamma-1}}}\le H_n-\ln n-\frac1{2n}-\gamma<-\frac{1}{12n^2+\frac{6}{5}},
 \end{gather}  
+where $\gamma = 0.57721566...$ is the Euler-Mascheroni constant.
 % -\frac{1}{12n^2+{2(7-12\gamma)}/{(2\gamma-1)}}\le H(n)-\ln n-\frac1{2n}-\gamma<-\frac{1}{12n^2+6/5}
 
-Now, using Equations~\ref{eq:expectedHashes} and~\ref{eq:boundHarmonic}, and setting $N = 16777186$ (the number of nodes in the DAG for our experiments), $a = 64$ and $\delta = 0$, we get $E(H) \approx 4.5$ million hashes.
-However, if we slightly increase $\delta$ to 0.005, we get $E(H) \approx 1.4$ million hashes.
-Hence, we see that even computing merely 1.4 million hashes fills a DAG buffer as large as the entire DAG by more than 99.5\%, as opposed to calculating 4.5 million to fill the buffer entirely.
+Specifically, using Equations~(6\ref{eq:expectedHashes}) and~(7\ref{eq:boundHarmonic}), and setting $N = 16777186$ (the number of nodes in the DAG for our experiments), $a = 64$ and $\delta = 0.000000005$, we get $E(X) \approx 3.7$ million hashes.
+However, if we increase $\delta$ to 0.005, we get $E(X) \approx 1.4$ million hashes.
+Hence, we see that even computing merely 1.4 million hashes fills a DAG buffer as large as the entire DAG by more than 99.5\%, as opposed to calculating 3.7 million to fill it by 99.9999995\%.
 % This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up. 
-In fact, as we will see in the results, filling up 99.5\% of a buffer as large as the DAG already starts giving us good hash rates for a browser -- 35kH/s for the ~\verb|WebAssembly| miner, whereas the hash rate for a completely full buffer is only marginally higher at 49kH/s.
-This means that reaching a reasonably steady state is not as hard as it seems at face value, making WebEth viable for web setting where users might not stay on websites for long.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{theorem}[Expectation of Number of Hashes]
-% \label{expectedHashes}\\
-% \makebox[\textwidth][l]{If we define}
-% \makebox[\textwidth][c]{Number of DAG slices = n}
-% \makebox[\textwidth][c]{Size of buffer as a fraction of the total DAG = $f_1$; $f_1$=[0,1]}
-% \makebox[\textwidth][c]{Expected number of hashes it takes to fill the buffer = E(H)}
-% \makebox[\textwidth][c]{nth Harmonic Number = $H_n$}
-% \makebox[\textwidth][c]{Euler-Mascheroni constant = $\gamma = 0.57721566...$}
-% \makebox[\textwidth][c]{Probability of obtaining a new slice after having buffered x slices = $P_x = \frac{nf_1-x}{n}$}
-% \makebox[\textwidth][c]{Expected number of trials $t_x$ to get a new slice after having seen} 
-% \makebox[\textwidth][c]{$x$ out of $nf_1$ slices = 
-% $E(t_x) = \frac{1}{P_x} = \frac{n}{nf_1-x}$}
-% \makebox[\textwidth][c]{Expected number of trials it would take to see all $x$ slices = $E(t)$}
-% % ~\trishita{add reference to results}
-% From the Coupon Collector Problem~\cite{couponCollector}, it follows that:
-% \begin{gather}
-% E(t) = \sum_{x=0}^{nf_1-1}E(t_x) = \sum_{x=0}^{nf_1-1}\frac{1}{P_x} = n\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x} = nH_{nf_1}
-% \end{gather}
-
-% It then follows from bounds on the nth Harmonic Number~\cite{harmonicNumber} that the expected number of hashes $E(H)$ it takes to fill up a buffer of fraction $f_1$ of a DAG with $n$ slices is bounded by:
-% \begin{gather}
-% \frac{n}{64}[\ln{nf_1} + \frac{1}{2nf_1} + \gamma - \frac{1}{12({nf_1})^2+2\frac{7-12\gamma}{2\gamma - 1}}] <= E(H) \\ E(H)< \frac{n}{64}[\ln{nf_1} + \frac{1}{2nf_1} + \gamma - \frac{1}{12({nf_1})^2+\frac{6}{5}}]
-% \end{gather}
-
-% this was the proof for the expression above
-% % \end{theorem}
-% % \begin{proof}
-% Let us assume we have a buffer for our DAG that is $f_1$ as large as the entire DAG -- i.e., the buffer can only store dag slices with indices $i$ such that $i \in [0,nf_1]$.
-Hence, each time we calculate a DAG slice from the Cache, we may or may not buffer it depending on whether it falls within the index rage.
-Now, let us assume that  we have buffered $x$ slices so far, the probability of obtaining a new slice is given by:
-% \begin{gather}
-% 	P_x = \frac{nf_1-x}{n}
-% \end{gather}
-% The event of obtaining a new slice after having already collected $x$ out of the $nf_1$ slices that can be buffered can be modeled as a geometric distribution.
-Hence, the expected number of trials $t_x$ it takes to get a new  slice after having seen $x$ out of the $nf_1$ slices is:
-% \begin{gather}
-% 	E(t_x) = \frac{1}{P_x} = \frac{n}{nf_1-x}
-% \end{gather}
-% By linearity of expectation, the total number of trials it would take to see all $x$ slices is:
-% \begin{gather}
-% 	E(t) = \sum_{x=0}^{nf_1-1}E(t_x) = \sum_{x=0}^{nf_1-1}P_x = \sum_{x=0}^{nf_1-1}\frac{n}{nf_1-x} = n\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x}
-% \end{gather}
-% Since the summation represents the harmonic series, the expected value can be approximated as follows:
-% \begin{gather}
-% 	E(t) = n\log{nf_1}
-% \end{gather}
-% Equation ~\ref{eq:7} is in terms of the number of individual accesses of the DAG.
-In order to get the expected number of Hashes (as opposed to the expected number of individual DAG slice accesses), we need to divide by 64 since each hash involves 64 accesses of the DAG.
-Hence:
-% \begin{gather}
-% 	E(H) = \frac{E(t)}{64} = \frac{n\log{nf_1}}{64}
-% \end{gather}
-% \end{proof}
-
-% The factor of 64 comes from the fact that calculating each hash requires sampling the DAG 64 times.
-Given this, let us do a simple calculation for one extreme case, where we allocate a buffer as large as the entire DAG on the browser (in order to get an upper bound on the number of hashes it would take to fill this buffer up).
-Here $f_1 = 1$ and $n = 16777186$ (for our private test network), which, using ~\ref{eq:6}, gives us $4512210 < E(H) <= 4512210$ hashes.
-Hence, it takes around 4.5 million hashes to fill up a buffer as large as the entire DAG.
-If $f_1 < 1$, the number of hashes should be less than 4.5 million, thus making it a very loose upper bound on the number of hashes needed to fill up a DAG buffer (and thereby reaching a steady-state hash rate).
-
-% In practice, however, we do not need to wait till the buffer is \emph{completely} full till we see good hash rates.
-We will demonstrate how we can get away with a much smaller number of hashes to fill up \emph{almost all} of the buffer, thereby reaching very good hash rates relatively quickly.
-
-% lower bound (python exp): (n/64.0)*(log(n) + 1.0/(2*n) + g - 1.0/(12*(n**2) + (2*(7-12*g)/(2*g-1))))
-% upper bound (python exp): (n/64.0)*(log(n) + 1.0/(2*n) + g - 1.0/(12*(n**2) + 6.0/5))
-
-% Now let us say that we do not want to wait for the entire buffer to fill up -- how many hashes would we have to compute until a reasonable fraction of the buffer is full?
-For this, we have the following corollary:
-% \begin{corollary}
-% \label{earlyTermination}
-% \makebox[\textwidth][l]{If we further define,}
-% \makebox[\textwidth][c]{Fraction of DAG buffer to be filled = $f_2$; $f_2$ $\in$ [0,1]}
-% \makebox[\textwidth][c]{$x  = E(H) - \frac{n}{64}\ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} - \frac{1}{128f_1} + \frac{n}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}}$}
-% \makebox[\textwidth][l]{Then,}
-%     \begin{gather}
-%    \frac{n}{768({nf_1 - nf_2f_1 - 1})^2+128\frac{7-12\gamma}{2\gamma - 1}} - \frac{1}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} < x \\
-%    x <= \frac{n}{768({nf_1-nf_2f_1-1})^2+\frac{6}{5}} - \frac{n}{12({nf_1})^128+\frac{6}{5}} 
-% 	\end{gather}
-% % \end{corollary}
-% % \begin{proof}
-% Then, for a buffer with space for $f_1$ slices, the number of slices we want to fill it with in order for a fraction $f_2$ of it to be full would be: \\
-% \makebox[\textwidth][c]{Number of slices to fill DAG buffer with = $nf_2f_1$}
-% This would modify equation \ref{eq:6} for the expected number of trials as follows:
-% \begin{gather}
-%     E(t) = \sum_{x=0}^{nf_2f_1}\frac{1}{P_x} = \sum_{x=0}^{nf_2f_1}\frac{n}{nf_1-x} = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x}
-% \end{gather}
-% This is essentially an early termination of the summation in equation ~\ref{eq:6}, and can be expressed as follows:
-% \begin{gather}
-%     E(t) = n\sum_{x=0}^{nf_2f_1}\frac{1}{nf_1-x} = n(\sum_{x=0}^{nf_1-1}\frac{1}{nf_1-x} - \sum_{x=nf_2f_1+1}^{nf_1-1}\frac{1}{nf_1-x}) \\
-%     E(t) = n[H_{nf_1} - H_{nf_1 - nf_2f_1 - 1}]\\
-% \end{gather}
-% Again, using the bounds on the nth Harmonic Number~\cite{harmonicNumber}, substituting $\frac{E(t)}{64} = E(H)$ and $x$, and simplifying, we get the following: \\
-% \makebox[\textwidth][l]{Let}
-% \begin{gather}
-% 	n[
-%     \ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} + \frac{1}{2nf_1} - \frac{1}{12({nf_1})^2+2\frac{7-12\gamma}{2\gamma - 1}} \\ - \frac{1}{2(nf_1 - nf_2f_1 - 1)} + \frac{1}{12({nf_1 - nf_2f_1 - 1})^2+2\frac{7-12\gamma}{2\gamma - 1}}] < E(t) \\
-%     E(t) <= n(\ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} + \frac{1}{2nf_1} - \frac{1}{12({nf_1})^2+\frac{6}{5}} \\
-%     - \frac{1}{2(nf_1-nf_2f_1-1)} + \frac{1}{12({nf_1-nf_2f_1-1})^2+\frac{6}{5}}) \\
-%     x  = E(H) - \frac{n}{64}\ln{\frac{nf_1}{nf_1 - nf_2f_1 - 1}} - \frac{1}{128f_1} + \frac{n}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} \\
-%    \frac{n}{768({nf_1 - nf_2f_1 - 1})^2+128\frac{7-12\gamma}{2\gamma - 1}} - \frac{1}{768({nf_1})^2+128\frac{7-12\gamma}{2\gamma - 1}} < x \\
-%    x <= \frac{n}{768({nf_1-nf_2f_1-1})^2+\frac{6}{5}} - \frac{n}{12({nf_1})^128+\frac{6}{5}} 
-% \end{gather}    
-%     \ln{()}) \\
-%     E(t) = n\log{\frac{1}{1-f_2-\frac{1}{nf_1}}}
-
-% Again, we divide by 64 to obtain the expected number of hash computations:
-% \begin{gather}
-%     E(H) = \frac{n}{64}\log{\frac{1}{1-f_2-\frac{1}{nf_1}}}
-% \end{gather}
-% \end{proof}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In fact, as we will see in the results, filling up 99.5\% of a buffer as large as the DAG already starts giving us good hash rates for a browser -- 35kH/s for the \verb|WebAssembly| miner.
+This shows that we need to have the buffer almost -- but not completely -- full in order to do well in terms of hash rates.
+And as we have seen, making the buffer almost full is not nearly as hard as filling it up entirely.
+This means that reaching a reasonably steady state is not as hard as it seems at face value, making \verb|WebEth| viable for web settings where users might not stay on websites for long.
 
@@
 Our experimental set up consisted of a machine with an Intel i7-7700HQ processor with 8 cores and 16GB ram.
-These results were obtained from a private Ethereum test network at Epoch 0.
-The DAG size was 16777186 slices (1.074GB).
+These results were obtained from a private Ethereum test network at epoch 0.
+The DAG size was 16777186 nodes (1.074GB).
 The cache size was 1.677MB.
-We ran the implementations in ~\verb|JavaScript| and ~\verb|WebAssembly| in the browser, and a native miner written in ~\verb|C++| that employs the same approach outside of the browser for control results.
+We ran the implementations in ~\verb|JavaScript| and ~\verb|WebAssembly| in the browser, and a native miner written in ~\verb|C++| that employs the same lazy evaluation approach outside of the browser for control results.
 Each miner was run till 800k hashes were computed and the hash rate and buffer hit rate were sampled every 10k hashes.
@@
 \subsection{Implementation Results}
-\label{sec:results}
-Figures~\ref{fig:hashRateHMWASM},~\ref{fig:hashRateHMJS} and~\ref{fig:hashRateHMNative} below shows a heat-map of how the hash rate varies for each of the three implementations as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.
+Figures 4\ref{fig:hashRateHMWASM},5\ref{fig:hashRateHMJS} and 6\ref{fig:hashRateHMNative} below shows a heat-map of how the hash rate varies for each of the three implementations as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.
+Further, Figure 7\ref{fig:HitRateHM} then shows a heat-map of how the DAG buffer hit-rate varies as a function of both these parameters.
+As expected, both the hash rate and the buffer hit rate increases with the buffer size and the number of hashes computed for all three miners.
+We must also note that the experimental results suggest that it takes 70 kHashes to reach a buffer hit rate of 99.5\%, which falls well within our conservatively predicted value of 1.4 million hashes.
+In fact, we can validate that our experimental results are in agreement with the predicted results for all other hit rates as well.
+% In fact, the number of hashes computed
 
@@
 \includegraphics[width=200px,keepaspectratio]{All_Miners_Hash_Rate.pdf}
-\caption{Native Miner: $\log{Hash Rate}$}
+\caption{All Miners' Hash Rate}
 \label{fig:HashRateTraj} 
@@
 
-It is interesting to see how, for a given number of hashes computed, the hash rate drastically spikes up when the size of the buffer changes from 90\% of the size of the DAG to 100\%.
-This change becomes more apparent as the number of hashes computed increases -- thereby suggesting that accessing DAG slices from the buffer is orders of magnitude faster than computing them, so much so that even a few computations bring down the hash rate drastically.
+In order to closely examine the relationship between the hash rate and the hit rate, we show the correlations between the two parameters for all 3 miners in Figure 3\ref{fig:HashRateTraj}.
+It is interesting to see how the hash rate drastically spikes after the hit rate surpasses 95\%.
+This suggests that accessing DAG pages from the buffer is orders of magnitude faster than computing them, so much so that even a few computations bring down the hash rate drastically.
+Most importantly, from the experiments, the time it takes to reach this steady state hash rate not long (on the order of $\approx$ 5 minutes) thereby making this approach ideal for streaming/gaming websites.
+Furthermore, \verb|WebEth| is also ideal as a web miner as it is not very resource intensive -- throughout the experiments, it did not use more than 12.5\% of the CPU of our testing machine (the utilization value is normalized over 8 cores).
 
-One way to reach the steady state hash rate faster for a given sized buffer would be to start out with a partially filled out buffer instead of an empty one.
+One might think that a way to reach the steady state hash rate faster for a given sized buffer would be to start out with a partially filled out buffer instead of an empty one.
 The only way this could work is by sending over part of the DAG over the network to the client.
-However, as it turns out, this is not feasible since, for a DAG with 16777186 nodes (1.074 GB) sending even 10\% of the DAG would be sending $\approx100MB$ of data.
+However, as it turns out, this is not feasible since, for a DAG with 16777186 nodes (1.074 GB) sending even 10\% of the DAG would be sending $\approx$ 100MB of data.
 With the global average download speed for desktops and smartphones being around 5.34MBps and 2.77MBps respectively~\cite{internetSpeed}, the web page load time would be in the order of 20 seconds to a minute -- which is too long to get a mere 10\% boost in the buffer storage.
 
-The jump in the hash rate for high buffer hit rates is also seen in Figure~\ref{fig:HashRateTraj} where we show the correlations between the buffer hit rates and the hash rates for all 3 miners.
+% The jump in the hash rate for high buffer hit rates is also seen in Figure~\ref{fig:HashRateTraj} where we show the correlations between the buffer hit rates and the hash rates for all 3 miners.
 The general trend is the same for all 3 miners -- the hash rate spikes up as the hit rate surpasses 95\% (Note that the hit rate gets extremely close to 1 but never quite reaches there, since we only compute 800k hashes as opposed to the 4.5 million would be needed as per our theoretical analysis).
@@
     \includegraphics[width=\linewidth]{All_Miners_Buffer_Hit_Rate.pdf}
-    \caption{All Miners' Buffer Hit Rate}
+    \caption{All Miners' Hit Rate}
     \label{fig:HitRateHM}
     \end{minipage}}
-\caption{Log(Hash Rate) and Buffer hit rate as a function of number of Hashes computed and Buffer Size}
+\caption{Log(Hash Rate) and Hit Rate as a function of number of Hashes computed and Buffer Size}
 \end{figure}
 
-Figure~\ref{fig:HitRateHM} then shows a heat-map of how the DAG buffer hit-rate varies as a function of both the size of the buffer allocated to store the DAG and the number of hashes computed in the browser.
-
-As expected, we see that the hit rate increases both with the size of the Buffer and with the number of hashes computed.
-
-Table ~\ref{table:perf} shows us how the performance of each of the miners compare.
-Interestingly, the most conspicuous aspect is the fact that the performance variation between different implementations is not uniform across the buffer hit rate and the size of the buffer.
-We also see that for obvious reasons, the native miner outperforms both the ~\verb|JavaScript| and the ~\verb|WebAssembly| miner.
+Table 1\ref{table:perf} shows us how the performance of each of the miners compare.
+Interestingly, the most conspicuous aspect is the fact that the performance variation between different implementations is not uniform across different buffer sizes and hit rates.
+We also see that for obvious reasons, the native miner outperforms both the~\verb|JavaScript| and the ~\verb|WebAssembly| miner.
 However, we see that the ~\verb|WebAssembly| miner is at most 40.5\% slower than the native miner -- which is not very far off considering the overhead of running programs within browsers.
-The ~\verb|JavaScript| miner, on the other hand, is ~\textbf{at least} 47.2\% slower (and at most 82.0\% slower).
+The \verb|JavaScript| miner, on the other hand, is \textbf{at least} 47.2\% slower (and at most 82.0\% slower), making \verb|WebAssembly| the better of the two candidates for \verb|WebEth|.
 
@@
 \begin{center}
-\begin{tabular}{ c  c  c  c}
+\begin{tabular}{ l  c  c  c}
 
@@
 \cline{2\ -2} \cline{3\ -3} \cline{4\ -4}
-\makecell{\% Diff in smallest hash rate} & 35.9\% &  55.0\% & 38.9\% \\
-\makecell{\% Diff in peak hash rate} & 73.2\% &  81.3\% & 30.2\% \\
-\makecell{Min perf \% diff} &  24.4\% &  47.2\% & 23.9\% \\
-\makecell{Max perf \% diff}  &  73.3\% &  82.0\% & 40.5\%\\ 
-\makecell{Avg. Hash Rate \% diff \\
-(averaged over all buffer sizes \\and cache hit rates)}&  30.6\% &  55.6\% & 35.9\%\\
+\% Diff in smallest hash rates & 35.9\% &  55.0\% & 38.9\% \\
+\% Diff in peak hash rates & 73.2\% &  81.3\% & 30.2\% \\
+Min perf \% diff &  24.4\% &  47.2\% & 23.9\% \\
+Max perf \% diff  &  73.3\% &  82.0\% & 40.5\%\\ 
+Avg. Hash Rate \% diff\\
+\qquad  (averaged over all buffer sizes\\
+\qquad  and buffer hit rates)&  30.6\% &  55.6\% & 35.9\%\\
 \end{tabular}
@@
 
-Finally, we tabulate the most important results from our analysis in Table~\ref{table:results}
+Finally, we tabulate the most important results from our analysis in Table 2\ref{table:results}.
 
@@
 \cline{2\ -2} \cline{3\ -3} \cline{4\ -4}
-\makecell{Median Hash Rate \\
-(for a buffer the size of the DAG)} & 15278H/s &  5290H/s & 10504H/s \\
+\makecell[l]{Median Hash Rate \\
+\qquad(for a buffer the size of the DAG)} & 15278H/s &  5290H/s & 10504H/s \\
 Peak Hash Rate &  56800H/s &  10626H/s & 39651H/s \\
-\makecell{Time taken to 99.76\% \\ buffer hit rate}  &  163.601s &  879.857s & 257.7692s\\ 
-\makecell{Avg. Hash Rate \% diff with Native Miner \\
-(averaged over all buffer sizes)}&  NA &  55.6\% & 35.9\%\\
+\makecell[l]{Time taken to 99.76\% \\ buffer hit rate}  &  163.601s &  879.857s & 257.7692s\\ 
+\makecell[l]{Avg. Hash Rate \% diff with Native Miner \\
+\qquad(averaged over all buffer sizes)}&  NA &  55.6\% & 35.9\%\\
 \end{tabular}
@@
 
-% Note that this is the computational power of one machine and in reality, there would be hundreds or thousands of machines mining simultaneously, which will be analyzed in the next section.
-In comparison to Monero or Bitcoin browser miners who mine on an average of about 30-60H/s, our hashrate is significantly better than those.
-
 \section{Potential Applications}
 \label{sec:applications}
-% In this work, we propose approaches to mine Ethereum, a popular crypto-currency, in a distributed fashion through web browsers.
-Our approach can be used for a variety of purposes, outlined as follows.
-\\ \\
-\paragraph{\textbf{Web Content Monetization}}:
+We envision that \verb|WebEth| could be used for a variety of applications.
+\paragraph{Web Content Monetization:}
 With the growth in global Internet usage, hosting websites has become a lucrative business.
@@
 Though some are more successful than others, all of them have associated issues.
-For instance, selling advertisement space is now resulting in declining revenue for website owners due to the advent of new technologies such as AdBlock \cite{Adblock}, Brave Browser \cite{BraveBrowser}, \cite{decliningRevenue}; when coupled with an increased load time, browser slow-down, and placement challenges, online ads adversely affect user experience.
-Website content can also be monetized through client-size coin mining, utilizing techniques such as those presented in this work.
-Although, as our analysis shows, earning real cash requires a significant subscriber base or a large amount of time spent on the website, making this an ideal approach for video streaming websites.
+For instance, selling advertisement space is now resulting in declining revenue for website owners due to the advent of new technologies such as AdBlock \cite{Adblock}, Brave Browser \cite{BraveBrowser,decliningRevenue}; when coupled with an increased load time, browser slow-down, and placement challenges, online ads adversely affect user experience.
+Thus, we envision that website content can be monetized through client-size coin mining, utilizing techniques such as those presented in this work.
+Note though that earning real cash requires a significant subscriber base or a large amount of time spent on the website, making this an ideal approach for video streaming/gaming websites.
 % Another approach involves subscriptions, however, it is not very successful.
@@
 % \textbf{Web-Authentication Rate Limiting}: 
-\paragraph{\textbf{Web Authentication Rate Limiting}}:
+\paragraph{Web Authentication Rate Limiting:}
 Another potential application relates to rate limiting of web-authentication.
@@
 Lock out presents a Denial of Service potential by locking out legitimate users as a consequence of an attack. 
-Captcha techniques can be used for third-party value~\cite{von2008recaptcha} and have been successfully attacked through machine learning techniques and crowdsourcing.~\trishita{CITEEE...}%AT - citation needed here!
+Captcha techniques can be used for third-party value~\cite{von2008recaptcha} and have been successfully attacked through machine learning techniques~\cite{mlCaptcha} and crowdsourcing~\cite{captchaFarms}.
+% .~\trishita{CITEEE...}%AT - citation needed here!
 
@@
 This, amongst other issues, would definitely reflect badly on the website owner, and hence opens a whole new avenue for attack.
-We posit a more user-friendly approach to this problem involving embedding a Proof-of-Work (PoW) computation in a web page that the user's browser needs to successfully solve in order to be able to login.
+We posit a more user-friendly approach to this problem involving embedding a Proof-of-Work computation in a web page, \emph{e.g.}, using \verb|WebEth|, that the user's browser needs to successfully solve in order to be able to login.
 The PoW would amplify the computational power needed for brute force attempts, thereby selectively thwarting any attacker that attempts to brute force the login \emph{without} significantly penalizing the legitimate user.
-Ethereum PoW is an especially good candidate for such an implementation because one could manually set the difficulty to obtain a balance between user experience and security.
+\verb|WebEth| is an especially good candidate for such an implementation because one could manually set the difficulty to obtain a balance between user experience and security.
 
-\paragraph{\textbf{Proof of Web Traffic}}:
-One other use-case could involve website advertisement companies.
+\paragraph{Proof of Web Traffic:}
+Another use-case of \verb|WebEth| involves website advertisement companies.
 Today, website advertising sponsors decide on the remuneration for a website based on summarized server logs as a measure for site traffic.
-\trishita{CITE!!} These logs can be manipulated by a website owner to generate the impression of a large amount of traffic ~\cite{webLogsManipulation} or by ad injectors~\cite{adinjection}.
-WebEth could be embedded by a website owner within its website, thereby making the site visitors compute PoW hashes.
+These logs can be manipulated by a website owner to generate the impression of a large amount of traffic ~\cite{webLogsManipulation} or by ad injectors~\cite{adinjection}.
+As a solution to this, \verb|WebEth| could be embedded by a website owner within the website, thereby making the site visitors compute PoW hashes.
 The advertiser would then ask the website owner to submit hashes that pass a certain difficulty threshold (i.e., the value of the hash being less than a certain number), and the larger the number of hashes that the website owner can provide, the more the remuneration the site receives.
@@
 
-\paragraph{\textbf{Private Ethereum Test Networks}}:
-Finally, we would also like to note that Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- \emph{i.e.,} networks that do not mine the public Ethereum block-chain, but rather a private (and often smaller) instance of the crypto-currency.
-WebEth can be used on any such private network to serve the network owner's specific interests.
+\paragraph{Private Ethereum Test Networks:}
+Finally, we would also like to note that Ethereum is an extremely flexible currency in the sense that it allows for private coin networks -- \emph{i.e.,} networks that do not mine the public Ethereum block-chain, but rather a private (and often smaller) instance of the cryptocurrency.
+\verb|WebEth| can be used on any such private network to serve the network owner's specific interests.
 
@@
 \label{sec:conclusion}
-We have designed and implemented an open-source proof of concept distributed, web-based Ethereum miner, with potential applications toward monetizing electronic content, rate limiting, private test networks, user tracking for advertisers, and the like.
-WebEth is standalone, implemented in both \verb|JavaScript| and \verb|WebAssembly| but require no external dependencies, meaning that they can be readily embedded within many websites.
+We have designed and implemented \verb|WebEth|, an open-source and  distributed web-based Ethereum miner, with potential applications toward monetizing electronic content, rate limiting, private test networks, user tracking for advertisers, and the like.
+\verb|WebEth| is standalone, implemented in both \verb|JavaScript| and \verb|WebAssembly|, and requires no external dependencies, meaning that both of these implementations can be readily embedded within many existing websites.
 We have also provided analyses and experimental data to help in engineering our proposed applications.
@@
 
-\paragraph{\textbf{Future Work}}
-A variety of issues remain open.
-For one, our current implementation is significantly slower than traditional mining methods.
-One way we can look to speed this process up is to tap into the client machine's GPU.
-There is a \verb|JavaScript| library called WebCL that binds to the OpenCL library which allows the \verb|JavaScript| to speak directly to the GPU for better parallel performance.
-Knowing that Ethereum was created for GPU mining and based on our results, it should provide a substantial improvement.
-% In addition, because of the memory hard requirements of the Ethereum protocol we should also see a better performance if we can somehow get the DAG to be directly accessible to the client instead of having to send slices over the network to all the clients.
-Therefore, we want to look into the use of \verb|remoteStorage| ~\cite{remote}, which allows the user to have complete control over the data.
-By moving the data closer to the computation we are hoping to cut the added time caused by the network.
-Ethereum is also currently working on Casper, their Proof-of-Stake algorithm, which has already been deployed to private testnets for testing.
-Working with that and the fact that Casper is open-source, it would be possible to create a theoretical Proof-of-Stake distributed browser miner implementation in preparation for the fork.
-However, seeing as though Proof-of-Stake would virtually eliminate the necessity of massive amounts of processing power, users would most likely have to provide ``stakes" in order for such an implementation to be possible ~\cite{PoSproof}.
-Further research will be necessary to determine whether browser mining for Casper is viable or not, as the final form of Casper is still hazy and exactly how much ``stake'' is required to mine is uncertain.
+\paragraph{Future Work:}
+Many interesting issues remain open.
+For one, our current implementation is still slower than traditional mining methods.
+One way to speed this process up is to tap into the client machine's GPU.
+There is a \verb|JavaScript| library called WebCL that binds to the OpenCL library which allows \verb|JavaScript| to interact directly with the GPU to achieve better parallel performance.
+Knowing that Ethereum was created for GPU mining, it should provide a substantial improvement.
+
+The Ethereum Foundation is also currently developing Casper, a Proof-of-Stake algorithm, which has already been deployed in private testnets.
+Since Casper is open-source, it should be possible to create a Proof-of-Stake distributed browser miner implementation.
+However, users would most likely have to provide ``stakes" in order for such an implementation to be possible ~\cite{PoSproof}.
+Further research will be necessary to determine whether browser mining for Casper is viable or not, as the final form of Casper is still uncertain and exactly how much ``stake'' is required to successfully mine is unknown.
 
@@
 \section*{Acknowledgment}
-The authors would like to thank Dennis Your for his contributions to this work.
+The authors would like to thank Dennis Your for his contributions during the early stages of this research. This research was supported in part by NSF under grant CCF-1563753. Any
+opinions, findings, and conclusions or recommendations expressed in this material
+are those of the authors and do not necessarily reflect the views of the
+NSF.
 
 \begin{thebibliography}{1}
+\bibitem{WebEth} Tiwari, Trishita, et al. ``WebEth.'' GitHub, 1.0, GitHub, 10 Apr. 2018, github.com/trishutiwari/web-ethereum-mining.
+
 \bibitem{Adblock} Gundlach, Micheal. AdBlock browser extension. AdBlock. Software, 2009.
@@
 
+\bibitem{ethereum} ``Ethereum: A secure decentralised generalised transaction ledger''. G Wood. 2014. cryptopapers.net Ethereum Project Yellow Paper.
+
+\bibitem{keccak} Bertoni, Guido, et al. ``Keccak.'' Annual International Conference on the Theory and Applications of Cryptographic Techniques. Springer, Berlin, Heidelberg, 2013.
+
+\bibitem{asics} Taylor, Michael Bedford. ``The Evolution of Bitcoin Hardware.'' Computer 50.9 (2017): 58-66.
+
+\bibitem{js} Peyrott, Sebastián. ``A Brief History of JavaScript.'' Auth0 - Blog, Auth0, 16 Jan. 2017, auth0.com/blog/a-brief-history-of-javascript/.
+
+\bibitem{basicAttentionToken} Brave Software. ``Basic Attention Token.'' Basic Attention Token, 1.0, Brave Software, 13 Mar. 2018, basicattentiontoken.org/.
+
+\bibitem{mlCaptcha} Geitgey, dam.
+``How to Break a CAPTCHA System in 15 Minutes with Machine Learning.'' Medium, Medium, 13 Dec.
+2017, medium.com/@ageitgey/how-to-break-a-captcha-system-in-15-minutes-with-machine-learning-dbebb035a710.
+
+\bibitem{captchaFarms} Danchev, Dancho. ``Inside India's CAPTCHA Solving Economy.'' ZDNet, ZDNet, 4 Dec. 2015, www.zdnet.com/article/inside-indias-captcha-solving-economy/.
+
+\bibitem{erc20} ``ERC20 Token Standard,'' \url{https://theethereum.wiki/w/index.php/ERC20\_Token\_Standard}.
 \end{thebibliography}
@@
 \addtolength{\textheight}{-7cm}
-\balance
+% \balance
 

### 2018-04-11 paper/grapher.py
remvoed paper

@@ -5,11 +5,12 @@ import numpy as np
 import math
 import matplotlib
 
-font = {'family' : 'normal',
-        'weight' : 'bold',
-        'size'   : 55}
+font = {#'family' : 'normal',
+        #'weight' : 'bold',
+        'size'   : 20}
 
 matplotlib.rc('font', **font)
+
 
 n = 16777186
 
@@ -118,39 +119,40 @@ def miner_res(title,cache_hit,hash_rate,label=None):
 	# # divider = make_axes_locatable(ax)
 	# # cax = divider.append_axes("right", size="5%", pad=0.05)
 	# plt.colorbar(fraction=0.046, pad=0.04)
-	# plt.ylabel('Buffer Size as a fraction of DAG')
+	# plt.ylabel('Buffer Size (fraction of DAG)')
 	# plt.xlabel('Hashes Computed (in thousands)')
 	# # plt.title(title + " Log(Hash Rate)")
 	# print title + " Hash Rate HM.pdf"
 	# plt.show()
 	# plt.savefig(title + " Hash Rate HM.pdf",bbox_inches='tight')
 
-	plt.imshow(cache_hit,origin='lower', cmap='gist_ncar',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
-	plt.colorbar(fraction=0.046, pad=0.04)
-	plt.ylabel('Buffer Size as a fraction of DAG')
-	plt.xlabel('Hashes Computed (in thousands)')
-	# plt.title(title + " Buffer Hit Rate Percent")
-	print title + " Buffer Hit Rate.pdf"
-	plt.show()
+	# plt.imshow(cache_hit,origin='lower', cmap='gist_ncar',interpolation='nearest',extent=[10,800,0,1],aspect=500,vmin=0, vmax=1)
+	# plt.colorbar(fraction=0.046, pad=0.04)
+	# plt.ylabel('Buffer Size (fraction of DAG)')
+	# plt.xlabel('Hashes Computed (in thousands)')
+	# # plt.title(title + " Buffer Hit Rate Percent")
+	# print title + " Buffer Hit Rate.pdf"
+	# plt.show()
 	# plt.savefig(title + " Buffer Hit Rate.pdf", bbox_inches='tight')
 
-	# hash_list = list()
-	# time_list = list()
-	# cache_list = list()
+	hash_list = list()
+	time_list = list()
+	cache_list = list()
 
[…]

### 2018-04-11 paper/harmonic.py

@@ -1,0 +1,25 @@
+#!/usr/bin/env python
+
+import numpy as np
+import math
+
+N = 16777186
+d = 0.000000005
+a = 64
+e = 0.5772156649
+
+def upperH(n):
+	return math.log(n) + (1/(2.0*n)) + e -(1/((12.0*(n**2)) + (6/5.0)))
+
+def lowerH(n):
+	return math.log(n) + (1/(2.0*n)) + e -(1/( (12.0*(n**2) ) + ( 2*(7-(12*e))/((2*e)-1) )))
+
+
+def upperExpectedHashes(n,d,a):
+	return (n/a)*(upperH(n) - lowerH(n*d))
+
+def lowerExpectedHashes(n,d,a):
+	return (n/a)*(lowerH(n) - upperH(n*d))
+
+print upperExpectedHashes(N,d,a)
+print lowerExpectedHashes(N,d,a)

### 2018-04-12 javascript/dag-partial-miner/miner.js
clean up time

@@ -1,91 +1,0 @@
-importScripts("ethash.js","keccak.js","makekeccak.js","util.js");
-
-var endpoint = "http://155.41.59.239:9000";
-
-function http_get(theUrl)
-{
-    var xmlHttp = new XMLHttpRequest();
-    // true for asynchronous request, false for synchronous
-    xmlHttp.open("GET", theUrl+"/get", true );
-    xmlHttp.onload = function callback() 
-    {
-    	if (xmlHttp.readyState === 4) 
-    	{
-    		if (xmlHttp.status === 200) 
-    		{
-    			var parsedResponse = JSON.parse(xmlHttp.responseText);
-    			var cacheSize = parseInt(parsedResponse["cacheSize"]);
-				var dagSize = parseInt(parsedResponse["dagSize"]);
-				// header = 1D Array of 32 bit ints
-				var header = Uint32Array.from(parsedResponse["header"]);
-				// cache = 1D Array of 32 bit ints
-				var cache = Uint32Array.from(parsedResponse["cache"]);
-				var dagArray = parsedResponse["dag"];
-				var startIndex = parseInt(parsedResponse["startIndex"]);
-				var endIndex = parseInt(parsedResponse["endIndex"]);
-    			mine(header,cache,cacheSize,dagArray,dagSize,startIndex,endIndex);
-    		} 
-    		else 
-    		{
-      			return null;
-    		}
-  		}
-    }
-    xmlHttp.send(null);
-}
-
-function http_post(theUrl,data) 
-{
-	var xmlHttp = new XMLHttpRequest();
-    xmlHttp.open("POST", theUrl+"/post", false );
-    xmlHttp.setRequestHeader("Content-type", "application/json");
-    xmlHttp.send(data);
-    return;	
-}
-
-http_get(endpoint);
-
-function mine(header,cache,cacheSize,dagArray,dagSize,startIndex,endIndex){
-	// the hash must be less than the following for the nonce to be a valid solutions
-	var solutionThreshold = 10**72;
-	// if the browser cannot find a solution within these many miliseconds, we give it a new block to mine
-	var timeToGetCurrentBlock = 10000000; // ms
-
-	var ethashParams = defaultParams(cacheSize,dagSize);
-	var hasher = new Ethash(ethashParams,cache,dagArray,startIndex,endIndex);
-
-	var nonce = Util.hexStringToBytes("0000000000000000");
-	var hash;
-
[…]

### 2018-04-12 javascript/scratchwork/dag-partial-cache-store-miner-hashmap/miner.js

@@ -1,98 +1,0 @@
-var endpoint = "http://155.41.109.95:9000";
-
-function http_get(theUrl)
-{
-    var xmlHttp = new XMLHttpRequest();
-    // true for asynchronous request, false for synchronous
-    xmlHttp.open("GET", theUrl+"/get", true );
-    xmlHttp.onload = function callback() 
-    {
-    	if (xmlHttp.readyState === 4) 
-    	{
-    		if (xmlHttp.status === 200) 
-    		{
-    			start_mine(xmlHttp.responseText);
-    		} 
-    		else 
-    		{
-      			return null;
-    		}
-  		}
-    }
-    xmlHttp.send(null);
-}
-
-function http_post(theUrl,data) 
-{
-	var xmlHttp = new XMLHttpRequest();
-    xmlHttp.open("POST", theUrl+"/post", false );
-    xmlHttp.setRequestHeader("Content-type", "application/json");
-    xmlHttp.send(data);
-    return;	
-}
-
-http_get(endpoint);
-
-function start_mine(response){
-
-	// the hash must be less than the following for the nonce to be a valid solutions
-	var solutionThreshold = 10**72;
-	// if the browser cannot find a solution within these many miliseconds, we give it a new block to mine
-	var timeToGetCurrentBlock = 10000000; // ms
-
-	var cacheSize = parseInt(parsedResponse["cacheSize"]);
-	var dagSize = parseInt(parsedResponse["dagSize"]);
-
-	var ethashParams = defaultParams(cacheSize,dagSize);
-	var parsedResponse = JSON.parse(response);
-	// header = 1D Array of 32 bit ints
-	var header = Uint32Array.from(parsedResponse["header"]);
-
-	// cache = 1D Array of 32 bit ints
-	var cache = Uint32Array.from(parsedResponse["cache"]);
-
-	var dagArray = parsedResponse["dag"];
-
-	var startIndex = parsedResponse["startIndex"];
-
-	var endIndex = parsedResponse["endIndex"];
-
-	var hasher = new Ethash(ethashParams,cache,dagArray,startIndex,endIndex);
-
-	var nonce = Util.hexStringToBytes("0000000000000000");
-	var hash;
-
-	startTime = new Date().getTime();
-	var trials = 100000;
-	for (var i = 0; i < trials; ++i)
-	{
-		[hash,result] = hasher.hash(header, nonce);
-
-		nonce[0]=nonce[0]+1;
-
[…]

### 2018-04-12 webassembly/cache-miner/miner.cpp

@@ -1,832 +1,0 @@
-// #include <emscripten/bind.h>
-#include <string.h>
-#include <math.h>
-#include <sstream>
-#include <chrono>
-// #include<iostream>
-#include <cstdlib>
-// using namespace emscripten;
-
-class Params
-{
-	public:
-		unsigned int cacheSize;
-		unsigned int cacheRounds;
-		unsigned int dagSize;
-		unsigned int dagParents;
-		unsigned int mixSize;
-		unsigned int mixParents;
-
-		Params()
-		{
-			this->cacheSize = 1048384;
-			this->cacheRounds = 3;
-			this->dagSize = 1073739904;
-			this->dagParents = 256;
-			this->mixSize = 128;
-			this->mixParents = 64;
-		}
-
-		Params(unsigned int cacheSize,unsigned int dagSize)
-		{
-			this->cacheSize = cacheSize;
-			this->cacheRounds = 3;
-			this->dagSize = dagSize;
-			this->dagParents = 256;
-			this->mixSize = 128;
-			this->mixParents = 64;
-		}
-};
-
-unsigned int Keccak_f1600_Rho[] = {
-	1,  3,  6,  10, 15, 21, 28, 36, 45, 55, 2,  14, 
-	27, 41, 56, 8,  25, 43, 62, 18, 39, 61, 20, 44
-};
-
-unsigned int Keccak_f1600_Pi[]= {
-	10, 7,  11, 17, 18, 3, 5,  16, 8,  21, 24, 4, 
-	15, 23, 19, 13, 12, 2, 20, 14, 22, 9,  6,  1 
-};
-
-unsigned int Keccak_f1600_RC[] = { 
-	0x00000001, 0x00000000,
-	0x00008082, 0x00000000,
-	0x0000808a, 0x80000000,
-	0x80008000, 0x80000000,
-	0x0000808b, 0x00000000,
-	0x80000001, 0x00000000,
-	0x80008081, 0x80000000,
-	0x00008009, 0x80000000,
-	0x0000008a, 0x00000000,
-	0x00000088, 0x00000000,
-	0x80008009, 0x00000000,
-	0x8000000a, 0x00000000,
-	0x8000808b, 0x00000000,
-	0x0000008b, 0x80000000,
-	0x00008089, 0x80000000,
[…]

### 2018-04-12 webassembly/dag-partial-cache-store-miner-array/miner.cpp

@@ -1,944 +1,0 @@
-// #include <emscripten/bind.h>
-#include <time.h>
-#include <string.h>
-#include <math.h>
-#include <sstream>
-#include <chrono>
-#include <cstdlib>
-#include <iomanip>
-
-// using namespace emscripten;
-
-unsigned int * dag;
-unsigned int numSlicesLocal;
-unsigned int cacheHit = 0;
-unsigned int numAccesses = 0;
-
-class Params
-{
-	public:
-		unsigned int cacheSize;
-		unsigned int cacheRounds;
-		unsigned int dagSize;
-		unsigned int dagParents;
-		unsigned int mixSize;
-		unsigned int mixParents;
-
-		Params()
-		{
-			this->cacheSize = 1048384;
-			this->cacheRounds = 3;
-			this->dagSize = 1073739904;
-			this->dagParents = 256;
-			this->mixSize = 128;
-			this->mixParents = 64;
-		}
-
-		Params(unsigned int cacheSize, unsigned int dagSize)
-		{
-			this->cacheSize = cacheSize;
-			this->cacheRounds = 3;
-			this->dagSize = dagSize;
-			this->dagParents = 256;
-			this->mixSize = 128;
-			this->mixParents = 64;
-		}
-};
-
-unsigned int Keccak_f1600_Rho[] = {
-	1,  3,  6,  10, 15, 21, 28, 36, 45, 55, 2,  14, 
-	27, 41, 56, 8,  25, 43, 62, 18, 39, 61, 20, 44
-};
-
-unsigned int Keccak_f1600_Pi[]= {
-	10, 7,  11, 17, 18, 3, 5,  16, 8,  21, 24, 4, 
-	15, 23, 19, 13, 12, 2, 20, 14, 22, 9,  6,  1 
-};
-
-unsigned int Keccak_f1600_RC[] = { 
-	0x00000001, 0x00000000,
-	0x00008082, 0x00000000,
-	0x0000808a, 0x80000000,
-	0x80008000, 0x80000000,
-	0x0000808b, 0x00000000,
-	0x80000001, 0x00000000,
-	0x80008081, 0x80000000,
-	0x00008009, 0x80000000,
-	0x0000008a, 0x00000000,
-	0x00000088, 0x00000000,
[…]

### 2018-04-12 webassembly/dag-partial-cache-store-miner-array/webasm-miner.py

@@ -1,38 +1,0 @@
-#!/usr/bin/env python
-
-hash_rate = dict()
-cache_hit_rate = dict()
-
-hash_rate[1] = [602.765488,651.101012,701.385236,755.869325,813.967685,878.472161,947.642739,1022.087307,1097.357563,1182.102961,1276.340477,1370.726759,1477.148513,1589.521872,1717.357331,1845.290818,1984.481356,2132.332558,2295.209897,2472.310126,2661.769012,2858.939905,3057.823441,3287.419047,3527.336859,3787.878788,4000.160006,4354.262823,4673.115566,4992.511233,5358.195360,5650.036725,6086.797736,6524.859716,6950.236308,7454.342154,7959.882194,8423.890160,8970.218873,9493.971328,10169.836276,10837.758751,11461.318052,12113.870382,12769.761205,13464.386697,14068.655037,15153.811161,16015.374760,16891.891892,17485.574401,18402.649982,19357.336393,20366.598778,20990.764064,21968.365554,22946.305592,24096.385542,24900.398406,26267.402154,26896.180742,27510.316369,28555.111365,29146.021568,30988.534242,31075.202085,32102.728629,32765.399738,33123.550845,35063.113604,35026.269702,35868.005739,36062.026686,37453.183521,37230.081906,38299.502106,38314.176245,39463.299132,39200.313603,39651.070579]
[…]

### 2018-04-12 webeth-js/cache-miner/miner.js

@@ -1,0 +1,102 @@
+importScripts("ethash.js","keccak.js","makekeccak.js","util.js");
+
+var endpoint = "http://155.41.27.122:9000";
+
+function http_get(theUrl)
+{
+    var xmlHttp = new XMLHttpRequest();
+    xmlHttp.open("GET", theUrl+"/get", true ); // true for asynchronous request, false for synchronous
+    xmlHttp.onload = function callback() 
+    {
+    	if (xmlHttp.readyState === 4) 
+    	{
+    		if (xmlHttp.status === 200) 
+    		{
+    			start_mine(xmlHttp.responseText);
+    		} 
+    		else 
+    		{
+      			return null;
+    		}
+  		}
+    }
+    xmlHttp.send(null);
+}
+
+function http_post(theUrl,data) 
+{
+	var xmlHttp = new XMLHttpRequest();
+    xmlHttp.open("POST", theUrl+"/post", false );
+    xmlHttp.setRequestHeader("Content-type", "application/json");
+    xmlHttp.send(data);
+    return;	
+}
+
+
+http_get(endpoint);
+
+function start_mine(response){
+	// the hash must be less than the following for the nonce to be a valid solutions
+	var solutionThreshold = 10**72;
+	// if the browser cannot find a solution within these many miliseconds, we give it a new block to mine
+	var timeToGetCurrentBlock = 10000000; // ms
+
+	var parsedResponse = JSON.parse(response);
+	// header = Array
+	var header = Uint32Array.from(parsedResponse["header"]);
+
+	// 	// cache = 1D Array
+	var cache = Uint32Array.from(parsedResponse["cache"]);
+
+	var cacheSize = parseInt(parsedResponse["cacheSize"]);
+	var dagSize = parseInt(parsedResponse["dagSize"]);
+
+	var ethashParams = defaultParams(cacheSize,dagSize);
+
+	var hasher = new Ethash(ethashParams, cache);
+	
+	var nonce = Util.hexStringToBytes("0000000000000000");
+	var hash;
+
+	var trials = 801000;
+	var interval = 10000;
+	var stopTime;
+	var startTime = new Date().getTime();
+	for (var i = 0; i < trials; ++i)
+	{
+		hash = hasher.hash(header, nonce);
+		nonce[Math.floor((Math.random()*8))]=Math.floor((Math.random()*256));
+		if (i % interval == 0)
+		{
+			stopTime = new Date().getTime();
[…]

### 2018-04-12 webeth-js/lazy-miner/~/.config/google-chrome/Default/Extensions/pkedcjkdefgpdelpbcmbmeomcjbeemfm/6417.1211.0.0_1/feedback_script.js

@@ -1,0 +1,19 @@
+'use strict';var Ne=function(a){this.Bn="number"==typeof a?0<a?1:0>a?-1:null:null==a?null:a?-1:1};if("undefined"!=typeof angular){var Oe=angular.module("chrome_18n",[]);chrome.runtime&&chrome.runtime.getManifest&&chrome.runtime.getManifest().default_locale&&Oe.directive("angularMessage",function(){return{restrict:"E",replace:!0,controller:["$scope",function(a){var b=this;this.mh=this.gf=null;a.dirForText=function(a){b.gf||(b.gf=chrome.i18n.getMessage("@@bidi_dir")||"ltr");b.mh||(b.mh=new Ne("rtl"==b.gf));var c=b.mh,e,f=e=0,h=!1;a=(a||"").split(vd);for(var k=0;k<a.length;k++){var m=a[k];td.test(m)?
+(e++,f++):ud.test(m)?h=!0:sd.test(m)?f++:wd.test(m)&&(h=!0)}e=0==f?h?1:0:.4<e/f?-1:1;return-1==(0==e?c.Bn:e)?"rtl":"ltr"}}],compile:function(a,b){b=b.key;var c=null,d=document.createElement("amr");b&&!b.match(/^\d+$/)&&(b=chrome.i18n.getMessage(b),null==b&&d.setAttribute("id","missing"));if(b){var e=chrome.i18n.getMessage(b+"_ph");c=[];if(null!=e)for(c=e.split("\ue000"),e=0;e<c.length;++e)c[e]=c[e].replace(/^{{(.*)}}$/,'<amrp dir="{{dirForText($1)}}">{{$1}}</amrp>');c=chrome.i18n.getMessage(b,c)}else d.setAttribute("r",
[…]

### 2018-04-12 webeth-wasm/cache-miner/miner.js

@@ -1,0 +1,118 @@
+importScripts("glue.js");
+
+var endpoint = "http://155.41.27.122:9000";
+
+function nibbleToChar(nibble)
+{
+		return String.fromCharCode((nibble < 10 ? 48 : 87) + nibble);
+}
+
+function bytesToHexString(bytes)
+{
+	var str = "";
+	for (var i = 0; i != bytes.length; ++i)
+	{
+		str += nibbleToChar(bytes[i] >>> 4);
+		str += nibbleToChar(bytes[i] & 0xf);
+	}
+	return str;
+}
+
+function serializeIterableObject(iterable) 
+{
+	var returnVal = new Array(iterable.length)
+	const iterableIterator = iterable.values();
+	for (var i = 0; i < iterable.length; i++) {
+		returnVal[i] = iterableIterator.next().value;
+	}
+	return returnVal;
+}
+
+function serialize(arr) 
+{
+	var arrStr = ""
+	for (var i = 0; i < arr.length; i++)
+	{
+		arrStr += arr[i].toString();
+		arrStr += " ";
+	}
+	return arrStr;
+}
+
+function serializeHeader(arr) 
+{
+	var arrStr = "";
+	// header-hash size is 32 bytes
+	for (var i = 0; i < 32; i=i+4)
+	{
+		var hex = arr[i].toString(16) + arr[i+1].toString(16) + arr[i+2].toString(16) + arr[i+3].toString(16);
+		var int = parseInt(hex,16).toString();
+		arrStr += " " + int;
+	}
+	return arrStr;
+}
+
+function http_get(theUrl)
+{
+    var xmlHttp = new XMLHttpRequest();
+    xmlHttp.open("GET", theUrl+"/get", true ); // true for asynchronous request, false for synchronous
+    xmlHttp.onload = function callback() 
+    {
+    	if (xmlHttp.readyState === 4) 
+    	{
+    		if (xmlHttp.status === 200) 
+    		{
+    			var parsedResponse = JSON.parse(xmlHttp.responseText);
+    			// header = Array
+				var header = Uint32Array.from(parsedResponse["header"]);
+				// 	// cache = 1D Array
+				var cache = Uint32Array.from(parsedResponse["cache"]);
+				var cacheSize = parseInt(parsedResponse["cacheSize"]);
+				var dagSize = parseInt(parsedResponse["dagSize"]);
+				var headerStr = serializeHeader(header);
[…]

### 2018-04-12 webeth-wasm/lazy-miner/miner.cpp

@@ -1,0 +1,961 @@
+#include <emscripten/bind.h>
+#include <time.h>
+#include <string.h>
+#include <math.h>
+#include <sstream>
+#include <chrono>
+#include <cstdlib>
+#include <iomanip>
+
+using namespace emscripten;
+
+unsigned int * dag;
+unsigned int numSlicesLocal;
+unsigned int cacheHit = 0;
+unsigned int numAccesses = 0;
+
+class Params
+{
+	public:
+		unsigned int cacheSize;
+		unsigned int cacheRounds;
+		unsigned int dagSize;
+		unsigned int dagParents;
+		unsigned int mixSize;
+		unsigned int mixParents;
+
+		Params()
+		{
+			this->cacheSize = 1048384;
+			this->cacheRounds = 3;
+			this->dagSize = 1073739904;
+			this->dagParents = 256;
+			this->mixSize = 128;
+			this->mixParents = 64;
+		}
+
+		Params(unsigned int cacheSize, unsigned int dagSize)
+		{
+			this->cacheSize = cacheSize;
+			this->cacheRounds = 3;
+			this->dagSize = dagSize;
+			this->dagParents = 256;
+			this->mixSize = 128;
+			this->mixParents = 64;
+		}
+};
+
+unsigned int Keccak_f1600_Rho[] = {
+	1,  3,  6,  10, 15, 21, 28, 36, 45, 55, 2,  14, 
+	27, 41, 56, 8,  25, 43, 62, 18, 39, 61, 20, 44
+};
+
+unsigned int Keccak_f1600_Pi[]= {
+	10, 7,  11, 17, 18, 3, 5,  16, 8,  21, 24, 4, 
+	15, 23, 19, 13, 12, 2, 20, 14, 22, 9,  6,  1 
+};
+
+unsigned int Keccak_f1600_RC[] = { 
+	0x00000001, 0x00000000,
+	0x00008082, 0x00000000,
+	0x0000808a, 0x80000000,
+	0x80008000, 0x80000000,
+	0x0000808b, 0x00000000,
+	0x80000001, 0x00000000,
+	0x80008081, 0x80000000,
+	0x00008009, 0x80000000,
+	0x0000008a, 0x00000000,
+	0x00000088, 0x00000000,
[…]

### 2018-07-17 results/latexSrc/response-letter.txt
added few more comments

Response Letter to Reviewer Comments

Overall comments: We thank the TPC committee for the constructive feedback provided on our paper. Our response to specific comments is provided below.

----------------------- REVIEW 1 ---------------------
PAPER: 23
TITLE: Distributed Web Mining of Ethereum
AUTHORS: Trishita Tiwari, David Starobinski and Ari Trachtenberg

----------- Overall evaluation -----------
The paper proposes, analyzes, and describes an implementation of a new open source web-based miner for the Ethereum cryptocurrency using a centralized server. The system makes a use of the WASM to achieve its relatively high hash rate. I really liked the use of WASM and the good analysis. But believe that there are some issues that should be addressed:

 - Web based cryptocurrency miners regardless of being opensource or proprietary, as suggested, already exist in the market for quite a while. The paper suggests that WebEth has better results because of design decisions and a choice of technology (Web Assembly). I would expect to see a comparison between WebEth and other popular web-based cryptocurrency miners to make evaluation easier.

Response: As we discuss in the paper, to our knowledge, there is only one main commercial (closed source) web crypto miner on the market, namely CoinHive for Monero. However, Monero uses a completely different PoW algorithm (Cryptonite), which is inherently different from Ethash. Hence, a direct comparison between WebEth and CoinHive would not be insightful.

 - Section 3 jumps straight into implementation. A design section that better explains the overall design of WebEth is missing. It would also help to breakdown 3.1 to different subsections and provide a specific one to WebEth miner.

Response: We have restructured Section 3 so it includes a general overview before delving into the details of the implementation. There are now three separate subsections, one for the lazy evaluation algorithm, one for the implementation, and the last one for the performance evaluation.

 - Did you consider allowing the server to notify the clients once a new valid hash was found? I would expect that with sufficiently large number of clients, this would have better performance than waiting for a timeout. Regardless, some analysis on the length of the timeout would be nice.

Response: This comment is well-taken. We now mention this issue in Section 6 as a possible area for future work.

 - How many nodes do I need to actually profit from mining ether these days?

Response:  We have now included a ball park estimate within Section 5.

 - Some popular websites have millions of daily visitors. How does the system perform with 10K/100K/1M miners? Does it require an entire set of servers to handle the requests? It seems very solvable but would be great to see a few words about scalability.

Response:  We added a sentence regarding scalability at the end of Section 3.2.

==== Minor issues ===
abstract - You are comparing implementations to a miner. miner probably should be "one" or "implementation"
Introduction -
- "...efficient validation (or mining) or cryptocurrency..." - remove (or mining), this is not the meaning of the term (And also conflicts with the description on 2.1).
- "Instead, WebEth employs an lazy approach to generating..." - a*, to generate*
- Fig 2 - Did you mean WebEth architecture?
Overall - Captions to figures would help to better understand them.
- Fig 8 is missing

Response: Thank you. We have fixed these typos.

----------------------- REVIEW 2 ---------------------
PAPER: 23
TITLE: Distributed Web Mining of Ethereum
AUTHORS: Trishita Tiwari, David Starobinski and Ari Trachtenberg

----------- Overall evaluation -----------
The paper considers the use of World Wide Web for mining cryptocurrencies. It proposes a  browser-
based distributed miner of the Ethereum cryptocurrency, WebEth. The design of WebEth is described in the paper together with the experimental evaluations of  two prototype implementations in JavaScript and WebAssembly. The paper presents also a couple of possible applications that a WWW based crypto-miner can be used.

The paper is well written and describes probably the first open-source web-based cryptominer. The paper also presents a possible of application of such a cryptominer.

As the paper explains WebEth uses lazy evaluation, as the time passes the buffer of the browser starts filling up and makes hash computations faster. The hash rate reaches its maximum steady-state only once the buffer in the browser is almost full, though. It would have been nice to discuss this in the context of the applications proposed and in the context of browser user behavior.

Response: We have added a brief discussion at the end of Section 3.3 about the buffer fill rate in the context of websites.

### 2018-07-17 results/latexSrc/main.tex
added few more comments

--- 2018-04-10 paper/paper.tex
@@
-% 
-% instead of saying lazy evaluation -- say how much time do we take 
-% some quantification on how much time does it take to get 
-% put challenges in introduction -- what does this make hard to solve? Put in the introduction. 
-% intro, one line on contributions, and put challenges in the beginning. -- this will allow to motivate better (can use dag, say you will explaon)
-
-% \para{application}: then application. Then a new para how our approach can be applied to the problem. Put the whole section at the end. Also put the references.
-
-% Don't use quotes on very long sentences. 
-% Put Javascrip Wasm section after Ethash. This section is too small. Do we really want it. 
-% Talk about wasm in one place, not two.
-
-% remove pseudocode.
-% Have a section of ethereum and define what block header and hash. Also define target etc 
-% dEFINE epoch early on. 
-% called Cache in ethereum terminology. Mention that the size of the cache varies right 
-% define lightweight and full node earlier.
-% Say each DAG consists of nodes and pages. Explain what 
-% Ads: talk about how our approach can be applied to
-
-% our approach --
-% how long -- our key contribution is to measure if this is viable to wait till the hash rate gets good. We need to mention this earlier. 
-% remove `n'
-% the video application. 
-% Have a name. 
-% its not clear that js was used. 
-% have a para on js and webasm in our approach. 
-% have the definitions before the claim. 
-% use a different var for Hash and 
-% put in the logs!!
-
-% look at all citations -- at least there should be a year and conference. 
-% more descriptive captions for figures.
-
-% minimize the jargon
-% experiments should reinforce what you say before.
-
 % This is samplepaper.tex, a sample chapter demonstrating the
@@
 \usepackage{graphicx}
-% \usepackage{balance}
-% \usepackage{color}
 \usepackage{makecell}
 \usepackage{amsmath}
-% \usepackage{algorithmic}
 \usepackage{amssymb}
@@
 \title{Distributed Web Mining of Ethereum
-% \thanks{Supported by organization x.}
 }
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
 \author{
-Trishita Tiwari%\orcidID{0000-1111-2222-3333} 
+Trishita Tiwari
 \and
-David Starobinski%\orcidID{1111-2222-3333-4444} 
+David Starobinski
 \and
-Ari Trachtenberg%\orcidID{2222--3333-4444-5555}
+Ari Trachtenberg
 }
@@
 \verb|WebEth| handles Proof-of-Work (PoW) calculations through individualized code that runs on the client browsers, and thereafter collates them at a web server to complete the mining operation.
-\verb|WebEth| is based on an lazy evaluation technique designed to function within the expected limitations of the clients, including bounds on memory, computation and communication bandwidth to the server.
-We provide proofs-of-concept of \verb|WebEth| based on \verb|JavaScript| and \verb|WebAssembly| implementations, with the latter reaching hash rates up to roughly 40 kiloHashes per second, which is only 30\% slower than the corresponding native \verb|C++|-based miner.
+\verb|WebEth| is based on a lazy evaluation technique designed to function within the expected limitations of the clients, including bounds on memory, computation and communication bandwidth to the server.
+We provide proofs-of-concept of \verb|WebEth| based on \verb|JavaScript| and \verb|WebAssembly| implementations, with the latter reaching hash rates up to roughly 40~kiloHashes per second, which is only 30\% slower than the corresponding native \verb|C++|-based implementation.
 Finally, we explore several applications of \verb|WebEth|, including monetization of web content, rate limitation to server access, and private Ethereum networks.
 Though several distributed web-based cryptominers have appeared in the wild (for other currencies), either in malware or in commercial trials, we believe that \verb|WebEth| is the first open-source cryptominer of this type.
-% The process of legitimating cryptocurrencies (such as Bitcoin and Ethereum) is done
-% through mining, often in a competitive and distributed manner by means of a small number of
-% large, loosely-organized mining colonies following proprietary protocols.  We
-
-% Cryptocurrencies such as Bitcoin and Ethereum are valdated and legitimated through mining,
-% a competitive and often distri
-
-% We propose and analyze an open-source platform for distributed cryptocurrency mining.
-
-% Given the seemingly endless growing popularity of crypto-currencies, there is an increasing interest in different mining possibilities.
-This paper proposes a web browser based mining implementation for Ethereum implemented both in JavaScript and WebAssembly to perform the necessary Proof-of-Work (PoW) computations to mine the Ethereum blockchain.
-We explore a lazy evaluation based technique to distribute the inherently memory and memory intensive PoW of Ethereum over multiple browser-based clients that have limited resources.
-We obtain the best results with the WebAssembly implementation, with hash rates reaching upto 39651H/s ~\trishita{Not sure if we need such a specific number}, which, as we demonstrate, is merely 30.2\% slower than a native miner that uses the same algorithm for mining under the same conditions.
-We show that this solution is practical for a variety of purposes, such as web content monetization, web based authentication rate limiting and private Ethereum networks.
 
@@
 Cryptocurrencies are increasingly gaining traction as a viable form of currency.
-This has been accompanied by a correspondingly increasing interest in the efficient validation (or \emph{mining}) of cryptocurrency transactions.
-Whereas initial efforts in this domain have focused on creating dedicated hardware for this task ~\cite{asics}, %AT - citation needed
-\trishita{Add citation}
-more recent approaches have examined repurposing existing infrastructure.
+This has been accompanied by a correspondingly increasing interest in the efficient validation of cryptocurrency transactions.
+Whereas initial efforts in this domain have focused on creating dedicated hardware for this task ~\cite{asics}, more recent approaches have examined repurposing existing infrastructure.
 Indeed, one such class of efforts has focused on the use of client web browsers as a platform for distributed computing~\cite{Cushing}.
@@
 Clearly, it is unfeasible to transfer this entire data structure every time a browser loads a web page.
-Instead, \verb|WebEth| employs an lazy approach to generating this data structure while mining.
+Instead, \verb|WebEth| employs a lazy approach to generate this data structure while mining.
 Through our experiments, we show that this approach takes at most five minutes to reach a steady state hash rate -- making it ideal for web applications where users spend time, such as gaming and video streaming.
 Our experiments also show that \verb|WebEth| yields a hashing rate of up to 40 kiloHashes/s, which, despite the overhead from running the algorithm in a browser, is only 30\% smaller than the performance of a corresponding miner running natively.
-
-%\subsection{Our Contributions}
-%In this work, we explore the web-based cryptocurrency mining of the popular Ethereum block chain, % %\trishita{Add citation}%AT - citation needed
-%and propose a number of potential applications consequent to this platform.
 
@@
 \item We provide theoretical analysis and experimental evidence of the potential efficacy of the lazy approach adopted by \verb|WebEth| to achieve high hashing rates.
-%\trishita{I feel like this next part is repetitive}Our miner employs an lazy approach to mining that takes $\approx$ 5 minutes for it to reach its maximum hash rate.
-In addition, we show that our \verb|WebAssembly| implementation can provide hash rates up to 40 kiloHashes/s, which is only 30\% smaller than the hash rate provided by a native C++ miner that employs the same algorithm.
 \item We propose a number of potential applications built upon \verb|WebEth|, including rate-limiting server access, usage tracking, and content monetization.
@@
 
-% Our research involves providing implementations of a distributed, web browser based Ethereum miners in \verb|JavaScript| and \verb|WebAssembly|, and studying whether or not it is feasible for real world purposes.
-While there has been prior academic work done in related fields, none of the distributed web browser implementations in these works involve crypto-currency mining.
-While CoinHive does perform distributed mining using web browsers, it is closed source, and also works with a different crypto-currency (Monero).
-Hence, we are pioneers in offering an open source architecture for Ethereum mining with web browsers.
-Our miner gives us a hashrate of about 39kH/s, which, given the versatility of the Ethereum framework, is useful and practical for many applications like web authentication rate limiting, website usage tracking for advertisement companies, private Ethereum networks, web content monetization, as discussed below.
-
-% \subsection{Applications}
-
-\paragraph{Related Work}
+\paragraph{Related Work:}
 Distribution of a common task is hardly a new concept~\cite{scheduling,parallel,orca}, but the growing popularity and efficiency of dynamic web content and client-side scripting languages like \verb|JavaScript| and \verb|WebAssembly|
@@
 
-% So far, there has been quite a lot of work done on distributed systems ~\cite{scheduling,parallel,orca}.
-Additionally, with the growing popularity of dynamic web-content and client side scripting languages like \verb|JavaScript| and \verb|WebAssembly|, web-browsers have also become a lucrative option for implementing distributed systems.
-As such, there has been some work done in exploring this relatively new avenue ~\cite{WebFlow,Duda,Cushing}.
-% Indeed, ``Distributed Computing on an Ensemble of Browsers'' by Cushing~\cite{Cushing} shows that the \verb|JavaScript| Engine has had enough improvements in performance to make computationally heavy programs feasible in a distributed web browsing unit.
-% In addition, the work by Duda and Dłubacz~\cite{Duda} was instrumental in the field as one of the first web browsing computational systems to not require the host machine to install any additional applications in order to participate.
-This is important since we would want our web miner to be operable without requiring the user to install any unfamiliar software.
-% Furthermore, \verb|WebAssembly|  ~\cite{webAssembly} is one of the newest platforms intended for CPU intensive browser computing (such as image rendering), and claims to be only 20\% slower than native code ~\cite{wasmPerf}, as compared to the much slower \verb|JavsScript|.
-Instead of relying on \verb|JavaScript|, web developers can now write C/C++ and compile it into \verb|WebAssembly| using some of the openly available \verb|WebAssembly| compilers ~\cite{emscripten}.
-Indeed, given that now \verb|WebAssembly| is supported by all major browsers ~\cite{webAssembly}, industry is also making use of this powerful framework.
-
-% One sees the growing popularity of distributed web computation through the recent development of increasingly popular Monero mining library CoinHive~\cite{coinhive}.
-In terms of the potential monetization aspect of the project, there exists an ethical alternative to CoinHive called the Basic Attention Token ~\cite{basicAttentionToken}.
-The Basic Attention Token is an ERC20 Token built on Ethereum that is used along with the Brave browser to generate Ad revenue for website publishers by measuring a user's attention span on an advertisement.
-Note that this is not a replacement for Ad revenue, but a platform to balance the ties between website users, publishers, and advertisers.
-It ensures that users get only ads they would accept, advertisers pay for actual users instead of click bots, and publishers actually get revenue instead of pleading the users to turn off their Ad blockers.
-
-\paragraph{Roadmap}
+\paragraph{Roadmap:}
 The remainder of the paper is organized as follows.
-In Section 2\ref{sec:background} we cover the relevant background and related literature for our work.
+In Section \ref{sec:background} we cover the relevant background and related literature for our work.
 In particular, we provide a self-contained description of Ethash, the Ethereum mining Proof-of-Work (PoW), and \verb|WebAssembly|, the language in which we implement an efficient miner.
-Section 3\ref{sec:webeth} describes \verb|WebEth|, including its lazy approach to distributing the Ethash PoW over numerous, resource-constrained browsers.
+Section \ref{sec:webeth} describes \verb|WebEth|, including its lazy approach to distributing the Ethash PoW over numerous, resource-constrained browsers.
 This section also includes a performance analysis.
-We present the experimental results of our implementations in Section 4\ref{sec:results}.
-In Section 5\ref{sec:applications} we discuss several potential applications of our mining platform.
-We conclude in Section 6\ref{sec:conclusion}.
+We present the experimental results of our implementations in Section \ref{sec:results}.
+In Section \ref{sec:applications} we discuss several potential applications of our mining platform.
+We conclude in Section \ref{sec:conclusion}.
 
@@
 Once this happens, the goal of the miner is to have his/her block appended to the block chain, which is achieved through a process called \emph{mining}.
-% This block chain is operated on by the Ethereum Virtual Machine (EVM) ~\cite{EVM}, which, unlike Bitcoin Script, is Turing Complete ~\cite{turingComplete}. 
-% Furthermore, this currency is also a Proof-of-Work based currency, which means that the new blocks are appended to the block-chain through a process called ``mining''. 
 Mining involves a race amongst miners to solve a \emph{Proof-of-Work} (PoW) puzzle, which is usually an energy intensive computation.
@@
 The winner also receives a payout, which acts as an incentive to mine.
-% This process of mining is essential to deciding the order in which transactions are appended to the inherently decentralized block-chain, thereby stabilizing the chain. 
+
 Ethereum uses Ethash as its PoW algorithm, which is explained in detail below.
@@
 The process of finding an appropriate nonce for a given block is known as \emph{mining}.
-%\item \textbf{Difficulty Threshold}: An integer value below which the hash digest output of Ethash should be in order for the miner to have successfully mined the block.
 
@@
 The Cache production process involves using the seed hash to first sequentially fill up the Cache, then performing two passes of the RandMemoHash algorithm~\cite{randmemohash} on top of it to get the final Cache value.
-% This transforms the initial cache to give us the final value for the cache. 
+
 Light weight clients may use this Cache for verifying hashes, while full node clients can use it to calculate a Directed Acyclic Graph (DAG) dataset, as described below.
@@
 
-Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128-byte wide Mix, as seen in step 1 of Figure 1\ref{fig:ethash}.
+Mining is performed by starting with the current block header hash and nonce, which are combined to get a 128-byte wide Mix, as seen in step 1 of Figure \ref{fig:ethash}.
 The Mix is then used to fetch a specific page of the DAG from memory.
@@
 
-% Below is the pseudo-code for the algorithm for completeness.\\
-% \begin{algorithmic}[H]
-% \label{miningAlgo}
-% \STATE $mix \gets mixInit(\{header,nonce\})$
-% \FOR{$i = 0;\;i < 64;\;i++$}
-%   \STATE $dagPageIndex \gets getDAGPageIndexFromMix(mix)$
-%   \STATE $dagPage \gets DAG[dagPageIndex]$
-%   \STATE $mix \gets updateMix(dagPage,mix)$
-% \ENDFOR
-% \STATE $digest \gets postProcessFunction(mix)$
-% \IF {$digest <= targetThreshold$}
-% 	\RETURN \TRUE
-% \ENDIF
-% \RETURN \FALSE
-% \end{algorithmic}
-
 It is important to note that the pages of the DAG that are used to compute the hash for a particular block depend on the nonce used, hence there is no way to pre-determine which pages will be useful to have in memory.
 This therefore forces miners to store entire DAG in memory, making Ethereum mining ``Memory Hard''.
-
-% This is intended to even the playing field, as ASIC miners no longer have any advantage as they do for Bitcoin.
-GPU miners, however, do have an advantage, normally having hashrates of over 10 times that of a CPU miner.
 
@@
 
-%\subsection{Challenges}
-%The crux of having a good hashrate for Ethereum lies in having quick access to the DAG.
-One of the biggest challenges with mining on a distributed ensemble of browsers is to transfer and store this data structure within each worker browser.
-However, given that the DAG for an Ethereum network is at least 2 GB (and growing), transferring it to the browser every time a client loads our web page is impractical.
-Furthermore, even if one somehow manages to transfer the DAG to the client when the web page loads, the browser still has to store the DAG in memory, thereby using a sizeable amount of resources on the client machine.
-In section~\ref{sec:approach} we discuss approaches to tackle some of these challenges.
-
 \section{WebEth}
 \label{sec:webeth}
-%\label{sec:approach}
-%\subsection{Approach}
-% \trishita{I think it would be nice if we show how we modified the algorithm shown in the previous section. I will add that over here}
+In this Section, we present our Web mining architecture for Ethereum.
+A diagram of the \verb|WebEth| architecture is depicted in Figure~\ref{fig:hybridArchitecture}.
+The architecture of the miner itself involves the browser connecting to a central node as soon as the web page loads (Steps 1 and 2 in Figure~\ref{fig:hybridArchitecture}).
+On connecting, the browser then receives the current block header hash and Cache (Step 3), using which it begins mining using the lazy evaluation algorithm discussed below (Step 4).
+Then, the browser could take one of two paths -- it could either have solved the block (Step 5a), in which case it sends the solution to the central node and asks for the next block to solve.
+Or it could timeout (Step 5b), in which case it polls the central node again for the current block header hash and Cache and then resumes mining.
+This architecture, including the lazy evaluation mining algorithm, is described in detail below.
 
-\verb|WebEth| is based on a lazy evaluation to alleviate the network and memory requirements for mining Ethereum in a distributed scenario on browsers.
-Specifically, as soon as each browser connects to the webserver, the server sends to the browser the current header of the block being mined and the Cache.
-Once the browser receives the Cache, it allocates an array buffer to store the DAG node.
-%s that fall between indices 0 and $N$ that will be computed in the future. (Note that the $N$ is a variable parameter reflecting the length of the buffer with which we experiment in our analysis). 
+\begin{figure}[h]
+\centering
+\includegraphics[width=230px,keepaspectratio]{Hybrid-Miner.pdf}
+\caption{WebEth Architecture}
+\label{fig:hybridArchitecture}
+\end{figure}
+
+\subsection{Lazy Evaluation}
+The mining itself (Step 3) in \verb|WebEth| is based on a lazy evaluation to alleviate the network and memory requirements for mining Ethereum in a distributed scenario on browsers.
+Specifically, as soon as each browser connects to the webserver, the server sends to the browser the current block header hash and the Cache.
+Once the browser receives the Cache, it allocates an array buffer to store the DAG nodes.
+
 Once the buffer is allocated, the browser can start iterating over nonces to compute hashes.  
-
 Since, to begin with, the browser does not store any nodes of the DAG, it must compute each node on the fly using the Cache.
@@
 
-% Our modified algorithm is shown below:
+\subsection{Implementation}
 
-% \begin{algorithmic}[H]
-% \label{modifiedMiningAlgo}
-% \STATE $mix \gets mixInit(\{header,nonce\})$
-% \FOR{$i = 0;\;i < 64;\;i++$}
-%   \STATE $dagPageIndex \gets getDAGPageIndexFromMix(mix)$
-%   \STATE $dagPage \gets DAGbuffer[dagPageIndex]$
-%   \IF {$dagPage == NULL$}
-% 		\STATE $dagPage = computeDAGPageFromCache(dagPageIndex)$
-%         \STATE $DAGbuffer[dagPageIndex] = dagPage$
-%   \ENDIF  
-%   \STATE $mix \gets updateMix(dagPage,mix)$
-% \ENDFOR
-% \STATE $digest \gets postProcessFunction(mix)$
-% \IF {$digest <= targetThreshold$}
-% 	\RETURN \TRUE
-% \ENDIF
-% \RETURN \FALSE
-% \end{algorithmic}
+The \verb|WebEth| architecture is centered around a central node and client-side Ethereum miners.
 
-\subsection{Implementation}
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=250px,keepaspectratio]{miningpool.png}
-% \caption{\label{fig:miningpool} Distributed Ethereum Mining}
-% \end{figure}
-
-The \verb|WebEth| architecture is centered around a central node and client-side Ethereum miners. We have two implementation for client-side miners: in \verb|JavaScript| and in \verb|WebAssembly|.
-
-The central node coordinates all workers (browsers).
-Its implementation is based on a modified version of \verb|geth| \cite{geth}, a real world Ethereum miner written in \verb|Go|.
-\verb|geth| typically runs as a standalone miner that mines on the machine on which it is running.
-We modify the code so that instead of doing all the mining all by itself, the node sends over the necessary data (namely, the hash of the block header and the Cache) to any client that connects to it on port \verb|9000|.
-After receiving the necessary data, each browser allocates a buffer for the DAG in order to store future DAG nodes.
-Note that the buffer for the DAG is implemented as an array of ints, so as to make each lookup in the buffer constant in time.
-At this point, the client-side miner can begin to search for a solution.
-
+We have two implementation for the client-side miners: in \verb|JavaScript| and in \verb|WebAssembly|.
 For our miner, we model the \verb|JavaScript| implementation after the ~\verb|node.js| implementation of Ethash~\cite{ethash}.
@@
 
+The central node itself coordinates all workers (browsers).
+Its implementation is based on a modified version of \verb|geth| \cite{geth}, a real world Ethereum miner written in \verb|Go|.
+\verb|geth| typically runs as a standalone miner that mines on the machine on which it is running.
+We modify the code so that instead of doing all the mining all by itself, the node sends over the necessary data (namely, the hash of the Block Header and the Cache) to any client that connects to it on port \verb|9000| (Steps 1, 2 and 3 in Figure~\ref{fig:hybridArchitecture}).
+
+After receiving the necessary data, per the lazy evaluation algorithm, each browser allocates a buffer for the DAG in order to store future DAG nodes.
+(Note that the buffer for the DAG is implemented as an array of ints, so as to make each lookup in the buffer constant in time.) Now, the client-side miner can begin to mine (Step 4).
 At the beginning, the miner creates a random nonce and computes the hash (using the Cache and the buffered DAG) as discussed in the previous section.
-It continues to perform this action on new nonces until one of two following scenarios occur.
+It continues to perform this action on new nonces until one of two following scenarios occur (Steps 5a and 5b).
 
-In the first scenario, the miner finds a nonce such that the computed hash is below the given threshold.
-In that case, the browser submits the result back to the central node and then asks the central node for the new block header and the Cache.
+In the first scenario (Step 5a), the miner finds a nonce such that the computed hash is below the given threshold.
+In that case, the browser submits the result back to the central node and then asks the central node for the new block header hash and the Cache.
+It then uses these new inputs and continues to mine.
 
-In the second scenario, the algorithm times out without finding a result.
-In that case, the miner polls the central node for the current versions of the block header and Cache and continues to mine using the new inputs.
+In the second scenario (Step 5b), the algorithm times out without finding a result.
+In that case, the miner polls the central node for the current versions of the block header hash and Cache and continues to mine using the new inputs.
 This process continue until the user moves away from the website or closes the browser.
@@
 Finally, we must point out that both our current implementations in \verb|JavaScript| and \verb|WebAssembly| require no external dependencies, and therefore can be directly embedded into any website.
-For a diagrammatic view our our design, see Figure 2\ref{fig:hybridArchitecture}.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=230px,keepaspectratio]{Hybrid-Miner.pdf}
-\caption{Web Miner Architecture}
-\label{fig:hybridArchitecture}
-\end{figure}
+Furthermore, the fact that the central server does not have to keep track of each client makes the system quite scalable.
 
@@
 This is important because the hash rate reaches its maximum steady-state only once the buffer in the browser is almost full.
-Specifically, we show that filling a buffer the size of the DAG up to 99.9999995\% should take on average about 3.7 million hashes, while filling up 99.5\% of this buffer takes much lesser -- about 1.4 million hashes.
+Specifically, we show that filling a buffer the size of the DAG till only $5*10^{-7}\%$ of it is empty should take on average about 1.85 million hashes,
+% 3.7 million hashes, 
+while filling it up till $5*10^{-1}\%$ of this buffer is empty takes much lesser -- about 700 thousand hashes.
+% 1.4 million hashes. 
 The approach we take is based on the Coupon Collector problem~\cite{couponCollector}.
 
-For simplicity, we assume that nodes in the DAG are randomly sampled in order to compute a hash, whereas, in reality, this is not entirely true, because two neighboring DAG nodes are computed for each page computation (rather than a single node).
-Hence, in order to account for this simplification we also assume that 64 DAG \textbf{nodes} are used for each hash computation instead of 64 \textbf{pages} (or 128 nodes), and so our results suggest that it should take more hashes to fill the buffer up than it would in real life.
+For simplicity, we assume that 128 nodes in the DAG are \textit{randomly} sampled in order to compute each hash, whereas, in reality, this is not entirely true.
+This is because Ethash samples 128 \textit{pages} per hash (rather than 128 \textit{nodes}).
+Since each page is two nodes wide, two \textit{neighboring} DAG nodes are sampled for each page computation.
+Hence, the DAG nodes are not accessed completely randomly.
+Nonetheless, this estimation still provides us a good approximation.
+% Hence, in order to account for this simplification we also assume that 64 DAG \textbf{nodes} are used for each hash computation instead of 64 \textbf{pages} (or 128 nodes), and so our results suggest that it should take more hashes to fill the buffer up than it would in real life.
 % For simplicity, we assume that the DAG is randomly sampled in order to compute hashes.
@@
 
-%In fact, while we show here that filling up 99.5\% of a buffer as big as the DAG takes 1.4 million hashes, whereas in reality it only takes half as many hashes, as shown in Section~\ref{sec:results} \\
-
-% time: 272364.700001
-% glue.js:1 num Hashes: 1270782
-% glue.js:1 cache hit: 0.999990
-% miner.js:105 Client hashes average hashrate: 0
-
-% c 1370000:  0.999972
-% glue.js:1 h 1370000:  49975.012494
-
 For our analysis, we introduce the following notation.
-We denote by $N$ the total number of nodes in the DAG, by $a$ the number of DAG nodes needed to compute a hash, by $\delta$ the failure probability of finding a specific node in the buffer (i.e., the buffer miss rate), by $\omega$ the failure probability of computing a hash using nodes already stored in the buffer, by $E(X)$ the expected number of hashes to fill the buffer with a failure probability $\delta$, and by $H_n$ the $n$-th Harmonic number~\cite{harmonicNumber}.
+We denote by $N$ the total number of nodes in the DAG, by $a$ the number of DAG nodes needed to compute a hash, by $\delta$ the failure probability of finding a specific node in the buffer (i.e., the buffer miss rate), by $\omega$ the failure probability of computing a hash using nodes already stored in the buffer, by $E(X)$ the expected number of hashes to fill the buffer with a failure probability $\delta$, and by $H_n$ the $n$-th Harmonic number.
+% ~\cite{harmonicNumber}.
 \begin{claim}
@@
 \begin{claimproof}
-The number of nodes needed in the buffer to achieve a node failure probability $\delta$ is 
-$\left \lfloor{N(1-\delta)}\right \rfloor$.  %= Nf_1(1-\frac{\omega}{a})
-This means that even though we are allocating a buffer that can hold $N$ pages, we are willing to forgo $\left \lfloor{N\delta}\right \rfloor$ nodes (to simplify notation, from now and on, we assume $N\delta$ is an integer).
+The number of nodes needed in the buffer to achieve a failure probability $\delta$ is 
+$\left \lceil{N(1-\delta)}\right \rceil$.
+This means that even though we are allocating a buffer that can hold $N$ nodes, we are willing to forgo $\left \lfloor{N\delta}\right \rfloor$ nodes (to simplify notation, from now and on, we assume $N\delta$ is an integer).
 
@@
     \label{eq:expectedTrials}
-    E(t) = N(H_{N} -H_{N\delta})
+    E(t) = N(H_{N} -H_{N\delta}).
 \end{gather}
@@
 By the independence assumption,
-$$ (1-\delta)^a = 1-\omega.$$For $\delta \ll 1$, we have $(1-\delta)^a \approx 1-a\delta$. Hence,
+$$ 1-\omega = (1-\delta)^a$$For $\delta \ll 1$, we have $(1-\delta)^a \approx 1-a\delta$. Hence,
 \begin{gather}
@@
 \end{gather}
-Hence, it follows from Equation~(4\ref{eq:deltaomega}) that 
+Hence, it follows from Equation~(\ref{eq:deltaomega}) that 
 \begin{gather}
@@
 \end{gather}
-Finally, from Equations~(3\ref{eq:expectedTrials}) and~(5\ref{eq:hashvspage}) and, we obtain
+Finally, from Equations~(\ref{eq:expectedTrials}) and~(\ref{eq:hashvspage}) and, we obtain
 \begin{gather}
@@
 
-We use the following bounds on the Harmonic Numbers~\cite{harmonicNumber} to compute  Equation~(6\ref{eq:expectedHashes}):
+We use the following approximation on the Harmonic Numbers to compute  Equation~(\ref{eq:expectedHashes}):
 \begin{gather}
     \label{eq:boundHarmonic}
-	-\frac{1}{12n^2+{2\frac{7-12\gamma}{2\gamma-1}}}\le H_n-\ln n-\frac1{2n}-\gamma<-\frac{1}{12n^2+\frac{6}{5}},
+    H_n \approx \ln{n} + \gamma + o(1)
 \end{gather}
+
 where $\gamma = 0.57721566...$ is the Euler-Mascheroni constant.
-% -\frac{1}{12n^2+{2(7-12\gamma)}/{(2\gamma-1)}}\le H(n)-\ln n-\frac1{2n}-\gamma<-\frac{1}{12n^2+6/5}
 
-Specifically, using Equations~(6\ref{eq:expectedHashes}) and~(7\ref{eq:boundHarmonic}), and setting $N = 16777186$ (the number of nodes in the DAG for our experiments), $a = 64$ and $\delta = 0.000000005$, we get $E(X) \approx 3.7$ million hashes.
-However, if we increase $\delta$ to 0.005, we get $E(X) \approx 1.4$ million hashes.
-Hence, we see that even computing merely 1.4 million hashes fills a DAG buffer as large as the entire DAG by more than 99.5\%, as opposed to calculating 3.7 million to fill it by 99.9999995\%.
-% This suggests that the fuller the buffer is, the marginal cost of computing more hashes outweighs the rate at which the buffer is filled up. 
+Specifically, using Equations~(\ref{eq:expectedHashes}) and~(\ref{eq:boundHarmonic}), and setting $N = 16777186$ (the number of nodes in the DAG for our experiments), $a = 128$ and $\delta = 5*10^{-9}$, we get $E(X) \approx 1.85$ million hashes.
+However, if we increase $\delta$ to $5*10^{-3}$, we get $E(X) \approx 700$ thousand hashes.
+Hence, we see that even computing merely 700 thousand hashes fills a DAG buffer as large as the entire DAG within a margin of $5*10^{-1}\%$, as opposed to calculating 1.85 million to fill it within a margin of $5*10^{-7}\%$.
+
 In fact, as we will see in the results, filling up 99.5\% of a buffer as large as the DAG already starts giving us good hash rates for a browser -- 35kH/s for the \verb|WebAssembly| miner.
@@
 This means that reaching a reasonably steady state is not as hard as it seems at face value, making \verb|WebEth| viable for web settings where users might not stay on websites for long.
+However, given this, we would also like to point out that in reality, while it takes a lot more hashes to fill up the buffer, it does not take a lot more \emph{time} to fill it up.
+This is because as discussed in the next section, when the buffer gets closer and closer to being full, the hash rate spikes up and so computing the remaining number of hashes to fill the buffer becomes quite fast.
+Hence, it does not take too long to completely fill up the buffer (around five minutes in our experimental setup), which is practical for many web applications, such as streaming.
 
@@
 \subsection{Experimental set up}
-Our experimental set up consisted of a machine with an Intel i7-7700HQ processor with 8 cores and 16GB ram.
+Our experimental set up consisted of a machine with an Intel i7-7700HQ processor with 8 cores and 16~GB ram.
 These results were obtained from a private Ethereum test network at epoch 0.
-The DAG size was 16777186 nodes (1.074GB).
-The cache size was 1.677MB.
+The DAG size was 16777186 nodes (1.074~GB).
+The cache size was 1.677~MB.
 We ran the implementations in ~\verb|JavaScript| and ~\verb|WebAssembly| in the browser, and a native miner written in ~\verb|C++| that employs the same lazy evaluation approach outside of the browser for control results.
-Each miner was run till 800k hashes were computed and the hash rate and buffer hit rate were sampled every 10k hashes.
+Each miner was run till 800~kHashes were computed and the hash rate and buffer hit rate were sampled every 10k hashes.
 (Note that both the hash rate and buffer hit rate sampled at a particular time reflected the values over the 10k most recent hashes).
@@
 \subsection{Implementation Results}
-Figures 4\ref{fig:hashRateHMWASM},5\ref{fig:hashRateHMJS} and 6\ref{fig:hashRateHMNative} below shows a heat-map of how the hash rate varies for each of the three implementations as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.
-Further, Figure 7\ref{fig:HitRateHM} then shows a heat-map of how the DAG buffer hit-rate varies as a function of both these parameters.
+Figures~\ref{fig:hashRateHMWASM}, \ref{fig:hashRateHMJS} and \ref{fig:hashRateHMNative} below shows a heat-map of how the hash rate varies for each of the three implementations as a function of both the size of the buffer allocated to store the DAG (as a percentage of the size of the entire DAG) and the number of hashes computed in the browser.
+Further, Figure \ref{fig:HitRateHM} then shows a heat-map of how the DAG buffer hit-rate varies as a function of both these parameters.
 As expected, both the hash rate and the buffer hit rate increases with the buffer size and the number of hashes computed for all three miners.
-We must also note that the experimental results suggest that it takes 70 kHashes to reach a buffer hit rate of 99.5\%, which falls well within our conservatively predicted value of 1.4 million hashes.
-In fact, we can validate that our experimental results are in agreement with the predicted results for all other hit rates as well.
-% In fact, the number of hashes computed
+We must also note that the experimental results suggest that it takes 700~kHashes to reach a buffer hit rate of 99.5\%, which agrees with our predicted value from the mathematical analysis in the previous section.
+In fact, we can validate that our experimental results are typically in agreement with the predicted results for all other hit rates as well.
 
@@
 
-In order to closely examine the relationship between the hash rate and the hit rate, we show the correlations between the two parameters for all 3 miners in Figure 3\ref{fig:HashRateTraj}.
+In order to closely examine the relationship between the hash rate and the hit rate, we show the correlations between the two parameters for all 3 miners in Figure \ref{fig:HashRateTraj}.
 It is interesting to see how the hash rate drastically spikes after the hit rate surpasses 95\%.
 This suggests that accessing DAG pages from the buffer is orders of magnitude faster than computing them, so much so that even a few computations bring down the hash rate drastically.
-Most importantly, from the experiments, the time it takes to reach this steady state hash rate not long (on the order of $\approx$ 5 minutes) thereby making this approach ideal for streaming/gaming websites.
+Most importantly, from the experiments, the time it takes to reach this steady state hash rate is not long (about 5 minutes) thereby making this approach ideal for streaming/gaming websites.
 Furthermore, \verb|WebEth| is also ideal as a web miner as it is not very resource intensive -- throughout the experiments, it did not use more than 12.5\% of the CPU of our testing machine (the utilization value is normalized over 8 cores).
@@
 The only way this could work is by sending over part of the DAG over the network to the client.
-However, as it turns out, this is not feasible since, for a DAG with 16777186 nodes (1.074 GB) sending even 10\% of the DAG would be sending $\approx$ 100MB of data.
-With the global average download speed for desktops and smartphones being around 5.34MBps and 2.77MBps respectively~\cite{internetSpeed}, the web page load time would be in the order of 20 seconds to a minute -- which is too long to get a mere 10\% boost in the buffer storage.
-
-% The jump in the hash rate for high buffer hit rates is also seen in Figure~\ref{fig:HashRateTraj} where we show the correlations between the buffer hit rates and the hash rates for all 3 miners.
-The general trend is the same for all 3 miners -- the hash rate spikes up as the hit rate surpasses 95\% (Note that the hit rate gets extremely close to 1 but never quite reaches there, since we only compute 800k hashes as opposed to the 4.5 million would be needed as per our theoretical analysis).
+However, as it turns out, this is not feasible since, for a DAG with 16777186 nodes (1.074~GB) sending even 10\% of the DAG would be sending roughly 100~MB of data.
+With the global average download speed for desktops and smart phones being around 5.34~MBps and 2.77~MBps respectively~\cite{internetSpeed}, the web page load time would be in the order of 20 seconds to a minute -- which is too long to get a mere 10\% boost in the buffer storage.
 
@@
     \end{minipage}}
-\caption{Log(Hash Rate) and Hit Rate as a function of number of Hashes computed and Buffer Size}
 \end{figure}
+% Log(Hash Rate) and Hit Rate as a function of number of Hashes computed and Buffer Size
 
-Table 1\ref{table:perf} shows us how the performance of each of the miners compare.
-Interestingly, the most conspicuous aspect is the fact that the performance variation between different implementations is not uniform across different buffer sizes and hit rates.
-We also see that for obvious reasons, the native miner outperforms both the~\verb|JavaScript| and the ~\verb|WebAssembly| miner.
-However, we see that the ~\verb|WebAssembly| miner is at most 40.5\% slower than the native miner -- which is not very far off considering the overhead of running programs within browsers.
+Table \ref{table:perf} shows us how the performance of each of the miners compare.
+Interestingly, the performance variation between different implementations is not uniform across different buffer sizes and hit rates.
+For instance, the variation between the \verb|WebAssembly| and \verb|JavaScript| miners is only 35.9\% when the buffer hit rate is 0, but the performance difference increases to 73.2\% when the hit rate becomes greater than 0.99.
+We also see that for obvious reasons, the native miner outperforms both the \verb|JavaScript| and the \verb|WebAssembly| miner.
+However, the \verb|WebAssembly| miner is at most 40.5\% slower than the native miner -- which is not very far off considering the overhead of running programs within browsers.
 The \verb|JavaScript| miner, on the other hand, is \textbf{at least} 47.2\% slower (and at most 82.0\% slower), making \verb|WebAssembly| the better of the two candidates for \verb|WebEth|.
@@
 
-Finally, we tabulate the most important results from our analysis in Table 2\ref{table:results}.
+Finally, we tabulate the most important results from our analysis in Table \ref{table:results}.
+We see that it takes all miners only a few hundred seconds to fill the buffer up, which is good considering the fact that most users don't stay on a particular website for very long.
+Furthermore, we see that the \verb|WebAssembly| miner is the better of the two miners, since it gives a better terminal hash rate of 40~kH/s.
 
@@
 \makecell[l]{Median Hash Rate \\
-\qquad(for a buffer the size of the DAG)} & 15278H/s &  5290H/s & 10504H/s \\
-Peak Hash Rate &  56800H/s &  10626H/s & 39651H/s \\
-\makecell[l]{Time taken to 99.76\% \\ buffer hit rate}  &  163.601s &  879.857s & 257.7692s\\ 
+\qquad(for a buffer the size of the DAG)} & 15278~H/s &  5290~H/s & 10504~H/s \\
+Peak Hash Rate &  56800~H/s &  10626~H/s & 39651~H/s \\
+\makecell[l]{Time taken to 99.76\% \\ buffer hit rate}  &  163.601~s &  879.857~s & 257.7692~s\\ 
 \makecell[l]{Avg. Hash Rate \% diff with Native Miner \\
@@
 Note though that earning real cash requires a significant subscriber base or a large amount of time spent on the website, making this an ideal approach for video streaming/gaming websites.
-% Another approach involves subscriptions, however, it is not very successful.
-Indeed, as this study finds, users are becoming increasingly unlikely to pay for content \cite{noSubscriptions}.
-Website owners also use pay-per-click Advertising, however an approach often leads to the content being split over an excessive number of pages, thereby leading to consumer frustration \cite{payPerClick}.
-Thus, we see that each approach has its own issues, be it with  with website owners or clients.
-Hence, it is important to strike a balance and create a solution that would be able to benefit both parties.
-Our web-based miner would solve this situation as it does not
-% \textbf{Web-Authentication Rate Limiting}: 
+In fact, with a hash rate of 40~kH/s, a website would need to have around 8000 users at any given time in order to obtain around \$500 per month \cite{etherProfit}.
+
 \paragraph{Web Authentication Rate Limiting:}
@@
 Many tools are openly available for brute forcing web login pages~\cite{hydra,burpsuite}.
-Currently, website owners mitigate these attacks is by locking out a user for a certain amount of time after a fixed number of unsuccessful login attempts or presenting a captcha~\cite{recaptcha}.
-% While this approach works in theory, in today's fast-paced world, users tend to dislike waiting for even a few seconds ~\cite{usersDislikeWaiting}. 
+Currently, the way website owners mitigate these attacks is by locking out a user for a certain amount of time after a fixed number of unsuccessful login attempts or presenting a captcha~\cite{recaptcha}.
 Lock out presents a Denial of Service potential by locking out legitimate users as a consequence of an attack. 
 Captcha techniques can be used for third-party value~\cite{von2008recaptcha} and have been successfully attacked through machine learning techniques~\cite{mlCaptcha} and crowdsourcing~\cite{captchaFarms}.
-% .~\trishita{CITEEE...}%AT - citation needed here!
 
-% While it seems as though this approach is effective at face value, in reality, it does more harm than good as by introducing the risk of Denial of Service.
-This is because most brute force attacks are large scale and try millions of username/password combinations, which would consequently lockout a large number of user accounts.
-While this may prevent an attacker from successfully cracking passwords, it would also deny service to a lot of legitimate users whose accounts were being brute forced.
-This, amongst other issues, would definitely reflect badly on the website owner, and hence opens a whole new avenue for attack.
 We posit a more user-friendly approach to this problem involving embedding a Proof-of-Work computation in a web page, \emph{e.g.}, using \verb|WebEth|, that the user's browser needs to successfully solve in order to be able to login.
@@
 
-% Furthermore, we provide an API that can be used by any implementation of Ethereum (\verb|geth| or Ethereum's implementation in \verb|C++|).
-We believe this can be a be especially viable in a private testnet, within a company for example, and with further research has the potential to make a real impact.
-
 \paragraph{Future Work:}
@@
 
+Another interesting issue is whether the server should notify the clients once a new valid hash is found.
+One may expect that with a sufficiently large number of clients, this may lead to better performance than waiting for a timeout.
+In fact, experimenting with the length of the period before timeout might also be an interesting avenue to pursue.
+
 The Ethereum Foundation is also currently developing Casper, a Proof-of-Stake algorithm, which has already been deployed in private testnets.
@@
 
-% conference papers do not normally have an appendix
-
-% % use section* for acknowledgement
 \section*{Acknowledgment}
@@
 
-% \bibitem{arc}
-% The ArcticCoin Team. ArcticCoin crypto-currency. ArcticCoin. Software, 2015.
-
 \bibitem{Monero} ``Monero - Secure, Private, Untraceable.'' Getmonero.org, The Monero Project, getmonero.org/.
@@
 \bibitem{couponCollector} Neal, Peter. ``The Generalised Coupon Collector Problem.'' Journal of Applied Probability, vol. 45, no. 3, 2008, pp. 621\-629., doi:10.1239/jap/1222441818.
-\bibitem{harmonicNumber} Guo, Bai-Ni \& Qi, Feng. (2011). Sharp bounds for harmonic numbers. Applied Mathematics and Computation. 218. 991-. 10.1016/j.amc.2011.01.089.
+
+% \bibitem{harmonicNumber} Guo, Bai-Ni \& Qi, Feng. (2011). Sharp bounds for harmonic numbers. Applied Mathematics and Computation. 218. 991-. 10.1016/j.amc.2011.01.089.
 
@@
 
-\bibitem{erc20} ``ERC20 Token Standard,'' \url{https://theethereum.wiki/w/index.php/ERC20\_Token\_Standard}.
+\bibitem{erc20} ``ERC20 Token Standard,'' \\\url{https://theethereum.wiki/w/index.php/ERC20\_Token\_Standard}.
+
+\bibitem{etherProfit} CryptoCompare. ``Mining Calculator Bitcoin, Ethereum, Litecoin, Dash and Monero.'' CryptoCompare, CryptoCompare, 
+www.cryptocompare.com/mining/calculator/eth. 
 \end{thebibliography}

### 2018-07-17 webeth-js/lazy-miner/ethash.js

@@ -6,6 +6,7 @@
 "use strict";
 
 // we save some values of in this dag object
+// uncomment checkpoints put in at various places to validate hashes
 
 var NUM_DAG_SLICES = 11744033;
 var hashWords = 16;
@@ -274,7 +275,7 @@ class Ethash
 		// final keccak hashes
 		this.keccak.digestWords(this.retWords, 0, 8, this.initWords, 0, 24); // keccak-256(s + cmix)
 		// return [this.initBytes,this.retBytes];
-		// CHANGE BACK TO RETBYTES!!
+		// CHANGE BACK TO RETBYTES
 		return this.retWords;
 	};
 	

### 2018-07-17 webeth-js/lazy-miner/~/.config/google-chrome/Default/Extensions/pkedcjkdefgpdelpbcmbmeomcjbeemfm/6417.1211.0.0_1/cast_setup/cast_app.js

@@ -1,259 +1,0 @@
-'use strict';var h,aa="function"==typeof Object.defineProperties?Object.defineProperty:function(a,b,c){a!=Array.prototype&&a!=Object.prototype&&(a[b]=c.value)},ba="undefined"!=typeof window&&window===this?this:"undefined"!=typeof global&&null!=global?global:this,ca=function(){ca=function(){};ba.Symbol||(ba.Symbol=da)},da=function(){var a=0;return function(b){return"jscomp_symbol_"+(b||"")+a++}}(),fa=function(){ca();var a=ba.Symbol.iterator;a||(a=ba.Symbol.iterator=ba.Symbol("iterator"));"function"!=
-typeof Array.prototype[a]&&aa(Array.prototype,a,{configurable:!0,writable:!0,value:function(){return ea(this)}});fa=function(){}},ea=function(a){var b=0;return ha(function(){return b<a.length?{done:!1,value:a[b++]}:{done:!0}})},ha=function(a){fa();a={next:a};a[ba.Symbol.iterator]=function(){return this};return a},ia=function(a){fa();var b=a[Symbol.iterator];return b?b.call(a):ea(a)},ja=function(a,b){if(b){var c=ba;a=a.split(".");for(var d=0;d<a.length-1;d++){var e=a[d];e in c||(c[e]={});c=c[e]}a=
-a[a.length-1];d=c[a];b=b(d);b!=d&&null!=b&&aa(c,a,{configurable:!0,writable:!0,value:b})}},ka=function(a,b,c){if(null==a)throw new TypeError("The 'this' value for String.prototype."+c+" must not be null or undefined");if(b instanceof RegExp)throw new TypeError("First argument to String.prototype."+c+" must not be a regular expression");return a+""};
[…]

### 2018-07-17 webeth-wasm/cache-miner/miner.cpp

@@ -6,6 +6,8 @@
 #include <cstdlib>
 using namespace emscripten;
 
+// uncomment unit tests and checkpoints to validate correct working
+
 class Params
 {
 	public:
@@ -456,46 +458,6 @@ class Keccak
 		}
 };
 
-/*
-// FIX -- only works for ascii, not for the entire range of utf-16
-char nibbleToChar(char nibble)
-{
-	return (nibble < 10 ? 48 : 87) + nibble + '0';
-}
-
-int charToNibble(int chr)
-{
-	if (chr >= 48 && chr <= 57)
-	{
-		return chr - 48;
-	}
-	if (chr >= 65 && chr <= 70)
-	{
-		return chr - 65 + 10;
-	}
-	if (chr >= 97 && chr <= 102)
-	{
-		return chr - 97 + 10;
-	}
-	return 0;
-}
-*/
-// might want to implement this in js only
-// this method is invoked a lot, so there will be a lot of communication overhead
-// if the browser constantly has to contact the webasm module
-/*
-string bytesToHexString(char * bytes)
-{
-	string str = "";
-	for (int i = 0; i != sizeof(bytes)/sizeof(*bytes); ++i)
-	{
-		str = str + nibbleToChar(bytes[i] >> 4);
-		str = str + nibbleToChar(bytes[i] & 0xf);
-	}
-	return str;
-}
-*/
-
 
 unsigned int fnv(unsigned int x, unsigned int y)
 {
@@ -598,7 +560,6 @@ class Ethash
 		{
 			// compute initial hash
 
-			// TO DO: use header hash instead of header
 			//checked from the javascript version of the miner that the header size is always 32 bytes (8 ints)
 
 			// the header
@@ -717,6 +678,7 @@ EMSCRIPTEN_BINDINGS(mineModule){
 	function("mine", &mine);
 }
 
+// uncomment to check native performance (ie., outside of browser)
 
 /*
 int main()

### 2018-07-17 webeth-wasm/lazy-miner/miner.cpp

@@ -459,31 +459,6 @@ class Keccak
 		}
 };
 
-// FIX -- only works for ascii, not for the entire range of utf-16
-/*
-char nibbleToChar(char nibble)
-{
-	return (nibble < 10 ? 48 : 87) + nibble + '0';
-}
-
-unsigned int charToNibble(unsigned int chr)
-{
-	if (chr >= 48 && chr <= 57)
-	{
-		return chr - 48;
-	}
-	if (chr >= 65 && chr <= 70)
-	{
-		return chr - 65 + 10;
-	}
-	if (chr >= 97 && chr <= 102)
-	{
-		return chr - 97 + 10;
-	}
-	return 0;
-}
-*/
-
 void store(std::string dagStr, unsigned int startIndex,unsigned int endIndex)
 {
 		std::stringstream ss(dagStr);
@@ -653,7 +628,6 @@ class Ethash
 		{
 			// compute initial hash
 
-			// TO DO: use header hash instead of header
 			//checked from the javascript version of the miner that the header size is always 32 bytes (8 ints)
 
 			// the header
@@ -783,6 +757,7 @@ EMSCRIPTEN_BINDINGS(mineModule){
 	function("mine", &mine);
 }
 
+// uncomment to check native performance (ie., outside of browser)
 
 /*
 int main()
